# Introduction

This assessment report describes the sub-area population of `r spp` (*Sebastes caurinus*) off the California coast `r area` in U.S. waters, using data through 2022. The sub-area population south of Point Conception in California waters was also evaluated and is described in a separate assessment report. The `r spp` status for the California stock is determined by the combined estimates of spawning output from both sub-areas and is detailed in the [management](#management) Section. This assessment does not account for populations located in Mexican waters or other areas off the U.S. West Coast and assumes that these southern and northern populations do not contribute to nor take from the population being assessed here.

## Basic Information and Life History

```{r, echo=FALSE, results='asis'}
filein <- file.path(doc_dir, "shared_text",'1_intro_life_history_fishery_info.Rmd')
read_child(filein)
```

## Ecosystem Considerations


```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text", '1_ecosystem_consideration.Rmd')
read_child(filein)
```


## Historical and Current Fishery Information

Off the coast of California north of Point Conception, `r spp` is caught in both commercial and recreational fisheries. Recreational removals have been the largest source of fishing mortality of `r spp` across all years (Table \ref{tab:allcatches} and Figure \ref{fig:catch}). The recreational fishery is comprised of individual recreational fishers (Private/Rental, PR) and commercial passenger fishing vessels (CPFV) also known as party/charter (PC) which take groups of individuals out for day fishing trips. Across both types of recreational fishing, the majority of effort occurs around rocky reefs that can be accessed via day-trips. 

```{r, echo=FALSE, results='asis'}
filein <- file.path(doc_dir, "shared_text",'1_intro_ca_commercial.Rmd')
read_child(filein)
```

`r Spp` residing between Point Conception and the California/Oregon border are assessed here as a separate sub-area (Figure \ref{fig:ca-map}). This designation was made based on oceanographic, geographic, and fishery conditions. The `r spp` population in California waters was split at Point Conception due to water circulation patterns that create a natural barrier between nearshore rockfish populations to the north and south. The northern border for this assessment was defined as the California/Oregon border due to substantial differences in historical and current exploitation levels. Additionally, the fairly sedentary nature of adult `r spp` likely limits flow of fish between south and north of Point Conception. 

## Summary of Management History and Performance


```{r, echo=FALSE, results='asis'}

filein = file.path(doc_dir, "shared_text", '1_intro_management.Rmd')
read_child(filein)
```
Most commercial catch of `r spp` since about 2000 has been from the hook and line gear type and thus the most impactful management actions have been non-trawl RCA depth adjustments. Adjustment of that boundary north of 40$^\circ$ 10' N. lat. in 2009, restricting the nearshore fishery to waters less than 20 fathoms from their previous 30 fathom allowance, may have resulted in a shift in the size of `r spp` being landed to smaller fish as the fleet adjusted and markets developed for smaller "plate-sized" fish within the live fishery.  

## Foreign Fisheries


```{r, echo=FALSE, results='asis'}

filein = file.path(doc_dir, "shared_text", '1_foreign_fisheries.Rmd')
read_child(filein)
```


