## Fishery-Dependent Data

### Commercial Fishery

#### Landings and Discards
\

```{r, echo=FALSE, results='asis'}
general_wd = file.path(doc_dir, "shared_text")
filein = file.path(general_wd,'2f_commercial_removals.Rmd')
read_child(filein)
```


#### Composition Data
\

Biological data were extracted from the PacFIN Biological Data System on March 20, 2023. Length data for the commercial fleet were extracted from the PacFIN Biological Data System (BDS) with samples for north↨ of Point Conception beginning in 1978 (Tables \ref{tab:dead-com-len} and \ref{tab:live-com-len}). The commercial data was split by landed condition, live or dead, with the first data for the live fish fishery beginning in 1994. The number of length samples by fleet were highly variable with the largest number of sample by year being recorded in the 1990s for the dead fish fishery. In recent years, the number of length samples by year are limited for both fleets with the live fish with annual sample sizes less than 100 per year. The number of samples prior to the 1990s and in the 2000s for the dead fish fishery were sparse and variable across sizes. During model explorations any year with less than 20 sampled fish were considered too sparse to accurately reflect the fleet selectivity for that year (see [Appendix A](#excluded-data) for implied fits to these lengths). 

The majority of lengths observed by the commercial fleet landed dead `r spp` ranged between approximately 25 - 50 cm (Figure \ref{fig:com-dead-len-data}, detailed length compositions by year can be found in the Appendix, Section \ref{length-data}). Notably, in the early years of data prior to 1990 observed few smaller fish compared to later years. The mean length observed by year ranged between approximately 30 - 45 cm (Figure \ref{fig:mean-com-dead-len-data}). The mean observed length since 2010 slowly increase through 2018 with a drop in the mean observed age in the most recent years data.

The observed distribution of sizes sampled from the commercial live fish fleet were generally variable prior to 2011 with the length distributions since indicating a smaller range of sizes being landed after 2011 (Figure \ref{fig:com-live-len-data}). The observed mean length of fish landed live also clearly shows a drop in average sizes being landing starting in 2011 (Figure \ref{fig:mean-com-live-len-data}).  

The input sample sizes for all commercial data were calculated based on a combination of trips and fish sampled:

\begin{centering}

Input effN = $N_{\text{trips}} + 0.138 * N_{\text{fish}}$ if $N_{\text{fish}}/N_{\text{trips}}$ is $<$ 44

Input effN = $7.06 * N_{\text{trips}}$ if $N_{\text{fish}}/N_{\text{trips}}$ is $\geq$ 44

\end{centering}

### Recreational Fishery

#### Landings and Discards
\

```{r, echo=FALSE, results='asis'}
general_wd = file.path(doc_dir, "shared_text")
filein = file.path(general_wd,'2f_recreational_removals.Rmd')
read_child(filein)
```

#### Fishery Dependent Indices of Abundance
\

A number of indices of abundance were explored for the recreational fleet. Discarded catch is available from onboard observer surveys, but was not included in indices. Indices developed for the assessment include:

* MRFSS era dockside survey of the CPFV/PC fleet (1980-1999),
* Deb-Wilson Vandenberg survey of the CPFV/PC fleet (1988-1998),
* CDFW CPFV/PC onboard observer index (1999-2019), and
* CRFS PR1 sites dockside survey (2004-2019).

Due to limited sampling during 2020 due to the COVID-19 pandemic and inseason action taken by CDFW for 2022 reducing sub-bag limits for `r spp` across California, both recreational fishery indices of abundance excluded data collected after 2019.

Figure \ref{fig:mrfss-index-main} Appendix Section \ref{mrfss-cpfv-index}

Figure \ref{fig:crfs-index-main} Appendix Section \ref{onboard-cpfv-index}

Figure \ref{fig:dwv-index-main} Appendix Section \ref{dwv-cpfv-index}

Figure \ref{fig:crfs-pr-index-main} Appendix Section \ref{crfs-pr-index}

#### Composition Data

Length compositions were available from the following sources: 

* Recreational party/charter mode (CPFV/PC)

  + Miller and Goshall dockside survey (1959-1961, 1966)
  + Don Pearson onboard PC survey (1978-1984)
  + MRFSS CPFV/PC dockside survey (1980-1989, 1993-2003)
  + CRFS CPFV/PC onboard dockside survey (2004-2022)
  + Deb Wilson-Vandenberg onboard CPFV survey (1988-1998)

* Recreational private/rental mode (PR)

  + Miller and Gotshall dockside PR survey (1959)
  + MRFSS dockside PR survey (1980-1989, 1993-2003)
  + CRFS dockside PR survey (2004-2022)
  
  
The number of available fish and unique trips by year and fleet are in Tables \ref{tab:rec-len-samps}. MRFSS historical biological data were downloaded from RecFIN website in December 2022. CRFS biological data were also downloaded from RecFIN on February 18, 2023. The Miller and Goshall, Don Person, Deb-Wilson Vandenberg recreational survey data were downloaded from the SWFSC databases in February 2023. 

Between 1987 - 1989 and 1993-1998 there were recreational length data for the CPFV fleet from both MRFSS and Deb Wilson-Vandenberg data sets. During data exploration it was determined that the lengths in MRFSS from 1997 and 1998 were also included in the Deb Wilson-Vandenberg indicating that these data sources were duplicative for these years but also potentially other years where they overlapped. In order to avoid double using of data, the length data from MRFSS which had far fewered length samples for the overlapping years with Deb Wilson-Vandenberg for the CPFV fleet were removed from the data used within the model (see [Appendix A](#excluded-data) for implied fits to these lengths).

The majority of length samples for both recreational fleets, CPFV and PR, were unsexed. A wide range of sampled lengths from the recreational CPFV fleet were observed across all years with lengths generally ranging between 25 - 45 cm except for the late 1970s and early 1980s where a higher proportion of larger fish were sampled (Figure \ref{fig:rec-cpfv-len-data}). The mean length of lengths observed in the recreational CPFV fleet since approximately 1990s is relatively stable varying between 35 - 40 cm in length with high variability within the data in the early years (Figure \ref{fig:mean-rec-cpfv-len-data}). The range of lengths sampled from the recreational PR fleet are similar to those from the CPFV fleet with lengths in recent years ranging between 25 - 45 cm with slightly larger proportion of larger fish observed in the 1980s (Figures \ref{fig:rec-pr-len-data} and \ref{fig:mean-rec-pr-len-data}). 

Age composition data were available for select years from both the recreational CPFV and PR fleets. Historical age data collected from the CPFV fishery were available from this fleet from  1978, 1981, and 1984. The majority of these fish were sexed (only 4 total unsexed ages from 1978 and 1984) with an average age ranging from 10 to 14 across these years (Figures \ref{fig:rec-cpfv-caal-data} and \ref{fig:mean-rec-cpfv-age-data}). The historical age data from this fleet were input as marginal ages. There were a total of 250 age samples from the final model year, 2022, collected by a cooperative sampling program with the fleet coordinated by the SWFSC (Figures \ref{fig:rec-cpfv-caal-data} and ADD MARGINAL FIGURE). These data were collected by three CPFV vessels that operate north of Point Conception following random sampling protocols. The cooperative ages were compared to all the CPFV lengths collected by the CRFS sampling program to ensure that the sampling was representative of the fishery (Figure \ref{fig:coop-len-comparison} North). These ages were incorporated as either marginal or conditional age-at-length data depending upon how fish length were measured: carcass or whole fish. The carcass lengthed fish were included as marginals in order to avoid any potential measurement bias in the use of these ages. Finally, a total of 139 ages were collected from the PR fleet in 2022 (Figure \ref{fig:rec-pr-caal-data}). These data were used in the model as conditional age-at-length data as well.  

The approach to determine the number of unique trips by data source varied. Some data sources had unique trip numbers within the data (Don Pearson, Deb Wilson Vandenberg). Other data sources that lacked clear trip identifier applied a similar methodology as developed by Brian Soper that combines multiple fields of information to attempt to estimate trips sampled. The number of trips for MRFSS data was estimated using the year, wave, ID code, sampling site (INSITE), area, and mode. A similar methodology was done for CRFS  and Miller and Gotshall data that used data, county, water area, interview site, and mode. 
