## Fishery-Dependent Data

### Commercial Fishery {#commercial-fishery}

#### Landings and Discards
\

```{r, echo=FALSE, results='asis'}
general_wd = file.path(doc_dir, "shared_text")
filein = file.path(general_wd,'2f_commercial_removals.Rmd')
read_child(filein)
```


#### Composition Data 
\

Biological data were extracted from the PacFIN Biological Data System on March 20, 2023. Length data for the commercial fleet were extracted from the PacFIN Biological Data System (BDS) with samples from north of Point Conception beginning in 1978 (Tables \ref{tab:dead-com-len} and \ref{tab:live-com-len}). The commercial data was split by landed condition, live or dead, with the first data for the live fish fishery beginning in 1994. The number of length samples by fleet were highly variable with the largest number of samples by year being recorded in the 1990s for the dead fish fishery. In recent years, the number of length samples by year are limited for both fleets with annual sample sizes less than 100 per year. The number of samples prior to the 1990s and in the 2000s for the dead fish fishery were sparse and variable across sizes. During model explorations any years with less than 20 sampled fish were considered too sparse to accurately reflect the fleet selectivity for that year (see Appendix Section \ref{excluded-data} for implied fits to these lengths). 

The majority of lengths observed by the commercial fleet landing dead `r spp` ranged between approximately 25 - 50 cm (Figure \ref{fig:com-dead-len-data}, detailed length compositions by year can be found in the Appendix, Section \ref{length-data}). Notably, fewer small fish were observed in the early years of data prior to 1990 compared to later years. The mean length observed by year ranged between approximately 30 - 45 cm (Figure \ref{fig:mean-com-dead-len-data}). The mean observed length since 2010 slowly increased through 2018 with a drop in the mean observed age in the most recent years data. The age data from 2019-2022 commercial dead fleet contained enough samples for inclusion in the model and show the preference for larger/older fish than encountered in the live fish fishery (Figure \ref{fig:com-dead-age-data})

The observed distribution of sizes sampled from the commercial live fish fleet were generally variable prior to 2011 with the length distributions thereafter indicating a smaller range of sizes being landed (Figure \ref{fig:com-live-len-data}). The observed mean length of fish landed live also clearly shows a drop starting in 2011 (Figure \ref{fig:mean-com-live-len-data}).  

The input sample sizes for all commercial data were calculated based on a combination of trips and fish sampled:

\begin{centering}

Input effN = $N_{\text{trips}} + 0.138 * N_{\text{fish}}$ if $N_{\text{fish}}/N_{\text{trips}}$ is $<$ 44

Input effN = $7.06 * N_{\text{trips}}$ if $N_{\text{fish}}/N_{\text{trips}}$ is $\geq$ 44

\end{centering}

### Recreational Fishery {#recreational-fishery}

#### Landings and Discards
\

```{r, echo=FALSE, results='asis'}
general_wd = file.path(doc_dir, "shared_text")
filein = file.path(general_wd,'2f_recreational_removals.Rmd')
read_child(filein)
```

#### Indices of Abundance
\

A number of indices of abundance were explored for the recreational fleet. Discarded catch is available from onboard observer surveys, but was not included in indices. Indices developed for the assessment include:

* Deb-Wilson Vandenberg survey of the CPFV/PC fleet (1988-1998),
* CDFW CPFV/PC onboard observer index (2004-2019), and
* CRFS PR1 sites dockside survey (2004-2019).

Due to limited sampling during 2020 due to the COVID-19 pandemic and inseason action taken by CDFW for 2022 reducing sub-bag limits for `r spp` across California, both recreational fishery indices of abundance excluded data collected after 2019.

The Deb Wilson-Vandenberg data set originated from an onboard observer survey conducted by CDFW survey in California north of Point Conception from 1988-1998 and is referred to as the Deb Wilson-Vandenberg onboard observer survey [@reilly_onboard_1998]. During an observer trip the sampler rode along on the CPFV and recorded location-specific catch and discard information to the species level for a subset of anglers onboard the vessel. The subset of observed anglers is usually a maximum of 15 people and the observed anglers change during each fishing stop.  The catch cannot be linked to an individual, but rather to a specific fishing location.  The sampler also records the starting and ending time, number of anglers observed, starting and ending depth, and measured retained and discarded fish. The fine-scale catch and effort data allow us to better filter the data for indices to fishing stops within suitable habitat for the target species. See Appendix Section \ref{dwv-cpfv-index} for details on the data filtering, processing, and model selection. The Deb Wilson-Vandenberg CPFV index of abundance increased between 1988-1990 and then generally declined between 1991-1998 (Figure \ref{fig:dwv-index-main}).


```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text",'21f_crfs_cpfv_index.Rmd')
read_child(filein)
```

The CRFS CPFV index of abundance was stable in the early years of the time series and then shifted upwards in 2016 and was stable until  2019 (Figure \ref{fig:crfs-index-main}). See Appendix Section \ref{onboard-cpfv-index} for details on the data filtering, processing, and model selection.

Catch and effort data from CRFS dockside sampling of private boats from 2004-2019 and 2021-2022 were provided by CDFW for use in this assessment. The data include catch (number of fish) by species, number of anglers (i.e., effort units are angler trips), angler-reported distance from shore (Area X: inside/outside of 3 nm), county, port, interview site, year, month, and CRFS district. Only data through 2019 were used to develop an index of abundance due to potential changes in angler behavior in 2021 and management changes in 2022. See Appendix Section \ref{crfs-pr-index} for details on the data filtering, processing, and model selection. The CRFS PR index of abundance generally increased between 2004-2016, with the final years of the index stabilizing or slightly declining (Figure \ref{fig:crfs-pr-index-main}).


#### Composition Data 
\

Length compositions were available from the following sources: 

* Recreational party/charter mode (CPFV/PC)

  + Miller and Gotshall dockside survey (1959-1961, 1966)
  + Don Pearson onboard PC survey (1978-1984)
  + MRFSS CPFV/PC dockside survey (1980-1989, 1993-2003)
  + CRFS CPFV/PC onboard dockside survey (2004-2022)
  + Deb Wilson-Vandenberg onboard CPFV survey (1988-1998)

* Recreational private/rental mode (PR)

  + Miller and Gotshall dockside PR survey (1959)
  + MRFSS dockside PR survey (1980-1989, 1993-2003)
  + CRFS dockside PR survey (2004-2022)
  
  
The number of available fish and unique trips by year and fleet are in Table \ref{tab:rec-len-samps}. MRFSS historical biological data were downloaded from the RecFIN website in December 2022. CRFS biological data were also downloaded from RecFIN on February 18, 2023. The Miller and Goshall, Don Pearson, and Deb Wilson-Vandenberg recreational survey data were downloaded from the SWFSC databases in February 2023. 

Between 1987-1989 and 1993-1998 there were recreational length data for the CPFV fleet from both MRFSS and the Deb Wilson-Vandenberg data sets. During data exploration it was determined that the lengths in MRFSS from 1997 and 1998 were also included in the Deb Wilson-Vandenberg data, indicating that these data sources were duplicated for these years but also potentially other years where they overlapped. In order to avoid duplicate data, the length data from MRFSS, which had far fewer length samples for the overlapping years with Deb Wilson-Vandenberg for the CPFV fleet, were removed from the data used within the model (see [Appendix A](#excluded-data) for implied fits to these lengths).

The majority of length samples for both recreational fleets, CPFV and PR, were unsexed. A wide range of sampled lengths from the recreational CPFV fleet were observed across all years with lengths generally ranging between 25 - 45 cm except for the late 1970s and early 1980s where a higher proportion of larger fish were sampled (Figure \ref{fig:rec-cpfv-len-data}). The mean of lengths observed in the recreational CPFV fleet since approximately the 1990s has been relatively stable, varying between 35 - 40 cm, with high variability within the data in the early years (Figure \ref{fig:mean-rec-cpfv-len-data}). The range of lengths sampled from the recreational PR fleet are similar to those from the CPFV fleet with lengths in recent years ranging between 25 - 45 cm with a slightly larger proportion of larger fish observed in the 1980s (Figures \ref{fig:rec-pr-len-data} and \ref{fig:mean-rec-pr-len-data}). 

Age composition data were available for select years from both the recreational CPFV and PR fleets. Historical age data collected from the CPFV fishery were available from this fleet from  1978, 1981, and 1984. The majority of these fish were sexed (only 4 total unsexed ages from 1978 and 1984) with an average age ranging from 10 to 14 across these years (Figures \ref{fig:rec-cpfv-caal-data} and \ref{fig:mean-rec-cpfv-age-data}). The historical age data from this fleet were input as marginal ages. There were a total of 250 age samples from the final model year, 2022, collected by a cooperative sampling program with the fleet coordinated by the SWFSC (Figures \ref{fig:rec-cpfv-caal-data} and \ref{fig:rec-cpfv-marg-age-data}). These data were collected by three CPFV vessels that operate north of Point Conception following random sampling protocols. These same vessels are also observed by the CRFS onboard sampling program that collects length data. The cooperative ages were compared to all the CPFV lengths collected by the CRFS sampling program to ensure that the sampling was representative of the fleet as a whole (Figure \ref{fig:coop-len-comparison}). These ages were incorporated as either marginal or conditional age-at-length data depending upon how fish length was measured: carcass or whole fish. The carcass lengths were included as marginals in order to avoid any potential measurement bias in the use of these ages. Finally, a total of 139 ages were collected from the PR fleet in 2022 (Figure \ref{fig:rec-pr-caal-data}). These data were used in the model as conditional age-at-length data as well.  

The approach to determine the number of unique trips by data source varied. Some data sources had unique trip numbers within the data (Don Pearson, Deb Wilson-Vandenberg). Other data sources that lacked a clear trip identifier used combinations of multiple fields to attempt to estimate unique combinations that represented the number of trips sampled. The number of trips for MRFSS data was estimated using the year, wave, ID code, sampling site (INSITE), area, and mode. A similar methodology was applied for the CRFS and Miller and Gotshall data, where county, water area, interview site, and mode were used to determine the number of unique trips. 
