## Biological Data

### Natural Mortality
\

```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text",'2_biology_natural_mortality.Rmd')
read_child(filein)
```


### Maturation and Fecundity


```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text",'2_biology_maturity.Rmd')
read_child(filein)
```

The 50 percent size-at-maturity was estimated at `r round(model$MGparmAdj[,"Mat50%_Fem_GP_1"][1], 1)` cm with a slope of `r round(model$MGparmAdj$Mat_slope_Fem_GP_1[1], 2)` (Figure \ref{fig:maturity}). This area-specific maturity-at-length estimate is relatively similar but with fish maturing at a slightly larger size compared to the biological maturity curve assumed for `r spp` south of Point Conception. Additionally, these values are both slightly smaller compared to estimates by Hannah [-@hannah_length_2014] for fish observed in Oregon waters (34.8 cm) which estimated the 50 percent size-at-maturity of  and slope of -0.60.

```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text",'2_biology_fecundity.Rmd')
read_child(filein)
```



### Sex Ratio
\

```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text",'2_biology_sex_ratio.Rmd')
read_child(filein)
```


### Length-Weight Relationship
\

```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text",'2_biology_weight_length.Rmd')
read_child(filein)
```


### Growth (Length-at-Age)


### Ageing Precision and Bias