## Model Structure and Assumptions


### Model Changes from the Last Assessment 



### Modeling Platform and Structure

```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text",'31_modeling_platform.Rmd')
read_child(filein)
```



### Model Selection and Evaluation

The base assessment model for `r spp` was developed to balance parsimony and realism, and the goal was to estimate a spawning output trajectory for the population of `r spp` off the west coast of the U.S. The model contains many assumptions to achieve parsimony and uses many different sources of data to estimate reality. A series of investigative model runs were done to achieve the final base model.

### Bridging Analysis

The exploration of models began by bridging from the 2021 data-moderate assessment to Stock Synthesis version 3.30.20, which produced the same estimates for spawning biomass and depletion across the time series (Figures \ref{fig:bridge-ssb} and \ref{fig:bridge-depl}). 


### Key Assumptions and Structural Choices


### Priors

```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text",'31_model_priors.Rmd')
read_child(filein)
```


### Data Weighting



### Model Parameters
Describe estimated vs. fixed parameters, priors