## Model Structure and Assumptions

### Modeling Platform and Structure

```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text",'31_modeling_platform.Rmd')
read_child(filein)
```


### Model Selection and Evaluation

The base assessment model for `r spp` was developed to balance parsimony and realism, and the goal was to 
estimate a spawning output trajectory for the population of `r spp` off the coast of California, north and south of Point Conception. The model contains many assumptions to achieve parsimony and uses many different sources of data to estimate reality. A 
series of investigative model runs were done to achieve the final base model.


### Model Changes from the Last Assessment 

```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text",'31_changes_in_model_structure.Rmd')
read_child(filein)
```


### Bridging Analysis

The exploration of models began by bridging from the 2021 data-moderate assessment to Stock Synthesis version 3.30.21, which produced the same estimates for spawning output and relative spawning output across the time series (Figures \ref{fig:bridge-ssb} and \ref{fig:bridge-depl}). Additional bridging analysis was conducted examining the impact on a revised model structure and updating existing data sources, and adding new data into the model. First, the fishery fleet structure was modified from the 2021 structure where the new assessment separated commercial data into two fleets based on fish landed condition, dead or live, and the recreational data into two fleets, CPFV and PR. The 2021 recreational and commercial data were reprocessed  into the new model structure through 2021 and new selectivity parameters were added to the 2021 for the newly split data. The new data available in for this assessment were then added to the model retaining the same model structure where feasible in the following order:

1. Update externally estimated biology parameters for length-at-age, weight-at-age, and maturity.
2. Add new catch data for all fishery fleets.
3. Add all updated commercial and recreational length and age data.
4. Add the new fishery-dependent indices of abundance.
5. Add the CDFW ROV survey index of abundance and length data.
6. Add the CCFRP Hook and Line survey index of abundance, length, and age data.
7. Add selectivity blocks for the commercial and recreational fleets.
8. Adjust the estimation of annual recruitment deviations.
9. Add conditional-age-at-length data for the growth fleet and estimate growth parameters for both sexes.

The data bridging are shown in Figures \ref{fig:data-bridge-ssb-1}-\ref{fig:data-bridge-depl-2}. Revising the model structure, updating biology, and removals resulted in small changes to the estimated spawning output and stock status (Figures \ref{fig:data-bridge-ssb-1} and \ref{fig:data-bridge-depl-1}). Updating and adding the fishery lengths, ages, and indices resulted in a less depleted final population at the end of the time series. Adding and updating survey data, adding selectivity blocks, and estimating annual recruitment deviations and growth resulted in only minimal revisions in the population estimates (Figures \ref{fig:data-bridge-ssb-2} and \ref{fig:data-bridge-depl-2}). Adjusting the annual recruitment deviations (years estimates and bias adjustment) resulted in a small decline in end spawning output and relative spawning output. The final bridging step that added the condition-age-at-length data for the growth fleet and allowing the estimation of growth resulted in an increase in spawning output and relative spawning output at the end of the time series. 

To arrive at a final base model additional revisions to the model structure, selectivity blocks, revised selectivity parameterization were done in order to determine the best fit to the data.


### Key Assumptions and Structural Choices

```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text",'32_model_structure_assumptions.Rmd')
read_child(filein)
```

The northern California model is fit to two fishery-dependent indices of relative abundance: 1) CDFW CRFS onboard observer survey, and 2) CDFW CRFS private/rentals PR1 dockside survey. Additionally, a MRFSS CPFV dockside index was generated but due to data concerns was not included in the base model. The MRFSS CPFV dockside index is assumed to be proportional to changes in the relative abundance of the recreational party/charter fleet and represents retained fish only. The CDFW onboard observer index represents the same recreational party/charter fleet and includes both retained and discarded fish. The onboard index is specified as a separate “survey” fleet in the model because it overlaps in time with the MRFSS dockside time series. Both the MRFSS and onboard indices use the recreational party/charter fleet’s selectivity curve to define vulnerable size classes. The CRFS PR1 dockside index is linked to the recreational private/rental boat fleet, and had selectivity curve different from the party/charter fleet. 

Recreational length measurements are included as marginal length compositions (proportions at length, sexes combined) by year starting in 1959 for both the CPFV and PR modes. Fishery-dependent length composition data are also included for the commercial fleets starting in 1980 for the dead fishery and 1994 for the commercial live fleet. There were limited historical age data available for `r spp`. Age data available from the CPFV fleet in 1978, 1981, and 1984 were included as marginal ages in the base model. In recent years, age data was avaialble from the commercial dead, CPFV, and PR fleets and were input as conditional-age-at-length data, except for a subset of ages based on filleted length from the CPFV fleet in 2022 which were used as marginal ages.

Fishery-independent data sources in the southern California model are organized into two fleets: 1) CDFW ROV survey and 2) CCFRP Hook and Line survey. Each of the survey data sources were used to create an index of relative abundance and included marginal length compositions by sex and year. Age data from the CCFRP Hook and Line survey were included as conditional-age-at-length data by sex and year.   

Additional available age structures that could not be linked to one of the fleets above or represented a subset of information from a fleet were included in a growth fleet. The `r wcgbt` was not considered for an index of abundance, but is a source of conditional-age-at-length data and associated marginal length comps, both by sex and year. Additional age data collected by Adams and Pearson Research studies were inlcude in the growth fleet. Selectivity by the growth fleet was age-based and estimated to have full selectivity starting at age-1.

Time blocks on selectivity were explored extensively when setting up the initial model structure. A range of management changes to the commercial fishery were considered when determining periods of when selectivity may have been expected to change. Commercial removals for `r spp` are relatively low when compared to recreational removals for this species which limited the amount of composition data available to support estimation of changes in selectivity. Given this and the limited evidence in the available length data, time-invariant selectivity was selected for the commercial dead fleet. A single time block was assumed in the commercial live fleet due to a sharp decline in the mean size observed in this fleet starting in 2010. The STAT contacted various participants in the live fish fishery to determine what regulations and/or market changes may have created this shift in targeting but no clear cause was identified.  

The same time block structure was assumed both the recreational CPFV and PR fleets based on gear restrictions and depth closures. Selectivity blocked into three periods: 1916-2001, 2002-20016, and 2017-2022. In 2022 the sub-bag limit in the California recreational fishery was reduce to only allow one `r spp`. However, the amount of length samples in 2022 were not informative about a change in selectivity. Finally, a time block in selectivity was applied to the CCFRP Hook and Line survey starting in 2017 when the survey extended their sampling across California. 

The specification of when to estimate recruitment deviations is an assumption that affects the estimate of early model uncertainty around stock scale and status. Recruitment deviations were estimated from 1900 - 2019 to appropriately quantify uncertainty in the early model years. The earliest length-composition data occur in 1959 and limited age-composition data available in between 1975-1984. However, age data were not consistently on a yearly basis until 2002. The most informed years for estimating recruitment deviations were from about the early-1980s to 2018. The period from 1900 - 1969 was fit using an early recruitment deviation series with little or no bias adjustment, the main period of recruitment deviates occurred from 1970 - 2019 with an upward and downward ramping of bias adjustment, and 2020 onward recruitment deviations were assumed to be 0 due to limited information at the end of the time-series. [-@methot_adjusting_2011a] summarize the reasoning behind varying levels of bias adjustment based on the information available to estimate the deviates. The standard deviation of recruitment variability was assumed to be 0.50 based on the estimated variation in recruitment from the base model. Annual recruitment deviations were not forced to be fully zero centered during the main recruitment period in order to allow the data to fully inform the estimation and to avoid this constraint altering the annual estimates. Early model explorations revealed that forcing annual deviations to be zero-centered and when the selected period of the main recruitment impacted the annual estimates. Allowing annual recruitment deviations to not be fully zero-centered allowed the annual estimates to be informed by data rather than the model structure.

The following distributions were assumed for data fitting where the survey indices were lognormal and the compositional data had a multinomial error structure.


### Priors

```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text",'31_model_priors.Rmd')
read_child(filein)
```


### Data Weighting

Length composition data for the commercial fishery started with a sample size determined from the equation listed in 
Sections \ref{commercial-fishery}. The input sample size for the length composition data from recreational fishery was determined based on the number of estimated trips (described in Sections \ref{recreational-fishery}), the CCFRP Hook and Line survey was set equal to the number of positive drops by year, and the CDFW ROV were set equal to the number of positive transects. The majority of age-composition data were input as conditional-age-at-length with input sample size equal to the number of ages. The age-composition data from the historical CPFV samples were used as marginal age-composition with the input sample size set equal to the number of ages.     

The base  model was weighted using the "Francis method", which was based on equation TA1.8 in Francis [-@francis_data_2011] which was selected based on model stability and consistency in the model to identify the minimum likelihood estimate (MLE). This formulation looks at the mean length or age and the variance of the mean to determine if across years, the variability is explained by the model. If the variability around the mean does not encompass the model predictions, then that data source should be down-weighted. This method accounts for correlation in the data (i.e., the multinomial distribution). Since Francis data weighting is determined by the mean and variance in observations across years, the age data from the PR fleet had only one year of composition data were weighted based on recommended values from the McAllister-Ianelli Harmonic Mean Weight [-@mcallister_bayesian_1997].

Sensitivities were performed examining the difference in the model fits and results due to in weighting using McAllister-Ianelli Harmonic Mean Weighting [-@mcallister_bayesian_1997] and the Dirichlet Multinomial 
Weighting [-@thorson_model-based_2017].

### Model Parameters

There were 154 estimated parameters in the base model. These included one parameter for $R_0$, 8 parameters for growth, 
5 parameters for extra variability for the fishery and survey indices, 20 parameters for length-based selectivity and time 
blocking of the fleets and the surveys, and 120 recruitment deviations including 16 pre-model estimates (Table \ref{tab:params}).

Fixed parameters in the model were as follows. Steepness was fixed at 0.72, the mean of the prior. A sensitivity analysis and a likelihood profile were performed for steepness. Natural mortality was fixed at 0.108 yr^-1^ for females and males, the median of the prior. Estimation of natural mortality was explored during model development. The estimate of natural mortality uncertain and poorly informed by the data. When estimated natural mortality was low (around 0.090 yr^-1^) relative to the median of the prior which was based on maximum age; however, well within the prior distribution (SE = 0.31). The observations of fish greater than 50 years of age across the West Coast, not only this assessment area, is rare, so a natural mortality that would be associated with a maximum around 60 years of age did not seem well supported. Natural mortality was fixed in the base model but estimation of this parameter for both sexes was explored via sensitivities. 

The standard deviation of recruitment deviates was fixed at 0.50 ($\sigma_R$). Maturity-at-length was fixed as described above in Section \ref{maturation-and-fecundity}. A single California sex-specific length-weight relationship were fixed at externally derived estimates using the `r hkl` and `r wcgbt` length-weight observations (Figure \ref{fig:est-len-wght}). Finally, the length at age 2 for both sexes in the growth function was fixed based on the model estimates due to large uncertainty around these values.