# Appendices 

## Detailed Fits to Composition Data {#detailed-fit-comps}

### Length Composition Data {#length-data}

```{r, results='asis'}
plot_info = read.csv(file.path(model_dir, "plots", "plotinfotable_for_doc.csv"))
len_fit = plot_info[which(plot_info$category == "LenComp"), ]
plot.vec = grep("comp_lenfit_flt", len_fit$label)
filein = file.path(model_dir, "plots")
for (a in plot.vec){
	cap = gsub("<br>", " ", gsub("_", " ", len_fit$caption[a]))
	lab = gsub("_", "-", len_fit$label[a])
	add_figure(filein = file.path(filein, len_fit$file[a]), 
			   caption = cap, 
			   label = lab,
			   alt_caption = "See the CompReport file for detailed information on the composition data and the model fits.")
}
```

\newpage

### Age Composition Data {#age-data}


```{r, results='asis'}
 plot_info = read.csv(file.path(model_dir, "plots", "plotinfotable_for_doc.csv"))
 len_fit = plot_info[which(plot_info$category == "AgeComp"), ]
 plot.vec = grep("comp_agefit_flt", len_fit$label)
 filein = file.path(model_dir, "plots")
 for (a in plot.vec){
	cap = gsub("<br>", " ", gsub("_", " ", len_fit$caption[a]))
	lab = gsub("_", "-", len_fit$label[a])
 	add_figure(filein = file.path(filein, len_fit$file[a]), 
 			   caption = cap, 
 			   label = lab)
 }
```

\newpage



### Conditional-Age-at-Length Composition Data {#caal-data}


```{r, results='asis'}
plot_info = read.csv(file.path(model_dir, "plots", "plotinfotable_for_doc.csv"))
len_fit = plot_info[which(plot_info$category == "A@LComp"), ]
plot.vec = c(grep("comp_condAALfit_residsflt5mkt0", len_fit$label),
  grep("comp_condAALfit_residsflt7mkt0", len_fit$label),
	grep("comp_condAALfit_residsflt9mkt0", len_fit$label))
find = sort(len_fit$label[plot.vec], index.return = TRUE)$ix
plot.vec = plot.vec[find[2:length(find)]]
filein = file.path(model_dir, "plots")
for (a in plot.vec){
	cap = gsub("_", " ", len_fit$caption[a])
	lab = gsub("_", "-", len_fit$label[a])
	add_figure(filein = file.path(filein, len_fit$file[a]), 
			   caption = cap, 
			   label = lab,
			   alt_caption = "See the CompReport file for detailed information on the composition data and the model fits.")
}
```



```{r, results='asis'}
plot_info = read.csv(file.path(model_dir, "plots", "plotinfotable_for_doc.csv"))
len_fit = plot_info[which(plot_info$category == "A@LComp"), ]
plot.vec = c(grep("comp_condAALfit_Andre_plotsflt1mkt0", len_fit$label),
  grep("comp_condAALfit_Andre_plotsflt5mkt0", len_fit$label),
	grep("comp_condAALfit_Andre_plotsflt9mkt0", len_fit$label))
find = sort(len_fit$label[plot.vec], index.return = TRUE)$ix
plot.vec = plot.vec[find[2:length(find)]]
filein = file.path(model_dir, "plots")
for (a in plot.vec){
	cap = gsub("\n", ". ", gsub("%", " percent", gsub("<br>", " ", gsub("_", " ", len_fit$caption[a]))))
	lab = gsub("_", "-", len_fit$label[a])
	add_figure(filein = file.path(filein, len_fit$file[a]), 
			   caption = cap, 
			   label = lab,
			   alt_caption = "See the CompReport file for detailed information on the composition data and the model fits.")
}

```

## Implied Fit to Excluded Data {#excluded-data}

### Length Data 

The implied fits to the data not included in the base model due to low annual sample size are shown below.  

```{r, results='asis'}
plot_info = read.csv(file.path(model_dir, "plots", "plotinfotable_for_doc.csv"))
len_fit = plot_info[which(plot_info$category == "LenComp"), ]
plot.vec = c(grep("comp_gstlenfit_flt1mkt0", len_fit$label),
             grep("comp_gstlenfit_flt2mkt0", len_fit$label),
             grep("comp_gstlenfit_flt3mkt0", len_fit$label),
             grep("comp_gstlenfit_flt4mkt0", len_fit$label))
filein = file.path(model_dir, "plots")
for (a in plot.vec){
	cap = gsub("<br>", " ", gsub("_", " ", len_fit$caption[a]))
	lab = gsub("_", "-", len_fit$label[a])
	add_figure(filein = file.path(filein, len_fit$file[a]), 
			   caption = cap, 
			   label = lab,
			   alt_caption = "See the CompReport file for detailed information on the composition data and the model fits.")
}
``` 

\newpage


### Fishery-Dependent Indices of Abundance

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "index5_logcpuefit_Rec_CPFV.png"), 
caption = "Implied fit to log index data on log scale for the recreational (MRFSS) CPFV index of abundance. Lines indicate 95 percent uncertainty interval around index values based on the model assumption of lognormal error. Thicker lines (if present) indicate input uncertainty before addition of estimated additional uncertainty parameter.",
label = 'mrfss-cpfv-index-fit')
```

\pagebreak
