## Development of Indices of Abundance

### California Onboard CPFV Index of Abundance {#onboard-cpfv-index}

```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text",'21f_crfs_cpfv_index.Rmd')
read_child(filein)
```


In the assessment model, the recreational CPFV fleet is modeled as retained plus 
discarded fish. The proportion of observed discarded copper rockfish is small, 
averaging 3.5% over the time series (\@ref(tab:onboard-keepdiscard)) and are included in the index.

As described above the CDFW and Cal Poly onboard observer programs are identical 
in that the same protocols are followed.  The only difference is that Cal Poly
measures both retained and discarded fish from the observed anglers and CDFW
measures only discarded fish from the observed anglers. CDFW measures retained 
fish as part of the angler interview at the bag and trip level.  
Therefore, only retained fish were modeled in this index. 
The data went through a QA/QC process at the SWFSC which included mapping 
fishing drifts in ArcPro to determine if the recorded latitude and longitude were correct.  

We applied a number of data filters to the available data presented in Table 
\@ref(tab:onboard-filter). The onboard CPFV index restricts the time series to 2004-2019. 
The onboard observer survey 
began in 1999, but the sample sizes were small during the first years of the program. The 
years 1999-2003 also represent years where a number of regulations changed including gear limits, 
bag limits, and spatial closures.  Due to COVID-19, no onboard sampling took place in 2020. 
In 2021 the onboard sampling 
resumed in August, but not at full capacity. The southern California CPFV began an organized effort to avoid copper 
rockfish and encourage their clientele to release and descend copper rockfish 
when encountered. The northern California fleet also participated in this effort to an extent. 
In 2022, the CDFW implemented the one copper rockfish sub-bag 
limit and combined with avoidance by the fleet, the data for this year do not represent the available 
copper rockfish biomass. See the online supplementary material
or the history of regulation changes section for details.

The filters also included removal of the number of observed anglers and time fished at the tail 
ends of the distributions and removal of drifts occurring in depths outside copper rockfish's range 
(Table \@ref(tab:onboard-filter) and Figure \@ref(fig:onboard-depths)). 
We retained 17,458 drifts for index
 standardization, and 3,303 of those drifts encountered copper rockfish 
Table \@ref(tab:onboard-percentpos). 

We modeled catch per angler minutes fished (CPUE) by fishing drift. 
Prior to any modeling, the SWFSC QA/QC'd the data to ensure the location information was correct. 
Each drift was overlaid with the available interpreted substrate layer that characterizes 
rocky and hard substrate, assigned to a rocky reef, and the distance of the 
drift start location to rocky reef was calculated.  In addition, the depth of the start location was 
interpreted from the 2 m resolution bathymetry as well as 90 m resolution bathymetry 
layer for comparison. For drifts missing depth location, we assigned depth based on the 
best available depth based on the bathymetry.

To appropriately weight the onboard observer survey index by the available 
rocky substrate within a region, each drift was assigned to the closest area 
of rocky habitat. Hard bottom was extracted from 
the [California Seafloor Mapping Project](http://seafloor.otterlabs.org/index.html), 
along the mainland coast of southern California. These data 
were collected in state waters at a resolution of two meters, but did not extend into state waters 
past the mainland coast. Additional interpreted bathymetric data classifying the bottom type as 
rock or soft bottom were compiled by analysts at the University of California Santa Cruz and are now
also available from CDFW's website. We used the available interpreted rocky substrate data to expand the 
known area of rocky substrate to areas in southern California that lack substrate type. This 
expansion of the estimated rocky substrate assumes that the proportions of rocky substrate within 
and outside state waters are similar.  Copper rockfish are a nearshore species and the majority of 
observed encounters were within state waters (Table \@ref(tab:onboard-waterarea)).
This is, of course, an estimation of the amount of rocky substrate, and represents the best available data. The calculations can be found in the online supplementary material. Starting in 2017, depth restrictions eased in districts 
north of Point Conception and the recreational fleet targeted these depths 
(Figure \@ref(fig:onboard-depths)). The deeper waters (40-50 fm) are 
outside of the mapped hard bottom habitat, but could be assigned to the larger 
areas considered as a factor in the index.


The covariates explored for model selection included year and four categorical region levels (CRFS Districts 3-6), a categorical variable for month, and continuous depth and depth-squared. Trends in the average CPUE by region were similar in the filtered data set (Figure \@ref(fig:onboard-regioncpue)). A year and region interaction 
was included after visualizing the trends in average CPUE over time, but was not significant. The full model was selected by AICc and 
included year, depth, depth squared and region
(Table \@ref(tab:onboard-model_selection)). 

Indices were fit via MLE from the sdmTMB package in R. The Q-Q plot for the negative binomial model indicated a poor fit to the data, which as not surprising given the low percent of observed drifts encountering copper rockfish. A delta-Lognormal 
was selected over a delta-gamma by a delta AIC of 487.  The Q-Q plot indicated a much 
improved fit compared to the negative binomial model (Table \@ref(fig:onboard-qq)).
The relative abundance is predominantly flat during the time series, with a visible increase in CPUE in 2017 when deeper waters opened in portions of northern California after a 17 year closure (Table \@ref(tab:onboard-index) 
and Figure \@ref(fig:onboard-index)).  


```{r, results = 'asis'}
ind <- read.csv(file.path(data_dir, "rec_indices", "crfs_cpfv_onboard", "north", "start2004",
                    "keep_discard_prop.csv")) %>%
mutate(Proportion.discarded = round(Proportion.discarded, 3)) %>%
mutate(Proportion.discarded = scales::percent(Proportion.discarded))
col_names = c("Year", "Number Kept", "Number Discarded", "Proprtion Discarded")

sa4ss::table_format(x = ind,
             caption = "Number of observed copper rockfish retained and discarded by year.",
             label = "onboard-keepdiscard",
             col_names = col_names)                         
```

\newpage

```{r, results = 'asis'}
ind <- read.csv(file.path(data_dir, "rec_indices", "crfs_cpfv_onboard", "north",
                    "start2004", "target_water_area.csv")) %>%
   mutate(percent_N = scales::percent(round(percent_N, 3)))

col_names = c("District", "Inside State Waters", "Outside State Waters","Percent Inside")

sa4ss::table_format(x = ind,
             caption = "Number of observed drifts inside and outside of state waters by district, summed across years.",
             label = "onboard-waterarea",
            col_names = col_names)                         
```


\newpage

```{r, results = 'asis'}
ind <- read.csv(file.path(data_dir, "rec_indices", "crfs_cpfv_onboard", "north",
                     "percent_pos.csv")) %>%
                     mutate(percentpos = scales::percent((round(percentpos,3))))
col_names = c("Year", "Samples with Target", "Samples without Target", "Total Samples", "Percent Positive")

sa4ss::table_format(x = ind,
             caption = "Number of samples with and without copper rockfish.",
             label = "onboard-percentpos")#,
        #     col_names = col_names)                         
```

\newpage

```{r, results = 'asis'}
#ind <- read.csv(file.path(data_dir, "rec_indices", "crfs_cpfv_onboard", "north",
#                    "model_selection.csv"))
#col_names = c("Filter",	"Description",	"Number of Samples", "Positive Samples")

#sa4ss::table_format(x = ind,
#             caption = "Data filtering steps for the onboard CPFV survey.",
#             label = "onboard-filter",
#             col_names = col_names)                         
```


\newpage

```{r, results = 'asis'}

ind <- read.csv(file.path(data_dir, "rec_indices", "crfs_cpfv_onboard", "north", "start2004",
                   "deltalogn", "index_forSS.csv"))
ind <- ind[, c(1,4,5)]
col_names = c("Year", "Estimate", "logSE")

sa4ss::table_format(x = ind,
             caption = "Estimated relative index of abundance for the onboard CPFV survey.",
             label = "onboard-index",
             digits  = 4,
             col_names = col_names)                         
```

\newpage

```{r, results = 'asis'}
ind <- read.csv(file.path(data_dir, "rec_indices", "crfs_cpfv_onboard", "north", "start2004",
                    "data_filters.csv"))
#ind <- ind[, c(1,4,5)]
col_names = c("Filter",	"Description",	"Number of Samples", "Positive Samples")

sa4ss::table_format(
        x = ind,
        caption = "Data filtering steps for the onboard CPFV survey.",
        label = "onboard-filter",
        col_names = col_names,
        landscape = TRUE,
        custom_width = TRUE,
        format.args = list(big.mark = ","),
        col_to_adjust = c(2),
        width = c("8cm"))                        
```

\newpage

```{r, results = 'asis'}
ind <- read.csv(file.path(
  data_dir, "rec_indices", "crfs_cpfv_onboard", "north", "start2004",  "model_selection.csv"
))
col_names <- c("Intercept",	"Depth", "Depth-squared",	"Month", "Region", "Year", "DF",	"AICc",	"Delta AICc")

#sa4ss::table_format(
#  x = ind,
#  caption = "Model selection for the onboard CRFS CPFV survey.",
#  label = "onboard-model_selection",
#  digits = 2,
#  font_size = 8,
#  col_names = col_names
#)
```

\newpage
```{r, results = 'asis'}
sa4ss::add_figure(
filein = file.path(data_dir, "rec_indices", "crfs_cpfv_onboard", "north", "start2004",
                   "deltalogn", "index.png"), 
caption = "Index for the onboard CPFV survey.",
label = 'onboard-index')
```

\newpage

```{r, results = 'asis'}
sa4ss::add_figure(
filein = file.path(data_dir, "rec_indices", "crfs_cpfv_onboard", "north", "start2004",
                   "deltalogn", "qq.png"), 
caption = "Q-Q plot for the onboard CPFV survey.",
label = 'onboard-qq')
```

\newpage


```{r, results = 'asis'}
sa4ss::add_figure(
filein = file.path(data_dir, "rec_indices", "crfs_cpfv_onboard", "north", "start2004",
                   "average_cpue_by_district.png"), 
caption = "Average CPUE by district prior to standardization.",
label = 'onboard-regioncpue')
```

\newpage

```{r, results = 'asis'}
sa4ss::add_figure(
filein = file.path(data_dir, "rec_indices", "crfs_cpfv_onboard", "north", "start2004",
                   "copper_depths_gisdepthadded.png"), 
caption = "Distribution by year of depths where copper rockfish observed.",
label = 'onboard-depths')
```

\newpage


```{r, results = 'asis'}
sa4ss::add_figure(
filein = file.path(data_dir, "rec_indices", "crfs_cpfv_onboard", "north", "start2004",
                   "drifts_by_depth_district.png"), 
caption = "Depths of observed copper rockfish by district.",
label = 'onboard-depths2')
```

\newpage
