### CRFS PR Dockside Index of Abundance {#crfs-pr-index}

Catch and effort data from CRFS dockside sampling of private boats, 2004-2022, 
were provided by CDFW for use in this assessment. The PR dockside data housed 
on the Recreational Fisheries Information Network (RecFIN) were 
determined to include a number of complexities that precluded the ability to 
use them for an index of abundance. For the time period from 2004-2014 the authors 
re-created the interview, or trip level, data from the "i" sample files.  For 2015-2022 
the authors used files provided by CDFW from the CRFS dockside sampling program.

The data for both time periods included catch by species, number of anglers contributing to the catch, angler-reported area of fishing, 
gear, county, port, interview site, year, month, and CRFS district. The catch included 
the number of fish observed by the CRFS sample, the number of unobserved retained fish reported 
by the angler, and the number of discarded and descended fish reported by the angler.
The sample size of the 
unfiltered private boat data is much larger than the CPFV onboard observer data set, 
with 256,738 samples statewide from 2004-2022, 169,912 north 
of Point Conception and 86,826 south of Point Conception. 

Records were limited to the primary private and rental boats public-access sites, 
PR1 sites, which encompasses over 90% of the total private boat effort 
(Table \@ref(tab:pr-filter)). The CRFS interviews contain a small fraction 
(407 trips over the entire time series) of samples where the retained catch for 
rockfish is over the daily bag limit of 10 
fish per person. We did not remove these data from the index, but did 
only include sampler examined catch.  Rockfish species can be difficult to distinguish and there 
have not been any verification studies conducted to determine the uncertainty in angler reported 
unobserved catch.
Additional data filters included the exclusion of any samples from January and 
March, since those months have been closed to the recreational fishery north of Point 
Conception since 2005.  The time series was also restricted to 2004-2019.  Sampling during the 
COVID period (2020-2021) resulted in a higher fraction of the sampler examined catch in the 
"rockfish, general" category due to the social distancing requirements (Table \@ref(tab:pr-rfgen)). The CDFW 
implemented a one fish sub-bag limit for copper rockfish in 2022 and the quantiles and distribution of CPUE suggest that this 
regulation change impacted fishing behavior in the private boat fleet (Table \@ref(tab:pr-cpue) and 
Figure \@ref(fig:pr-bag)).

The angler reported water area was restricted to ocean areas in U.S. waters 
and a reported primary gear 
of hook-and-line or troll gear.  A number of trips reporting troll as the primary gear reported
a secondary gear of hook-and-line. To determine if the angler(s) interviewed targeted rockfish and
fished in rocky habitat, we retained trips if the angler reported the primary target species 
as rockfish or bottomfish or if rockfish was reported as the secondary target species. This filter 
replaced the Stephens-MacCall [@stephens_multispecies_2004] filtering approach. We retained 75,307 angler 
interviews for index standardization, with 15,549 including sampled examined copper rockfish (Table \@ref(tab:pr-filter)).  

We modeled retained catch per angler days with a negative binomial GLM in the R package sdmTMB. The initial model exploration included 
a delta-lognormal model that did not converge and a delta-gamma model, which did converge.  However, the proportion of zeroes was 
reproduced when the model was fit with a Bayesian negative binomial GLM (Figure \@ref(fig:pr-prop-zero)) and was retained despite the 
tail on the QQ plot of the MLE fit (Figure \@ref(fig:pr-qq)).  There are a handful of samples 
with higher than average CPUE and the authors checked with CDFW to determine whether the samples should still be included. 
CDFW indicated data sheets were not available prior to 2012, but the catches were less than 
the bag limits, and should be assumed to be correct. The significant year and region interaction was included in the final 
model selection and the index was area weighted based on the amount of interpreted rocky substrate in each district.  The ports along the northern 
California port are such that there is little overlap in the fishing grounds between ports, with the exception being the San Francisco Bay area. 
However, the private/rental fleet has a shorter range than the CPFV fleet and how we aggregated the data for the area weighting is appropriate (Figure \@ref(fig:pr-districtcpue)). 

Based on AICc values from maximum likelihood fits Table \@ref(tab:pr-modelselect), 
a main effects model including year, district and a year and district interaction. 
Month and primary target species were modeled as categorical covariates 
 (Table \@ref(tab:pr-index) and Figure \@ref(fig:pr-index)).

<!--Tables -->

\newpage

```{r, results = 'asis'}
library(dplyr)
ind <- read.csv(file.path(
  data_dir, "rec_indices", "crfs_pr_dockside", "bag_change_visuals",
  "pr_bag_limit_by_year.csv"
)) %>%
 mutate_at(2:6, funs(round(., 3)))

col_names <- c("Year", "Minimum", "25th Quantile", "Median", "75th Quantile", "Maximum")

sa4ss::table_format(
  x = ind,
  caption = "Summary values of the copper rockfish retained per angler (CPUE) to look at the effects of the sub-bag limit.",
  label = "pr-cpue",
  col_names = col_names,
  align = "r"
)
```

\newpage

```{r, results = 'asis'}
ind <- read.csv(file.path(
  data_dir, "rec_indices", "crfs_pr_dockside", "PR_obs_unobs.csv"
)) %>%
  mutate(Percent.RFGEN = scales::percent(Percent.RFGEN))

col_names <- c("Year", "Unspeciated", "Speciated", "Percent unspeciated")

sa4ss::table_format(
  x = ind,
  caption = "Summary of the number of speciated and unspeciated (RFGEN) rockfish 
  per year across all of California.",
  label = "pr-rfgen",
  col_names = col_names,
  align = "r",
  format.args = list(big.mark = ",")
)
```

\newpage

```{r, results = 'asis'}
ind <- read.csv(file.path(
  data_dir, "rec_indices", "crfs_pr_dockside", "north",
  "rm_last2yrs_area_weighted", "percent_pos.csv"
)) %>%
  mutate(percentpos = scales::percent(round(percentpos, 3)))
col_names <- c(
  "Year", "Trips with Target", "Trips without Target", "Total trips",
  "Percent with Target"
)

sa4ss::table_format(
  x = ind,
  caption = "Number of samples and percent positive for the dockside PR survey.",
  label = "pr-percentpos",
  col_names = col_names,
  format.args = list(big.mark = ",")
)
```

\newpage


```{r, results = 'asis'}
ind <- read.csv(file.path(
  data_dir, "rec_indices", "crfs_pr_dockside", "north",
   "rm_last2yrs_area_weighted", "data_filters.csv"
))
col_names <- c("Filter", "Description", "Number of Samples", "Positive Samples")

sa4ss::table_format(
  x = ind,
  caption = "Data filtering steps for the CRFS PR dockside survey.",
  label = "pr-filter",
  col_names = col_names,
  font_size = 9,
  landscape = TRUE,
  align = "l",
  custom_width = TRUE,
  format.args = list(big.mark = ","),
  col_to_adjust = c(2),
  width = c("8cm")
)
```

\newpage

```{r, results = 'asis'}
ind <- read.csv(file.path(
  data_dir, "rec_indices", "crfs_pr_dockside", "north", "rm_last2yrs_area_weighted",
  "model_selection.csv"
))
col_names <- c("Intercept",	"District",	"Month",	"Target Species",
"Year",	"District:Year", "Offset", "DF",	"AICc",	"Delta AICc")

sa4ss::table_format(
  x = ind,
  caption = "Model selection for the dockside PR survey.",
  label = "pr-modelselect",
  digits = 2,
  font_size = 8,
  col_names = col_names
)
```


\newpage

```{r, results = 'asis'}
ind <- read.csv(file.path(
  data_dir, "rec_indices", "crfs_pr_dockside",
  "north", "rm_last2yrs_area_weighted", "Index_forSS.csv"
))
ind <- ind[, c(1, 4, 5)]
col_names <- c("Year", "Estimate", "logSE")

sa4ss::table_format(
  x = ind,
  caption = "Estimated relative index of abundance for the dockside PR survey.",
  label = "pr-index",
  col_names = col_names,
  digits = 4
)
```

\newpage

<!--Figures -->


```{r, results = 'asis'}
sa4ss::add_figure(
  filein = file.path(
    data_dir, "rec_indices", "crfs_pr_dockside", "bag_change_visuals",
    "pr_copper_cpue_year_area_max5.png"
  ),
  caption = "Distribution by year of the number of copper rockfish retained per angler. 
  This includes sampler observed and angler reported catch. The vertical line at 1 represents the sub-bag 
  limit implemented in 2022.",
  label = "pr-bag"
)
```

\newpage

```{r, results = 'asis'}
sa4ss::add_figure(
  filein = file.path(
    data_dir, "rec_indices", "crfs_pr_dockside", "north", "rm_last2yrs_area_weighted",
    "average_cpue_by_cnty.png"
  ),
  caption = "Average CPUE by county prior to standardization.",
  label = "pr-districtcpue"
)
```


\newpage

```{r, results = 'asis'}
sa4ss::add_figure(
  filein = file.path(
    data_dir, "rec_indices", "crfs_pr_dockside", "north", "rm_last2yrs_area_weighted",
    "index.png"
  ),
  caption = "Index for the dockside PR survey.",
  label = "pr-index"
)
```

\newpage

```{r, results = 'asis'}
sa4ss::add_figure(
  filein = file.path(
    data_dir, "rec_indices", "crfs_pr_dockside", "north",
    "rm_last2yrs_area_weighted", "negbin_prop_zero_main_effects.png"
  ),
  caption = "Predicted proportion of zeroes from the Bayesian fit to the main effects model.",
  label = "pr-prop-zero"
)
```




\newpage

```{r, results = 'asis'}
sa4ss::add_figure(
  filein = file.path(
    data_dir, "rec_indices", "crfs_pr_dockside", "north",
    "rm_last2yrs_area_weighted", "qq.png"
  ),
  caption = "QQ plot for the dockside PR survey.",
  label = "pr-qq"
)
```

\newpage

