### CCFRP Index of Abundance {#ccfrp-index}

The California Collaborative Fisheries Research Program, [CCFRP](https://www.mlml.calstate.edu/ccfrp/), 
is a fishery-independent 
hook-and-line survey designed to monitor nearshore fish populations at a series of sampling 
locations both inside and adjacent to MPAs 
[@starr_variation_2015a; @wendt_collaborative_2009].  The CCFRP survey began in 
2007 along the central coast of California and was designed in collaboration 
with academics, NMFS scientists and fishermen. 
From 2007-2016 the CCFRP project was focused on the central California coast,
and has monitored four MPAs consistently. In 2017, the CCFRP expanded coastwide within California.  
The index of abundance was developed from the four MPAs sampled consistently 
(A&ntilde;o Nuevo and Point Lobos 
by Moss Landing Marine Labs; Point Buchon and Piedras Blancas by Cal Poly).

The survey design for CCFRP consists 500 x 500 m cells both within and 
adjacent to each MPA. On any given survey day site cells are randomly 
selected within a stratum (MPA and/or reference cells).  CPFVs are chartered 
for the survey and the fishing captain is allowed to search within the cell for 
a fishing location.  During a sampling event, each cell is fished for a total of 
30-45 minutes by volunteer anglers. Each fish encountered is recorded, measured, 
and released (or descended to depth) and can later be linked back to a particular angler, . 
 CCFRP samples shallower depths to avoid barotrauma-induced mortality.  
 Starting in 2017, a subset of fish have been retained to collect otoliths and fin 
clips that provide needed biological information for nearshore species. For the 
index of abundance, CPUE was modeled at the level of the drift, similar to the 
fishery-dependent onboard observer survey described above.

The CCFRP data are quality controlled at the time they are key punched and little 
filtering was needed for the index. 
Cells not consistently sampled over time were excluded as well as cells that never 
encountered `r spp`.
The full dataset for northern California contained 8,770 drifts, 23% of which encountered 
`r spp`.  After applying filters to remove drifts from sites that were not consistently sampled,
marked for exclusion in the data, or did not fish a minimum of 15 minutes, 7,078 drifts remained for 
for index standardization, with 1,757 drifts encountering `r spp`.

The CCFRP index includes all of the MPAs currently sampled from 2017-2022 and the core central California sampling sites from 2007-2022. Trends inside all of the MPAs sampled increased from 2017-2020. The final index (Table \@ref(tab:ccfrp-index)) represents a similar trend to the arithmetic mean of the annual CPUE (Figure \@ref(fig:ccfrp-avg-cpue)). We modeled retained catch per angler hour (CPUE; number of fish per angler hour) using MLE in the sdmTMB package. Indices with a year and area (location along the coast) interaction were not considered in model selection due to the expansion of the survey in 2007, but a year and MPA interaction was modeled. Figure \@ref(fig:ccfrp-avg-cpue) mean by inside (MPA) and outside (REF) MPAs over  time and illustrates the distinct trends of increasing average CPUE over time.

A negative binomial model was fit to the drift-level data (catch with a log offset for angler 
hours). Because the average observed CPUE inside MPAs and in the reference sites exhibited 
differing trends, we explored a year:mpa/reference site interaction, which was selected as the best 
fit model by AIC Table \@ref(tab:ccfrp-model-selection)), The final model included
year, mpa/reference categorization, depth, depth squared, and a year:mpa/reference interaction. 
The model was fit using the sdmTMB R package (version 0.3.0). 

Based on work completed at the SWFSC, we estimate that the percent of rocky reef habitat from Point Conception to the California/Oregon border within California state waters is 892 $km^2$, of which approximately 23% is in MPAs that prohibit the harvest of groundfish (pers comm. Rebecca Miller, UCSC). There is recreational fishing outside of state waters, but habitat maps are not available at the same 2-m resolution and do not allow for direct comparisons. The final index was weighted, giving 20% of the model weight to MPAs and 80% of model 
weight to the "open" areas within the state.



```{r, results = 'asis'}

tab <- read.csv(file.path(data_dir, "survey_indices", "ccfrp", "north", "dataFilters.csv"))

sa4ss::table_format(x = tab,
             caption = "Data filtering for the CCFRP survey.",
             label = "ccfrp-data-filter",
             align = 'l',
             longtable = TRUE,
             font_size = 7,
             landscape = TRUE)                         
```

\newpage

```{r, results = 'asis'}

tab <- read.csv(file.path(data_dir, "survey_indices", "ccfrp", "north", "model_selection.csv"))

sa4ss::table_format(x = tab,
             caption = "Model selection for the CCFRP survey.",
             label = "ccfrp-model-selection",
             align = 'l',
             longtable = TRUE,
             font_size = 7,
             landscape = TRUE)                         
```

\newpage

```{r, results = 'asis'}

ind <- read.csv(file.path(data_dir, "survey_indices", "ccfrp", "north", "area_weighted", "index_forSS.csv"))
ind <- ind[, c(1,4,5)]
col_names = c("Year", "Estimate", "logSE")

sa4ss::table_format(x = ind,
             caption = "Estimated relative index of abundance for the CCFRP survey.",
             label = "ccfrp-index",
             col_names = col_names)                         
```

\newpage

\FloatBarrier

```{r, results = 'asis'}
#sa4ss::add_figure(
#filein = file.path(data_dir, "survey_indices", "ccfrp", "north", "mpa_site_cpue.png"), 
#caption = "Map of CCFRP and CDFW ROV sampling sites with the total number of copper rockfish 
#observed by site. The 3nm maritime limit and outline of California MPAs are also shown.  The CDFW blocks are 
##colored a darker blue where experts have indicated copper rockfish can be found.",
#label = 'ccfrp-avg-cpue')
```

\FloatBarrier
\newpage

```{r, results = 'asis'}
sa4ss::add_figure(
filein = file.path(data_dir, "survey_indices", "ccfrp", "north", "mpa_site_cpue.png"), 
caption = "Average CPUE by site with trends prior to standardization in the MPA and REF areas.",
alt_caption = "The average CPUE is higher in the MPAs at Piedras Blancas, Point Lobos and Stewarts Point.",
label = 'ccfrp-avg-cpue')
```

\newpage
```{r, results = 'asis'}
sa4ss::add_figure(
filein = file.path(data_dir, "survey_indices", "ccfrp", "north", "area_weighted", "qq.png"), 
caption = "QQ-plot for the CCFRP survey.",
alt_caption = "The q q plots indicates a fairly good fit to the index.",
label = 'ccfrp-qq')
```


\newpage

```{r, results = 'asis'}
sa4ss::add_figure(
filein = file.path(data_dir, "survey_indices", "ccfrp", "north", "area_weighted", "Index.png"), 
caption = "The weighted relative index of abundance.",
alt_caption = "The weighted index is relatively flat until 2015 and then increases.",
label = 'ccfrp-index')
```

