## CPFV Fleet Description, Sampling, and Trip Types  {#cpfv-samples}

During the 2021 copper rockfish stock assessment meeting and during the pre-assessment workshop for the 2023 groundfish assessments, concern was raised regarding possible biases in the available data by trip types. This appendix describes the sampling and available data from two recent years as an example of the relationship between the available data and catches for copper rockfish.

CDFW conducts several surveys are part of the CRFS program, including an onboard observer survey, angler interviews, and a required CPFV logbook for each trip. The [CRFS sampling manual](https://nrm.dfg.ca.gov/FileHandler.ashx?DocumentID=62348&inline) outlines the sampling methodologies for each survey component.  The state of California allows the filleting of fish at sea; to accurately identify rockfish to species and obtain measurements of whole fish the majority of angler interviews occur onboard the vessel for the CPFV fleet.  The CPFV fleet is not required to speciate the catch and only one block number is recorded per entry. For this reasons the CPFV logbook data are rarely used to develop an index of abundance for groundfish species. However, the CPFV logbook data provide insight into the spatial distribution of fishing effort.

The [California Fisheries Recreational Fisheries Survey Methods](https://nrm.dfg.ca.gov/FileHandler.ashx?DocumentID=36136&inline) indicates the CPFV "sampling goal is to sample onboard at the historical sampling frequency of two to five percent of estimated CPFV trips of interest (e.g., trips targeting groundfish, inshore and coastal pelagic species) at each CPFV landing and to sample other CPFV trip types dockside." California is divided into six regions for the CRFS sampling, and these represent the finest stratification for catch and effort estimates (Figure \@ref(fig:crfs-districts)).  

The CPFV fleet north and south of Point Conception are fundamentally different in terms of the vessels fishing, available target species, and also fishery regulations over the past twenty years. The CPFVs north of Point Conception targeting groundfish do not typically target other species on the same trip, with the exception being a half-day bottomfish trip mixed with a half-day of Dungeness crab pot fishing. The fleet north of Bodega Bay California is dominated by smaller 6-pack vessels with limited capacity.  It may not be possible for a sampler to ride onboard a 6-pack vessel if the vessel is at capacity. Overnight trips are extremely rare in northern California. In addition, it is important to note that even though Santa Barbara county spans Point Conception, all of the fish encountered off Santa Barbara county north of Point Conception are landed in San Luis Obispo county in District 3. 

In southern California, the diversity of target species is higher an includes several bass species, state managed gamefish, coastal pelagics, and highly migratory species, as well as boats that fish in Mexican waters. The trip types in southern California include half-day trips where a CPFV will run two trips a day, three-quarter day trips to fishing grounds further offshore, such as the Channel Islands, and overnight trips that can access areas like San Nicholas in the southern Channel Island or may be combination trips fishing for tunas, but also catching rockfish limits. The diversity of trip types and mixed target trips in southern California pose a challenge for both sampling and managing the fisheries.

We filtered the CPFV logbook data to trips that recorded at least one rockfish and the CPFV onboard observer data to trips that encountered at least 1 percent groundfish species. We aggregated within each dataset across 2018 and 2019 and areas where necessary to ensure confidentiality requirements were met. The tables below represent an aggregation of data from 2018 and 2019 combined as they are the two years pre-COVID that best represent the CPFV fleet's activity. We extracted data from the CPFV logbook data and the onboard observer sampled trips to describe the differences in portion of trips sampled and the distribution of copper rockfish catches. In the CPFV logbooks, 60 trips were recorded as multi-day trips in northern California. This represented less then 1 percent of the trips in northern California and we did not investigate the accuracy of these entries. Approximately 6 percent of the logbooks from District 1 recorded a block number in Mexican waters as the primary location fished. Fewer than 10 trips that recorded block numbers along the mainland of southern California were recorded a multi-day trips.  These were removed from the tables below. 

The combined onboard observer sampling rate for 2018-2019 was 3 percent of all CPFV trips in the data used. There were no trips observed onboard in CRFS District 5 during 2018-2019, but 1,052 CPFV logbook records were submitted that recorded at least one rockfish. Grouping the districts by north and south of Point Conception, 2 percent of all trips in northern California were sampled onboard (Table \@ref(tag:percent-observed)). In southern California, 4 percent of single day trips were observed and less than 1 percent of multi-day trips were observed.

We broke the data in southern California down further to explore sampling effort by trip type, and assigned a CPFV logbook entry to a region based on the recorded block number (Table \@ref(tab:logbook-triptype)). The offshore region was a catch-all that included blocks outside the range of a half-day trip, but not within the vicinity of an island. In CRFS District 1, 79 percent of the observed trips were half-day day trips, which can access the District 1 mainland. In District 2, 29 percent of the observed trips were half-day day trips. The vessels in District 2 typically offer fewer half-day day trips and fish the nearshore when weather precludes crossing the channel to the northern Channel Islands.

To put these sampling rates in context for copper rockfish, we explored the total estimated mortality related to the distribution of sampling. The total mortality of copper rockfish in metric tons from 2018-2019 from the CPFV fleet by CRFS District is in Table \@ref(tab:catch-example). Fifty-two percent of the total copper rockfish mortality was from northern California and 48 percent from southern California.  Within northern California, 50 percent of the total mortality originated from District 3, and in southern California, 81 percent of the total mortality originated from District 2. 

From the onboard observer trips in District 1, 37 percent of the observed coppers were from half-day day trips, 42 percent from three-quarter to full day trips, and 21 percent of the observed copper rockfish were from the five observed multi-day trips (Table \@ref(tab:onboard-coppers)). 

In District 2, 17 percent of the observed copper were from half-day day trips, 75 percent from the three-quarter to full day trips and 8 percent from overnight trips. When weather allows, the northern Channel Islands can be accessed from CRFS District 2 during a three-quarter to full day trip or a multi-day trip, depending on the port. For instance, the CPFVs from Oxnard, California access the northern Channel Island during multi-day trips, and the same areas are accessed by the three-quarter to full day boats out of Santa Barbara Landing. 


\newpage

```{r, results = 'asis'}
sa4ss::add_figure(
filein = file.path(data_dir, "rec_indices", "cpfv_logbook_summaries", "crfs_districts.png"), 
caption = "Map of the CDFW CRFS sampling Districts.",
label = 'crfs-districts')
```

\pagebreak

```{r, results = 'asis'}
ind <- read.csv(file.path(data_dir, "rec_indices", "cpfv_logbook_summaries", "area_percent_observed.csv"))
col_names = c("Area", "Single day", "Multi day")

sa4ss::table_format(x = ind,
             caption = "The percent of trips sampled onboard by trip type and area for 2018 and 2019, using the number of trips observed and CPFV logbook trips described in the text.",
             label = "percent-observed",
             col_names = col_names)                         
```

\newpage 

```{r, results = 'asis'}
ind <- read.csv(file.path(data_dir, "rec_indices", "cpfv_logbook_summaries", "copp_catch_2018_2019.csv"))
col_names = c("District", "2018", "2019", "Total")

sa4ss::table_format(x = ind,
             caption = "Total mortality in metric tons of copper rockfish from 2018 and 2019 from the CPFV fleet by CRFS District.",
             label = "catch-example",
              align = "r",
             col_names = col_names)                         
```

\newpage

```{r, results = 'asis'}
ind <- read.csv(file.path(data_dir, "rec_indices", "cpfv_logbook_summaries", "fordoc_onboard_copper_summary.csv"))
col_names = c("District",  "1/2 day trips", "3/4-1 day trips","Overnight trips")

sa4ss::table_format(x = ind,
             caption = "Number of copper rockfish observed during the CPFV trips sampled onboard by district and trip type from 2018-2019.",
              align = "r",
             label = "onboard-coppers",
             col_names = col_names)                         
```

\newpage

```{r, results = 'asis'}
ind <- read.csv(file.path(data_dir, "rec_indices", "cpfv_logbook_summaries", "fordoc_Onboard_trip_duration_observed.csv"))
col_names = c("District", "1/2 day trips", "3/4-1 day trips","Overnight trips", "Percent of trips with copper", "Total number of copper observed")

sa4ss::table_format(x = ind,
             caption = "Number of CPFV trips sampled as part of the onboard observer sruvey during 2018-2019 by trip type and District. District 4 and 6 were combined to retain confidentiality.  No trips from District 5 were sampled.",
             label = "onboard-trips",
             col_names = col_names)                         
```

\newpage


```{r, results = 'asis'}
ind <- read.csv(file.path(data_dir, "rec_indices", "cpfv_logbook_summaries", "fordoc_logbook_by_triptype.csv"))
col_names = c("Region", "Multi-day", "Single day")

sa4ss::table_format(x = ind,
             caption = "Number of CPFV logbook entries with at least one rockfish, grouped by region fished and trip type from 2018-2019.",
              align = "r",
             label = "logbook-triptype",
             col_names = col_names)                         
```



