## CPFV Fleet Description, Trip Types, and Sampling  {#cpfv-samples}

During the 2021 copper rockfish stock assessment review meeting and during the pre-assessment workshop for the 2023 groundfish assessments, concern was raised regarding possible biases in the available data from teh CPFV fleet. This appendix describes the CPFV fleet, including the differences between the fleet north and south of Point Conception and why sampling by trip type was raised as a concern in southern California.  We then used available data from the CPFV fleet from the two most recent years pre-COVID (2018 and 2019) as an example to illustrate the relationship between the data collected, and the distribution of effort and catches for copper rockfish. 


The goals was to compare the the number of trips CPFV logbook data with those from the CRFS onboard observer surveys. We did this by:
 \begin{enumerate}
 \item 


 \end{enumerate} 

*CPFV Fleet Description.* The CPFV fleets north and south of Point Conception are fundamentally different in terms of the size of the vessels, available target species, and accessible areas and depths. The CPFVs north of Point Conception targeting groundfish do not typically target other species on the same trip, with the exception being a half-day bottomfish trip mixed with a half-day of Dungeness crab pot fishing.  Overnight trips are extremely rare in northern California and weather is a more contstraining factor as you move north along the coast. There are few Coast Guard inspected vessels north of Bodega Bay, California and the recreational fleet is dominated by smaller 6-pack vessels with limited capacity.  

In southern California, the diversity of target species is higher and includes several bass species, state managed gamefish, coastal pelagics, and highly migratory species. There are three distinct trip types in southern California. The shortest of these is a half-day trip where a CPFV will run two trips a day. The three-quarter to full day trips are able to access fishing grounds further offshore, such as the Channel Islands. Overnight and multi-day access areas like San Nicholas Island and may target a combination of species, i.e., trips targeting tunas, but also catching rockfish. A number of CPFVs in southern California also transit to fish in Mexican waters for rockfish. The diversity of trip types and mixed target species within a trip in southern California pose a challenge for both sampling and managing the fisheries.


*Available CPFV Catch and Effort Data.* The components of the CDFW sampling programs used in this analysis are the CRFS CPFV onboard observer survey, CRFS angler interviews, and the mandatory, self-reported CPFV logbooks. 

The CRFS program divides California into six districts, and these represent the finest stratification of catch and effort estimates for stock assessments and management (Figure \@ref(fig:crfs-districts)). The [CRFS sampling manual](https://nrm.dfg.ca.gov/FileHandler.ashx?DocumentID=62348&inline) outlines the sampling methodologies for each survey component. The [California Fisheries Recreational Fisheries Survey Methods](https://nrm.dfg.ca.gov/FileHandler.ashx?DocumentID=36136&inline) indicates the CPFV mode "sampling goal is to sample onboard at the historical sampling frequency of two to five percent of estimated CPFV trips of interest (e.g., trips targeting groundfish, inshore and coastal pelagic species) at each CPFV landing and to sample other CPFV trip types dockside." 

The CRFS data collected onboard are a key component to obtaining species-specific information from the CPFV fleet because the state of California allows the filleting of fish at sea. To accurately identify rockfish species and obtain measurements of whole fish, the majority of CPFV angler interviews occur onboard the vessel. 

The CPFV logbooks include information on the the general location fished, number of anglers, number of fish retained and discarded, use of descending devices, as examples. The CPFV fleet is not required to speciate the catch and only one block number is recorded per entry. For these reasons the CPFV logbook data are not often used to develop an index of abundance for groundfish species. However, the CPFV logbook data provide insight into the spatial distribution of fishing effort and changes in effort over time.
 

*Data Summaries from 2018-2019.*  The goal of this exploratory analysis was to compare the CPFV logbook data and the onboard observer sampled trips to describe the differences in portion of trips sampled and the distribution of copper rockfish catches. In order to maintain confidentiality, we aggregated data within each dataset across 2018 and 2019 (and areas where necessary). These two years represent the two most recent years of data pre-COVID. 

We filtered the CPFV logbook data to trips that recorded at least one rockfish and the CPFV onboard observer data to trips that encountered at least 1 percent groundfish species. Additional filters applied to the CPFV logbook data included removing trips that recorded the primary fishing location in Mexican waters (6% of all trips). We also removed a small fraction (less than 10 trips) recorded as multi-day trips, but a fishing location along the mainland of southern California. 

The combined onboard observer sampling rate for 2018-2019 was 3 percent of all CPFV trips statewide in the filtered data. At a finer scale, of note is that no trips were observed onboard in CRFS District 5 during 2018-2019. However, 1,052 CPFV logbooks were submitted from District 5 ports that recorded at least one rockfish. When we grouped the data by the modeled areas north and south of Point Conception, we found that  2 percent of all trips in northern California were sampled onboard (Table \@ref(tab:percent-observed)). In southern California, 4 percent of single day trips were observed and less than 1 percent of multi-day trips were observed.

We then explored the southern California data further to look at sampling effort by trip type. The CPFV logbooks indicated if a trip was a single or multi-day, but does not differentiate between a half or three-quarter day trip. We assigned each CPFV logbook trip from southern California to a sub-region (District 1 mainland, District 1 mainland, northern Channel Islands, Southern Channel Islands, and Offshore) based upon the recorded block number (Table \@ref(tab:logbook-triptype)). The trips assigned to "Southern CA Offshore" were a catch-all that included blocks outside the range of a half-day trip, but not within the vicinity of an island. Approximately 16 percent of the CPFV logbooks in southern California were from multi-day trips. As expected, the trips recording a CDFW block near the mainland were recorded as half-day trips. More than twice as many trips to the northern Channel Islands were single-day trips vs multi-day trips. The vessels in District 2 typically offer fewer half-day day trips and fish the nearshore when weather precludes crossing the channel to the northern Channel Islands on a three-quarter day trip. 

In terms of the onboard sampling, in CRFS District 1, 79 percent of the observed trips were half-day day trips and in District 2, 29 percent of the observed trips were half-day day trips. 

To put these sampling rates in context for copper rockfish, we looked at the total estimated mortality by district related to the distribution of sampling. The total mortality of copper rockfish in metric tons from 2018-2019 from the CPFV fleet by CRFS District is in Table \@ref(tab:catch-example). Fifty-two percent of the total copper rockfish mortality was from northern California and 48 percent from southern California.  Within northern California, 50 percent of the total mortality originated from District 3, and in southern California, 81 percent of the total mortality originated from District 2. 

From the onboard observer trips in District 1, 37 percent of the observed coppers were from half-day day trips, 42 percent from three-quarter to full day trips, and 21 percent of the observed copper rockfish were from the five observed multi-day trips (Table \@ref(tab:onboard-coppers)). 

In District 2, 17 percent of the observed copper were from half-day day trips, 75 percent from the three-quarter to full day trips and 8 percent from multi-day trips. When weather allows, the northern Channel Islands can be accessed from CRFS District 2 during a three-quarter to full day trip or a multi-day trip, depending on the port. For instance, the CPFVs from Channel Islands Sportfishing in Oxnard, California access the northern Channel Islands during multi-day trips, and the same areas are accessed by the three-quarter to full day trips out of Santa Barbara Landing. 


\newpage

```{r, results = 'asis'}
sa4ss::add_figure(
filein = file.path(data_dir, "rec_indices", "cpfv_logbook_summaries", "crfs_districts.png"), 
caption = "Map of the CDFW CRFS sampling Districts.",
label = 'crfs-districts')
```

\pagebreak

```{r, results = 'asis'}
ind <- read.csv(file.path(data_dir, "rec_indices", "cpfv_logbook_summaries", "area_percent_observed.csv"))
col_names = c("Area", "Single day", "Multi day")

sa4ss::table_format(x = ind,
             caption = "The percent of trips sampled onboard by trip type and area for 2018 and 2019, using the number of trips observed and CPFV logbook trips described in the text.",
             label = "percent-observed",
             col_names = col_names)                         
```



```{r, results = 'asis'}
ind <- read.csv(file.path(data_dir, "rec_indices", "cpfv_logbook_summaries", "copp_catch_2018_2019.csv"))
col_names = c("District", "2018", "2019", "Total")

sa4ss::table_format(x = ind,
             caption = "Total mortality in metric tons of copper rockfish from 2018 and 2019 from the CPFV fleet by CRFS District.",
             label = "catch-example",
              align = "r",
             col_names = col_names)                         
```


```{r, results = 'asis'}
ind <- read.csv(file.path(data_dir, "rec_indices", "cpfv_logbook_summaries", "fordoc_onboard_copper_summary.csv"))
col_names = c("District",  "1/2 day trips", "3/4-1 day trips","Overnight trips")

sa4ss::table_format(x = ind,
             caption = "Number of copper rockfish observed during the CPFV trips sampled onboard by district and trip type from 2018-2019.",
              align = "r",
             label = "onboard-coppers",
             col_names = col_names)                         
```


```{r, results = 'asis'}
ind <- read.csv(file.path(data_dir, "rec_indices", "cpfv_logbook_summaries", "fordoc_Onboard_trip_duration_observed.csv"))
col_names = c("District", "1/2 day trips", "3/4-1 day trips","Overnight trips", "Percent of trips with copper", "Total number of copper observed")

sa4ss::table_format(x = ind,
             caption = "Number of CPFV trips sampled as part of the onboard observer survey during 2018-2019 by trip type and District. District 4 and 6 were combined to retain confidentiality.  No trips from District 5 were sampled.",
             label = "onboard-trips",
             col_names = col_names)                         
```



```{r, results = 'asis'}
ind <- read.csv(file.path(data_dir, "rec_indices", "cpfv_logbook_summaries", "fordoc_logbook_by_triptype.csv"))
col_names = c("Region", "Multi-day", "Single day")

sa4ss::table_format(x = ind,
             caption = "Number of CPFV logbook entries with at least one rockfish, grouped by region fished and trip type from 2018-2019.",
              align = "r",
             label = "logbook-triptype",
             col_names = col_names)                         
```



