---
geometry: margin=1in
month: "`r format(Sys.Date(), '%B')`"
year: "`r format(Sys.Date(), '%Y')`"
preamble: |
output:
  sa4ss::techreport_pdf:
    default
  bookdown::pdf_document2:
    keep_tex: true
lang: en
papersize: letter
---

```{r opts, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
knitr::knit_hooks$set(plot = function(x,options) {
      base = knitr::opts_knit$get('base.url')
      if (is.null(base)) base = ''
      alt = ifelse (is.null(options$alt),"",options$alt)
      cap = ifelse (is.null(options$caption),"",options$caption)
      if (alt != ""){
        sprintf('![%s](%s%s "%s")', cap, base, x, alt)
      } else {
        sprintf('![%s](%s%s)', cap, base, x)
        }
  })

load('saved_directories.Rdata')
load("00opts.Rdata")

spp <- "copper rockfish"
Spp <- "Copper rockfish"
area <- "north of Point Conception"

if(file.exists("00mod.Rdata")){
  load("00mod.Rdata")
} else {
  print("Model output not being read. Please run the read_model() function.")
}

source(file.path(doc_dir, "helper_functions.R"))

hkl <- "NWFSC Hook and Line survey"

#source(file.path(r_dir, "get_derived_quants.R"))

```

<!--chapter:end:00a.Rmd-->

---
author:
  - name: Melissa H. Monk
    code: 1
    first: M
    middle: H
    family: Monk
  - name: Chantel R. Wetzel
    code: 2
    first: C
    middle: R
    family: Wetzel
  - name: Julia Coates
    code: 3
    first: J
    middle: ''
    family: Coates
author_list: Monk, M.H., C.R. Wetzel, J. Coates
affiliation:
  - code: 1
    address: Southwest Fisheries Science Center, U.S. Department of Commerce, National
      Oceanic and Atmospheric Administration, National Marine Fisheries Service, 110
      McAllister Way, Santa Cruz, California 95060
  - code: 2
    address: Northwest Fisheries Science Center, U.S. Department of Commerce, National
      Oceanic and Atmospheric Administration, National Marine Fisheries Service, 2725
      Montlake Boulevard East, Seattle, Washington 98112
  - code: 3
    address: .na.character
address:
  - ^1^Southwest Fisheries Science Center, U.S. Department of Commerce, National Oceanic
    and Atmospheric Administration, National Marine Fisheries Service, 110 McAllister
    Way, Santa Cruz, California 95060
  - ^2^Northwest Fisheries Science Center, U.S. Department of Commerce, National Oceanic
    and Atmospheric Administration, National Marine Fisheries Service, 2725 Montlake
    Boulevard East, Seattle, Washington 98112
  - ^3^NA
---

<!--chapter:end:00authors.Rmd-->

---
bibliography:
 - sa4ss.bib
 - copper.bib
 - wcassess.bib
---

<!--chapter:end:00bibliography.Rmd-->

---
title: Status of Copper Rockfish (_Sebastes caurinus_) along the California North
  of Pt. Conception U.S. West coast in 2022
---

<!--chapter:end:00title.Rmd-->

\pagebreak
\pagenumbering{roman}
\setcounter{page}{1}

\renewcommand{\thetable}{\roman{table}}
\renewcommand{\thefigure}{\roman{figure}}


\setlength\parskip{0.5em plus 0.1em minus 0.2em}

<!--chapter:end:01a.Rmd-->

```{r executive, echo = FALSE}
executive <- list()
executive[["stock"]] <- paste0("This assessment reports the status of ",
  spp, " (_", spp.sci, "_) off the ", coast, 
  " coast using data through 2022.")
```

# Executive summary{-}

## Stock{-}

`r executive[["stock"]]`

## Catches{-}

Replace text with
trends and current levels.
Include Table for last 10 years.
Include Figure with long-term estimates.

I am testing references of Table \ref{tab:removalsES} and \ref{tab:north-removalsES}

\input{tex_tables/a_Catches_ES.tex}


\input{tex_tables/north_a_Catches_ES.tex}

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "catch2 landings stacked.png"), 
caption = "Landings by fleet used in the base model where catches in metric tons by fleet are stacked",
label = 'es-catch')
```

## Data and assessment{-}

This assessment uses the stock assessment framework
Stock Synthesis 
```{r es-modelversion, echo=FALSE} 
if (exists("model")) {
  strsplit(model$SS_version,";")[[1]][1]
}
```
(SS3).

Replace text with
date of last assessment,
type of assessment model,
data available,
new information, and
information lacking.

## Stock biomass and dynamics{-}

Replace text with
trends and current levels relative to virgin or historic levels and
description of uncertainty.
Include Table for last 10 years.
Include Figure with long-term estimates.

\input{tex_tables/b_SSB_ES.tex}

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots",
"ts7_Spawning_output_with_95_asymptotic_intervals_intervals.png"), 
caption = "Estimated time series of spawning output (circles and line: median; light broken lines: 95 percent intervals) for the base model",
label = 'es-sb')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "ts9_Relative_spawning_output_intervals.png"), 
caption = "Estimated time series of fraction of unfished spawning output (circles and line: median; light broken lines: 95 percent intervals) for the base model",
label = 'es-depl')
```

\clearpage

## Recruitment{-}

Replace text with
trends and current levels relative to virgin or historic levels and
description of uncertainty.
Include Table for last 10 years.
Include Figure with long-term estimates.

\input{tex_tables/c_Recr_ES.tex}

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "ts11_Age-0_recruits_(1000s)_with_95_asymptotic_intervals.png"), 
caption = "Estimated time series of age-0 recruits (1000s) for the base model with 95 percent intervals",
label = 'es-recruits')
```

```{r, results = 'asis'}
#add_figure(
#filein = file.path(model_dir, "plots", "recdevs2_withbars.png"), 
#caption = "Estimated time series of recruitment deviations",
#label = 'es-rec-devs')
```

\clearpage

## Exploitation status{-}

Replace text with
total catch divided by exploitable biomass or SPR harvest rate.
Include Table for last 10 years.
Include Figure with trend in f relative to target vs. trend in biomass relative to the target.

\input{tex_tables/d_SPR_ES.tex}

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "SPR2_minusSPRseries.png"), 
caption = "Estimated 1 - relative spawning ratio (SPR) by year for the base model. The management target is plotted as a red horizontal line and values above this reflect harvest in excess of the proxy harvest rate",
label = 'es-1-spr')
```

## Ecosystem considerations{-}


## Reference points{-}

Replace text with
management targets and definition of overfishing, including the harvest rate that brings the stock to equilibrium at $B_{40\%}$, i.e., the $B_{MSY}$ proxy and the equilibrium stock size that results from fishing at the default harvest rate, i.e., the $F_{MSY}$ proxy.
Include Table of estimated reference points for ssb, SPR, exploitation rate, and yield based on SSB proxy for MSY, SPR proxy for MSY, and estimated MSY values.


```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "SPR4_phase.png"), 
caption = "Phase plot of estimated 1-SPR versus fraction unfished for the base model",
label = 'es-phase')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "yield2_yield_curve_with_refpoints.png"), 
caption = "Equilibrium yield curve for the base case model. Values are based on the 2020
fishery selectivities and with steepness fixed at 0.80",
label = 'es-yield')
```


## Management performance{-}

Include Table of most recent 10 years of
catches in comparison with OFL, ABC, HG, and OY/ACL values,
overfishing levels,
actual catch and discard.
Include OFL (encountered), OFL (retained), and OFL (dead) if different due to discard and discard mortality.


```{r, results = 'asis'}

create_management_table(
  management_dir = management_dir, 
  doc_dir = doc_dir, 
  doc_names = c("nca", 'sca'),
  years = 2012:2022,
  table_names = c("copper_ca_north.csv", "copper_ca_south.csv"),
  prefix = "es")

```


## Unresolved problems and major uncertainties{-}


```{r, echo=FALSE, results='asis'}
filein = file.path(getwd(),'shared_text','unresolved_problems_uncertainties.Rmd')
read_child(filein)
```

## Decision table and projections{-}

Replace text with
projected yields (OFL, ABC, and ACL), spawning biomass, and stock depletion levels for each year.
OFL calculations should be based on the assumption that future catches equal ABCs and not OFLs.


```{r, results = 'asis'}

create_projection_table(
    management_dir = management_dir, 
    doc_dir = doc_dir, 
    fixed_removals = c(70, 70),
    doc_names = c("nca", 'sca'),
    years = 2023:2034,
    table_names = c("copper_ca_north.csv", "copper_ca_south.csv"),
    prefix = 'es')

```



## Scientific uncertainty{-}

```{r, echo=FALSE, results='asis'}
filein = file.path(getwd(), "shared_text",'scientific_uncertainty.Rmd')
read_child(filein)
```

## Research and data needs{-}

```{r, echo=FALSE, results='asis'}
filein = file.path(getwd(), "shared_text",'research_and_data_needs.Rmd')
read_child(filein)
```

<!--chapter:end:01executive.Rmd-->

\pagebreak
\setlength{\parskip}{5mm plus1mm minus1mm}
\pagenumbering{arabic}
\setcounter{page}{1}
\renewcommand{\thefigure}{\arabic{figure}}
\renewcommand{\thetable}{\arabic{table}}
\setcounter{table}{0}
\setcounter{figure}{0}

<!--chapter:end:10a.Rmd-->

# Introduction
## Basic Information and Life History
This assessment reports the status of `r spp` (*Sebastes caurinus*) off the California coast, north of Point Conception, using data through 2022.

```{r, echo=FALSE, results='asis'}
filein <- file.path(doc_dir, "shared_text",'1_intro_life_history_fishery_info.Rmd')
read_child(filein)
```

## Ecosystem Considerations
Replace text.

## Historical and Current Fishery Information

Off the coast of California, north of Point Conception, `r spp` is caught in both commercial and recreational fisheries. Recreational removals have been the largest source of fishing mortality, comprising nearly 85 percent of total removals of `r spp` across all years (Table XX and Figure XX). The landings from the commercial fishery have been minimal by year, expect for a brief period between the mid-1980s and early-2000s. 

```{r, echo=FALSE, results='asis'}
filein <- file.path(doc_dir, "shared_text",'1_intro_ca_commercial.Rmd')
read_child(filein)
```

`r Spp` residing between Point Conception and the California/Oregon border are assessed here as a single, separate stock (Figure \ref{fig:map}). This designation was made based on oceanographic, geographic, and fishery conditions. The `r spp` population in California waters was split at Point Conception due to water circulation patterns that create a natural barrier between nearshore rockfish populations to the north and south. The northern border for this assessment was defined as the California/Oregon border due to substantial differences in historical and current exploitation levels. Additionally, the fairly sedentary nature of adult `r spp`, likely limits flow of fish between northern California and areas to the north. 

## Summary of Management History and Performance
Replace text.

## Foreign Fisheries
Replace text.

<!--chapter:end:11introduction.Rmd-->

# Data

Data comprise the foundational components of stock assessment models.
The decision to include or exclude particular data sources in an assessment model depends on many factors.
These factors often include, but are not limited to,
the way in which data were collected (e.g., measurement method and consistency);
the spatial and temporal coverage of the data;
the quantity of data available per desired sampling unit;
the representativeness of the data to inform the modeled processes of importance;
timing of when the data were provided;
limitations imposed by the Terms of Reference; and
the presence of an avenue for the inclusion of the data in the assessment model.
Attributes associated with a data source can change through time,
as can the applicability of the data source when different modeling approaches are explored (e.g., stock structure or time-varying processes).
Therefore, the specific data sources included or excluded from this assessment should not necessarily constrain the selection of data sources applicable to future stock assessments for `r spp`.
Even if a data source is not directly used in the stock assessment they can provide valuable insights into biology, fishery behavior, or localized dynamics.

Data from a wide range of programs were available for possible inclusion in the current assessment model.
Descriptions of each data source included in the model (Figure \@ref(fig:data-plot)) and sources that were explored but not included in the base model are provided below.
Data that were excluded from the base model were explicitly explored during the development of this stock assessment or have not changed since their past exploration in a previous `r spp` stock assessment.
In some cases, the inclusion of excluded data sources were explored through sensitivity analyses (see Section \@ref(assessment-model)).

<!--chapter:end:20data.Rmd-->

## Fishery-Dependent Data

### Commercial Fishery

#### Landings and Discards
\

```{r, echo=FALSE, results='asis'}
general_wd = file.path(doc_dir, "shared_text")
filein = file.path(general_wd,'2f_commercial_removals.Rmd')
read_child(filein)
```


#### Composition Data

Biological data were extracted from the PacFIN Biological Data System on March 20, 2023. Length data for the commercial fleet were extracted from the PacFIN Biological Data System (BDS) with samples for north↨ of Point Conception beginning in 1978 (Tables \ref{tab:dead-com-len} and \ref{tab:live-com-len}). The commercial data was split by landed condition, live or dead, with the first data for the live fish fishery beginning in 1994. The number of length samples by fleet were highly variable with the largest number of sample by year being recorded in the 1990s for the dead fish fishery. In recent years, the number of length samples by year are limited for both fleets with the live fish with annual sample sizes less than 100 per year. The number of samples prior to the 1990s and in the 2000s for the dead fish fishery were sparse and variable across sizes. During model explorations any year with less than 20 sampled fish were considered too sparse to accurately reflect the fleet selectivity for that year (see [Appendix A](#excluded-data) for implied fits to these lengths). 

The majority of lengths observed by the commercial fleet landed dead `r spp` ranged between approximately 25 - 50 cm (Figure \ref{fig:com-dead-len-data}, detailed length compositions by year can be found in the Appendix, Section \ref{length-data}). Notably, in the early years of data prior to 1990 observed few smaller fish compared to later years. The mean length observed by year ranged between approximately 30 - 45 cm (Figure \ref{fig:mean-com-dead-len-data}). The mean observed length since 2010 slowly increase through 2018 with a drop in the mean observed age in the most recent years data.

The observed distribution of sizes sampled from the commercial live fish fleet were generally variable prior to 2011 with the length distributions since indicating a smaller range of sizes being landed after 2011 (Figure \ref{fig:com-live-len-data}). The observed mean length of fish landed live also clearly shows a drop in average sizes being landing starting in 2011 (Figure \ref{fig:mean-com-live-len-data}).  

The input sample sizes for all commercial data were calculated based on a combination of trips and fish sampled:

\begin{centering}

Input effN = $N_{\text{trips}} + 0.138 * N_{\text{fish}}$ if $N_{\text{fish}}/N_{\text{trips}}$ is $<$ 44

Input effN = $7.06 * N_{\text{trips}}$ if $N_{\text{fish}}/N_{\text{trips}}$ is $\geq$ 44

\end{centering}

### Recreational Fishery

#### Landings and Discards
\

```{r, echo=FALSE, results='asis'}
general_wd = file.path(doc_dir, "shared_text")
filein = file.path(general_wd,'2f_recreational_removals.Rmd')
read_child(filein)
```

#### Fishery Dependent Indices of Abundance
\

Appendix Section \ref{mrfss-cpfv-index}

Appendix Section \ref{onboard-cpfv-index}

Appendix Section \ref{dwv-cpfv-index}

Appendix Section \ref{crfs-pr-index}

#### Composition Data

Length compositions were available from the following sources: 

* Recreational party/charter mode (CPFV/PC)

  + Miller and Goshall dockside survey (1959-1961, 1966)
  + Don Pearson onboard PC survey (1978-1984)
  + MRFSS CPFV/PC dockside survey (1980-1989, 1993-2003)
  + CRFS CPFV/PC onboard dockside survey (2004-2022)
  + Deb Wilson-Vandenberg onboard CPFV survey (1988-1998)

* Recreational private/rental mode (PR)

  + Miller and Gotshall dockside PR survey (1959)
  + MRFSS dockside PR survey (1980-1989, 1993-2003)
  + CRFS dockside PR survey (2004-2022)
  
  
The number of available fish and unique trips by year and fleet are in Tables \ref{tab:rec-len-samps}. MRFSS historical biological data were downloaded from RecFIN website in December 2022. CRFS biological data were also downloaded from RecFIN on February 18, 2023. The Miller and Goshall, Don Person, Deb-Wilson Vandenberg recreational survey data were downloaded from the SWFSC databases in February 2023. 

Between 1987 - 1989 and 1993-1998 there were recreational length data for the CPFV fleet from both MRFSS and Deb Wilson-Vandenberg data sets. During data exploration it was determined that the lengths in MRFSS from 1997 and 1998 were also included in the Deb Wilson-Vandenberg indicating that these data sources were duplicative for these years but also potentially other years where they overlapped. In order to avoid double using of data, the length data from MRFSS which had far fewered length samples for the overlapping years with Deb Wilson-Vandenberg for the CPFV fleet were removed from the data used within the model (see [Appendix A](#excluded-data) for implied fits to these lengths).

The majority of length samples for both recreational fleets, CPFV and PR, were unsexed. A wide range of sampled lengths from the recreational CPFV fleet were observed across all years with lengths generally ranging between 25 - 45 cm except for the late 1970s and early 1980s where a higher proportion of larger fish were sampled (Figure \ref{fig:rec-cpfv-len-data}). The mean length of lengths observed in the recreational CPFV fleet since approximately 1990s is relatively stable varying between 35 - 40 cm in length with high variability within the data in the early years (Figure \ref{fig:mean-rec-cpfv-len-data}). The range of lengths sampled from the recreational PR fleet are similar to those from the CPFV fleet with lengths in recent years ranging between 25 - 45 cm with slightly larger proportion of larger fish observed in the 1980s (Figures \ref{fig:rec-pr-len-data} and \ref{fig:mean-rec-pr-len-data}). 

Age composition data were available for select years from both the recreational CPFV and PR fleets. Historical age data collected from the CPFV fishery were available from this fleet from  1978, 1981, and 1984. The majority of these fish were sexed (only 4 total unsexed ages from 1978 and 1984) with an average age ranging from 10 to 14 across these years (Figures \ref{fig:rec-cpfv-age-data} and \ref{fig:mean-rec-cpfv-ag-data}). The historical age data from this fleet were input as marginal ages. There were a total of 250 age samples from the final model year, 2022, collected by a cooperative sampling program with the fleet coordinated by the SWFSC (Figures \ref{fig:rec-cpfv-caal-data} and ADD MARGINAL FIGURE). These data were collected by three CPFV vessels that operate north of Point Conception following random sampling protocols. The cooperative ages were compared to all the CPFV lengths collected by the CRFS sampling program to ensure that the sampling was representative of the fishery (Figure \ref{fig:coop-len-comparison} North). These ages were incorporated as either marginal or conditional age-at-length data depending upon how fish length were measured: carcass or whole fish. The carcass lengthed fish were included as marginals in order to avoid any potential measurement bias in the use of these ages. Finally, a total of 139 ages were collected from the PR fleet in 2022 (Figure \ref{fig: rec-pr-caal-data}). These data were used in the model as conditional age-at-length data as well.  

The approach to determine the number of unique trips by data source varied. Some data sources had unique trip numbers within the data (Don Pearson, Deb Wilson Vandenberg). Other data sources that lacked clear trip identifier applied a similar methodology as developed by Brian Soper that combines multiple fields of information to attempt to estimate trips sampled. The number of trips for MRFSS data was estimated using the year, wave, ID code, sampling site (INSITE), area, and mode. A similar methodology was done for CRFS  and Miller and Gotshall data that used data, county, water area, interview site, and mode. 

<!--chapter:end:21f-.Rmd-->

## Fishery-Independent Data

<!--chapter:end:21s-.Rmd-->

### California Cooperative Fisheries Research Program Survey

#### Index of Abundance
\

Since 2007, the \gls{s-ccfrp} has monitored several areas in California to evaluate the performance of \glspl{mpa} and understand nearshore fish populations [@starr_variation_2015; @wendt_collaborative_2009]. In 2017, the survey expanded beyond the four \Gls{mpa}s in central California (A&ntilde;o Nuevo, Point Lobos, Point Buchon, and Piedras Blancas) to include the entire California coast.
Fish are collected by volunteer anglers aboard \glspl{cpfv} guided by one of the following academic institutions based on proximity to fishing location: Humboldt State University; Bodega Marine Laboratories; Moss Landing Marine Laboratories; Cal Poly San Luis Obispo; University of California, Santa Barbara; and Scripps Institution of Oceanography.

Surveys consist of fishing with hook-and-line gear for 30-45 minutes within randomly chosen 500 by 500 m grid cells within and outside \glspl{mpa}. Prior to 2017, all fish were measured for length and release or descended to depth; since then, some were sampled for otoliths and fin clips.

Appendix Section \ref{ccfrp-index}

#### Composition Data

<!--chapter:end:21s-ccfrp.Rmd-->

### California Department of Fish and Wildlife Remotely Operated Vehicle Survey

#### Index of Abundance 
\

The California Department of Fish and Wildlife (CDFW) in collaboration with Marine Applied Research and Exploration (MARE) have been conducting remotely operated vehicle (ROV) surveys along the California coast in Marine Protected Areas (MPAs) and reference sites adjacent to them since 2004 for the purposes of long-term monitoring of changes in size, density (fish/square meter) and length of fish and invertebrate species along the California coast. Surveys of the entire coast have now been undertaken twice, each taking three years to complete, 2014-2016 and again in 2019-2021. The survey conducted multiple 500 meter transects across rocky reef survey sites. Sample sites were selected by first randomly selecting the deepest transect at a given site, then selecting transects on a constant interval into shallower depths. Transects were designed to be oriented parallel to general depth contours, though they were carried out using a fixed bearing that crossed depths in some cases.

The data were explored using a super year approach where the central years, 2015 and 2020, were designated as the super year and the data were split north and south of Point Conception. The effort of the survey were split roughly equally between sites that were within MPAs or areas open to fishing (referred to as "Reference") with sampling across most sites (termed "MPA group") within each super year. The number of transects and the number of `r spp` by site and super year are shown in Table \ref{tab:rov-obs} with the number of observations across all years by location shown in Figure \ref{fig:rov-obs-loc}.  The trend in the calculated catch-per-unit-effort based on the data alone was highly variable across sampling locations and by MPA or Reference area (Figure \ref{fig:rov-raw-cpue}).   

CDFW provided an initial analysis of the CDFW ROV survey data which helped form the considered modeling approaches for these data. The final selected model was assumed a negative binomial error structure with covariates for super year, site designation (MPA or Reference), and super year site designation interaction. The estimated index of abundance based on the proportion of hard substrate either in MPA (20 percent) or Reference (80 percent) areas in California `r area`. The weighted index of abundance increases between the two super years 2015 and 2020 (Figure \ref{fig:rov-index-main}). Details regarding the index of abundance, sample sizes, and model selection can be found in the Appendix Section \ref{cdfw-rov-index}.

#### Composition Data


CDFW provided annual fish length measurement made from images taken with stereo-cameras in 2016, 2019, 2020, and 2021 (Figure \ref{fig:rov-len}). The corresponding length data were weighted by MPA/Reference area and were grouped by super year (Figure \ref{fig:rov-len-data}). The input sample size was set equal to the weighted number of unique transects `r area`.  

<!--chapter:end:21s-rov.Rmd-->

### Growth Data {#growth-data}

A significant amount of additional length-at-age not associated with fishery fleets or surveys incorporated in the model were available for `r spp`. These independent age data collection efforts from four programs `r area` since 2001: 227 otoliths collected by the NWFSC WCGBT survey, 430 otoliths collected by a research survey conducted by Don Pearson, 45 otoliths from CDFW special collections, and 77 otoliths collected by Abrams research program, and  (Table \ref{tab:growth-age-samps}). The ages collected by these three sources were included in the model as a "growth" fleet that was not associated with removals or an index of abundance. These collection had a wide distribution of length and ages observed (Figures \ref{fig:growth-len-dist} and \ref{fig:growth-age-dist}).

<!--chapter:end:21s-ygrowth.Rmd-->

## Additional Considered Data Sources

### Northwest Fisheries Science Center West Coast Groundfish Bottom Trawl Survey

The \Gls{s-wcgbt} is based on a random-grid design; covering the coastal waters from a depth of 55-1,280 m [@bradburn_2003_2011]. This design generally uses four industry-chartered vessels per year assigned to a roughly equal number of randomly selected grid cells and divided into two 'passes' of the coast. Two vessels fish from north to south during each pass between late May to early October. This design therefore incorporates both vessel-to-vessel differences in catchability, as well as variance associated with selecting a relatively small number (approximately 700) of possible cells from a very large set of possible cells spread from the Mexican to the Canadian borders.

<!--chapter:end:21s-zsurveys_not_included.Rmd-->

## Biological Data

### Natural Mortality

```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text",'2_biology_natural_mortality.Rmd')
read_child(filein)
```


### Maturation and Fecundity


```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text",'2_biology_maturity.Rmd')
read_child(filein)
```

The 50 percent size-at-maturity was estimated at `r round(model$MGparmAdj[,"Mat50%_Fem_GP_1"][1], 1)` cm with a slope of `r round(model$MGparmAdj$Mat_slope_Fem_GP_1[1], 2)` (Figure \ref{fig:maturity}). This area-specific maturity-at-length estimate is relatively similar but with fish maturing at a slightly larger size compared to the biological maturity curve assumed for `r spp` south of Point Conception. Additionally, these values are both slightly smaller compared to estimates by Hannah [-@hannah_length_2014] for fish observed in Oregon waters (34.8 cm) which estimated the 50 percent size-at-maturity of  and slope of -0.60.

```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text",'2_biology_fecundity.Rmd')
read_child(filein)
```


### Sex Ratio

```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text",'2_biology_sex_ratio.Rmd')
read_child(filein)
```


### Length-Weight Relationship

```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text",'2_biology_weight_length.Rmd')
read_child(filein)
```


### Growth (Length-at-Age) {#length-at-age}

Length-at-age was estimated for male and female `r spp` informed by age data from the fisheries, the CCFRP survey, and independent age data collected effort from three programs `area` since 2002: 207 otoliths collected by the NWFSC WCGBT survey, 426 otoliths collected by a research survey conducted by Don Pearson, 74 from a research survey conducted by Abrams, 45 from CDFW special collections, and 210 otoliths collected by a cooperative research survey by the SWFSC and CPFV funded by the Sportfishing Association of California (Table \ref{tab:growth-age-samps}). The ages collected by these three sources were included in the model as a "growth" fleet that was not associated with removals or an index of abundance. 

Sex-specific growth parameters `area` were initially estimated external to the model at the following values:

\begin{centering}

Females $L_{\infty}$ = 48.5 cm; $L_1$ = 9.1 cm; $k$ = 0.174 per year

Males $L_{\infty}$ = 46.8 cm; $L_1$ = 5.3 cm; $k$ = 0.207 per year

\end{centering}

\vspace{0.50cm}

These values were used as starting parameter values within the base model prior to estimating each parameter for male and female `r spp`.

### Ageing Precision and Bias

```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text",'2_biology_ageing_error.Rmd')
read_child(filein)
```

<!--chapter:end:22biology.Rmd-->

## Environmental and Ecosystem Data

<!--chapter:end:23enviro.Rmd-->

# Assessment Model


<!--chapter:end:30model.Rmd-->

## Summary of Previous Assessments and Reviews


### History of Modeling Approaches 

```{r, echo=FALSE, results='asis'}

filein = file.path(doc_dir, "shared_text", '31_summary_previous_assessments.Rmd')
read_child(filein)
```


### Most Recent STAR Panel and SSC Recommendations


```{r, echo=FALSE, results='asis'}

filein = file.path(doc_dir, "shared_text", '31_ssc_summary.Rmd')
read_child(filein)
```



### Response to Groundfish Subcommittee Requests

To be completed post-STAR panel.

<!--chapter:end:31summary.Rmd-->

## Model Structure and Assumptions


### Model Changes from the Last Assessment 



### Modeling Platform and Structure

The assessment was conducted used Stock Synthesis version 3.30.20 developed by Dr. Richard Methot at the NOAA, NWFSC [@methot_stock_2013]. This most recent version was used because it included improvements and corrections to older model versions.  The previous assessment of `r spp` also used Stock Synthesis but an earlier version, 3..30.16; model bridging was performed between both versions of Stock Synthesis and discussed below.  The R package [r4ss](https://github.com/r4ss/r4ss), version 1.38.0, along with R version 4.0.1 were used to investigate and plot model fits. 

### Model Selection and Evaluation

The base assessment model for `r spp` was developed to balance parsimony and realism, and the goal was to estimate a spawning output trajectory for the population of `r spp` off the west coast of the U.S. The model contains many assumptions to achieve parsimony and uses many different sources of data to estimate reality. A series of investigative model runs were done to achieve the final base model.

### Bridging Analysis

The exploration of models began by bridging from the 2021 data-moderate assessment to Stock Synthesis version 3.30.20, which produced the same estimates for spawning biomass and depletion across the time series (Figures \ref{fig:bridge-ssb} and \ref{fig:bridge-depl}). 


### Key Assumptions and Structural Choices


### Priors

```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text",'31_model_priors.Rmd')
read_child(filein)
```


### Data Weighting



### Model Parameters
Describe estimated vs. fixed parameters, priors

<!--chapter:end:32structure.Rmd-->

## Base Model Results


### Parameter Estimates

### Fits to the Data

### Population Trajectory

### Reference Points



<!--chapter:end:33results.Rmd-->

## Model Diagnostics
Describe all diagnostics

### Convergence

### Sensitivity Analyses

### Retrospective Analysis

### Likelihood Profiles

### Unresolved Problems and Major Uncertainties

<!--chapter:end:34diagnostics.Rmd-->

# Management 

## Reference Points

## Unresolved Problems and Major Uncertainties

## Harvest Projections and Decision Tables

## Evaluation of Scientific Uncertainty

## Research and Data Needs

<!--chapter:end:40management.Rmd-->

# Acknowledgments
Here are all the mad props!

<!--chapter:end:41acknowledgments.Rmd-->

\clearpage

# References
<!-- If you want to references to appear somewhere before the end, add: -->
<div id="refs"></div>
<!-- where you want it to appear -->
<!-- The following sets the appropriate indentation for the references
  but it cannot be used with bookdown and the make file because it leads
  to a bad pdf.
\noindent
\vspace{-2em}
\setlength{\parindent}{-0.2in}
\setlength{\leftskip}{0.2in}
\setlength{\parskip}{8pt}
 -->

<!--chapter:end:49bibliography.Rmd-->

\clearpage
# Tables

<!-- ======================================================= -->
<!-- ***************    Catches      *********************** --> 
<!-- ======================================================= -->

```{r, results = 'asis'}

years = startyr:endyr
nfleets = 4
dead_all = NULL

for (i in 1:nfleets){
  name = paste0("dead(B):_",i)
  dead = model$timeseries[model$timeseries$Yr %in% years, name]
  dead_all = cbind(dead_all, dead)
}
total.dead  <- round(apply(dead_all, 1, sum), 1)
out = cbind(years, round(dead_all, 1), total.dead)
out = as.data.frame(out)
col_names = c("Year", "Commercial (Dead)", "Commercial (Live)", "Rec. CPFV", "Rec. PR", "Total Landings")

table_format(x = out,
             caption = "Removals (mt) by fleet and the summed total landings (mt).",
             label = "allcatches",
             digits = 1,
             align = 'l',
             col_names = col_names)
```

\newpage

<!-- ======================================================= --> 
<!-- *********** Removals vs. OFL/ACL   ******************** --> 
<!-- ======================================================= --> 

```{r, results = 'asis'}

create_management_table(
  management_dir = management_dir, 
  doc_dir = doc_dir, 
  doc_names = c("nca", 'sca'),
  years = 2012:2022,
  table_names = c("copper_ca_north.csv", "copper_ca_south.csv"),
  prefix = NULL)

```

<!-- ======================================================= -->
<!-- *************** Com. Catch Ratio  ********************* --> 
<!-- ======================================================= -->

\include{tex_tables/historical_landings_tables_2020_revised_Avila_1953.tex}

\newpage


<!-- ======================================================= -->
<!-- ***************   Discard Data  *********************** --> 
<!-- ======================================================= -->


<!-- ======================================================= -->
<!-- *************** Commercial Data *********************** --> 
<!-- ======================================================= -->

\include{tex_tables/north_dead_trips_and_samples.tex}

\include{tex_tables/north_live_trips_and_samples.tex}

<!-- ======================================================= -->
<!-- ************* Recreational Data *********************** --> 
<!-- ======================================================= -->

\include{tex_tables/rec_north_sample_size_by_program.tex}

<!-- ======================================================= -->
<!-- ***************   Survey  Data  *********************** --> 
<!-- ======================================================= -->


<!-- ======================================================= -->
<!-- ***************   Survey  Data  *********************** --> 
<!-- ======================================================= -->

\include{tex_tables/north_growth_age_samples.tex}

<!-- ======================================================= -->
<!-- ***********   Model Structure      ******************** --> 
<!-- ======================================================= -->


<!-- ======================================================= -->
<!-- ***********   Model Parameters     ******************** --> 
<!-- ======================================================= -->


```{r, results = 'asis'}
mod_params = model$parameters[, 
                                (names(model$parameters) %in%
                                c("Num","Label","Value","Phase","Min",
                                  "Max","Status","Parm_StDev",
                                  "Pr_type","Prior","Pr_SD"))] 
mod_params[,'Value'] = round(as.numeric(mod_params[,'Value']),3)                                 
# Combine bounds into one column
mod_params$Min = paste('(', mod_params$Min, ', ', mod_params$Max, ')', sep='')
# Combine prior info to one column
mod_params$PR_type = ifelse(mod_params$Pr_type == 'No_prior' , 'None', paste(mod_params$Pr_type,' (', mod_params$Prior,  ', ', mod_params$Pr_SD, ')', sep = ''))
# Set long value to scientific notation
mod_params[mod_params$Label == "Wtlen_1_Fem",3] = format(mod_params[mod_params$Label == "Wtlen_1_Fem",3], scientific = TRUE)
mod_params[mod_params$Label == "Wtlen_1_Mal",3] = format(as.numeric(mod_params[mod_params$Label == "Wtlen_1_Mal",3]), scientific = TRUE)
mod_params[mod_params$Label == "Eggs_scalar_Fem",3] = format(as.numeric(mod_params[mod_params$Label == "Eggs_scalar_Fem",3]), scientific = TRUE)
mod_params[mod_params$Label == "L_at_Amax_Mal_GP_1",3] = round(as.numeric(mod_params[mod_params$Label == "L_at_Amax_Mal_GP_1",3]), 4)
mod_params[mod_params$Label == "VonBert_K_Mal_GP_1",3] = round(as.numeric(mod_params[mod_params$Label == "VonBert_K_Mal_GP_1",3]), 3)
mod_params[mod_params$Label == "CV_old_Mal_GP_1",3] = round(as.numeric(mod_params[mod_params$Label == "CV_old_Mal_GP_1",3]), 3)
# Remove the max, prior and prior sd columns
drops = c('Max', 'Prior', 'Pr_type', 'Pr_SD', 'Num')
mod_params = mod_params[, !(names(mod_params) %in% drops)]
rownames(mod_params) = c()
mod_params[,"Label"] = gsub("\\_", " ", mod_params[,"Label"])
mod_params[,"PR_type"] = gsub("\\_", " ", mod_params[,"PR_type"])
# Add column names
col_names = c('Parameter',
                         'Value',
                         'Phase',
                         'Bounds',
                         'Status',
                         'SD',
                         'Prior (Exp.Val, SD)')
table_format(x = mod_params,
             caption = "List of parameters used in the base model, including estimated values and standard deviations (SD), bounds (minimum and maximum), estimation phase (negative values not estimated), status (indicates if parameters are near bounds), and prior type information (mean and SD).",
             label = "params",
             align = 'l',
             col_names = col_names,
             longtable = TRUE,
             font_size = 9,
             landscape = TRUE,
             custom_width = TRUE,
             col_to_adjust = c(1,7), 
             width = c("7cm", "4cm"))                         
```

<!-- ======================================================= -->
<!-- ***********    Like Contributions  ******************** --> 
<!-- ======================================================= -->

\include{tex_tables/likelihoods.tex}

<!-- ======================================================= -->
<!-- ********  Reference Points & Management *************** --> 
<!-- ======================================================= -->

\include{tex_tables/e_ReferencePoints.tex}

\newpage


```{r, results = 'asis'}

create_projection_table(
    management_dir = management_dir, 
    doc_dir = doc_dir, 
    fixed_removals = c(70, 70),
    doc_names = c("nca", 'sca'),
    years = 2023:2034,
    table_names = c("copper_ca_north.csv", "copper_ca_south.csv"),
    prefix = NULL)

```

<!-- ======================================================= -->
<!-- ***********       Time Series      ******************** --> 
<!-- ======================================================= -->

\include{tex_tables/TimeSeries.tex}

\newpage


```{r, results = 'asis'}
create_biomass_table(
    doc_dir = doc_dir, 
    prefix = NULL,
    doc_names = c("nca", 'sca'),
    years = 2013:2023)

```


<!-- ======================================================= -->
<!-- ****************     Sensitivities      *************** --> 
<!-- ======================================================= -->



<!-- ======================================================= -->
<!-- ********  Reference Points & Management *************** --> 
<!-- ======================================================= -->

<!--chapter:end:52tables.Rmd-->

\clearpage
# Figures

<!-- ====================================================================== --> 
<!-- *******************    Assessment Map      *************************** --> 
<!-- ====================================================================== --> 

```{r, results = 'asis'}
add_figure(
filein = file.path(doc_dir, "shared_figures", "map.png"), 
caption = "Map of management area and the 2023 assessments areas for copper rockfish",
label = 'ca-map')
```


<!-- ====================================================================== -->  
<!-- ****************** Catches Used in the Model ************************* --> 
<!-- ====================================================================== -->  

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "catch2 landings stacked.png"), 
caption = "Landings by fleet used in the base model where catches in metric tons by fleet are stacked",
label = 'catch')
```	

<!-- ====================================================================== --> 
<!-- ******************* Data Used in the Model *************************** --> 
<!-- ====================================================================== --> 

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "data_plot.png"), 
caption = "Summary of data sources used in the base model",
label = 'data-plot')
```	

<!-- ======================================================= -->
<!-- *************** Commercial Data *********************** --> 
<!-- ======================================================= -->

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lendat_bubflt1mkt0_page2.png"), 
caption = "Length composition data from the commercial dead fleet",
label = 'com-dead-len-data')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lendat_data_weighting_TA1.8_Commercial_Dead.png"), 
caption = "Mean length for commercial dead fleet with 95 percent confidence intervals",
label = 'mean-com-dead-len-data')
```



```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lendat_bubflt2mkt0_page2.png"), 
caption = "Length composition data from the commercial live fleet",
label = 'com-live-len-data')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lendat_data_weighting_TA1.8_Commercial_Live.png"), 
caption = "Mean length for commercial live fleet with 95 percent confidence intervals",
label = 'mean-com-live-len-data')
```



<!-- ======================================================= -->
<!-- ************* Recreational Data *********************** --> 
<!-- ======================================================= -->

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lendat_bubflt3mkt0_page2.png"), 
caption = "Length composition data from the recreational CPFV fleet",
label = 'rec-cpfv-len-data')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lendat_data_weighting_TA1.8_Rec_CPFV.png"), 
caption = "Mean length for recreational CPFV fleet with 95 percent confidence intervals",
label = 'mean-rec-cpfv-len-data')
```


```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_agedat__multi-fleet_comparison.png"), 
caption = "Age composition data from the recreational CPFV fleet",
label = 'rec-cpfv-age-data')
```


```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_agedat_data_weighting_TA1.8_Rec_CPFV.png"), 
caption = "Mean age for recreational CPFV fleet with 95 percent confidence intervals",
label = 'mean-rec-cpfv-age-data')
```


```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_condAALdat_bubflt3mkt0.png"), 
caption = "Conditional age-at-length data for recreational CPFV collected in 2022",
label = 'rec-cpfv-caal-data')
```


```{r, results = 'asis'}
add_figure(
filein = file.path(data_dir, "ages", "plots", "coop_crfs_length_comparison.png"), 
caption = "Comparison of all length collected by the CRFS sampling program for the CPFV fleet to the lengths from the fish with ages from the cooperative sampling program. The length distributions in the area north of Point Conception are in general agreement while the distribution of lengths collected by this program does not align with the length samples from CRFS.",
label = 'coop-len-comparison')
```


```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_condAALdat_bubflt4mkt0.png"), 
caption = "Conditional age-at-length data for recreational PR collected in 2022",
label = 'rec-pr-caal-data')
```


```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lendat_flt4mkt0_page2.png"), 
caption = "Length composition data from the recreational PR fleet",
label = 'rec-pr-len-data')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lendat_data_weighting_TA1.8_Rec_PR.png"), 
caption = "Mean length for recreational PR fleet with 95 percent confidence intervals",
label = 'mean-rec-pr-len-data')
```




<!-- ======================================================= -->
<!-- ***************     CCFRP           ******************* --> 
<!-- ======================================================= -->


<!-- ======================================================= -->
<!-- ***************    CDFW ROV         ******************* --> 
<!-- ======================================================= -->


```{r, results = 'asis'}
sa4ss::add_figure(
filein = file.path(data_dir, "survey_indices", "rov", "plots", "rov_transect_collapsed_copper_north_protection_count.png"), 
caption = "The location and size of observations across all years and transects.",
label = 'rov-obs-loc')
```



```{r, results = 'asis'}
sa4ss::add_figure(
filein = file.path(data_dir, "survey_indices", "rov", "plots", "north_raw_cpue_by_mpa_group.png"), 
caption = "The trend of the calculated CPUE by each MPA and Reference group.",
label = 'rov-raw-cpue')
```


```{r, results = 'asis'}
sa4ss::add_figure(
filein = file.path(data_dir, "survey_indices", "rov", "glm_negbin_north_designation_depth", "Index.png"), 
caption = "The estimated weighted relative index of abundance.",
label = 'rov-index-main')
```


```{r, results = 'asis'}
sa4ss::add_figure(
filein = file.path(data_dir, "survey_indices", "rov", "plots", "rov_length_by_area_designation.png"), 
caption = "The distribution of lengths across all years for MPA and Reference area north and south of Point Conception.",
label = 'rov-len')
```


```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lendat_flt6mkt0.png"), 
caption = "Length composition data from the CDFW ROV survey",
label = 'rov-len-data')
```


```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lendat_data_weighting_TA1.8_CDFW_ROV.png"), 
caption = "Mean length for CDWF ROV survey with 95 percent confidence intervals",
label = 'mean-rec-pr-len-data')
```


<!-- ======================================================= -->
<!-- ***************  NWFSC WCGBT Survey  ****************** --> 
<!-- ======================================================= -->




<!-- ======================================================= -->  
<!-- ******************   Biology  ************************* --> 
<!-- ======================================================= -->  



```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "bio6_maturity.png"), 
caption = "Maturity as a function of length",
label = 'maturity')
```


```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "bio9_fecundity_len.png"), 
caption = "Fecundity as a function of length",
label = 'fecundity')
```


```{r, results = 'asis'}
add_figure(
filein = file.path(data_dir, "biology", "plots", "Length_Weight_All.png"), 
caption = "Estimated weight-at-length",
label = 'weight-length')
```



```{r, results = 'asis'}
add_figure(
filein = file.path(data_dir, "ages", "ageing_error", "B0_S3", "Reader_1_vs_Reader_2.png"), 
caption = "Distribution of double reads between age reader 1 and 2.",
label = 'age-error-dist')
```



```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots",  "numbers5_ageerrorSD.png"), 
caption = "Ageing imprecision standard deviation of observed age in years.",
label = 'age-error')
```



```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots",  "numbers10_ageerror_matrix_1.png"), 
caption = "Distribution of observed age at true age for ageing error type 1.",
label = 'age-error-matrix')
```




<!-- ======================================================= -->  
<!-- ******************   Bridge   ************************* --> 
<!-- ======================================================= -->



```{r, results = 'asis'}
add_figure(
filein = file.path(bridge_dir, "_plots", "0_model_convert_compare2_spawnbio_uncertainty.png"),
caption = "Model version bridge comparison of estimated spawning output",
label = 'bridge-ssb')
```

```{r, results = 'asis'}

add_figure(
filein = file.path(bridge_dir, "_plots", "0_model_convert_compare4_Bratio_uncertainty.png"),
caption = "Model version bridge comparison of estimated fraction unfished",
label = 'bridge-depl')
```


```{r, results = 'asis'}
add_figure(
filein = file.path(bridge_dir, "_plots", "full_bridge_compare2_spawnbio_uncertainty.png"),
caption = "Model structure and data bridging comparison of estimated spawning output",
label = 'data-bridge-ssb')
```

```{r, results = 'asis'}

add_figure(
filein = file.path(bridge_dir, "_plots", "full_bridge_compare4_Bratio_uncertainty.png"),
caption = "Model structure and data bridging comparison of estimated fraction unfished",
label = 'data-bridge-depl')
```



<!-- ====================================================================== -->
<!-- *********************    Priors            ********************** --> 
<!-- ====================================================================== -->

<!-- ====================================================================== -->
<!-- *********************  Model Est. Biology       ********************** --> 
<!-- ====================================================================== -->

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "bio1_sizeatage.png"),
caption = "Model estimated length-at-age in the beginning of the year. Shaded area indicates 95 percent distribution of length-at-age around the estimated growth curve",
label = 'mod-est-len-age')
```

<!-- ====================================================================== -->
<!-- *********************    Selectivity            ********************** --> 
<!-- ====================================================================== -->




<!-- ======================================================= -->  
<!-- ****************** Recruitment ************************ --> 
<!-- ======================================================= -->


```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "ts11_Age-0_recruits_(1000s)_with_95_asymptotic_intervals.png"), 
caption = "Estimated time series of age-0 recruits (1000s)",
label = 'recruits')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "recdevs2_withbars.png"), 
caption = "Estimated time series of recruitment deviations",
label = 'rec-devs')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "SR_curve.png"), 
caption = "Stock-recruit curve. Point colors indicate year, with warmer colors indicating earlier years and cooler colors in showing later years",
label = 'bh-curve')
```



<!-- ====================================================================== -->
<!-- *************** Fit to the Length & Age Data  ************************ --> 
<!-- ====================================================================== -->




<!-- ====================================================================== -->
<!-- ****************** Fit to the Index Data  **************************** --> 
<!-- ====================================================================== -->


```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "index5_logcpuefit_Rec_CPFV.png"), 
caption = "Fit to log index data on log scale for recreational (MRFSS) CPFV. Lines indicate 95% uncertainty interval around index values based on the model assumption of lognormal error. Thicker lines (if present) indicate input uncertainty before addition of estimated additional uncertainty parameter",
label = 'mrfss-cpfv-index-fit')
```




```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "index5_logcpuefit_DWV_CPFV.png"), 
caption = "Fit to log index data on log scale for Deb Wilson-Vandenberg CPFV survey. Lines indicate 95% uncertainty interval around index values based on the model assumption of lognormal error. Thicker lines (if present) indicate input uncertainty before addition of estimated additional uncertainty parameter",
label = 'dwv-cpfv-index-fit')
```




```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "index5_logcpuefit_CRFS_CPFV.png"), 
caption = "Fit to log index data on log scale for CRFS CPFV survey. Lines indicate 95% uncertainty interval around index values based on the model assumption of lognormal error. Thicker lines (if present) indicate input uncertainty before addition of estimated additional uncertainty parameter",
label = 'crfs-cpfv-index-fit')
```


```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "index5_logcpuefit_Rec_PR.png"), 
caption = "Fit to log index data on log scale for recreational (CRFS) PR. Lines indicate 95% uncertainty interval around index values based on the model assumption of lognormal error. Thicker lines (if present) indicate input uncertainty before addition of estimated additional uncertainty parameter",
label = 'crfs-pr-index-fit')
```




```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "index5_logcpuefit_CCFRP.png"), 
caption = "Fit to log index data on log scale for CCFRP survey. Lines indicate 95% uncertainty interval around index values based on the model assumption of lognormal error. Thicker lines (if present) indicate input uncertainty before addition of estimated additional uncertainty parameter",
label = 'ccfrp-index-fit')
```



```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "index5_logcpuefit_CDFW_ROV.png"), 
caption = "Fit to log index data on log scale for CDFW ROV survey. Lines indicate 95% uncertainty interval around index values based on the model assumption of lognormal error. Thicker lines (if present) indicate input uncertainty before addition of estimated additional uncertainty parameter",
label = 'rov-index-fit')
```


```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "index9_standcpueall.png"), 
caption = "Standardized indices overlaid. Each index is rescaled to have mean observation = 1.0.",
label = 'standardized-indices')
```


<!-- ======================================================= -->  
<!-- ****************** Time Series ************************ --> 
<!-- ======================================================= -->


```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "ts7_Spawning_output_with_95_asymptotic_intervals_intervals.png"), 
caption = "Estimated time series of spawning biomass",
label = 'ssb')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "ts1_Total_biomass_(mt).png"), 
caption = "Estimated time series of total biomass",
label = 'tot-bio')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "ts9_Relative_spawning_output_intervals.png"), 
caption = "Estimated time series of fraction of unfished spawning biomass",
label = 'depl')
```


<!-- ====================================================================== -->
<!-- ******************    Reference Points    **************************** --> 
<!-- ====================================================================== -->


```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "SPR2_minusSPRseries.png"), 
caption = "Estimated 1 - relative spawning ratio (SPR) by year",
label = '1-spr')
```

\clearpage

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "SPR4_phase.png"), 
caption = "Phase plot of the relative biomass (also referred to as fraction unfished) versus the SPR ratio where each point represents the biomass ratio at the start of the year and the relative fishing intensity in that same year. Lines through the final point show the 95 percent intervals based on the asymptotic uncertainty for each dimension. The shaded ellipse is a 95 percent region which accounts for the estimated correlations between the biomass ratio and SPR ratio",
label = 'phase')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "yield2_yield_curve_with_refpoints.png"), 
caption = "Equilibrium yield curve for the base case model. Values are based on the 2022
fishery selectivities and with steepness fixed at 0.72",
label = 'yield')
```

<!--chapter:end:53figures.Rmd-->

# Appendix A {#detailed-fit-comps}

## Detailed Fit to Length Composition Data {#length-data}

```{r, results='asis'}
plot_info = read.csv(file.path(model_dir, "plots", "plotinfotable_for_doc.csv"))
len_fit = plot_info[which(plot_info$category == "LenComp"), ]
plot.vec = grep("comp_lenfit_flt", len_fit$label)
filein = file.path(model_dir, "plots")
for (a in plot.vec){
	cap = len_fit$caption[a]
	lab = len_fit$label[a]
	add_figure(filein = file.path(filein, len_fit$file[a]), 
			   caption = cap, 
			   label = lab)
}
```

\newpage

## Detailed Fit to Age Composition Data {#age-data}


```{r, results='asis'}
# plot_info = read.csv(file.path(model_dir, "plots", "plotinfotable_for_doc.csv"))
# len_fit = plot_info[which(plot_info$category == "AgeComp"), ]
# plot.vec = grep("comp_agefit_flt", len_fit$label)
# filein = file.path(model_dir, "plots")
# for (a in plot.vec){
# 	cap = len_fit$caption[a]
# 	lab = len_fit$label[a]
# 	add_figure(filein = file.path(filein, len_fit$file[a]), 
# 			   caption = cap, 
# 			   label = lab)
# }
```

\newpage



## Detailed Fit to Conditional-Age-at-Length Composition Data {#caal-data}


```{r, results='asis'}
plot_info = read.csv(file.path(model_dir, "plots", "plotinfotable_for_doc.csv"))
len_fit = plot_info[which(plot_info$category == "A@LComp"), ]
plot.vec = c(grep("comp_condAALfit_residsflt5mkt0", len_fit$label),
  grep("comp_condAALfit_residsflt7mkt0", len_fit$label),
	grep("comp_condAALfit_residsflt9mkt0", len_fit$label))
find = sort(len_fit$label[plot.vec], index.return = TRUE)$ix
plot.vec = plot.vec[find[2:length(find)]]
filein = file.path(model_dir, "plots")
for (a in plot.vec){
	cap = len_fit$caption[a]
	lab = len_fit$label[a]
	add_figure(filein = file.path(filein, len_fit$file[a]), 
			   caption = cap, 
			   label = lab)
}
```



```{r, results='asis'}
plot_info = read.csv(file.path(model_dir, "plots", "plotinfotable_for_doc.csv"))
len_fit = plot_info[which(plot_info$category == "A@LComp"), ]
plot.vec = c(grep("comp_condAALfit_Andre_plotsflt1mkt0", len_fit$label),
  grep("comp_condAALfit_Andre_plotsflt5mkt0", len_fit$label),
	grep("comp_condAALfit_Andre_plotsflt9mkt0", len_fit$label))
find = sort(len_fit$label[plot.vec], index.return = TRUE)$ix
plot.vec = plot.vec[find[2:length(find)]]
filein = file.path(model_dir, "plots")
for (a in plot.vec){
	cap = len_fit$caption[a]
	lab = len_fit$label[a]
	add_figure(filein = file.path(filein, len_fit$file[a]), 
			   caption = cap, 
			   label = lab)
}

```

## Implied Fit to Excluded Length Data {#excluded-data}

The implied fits to the data not included in the base model due to low annual sample size are shown below.  

```{r, results='asis'}
plot_info = read.csv(file.path(model_dir, "plots", "plotinfotable_for_doc.csv"))
len_fit = plot_info[which(plot_info$category == "LenComp"), ]
plot.vec = c(grep("comp_gstlenfit_flt1mkt0", len_fit$label),
             grep("comp_gstlenfit_flt2mkt0", len_fit$label),
             grep("comp_gstlenfit_flt3mkt0", len_fit$label),
             grep("comp_gstlenfit_flt4mkt0", len_fit$label))
filein = file.path(model_dir, "plots")
for (a in plot.vec){
	cap = len_fit$caption[a]
	lab = len_fit$label[a]
	add_figure(filein = file.path(filein, len_fit$file[a]), 
			   caption = cap, 
			   label = lab)
}
``` 

\newpage

<!--chapter:end:60appendix_caal.Rmd-->

# Appendix B. MRFSS CPFV Dockside Index of Abundance {#mrfss-cpfv-index}

<!--chapter:end:61appendix_mrfss.Rmd-->

# Appendix C. California Onboard CPFV Index of Abundance {#onboard-cpfv-index}

<!--chapter:end:62appendix_crfs_onboard.Rmd-->

# Appendix D. Deb Wilson-Vandenberg Onboard CPFV Index of Abundance {#dwv-cpfv-index}

<!--chapter:end:63appendix_dwv_cpfv.Rmd-->

# Appendix E. CRFS PR Dockside Index of Abundance {#crfs-pr-index}

<!--chapter:end:64appendix_crfs_dockside.Rmd-->

# Appendix F. CCFRP Index of Abundance {#ccfrp-index}

<!--chapter:end:65appendix_ccfrp.Rmd-->


# Appendix G. CDFW ROV Index of Abundance {#cdfw-rov-index}


```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text",'10_appendix_rov.Rmd')
read_child(filein)
```

Minimal filtering were done to the data. Transects were removed based on four factors: 1) extreme estimates of effort (the estimated area of view below the ROV termed usable area), 2) any locations that were not sampled by both super year periods, 3) transect that were conducted crossing from MPA into reference areas, and 4) transects conducted across depths that never observed `r spp` within the survey (Table \ref{tab:rov-filtered}). Once the data were filtered the average calculated CPUE for each MPA and Reference groups were plotted to visualize the data (Table \ref{tab:rov-obs} and Figure \ref{fig:rov-raw-cpue}).

A range of alternative model structures were explored to generate an index of abundances including alternative error structures, covariates, and factors were considered when exploring how best to model these data. Based on model selection a model with super year, site designation (MPA or Reference), and super year site designation interaction was selected (Table \ref{tab:rov-model-selection}). A negative-binomial model was selected based on the distribution of the data and diagnostics (Figures \ref{fig:rov-qq} and \ref{fig:rov-prop-zero}) using sdmTMB [@anderson_sdmtmb_2022]. The model estimates were then area-weighted based on the estimated percent of habitat within MPAs based on habitat seafloor mapping data within state waters were north of Point Conception an estimate of 20% of rocky habitat within MPAs and 80% open to fishing. The weighted relative index of abundance is shown in Table \ref{tab:rov-index} and Figure \ref{fig:rov-index}.

\newpage

\input{tex_tables/rov_removed_records_north.tex}

\newpage

\input{tex_tables/north_copper_obs_designation_mpa_group_super_year.tex}

\newpage



```{r, results = 'asis'}

tab <- read.csv(file.path(data_dir, "survey_indices", "rov", "forSS", "north_model_selection.csv"))

sa4ss::table_format(x = tab,
             caption = "Model selection for the ROV survey.",
             label = "rov-model-selection",
             align = 'l',
             longtable = TRUE,
             font_size = 7,
             landscape = TRUE)                         
```

\newpage

```{r, results = 'asis'}

ind <- read.csv(file.path(data_dir, "survey_indices", "rov", "glm_negbin_north_designation_depth", "index_forSS.csv"))
ind <- ind[, c(1,4,5)]
col_names = c("Year", "Estimate", "logSE")

sa4ss::table_format(x = ind,
             caption = "Estimated relative index of abundance for the ROV survey.",
             label = "rov-index",
             col_names = col_names)                         
```


\newpage

```{r, results = 'asis'}
sa4ss::add_figure(
filein = file.path(data_dir, "survey_indices", "rov", "glm_negbin_north_designation_depth", "qq.png"), 
caption = "QQ-plot for the ROV survey.",
label = 'rov-qq')
```

\newpage


```{r, results = 'asis'}
sa4ss::add_figure(
filein = file.path(data_dir, "survey_indices", "rov", "glm_negbin_north_designation_depth", "proportion_zero.png"), 
caption = "Predicted zeros based on the data and replicates from a Stan model.",
label = 'rov-prop-zero')
```

\newpage

```{r, results = 'asis'}
sa4ss::add_figure(
filein = file.path(data_dir, "survey_indices", "rov", "glm_negbin_north_designation_depth", "Index.png"), 
caption = "The weighted relative index of abundance.",
label = 'rov-index')
```


<!--chapter:end:67appendix_rov.Rmd-->

