---
title: "Description of model revisions to the base models for copper rockfish"
author: Chantel R. Wetzel (NWFSC), Melissa H. Monk (SWFSC), and Julia Coates (CDFW)
month: "`r format(Sys.Date(), '%B')`"
year: "`r format(Sys.Date(), '%Y')`"
output:
  bookdown::pdf_document2:
    keep_tex: true
  sa4ss::techreport_pdf:
    default
lang: en
papersize: letter
---


```{r opts, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

knitr::knit_hooks$set(plot = function(x,options) {
      base = knitr::opts_knit$get('base.url')
      if (is.null(base)) base = ''
      alt = ifelse (is.null(options$alt),"",options$alt)
      cap = ifelse (is.null(options$caption),"",options$caption)
      if (alt != ""){
        sprintf('![%s](%s%s "%s")', cap, base, x, alt)
      } else {
        sprintf('![%s](%s%s)', cap, base, x)
        }
  })
library(sa4ss)
library(r4ss)
management_dir <- "N:/Assessments/CurrentAssessments/copper_rockfish_2023/management"
south_model_dir <- "N:/Assessments/CurrentAssessments/copper_rockfish_2023/models/sca/14.3_revised_pre-star_base"
north_model_dir <- "N:/Assessments/CurrentAssessments/copper_rockfish_2023/models/nca/9.11_revised_pre-star_base"

user <- Sys.getenv("USERNAME")
if( grepl("Chantel", user) ){
  user_dir <- "C:/Assessments/2023/copper_rockfish_2023"
} else {
  # Fill in Melissa's document directory below
  user_dir <- "C:/Users/melissa.monk/Documents/GitHub/copper_rockfish_2023"
}
# Based on the user
doc_dir <- file.path(user_dir, "documents")

load(file.path(doc_dir, "nca", "00mod.Rdata"))
north_model <- model

load(file.path(doc_dir, "sca", "00mod.Rdata"))
south_model <- model

source(file.path(doc_dir, "helper_functions.R"))

years <- 1916:2034
sb1 <- south_model$derived_quants[south_model$derived_quants$Label %in% paste0("SSB_", years), "Value"]
sb2 <- north_model$derived_quants[north_model$derived_quants$Label %in% paste0("SSB_", years), "Value"]
sb0 <- south_model$derived_quants[south_model$derived_quants$Label == "SSB_Virgin", "Value"] +
  north_model$derived_quants[north_model$derived_quants$Label == "SSB_Virgin", "Value"]

sb <-  round(sb1 + sb2, 2)
depl <- round(sb / sb0, 3)
quants <- data.frame(year = years, 
                     sb = sb, 
                     depl = depl)
depl_final <- quants[quants$year == '2023', 'depl']
sb_final <- quants[quants$year == '2023', 'sb']
min_depl <- min(quants$depl)
min_depl_year <- quants[quants$depl == min_depl, 'year']

years <- 2023:2026
est_ofl <- round(south_model$derived_quants[south_model$derived_quants$Label %in% paste0("OFLCatch_", years), "Value"] +
  north_model$derived_quants[north_model$derived_quants$Label %in% paste0("OFLCatch_", years), "Value"], 2)

est_abc <- round(south_model$derived_quants[south_model$derived_quants$Label %in% paste0("ForeCatch_", years), "Value"] +
  north_model$derived_quants[north_model$derived_quants$Label %in% paste0("ForeCatch_", years), "Value"], 2)


model_recent_depl <- data.frame(year = 2011:2022, depl = model$derived_quants[model$derived_quants$Label %in% paste0("Bratio_", 2011:2022), "Value"])

```

# Overview

Since the release of the documents and the start of the STAR panel each of the sub-area models, north and south of Point Conception, for copper rockfish in California have had revisions to the model data.  Each of these changes is described below and comparisons between the model as presented in the assessment documents and the revised base models are provide below in the [Figures Section](#figures).

# Data Revisions

## CDFW ROV Survey Data

Revised data for the CDFW ROV survey were provided to the STAT late on Thursday May 18th, 2023. It was determined that the line identifications for transects were not completely unique as previously thought. A small subset of transects were identified to have disparate sampling sites combined into transects (i.e., data collected across separate transects were combined into incorrect transects). This issue was identified to have occurred in a total of 12 transects across all years and areas and when corrected resulted in 12 revised transects and 12 newly identified transects. Unfortunately, a clear summary of the transects impacted by area, year, and sites were not provided by CDFW. The number of unique transects by year north and south of Point Conception in the revised data provided were examined.  South of Point Conception there were now a total of 894 transects across all years with 2 new transects in both 2014 and 2019. North of Point Conception there were a total of 916 transects with 3 new transects in both 2016 and 2020 and 1 new transect in both 2019 and 2021. The number of transect impacted by area was relatively small and was not expected to result in a meaningful change in the estimated indices of abundance. However, when the revised data were analyzed there was a non-negligible shift in the estimated scale of the index of abundance south of Point Conception. This change in scale was surprising given the limited changes in the data described by CDFW. Upon further analysis of the data there appears to be non-trivial revisions in estimates of varying attributes (e.g., proportion substrate type, depth, effort estimated through usable transect area) for a number of transects. The number of data points where measurements varied were greater than the known number of transects with revisions. The STAT communicated these unexpected findings to CDFW on May 24th, 2023. The response provided by on May 26th indicated that the estimates of the proportion of substrate types did differ from the original values based on an alternative calculation but the differences would be expected to by trivial.      

Unfortunately, given the limited timing to properly review and analyze any potential data corrections, the STAT make the decision to remove the ROV data from both sub-area models. While the STAT only identified issues with the revised data south of Point Conception, there were overall concerns that all of the ROV data requires additional QA/QC to ensure that the data are accurate.  

## Recreational Removals in 2020 and 2021

CDFW communicated to the STAT that the 2020 and 2021 recreational catches for each sub-area appeared to be higher than expected.  The recreational catches for these years were comprised of information from three sources do to sampling impacts related to COVID-19: copper rockfish sepeciated catches within RecFIN, CDFW generated proxy estimates for months with missing catches in 2020, and estimates of Sebastes genus catches in RecFIN that should be assigned as copper rockfish catches provided by CDFW. However, there was a miscommunication between the STAT and CDFW where the catch assigned to copper rockfish from the Sebastes genus also included the speciated catches for copper rockfish within RecFIN. Hence, adding the catches for copper rockfish within RecFIN resulted in a double counting of a subset of catches. On May 25th, 2023 CDFW provided revised Sebastes genus catches that did not include other copper rockfish RecFIN catches. The revised catches for the recreational CPFV and PR fleets in 2020 and 2021 decreased from the values in the original base model. The revised catches by fleet and year are:

**South of Point Conception**\
2020: CPFV 43.42 mt and PR 19.71 mt\
2021: CPFV 32.21 mt and no revisions to the PR catches

**North of Point Conception**\
2020: CPFV 36.47 mt and PR 55.13 mt \
2021: CPFV 31.91 mt and no revisions to the PR catches

## Revised Base Models

These revisions to each sub-area base model resulted in very small changes in the model estimates.  The California estimate of fraction unfished in 2023 change to `r 100*depl_final` percent from 42.1 percent. The fraction of unfished spawning output in 2023 for the area south of Point Conception increased to `r 100*round(south_model$derived_quants[south_model$derived_quants$Label == "Bratio_2023", "Value"], 3)` percent from 13.7 percent and the area north of Point Conception decreased to `r 100*round(north_model$derived_quants[north_model$derived_quants$Label == "Bratio_2023", "Value"], 3)` percent from 53.9 percent. Comparisons of the estimated spawning output and fraction unfished for each sub-area are shown in Figures \ref{fig:south-ssb} - \ref{fig:north-depl}. Summaries of the combined California revised time series are shown in Table \ref{tab:ca-status} and new projections are shown in Table \ref{tab:ca-proj}. Time series estimates for each sub-area model are shown in Tables \ref{tab:tab-south-ts} and \ref{tab:tab-north-ts}.

\pagebreak

# Tables

## California Stock

```{r, results = 'asis'}
create_biomass_table(
    doc_dir = doc_dir, 
    prefix = NULL,
    doc_names = c("nca", 'sca'),
    years = 1916:2023)
# tab:ca-status

```

\newpage


```{r, results = 'asis'}

create_projection_table(
    management_dir = management_dir, 
    doc_dir = doc_dir, 
    model_dir = south_model_dir, 
    fixed_removals = c(91.53, 94.69),
    doc_names = c("nca", 'sca'),
    years = 2023:2034,
    table_names = c("copper_ca_north.csv", "copper_ca_south.csv"),
    prefix = NULL)

```

\newpage

## South of Point Conception


```{r, results = 'asis'}

tab <- read.csv("south_TimeSeries.csv")
col_names <- c("Year",	"Total Biomass (mt)",	"Spawning Output",	"Total Biomass 3+ (mt)",	"Fraction Unfished",	"Age-0 Recruits",	"Total Mortality (mt)",	"1-SPR", 	"Exploitation Rate")

table_format(x = tab,
             caption = "Time series of population estimates from the revised base model for the sub-area south of Point Conception.",
             label = "tab-south-ts",
             align = 'l',
             digits = 3,
             col_names = col_names)
```

\newpage

## North of Point Conception


```{r, results = 'asis'}

tab <- read.csv("north_TimeSeries.csv")
col_names <- c("Year",	"Total Biomass (mt)",	"Spawning Output",	"Total Biomass 3+ (mt)",	"Fraction Unfished",	"Age-0 Recruits",	"Total Mortality (mt)",	"1-SPR", 	"Exploitation Rate")

table_format(x = tab,
             caption = "Time series of population estimates from the revised base model for the sub-area north of Point Conception.",
             label = "tab-north-ts",
             align = 'l',
             digits = 3,
             col_names = col_names)
```

\newpage

# Figures


```{r, results = 'asis'}
add_figure(
filein = "14.3_corrected_base_compare2_spawnbio_uncertainty.png", 
caption = "Estimated spawning output comparison for the sub-area model south of Point Conception between the original base model and models that remove CDFW ROV survey data, and the model with these data removed and revised 2020-21 recreational catches. The +Corrected Rec. Catches model is the revised base model.",
label = 'south-ssb')
```

\pagebreak


```{r, results = 'asis'}
add_figure(
filein = "14.3_corrected_base_compare2_spawnbio_uncertainty.png", 
caption = "Estimated fraction unfished comparison for the sub-area model south of Point Conception between the original base model and models that remove CDFW ROV survey data, and the model with these data removed and revised 2020-21 recreational catches. The +Corrected Rec. Catches model is the revised base model.",
label = 'south-depl')
```

\pagebreak


```{r, results = 'asis'}
add_figure(
filein = "9.10_corrected_base_compare2_spawnbio_uncertainty.png", 
caption = "Estimated spawning output comparison for the sub-area model north of Point Conception between the original base model and models that remove CDFW ROV survey data, and the model with these data removed and revised 2020-21 recreational catches. The +Corrected Rec. Catches model is the revised base model.",
label = 'north-ssb')
```

\pagebreak


```{r, results = 'asis'}
add_figure(
filein = "9.10_corrected_base_compare2_spawnbio_uncertainty.png", 
caption = "Estimated fraction unfished comparison for the sub-area model north of Point Conception between the original base model and models that remove CDFW ROV survey data, and the model with these data removed and revised 2020-21 recreational catches. The +Corrected Rec. Catches model is the revised base model.",
label = 'north-depl')
```

\pagebreak

