
## Stock{-}

This assessment reports the status of `r spp` (*Sebastes caurinus*) off the California coast in U.S. waters, using data through 2022. The stock of `r spp` in California waters was assessed using two sub-area models that captured distinct inter-stock dynamics split north and south of Point Conception, \PtC. The estimated dynamics for each assessed sub-area is described here along with the combined stock status for the California stock. This assessment does not account for populations located in Mexico waters or other areas off the U.S. West Coast and assumes that these southern and northern populations do not contribute to the population being assessed here.


## Catches{-}

Catches of `r spp` off the coast of California began slowly in the 1910s with catches steadily increasing in the 1940s north of Point Conception and with catches ramping up south of Point Conception in the 1960s (Figures \ref{fig:es-south-catch} and \ref{fig:es-north-catch}). The recreational fishery in California is the primary source of mortality for `r spp` where private/rental (PR) vessels are the primary source of historical removals across the state. Catches by commercial passenger fishing vessels (CPFV) ramped up between the 1960s to the 1980s across the state.  In recent years, the recreational removals in the north of Point Conception have been split between CPFV and PR vessels. In contrast, the CPFV fleet south of Point Conception is the primary source of mortality for `r spp`. Since 2013, catches south of Point Conception peaked in 2018 and then catches sharply declining in 2022 due to the sub-bag limit of one `r spp` in response to the 2021 assessments of `r spp` (Table \ref{tab:south-removalsES}). North of Point Conception total catch has fluctuated with the lowest catches in 2013 of just over 25 mt, a peak in 2020 at greater than 150 mt, and decreased removals in 2022 due to the sub-bag limit of one `r spp` implemented in January 2022 (Table \ref{tab:north-removalsES}).

\input{tex_tables/south_a_Catches_ES.tex}

\input{tex_tables/north_a_Catches_ES.tex}


```{r, results = 'asis'}
add_figure(
filein = file.path(south_model_dir, "plots", "catch2 landings stacked.png"), 
caption = "Landings by fleet used in the base model for the area south of Point Conception where catches in metric tons by fleet are stacked",
label = 'es-south-catch')
```


```{r, results = 'asis'}
add_figure(
filein = file.path(north_model_dir, "plots", "catch2 landings stacked.png"), 
caption = "Landings by fleet used in the base model for the area north of Point Conception where catches in metric tons by fleet are stacked",
label = 'es-north-catch')
```

\pagebreak

## Data and Assessment{-}

Length-based data-moderate assessments were conducted in 2021 for `r spp` off the U.S. West Coast. The population was assessed regionally with four separate population models south and north of Point Conception in California, Oregon, and Washington. Only the stock off the coast of California is being assessed in 2023 with two sub-area models split at Point Conception (\PtC).This assessment uses Stock Synthesis 3 (version V3.30.21.0). Each assessment model is a two-sex age-structured model operating on an annual time step covering the period 1916 to 2022, a twelve-year projection, and assumes an unfished population prior to 1916. Population dynamics are modeled
for ages 0 through 50, with age-50 being the accumulator age. The model is conditioned on catch from two sectors, commercial and recreational, divided among four fleets, and is informed by both fishery-dependent and fishery-independent indices of abundance. Additionally, the sub-area models are fit to length composition data from fishery-independent and fishery-dependent sources, as well as age compositions conditioned on length. Estimated discards from the commercial and recreational fleets were estimated externally and added to landings to represent total catch. The commercial fishery is split based on the landed condition of `r spp`, live or dead. The recreational fishery is split into two fleets, a PR and the CPFV boat modes. The model also incorporates an updated length-based maturity schedule and externally estimated length-weight relationship and fecundity-at-length function. The assessment fixes values for natural mortality of females and males at the median of the prior (0.108 yr^-1^) and estimates sex-specific growth parameters. Year-class strength is estimated as deviations from a Beverton-Holt stock-recruitment relationship beginning in 1965 in the south and 1970 north of Point Conception. Steepness of the Beverton-Holt stock-recruitment relationship is fixed at the mean of the prior, 0.72.

All the data sources included in each sub-area model for `r spp` in California have been re-evaluated for these assessments, including improvements and updates in the data (and associated analyses) that were used in the previous assessments. Additionally, new data types and sources were included in these assessment compared to the 2021 assessments which included a limited scope of data types and sources. Two fishery-independent data sources were added to these assessments, the CCFRP Hook and Line and CDFW ROV surveys. The CCFRP Hook and Line survey data (indices, lengths, and ages) have been included in other nearshore assessments in the past (e.g., vermilion rockfish). In contrast, this is the first time data from the CDFW ROV survey (indices and lengths) have been explored and used directly in a West Coast nearshore assessment. These assessments also include fishery-dependent indices of abundance from the CPFV and PR fleets, north and south of Point Conception, that were not included in the 2021 assessments.  Finally, this is the first assessment to include age composition data to support estimates of growth and population dynamics within the based models.

Multiple sources of uncertainty are explicitly included in this assessment, including parameter uncertainty using prior distributions, observational uncertainty through standard deviations of survey estimates, and model uncertainty through a comprehensive sensitivity analyses to data source and model structural assumptions. Base models were selected that best fit
the observed data while concomitantly balancing the desire to capture the central tendency across those sources of uncertainty, ensure model realism and tractability, and promote robustness to potential model mis-specification.


## Stock Output and Dynamics{-}

Spawning output of `r spp` was estimated within each sub-area model and is reported here for each area (Tables \ref{tab:south-ssbES} and \ref{tab:north-ssbES}) and the combined estimates for the California stock (Table \ref{tab:es-ca-status}). Uncertainty is estimated within each model and is only reported for the model area results south and north of Point Conception. The spawning output, in terms of millions of eggs, south of Point Conception was estimated at `r round(south_model$derived_quants[south_model$derived_quants$Label %in% paste0("SSB_", endyr), "Value"], 2)`, an unfished spawning output of `r round(south_model$derived_quants[south_model$derived_quants$Label == "SSB_Virgin", "Value"], 2)`, and relative spawning output of `r round(south_model$derived_quants[south_model$derived_quants$Label %in% paste0("SSB_", endyr), "Value"]/south_model$derived_quants[south_model$derived_quants$Label == "SSB_Virgin", "Value"] , 2)`. The spawning output north of Point Conception was estimated at `r round(north_model$derived_quants[north_model$derived_quants$Label %in% paste0("SSB_", endyr), "Value"], 2)`, an unfished spawning output of `r round(north_model$derived_quants[north_model$derived_quants$Label == "SSB_Virgin", "Value"], 2)`, and relative spawning output of `r round(north_model$derived_quants[north_model$derived_quants$Label %in% paste0("SSB_", endyr), "Value"]/north_model$derived_quants[south_model$derived_quants$Label == "SSB_Virgin", "Value"] , 2)`. Across California, the stock for `r spp`, has a combined spawning output of `r sb_final`, unfished spawning output of `r sb0`, and a relative spawning output of `r depl_final`. The stock is estimated to be above the management target at the start of 2023 (Figures \ref{fig:es-sb-all} and \ref{fig:es-depl-all}).  

The spawning output declined for each sub-area between the early 1970s and continued through the mid-1990s (Figures \ref{fig:es-sb} and \ref{fig:es-depl}). South of Point Conception, the population has remained at low levels until the early 2000s at which point the population began slowly increasing up until 2019 with the spawning output declining in the final years of the time series. In contrast, the portion of the stock north of Point Conception has been continually increasing since the sub-area low point in spawning output in the 1990s. 

\input{tex_tables/south_b_SSB_ES.tex}

\input{tex_tables/north_b_SSB_ES.tex}

\newpage

```{r, results = 'asis'}
create_biomass_table(
    doc_dir = doc_dir, 
    prefix = "es",
    doc_names = c("nca", 'sca'),
    years = 2013:2023)

```


```{r, results = 'asis'}

add_figure(
filein = file.path(doc_dir, "shared_figures", "spawning_output_combined.png"), 
caption = "Estimated combined time series of spawning output for copper rockfish in California waters",
label = 'es-sb-all')

add_figure(
filein = file.path(doc_dir, "shared_figures", "depletion_combined.png"), 
caption = "Estimated combined time series of fraction of relative spawning output for copper rockfish in California waters",
label = 'es-depl-all')

```


```{r, results = 'asis'}
add_figure(
filein = file.path(doc_dir, "shared_figures", "compare2_spawnbio_uncertainty.png"), 
caption = "Estimated time series of spawning output (circles and line: median; light broken lines: 95 percent intervals) for the model areas south and north of Point Conception",
label = 'es-sb')
```


```{r, results = 'asis'}
add_figure(
filein = file.path(doc_dir, "shared_figures", "compare4_Bratio_uncertainty.png"), 
caption = "Estimated time series of fraction of relative spawning output (circles and line: median; light broken lines: 95 percent intervals) for the model areas south and north of Point Conception",
label = 'es-depl')
```

\pagebreak

## Recruitment{-}

Recruitment deviations were estimated from 1965-2020 south of Point Conception and from 1970-2019 north of Point Conception. The estimated magnitude of recruitment deviations and years of strong or weak recruitment varied for each sub-area. The base model south of Point Conception estimated strong recruitment in 2009, 2010, and 2013 with multiple poor recruitment years at the end of the time series (Table \ref{tab:south-recrES} and Figures \ref{fig:es-recruits} and \ref{fig:es-rec-devs}). The sub-area model north of Point Conception estimated the largest recent recruitment deviations in 2007, 2017, and 2019 with series of poor recruitment occurring in the late 1990s and early 2000s (Table \ref{tab:north-recrES} and Figures \ref{fig:es-recruits} and \ref{fig:es-rec-devs}). Additionally, the magnitude of overall estimated recruitment variation, highs and lows, was greater in the sub-area south of Point Conception compared to the sub-area north of Point Conception.   

\input{tex_tables/south_c_Recr_ES.tex}

\newpage

\input{tex_tables/north_c_Recr_ES.tex}

```{r, results = 'asis'}
add_figure(
filein = file.path(doc_dir, "shared_figures", "compare10_recruits_uncertainty.png"), 
caption = "Estimated time series of age-0 recruits (1000s) for the model areas south and north of Point Conception with 95 percent intervals",
label = 'es-recruits')
```


```{r, results = 'asis'}
add_figure(
filein = file.path(doc_dir, "shared_figures", "compare12_recdevs_uncertainty.png"), 
caption = "Estimated time series of recruitment deviations for the model areas south and north of Point Conception.",
label = 'es-rec-devs')
```

\clearpage

## Exploitation status{-}

Trends in fishing intensity (1 - SPR) for both sub-areas dramatically increased in the 1970s, exceeded the management target $\text{SPR}_{50\%}$, and remained high until at least the late 1990s (Figure \ref{fig:es-1-spr}). The fishing intensity south of Point Conception declined in the early 2000s but remained above the target for the rest of the time series excluding one year (Table \ref{tab:south-exploitES}). The fishing intensity sharply decreased around 2000 north of Point Conception with fishing intensity remaining below the management target since, excluding recent spikes in 2017 and 2020 (Table \ref{tab:north-exploitES}).   

As a percentage of biomass (ages 3+), harvest rates south of Point Conception between 2013-2021 ranged between 0.16-0.21, with harvest rates declining in 2022 to 0.07 based on inseason management actions by California Department of Fish and Wildlife (CDFW) that reduced the sub-bag limit for `r spp` to one-fish across the state (Table \ref{tab:south-exploitES}). The harvest rates in the sub-area north of Point Conception since 2013 have ranged between 0.01-0.06 (Table \ref{tab:north-exploitES}).

\input{tex_tables/south_d_SPR_ES.tex}

\input{tex_tables/north_d_SPR_ES.tex}

```{r, results = 'asis'}
add_figure(
filein = file.path(doc_dir, "shared_figures", "compare6_SPRratio_uncertainty.png"), 
caption = "Estimated 1 - relative spawning ratio (SPR) by year for the model areas south and north of Point Conception. The management target is plotted as a red horizontal line and values above this reflect harvest in excess of the proxy harvest rate",
label = 'es-1-spr')
```

\pagebreak

## Ecosystem considerations{-}

```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text",'es_ecosystem_considerations.Rmd')
read_child(filein)
```

## Reference points{-}


```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text",'es_reference_points.Rmd')
read_child(filein)
```


\input{tex_tables/south_e_ReferencePoints_ES.tex}

\input{tex_tables/north_e_ReferencePoints_ES.tex}


```{r, results = 'asis'}

ref_south <- read.csv(file.path(south_model_dir, "tables", "e_ReferencePoints_ES.csv"))
ref_north <- read.csv(file.path(north_model_dir, "tables", "e_ReferencePoints_ES.csv"))

out <- c(
  round(ref_south[1, "Estimate"] + ref_north[1, "Estimate"], 2),
  round(ref_south[2, "Estimate"] + ref_north[2, "Estimate"], 2),
  round(ref_south[3, "Estimate"] + ref_north[3, "Estimate"], 2),
  round(ref_south[4, "Estimate"] + ref_north[4, "Estimate"], 2),
  round((ref_south[4, "Estimate"] + ref_north[4, "Estimate"]) /(ref_south[1, "Estimate"] + ref_north[1, "Estimate"]), 3),
  round(ref_south[7, "Estimate"] + ref_north[7, "Estimate"], 2),
  round(ref_south[10, "Estimate"] + ref_north[10, "Estimate"], 2),
  round(ref_south[12, "Estimate"] + ref_north[12, "Estimate"], 2),
  round(ref_south[15, "Estimate"] + ref_north[15, "Estimate"], 2),
  round(ref_south[17, "Estimate"] + ref_north[17, "Estimate"], 2),
  round(ref_south[20, "Estimate"] + ref_north[20, "Estimate"], 2)
)
row_names <- c("Unfished Spawning Output", "Unfished Age 3+ Biomass (mt)", "Unfished Recruitment", "Spawning Output (2023)",
               "Relative Spawning Ouput",
               "Proxy Spawning Output (SB40%)", "Yield with SPR Based on SB40% (mt)", "Proxy Spawning Output (SPR50)", 
               "Yield with SPR50 (mt)", "Spawning Output at MSY", "MSY (mt)")

out <- cbind(row_names, out)
col_names <- c("Quantity", "Estimate")

table_format(x = out,
             caption = "Summary of reference points and management quantities for copper rockfish in California waters",
             label = "ref-point-all-es",
             align = 'l',
             digits = 3,
             col_names = col_names,
             longtable = TRUE,
             custom_width = TRUE,
             col_to_adjust = c(1), 
             width = c("6cm"))  

```


```{r, results = 'asis'}
add_figure(
filein = file.path(doc_dir, "shared_figures", "compare15_phase_plot.png"), 
caption = "Phase plot of estimated 1-SPR versus fraction unfished for the model areas south and north of Point Conception.",
label = 'es-phase')
```


```{r, results = 'asis'}
add_figure(
filein = file.path(doc_dir, "shared_figures", "south_yield2_yield_curve_with_refpoints.png"), 
caption = "Equilibrium yield curve for the base case model south of Point Conception. Values are based on the 2022
fishery selectivities and with steepness fixed at 0.72",
label = 'south-es-yield')
```


```{r, results = 'asis'}
add_figure(
filein = file.path(doc_dir, "shared_figures", "north_yield2_yield_curve_with_refpoints.png"), 
caption = "Equilibrium yield curve for the base case model north of Point Conception. Values are based on the 2022
fishery selectivities and with steepness fixed at 0.72",
label = 'north-es-yield')
```


\pagebreak

## Management performance{-}

`r Spp` are currently management within the Nearshore Rockfish Complex north and south of 40$^\circ$ 10' N. lat. The complexes are managed based on overfishing limits (OFL) and annual catch limits (ACL) that are determined by summing the species-specific OFLs and ACLs (ACLs set equal to the Acceptable Biological Catches [ABCs]) contributions for all stocks managed in the complexes. Limits are shared among all commercial and recreational fleets with the various management procedures intended to maintain removals below the total OFL and ACL for the Nearshore Rockfish north and south complexes as a whole, rather than on a species by species basis.

The species-specific OFL and ACL contribution for `r spp` that is allocated to California waters, Nearshore Rockfish South and 25 percent of the Nearshore Rockfish North, is shown in Table \ref{tab:es-ca-management} as well as the total catch across California. Over the last ten years the catches of `r spp` have been below the species-specific ACLs in California. In 2021 all U.S. West Coast stocks of `r spp` were assessed that informed the 2023-24 harvest specifications species-specific OFLs and ACLs. In California waters the new OFLs and ACLs for the 2023-24 management cycle were significantly lower than early years, resulting in in-season management action by CDFW for 2022 to reduce removals based on the latest stock assessment.


```{r, results = 'asis'}

create_management_table(
  management_dir = management_dir, 
  doc_dir = doc_dir, 
  doc_names = c("nca", 'sca'),
  years = 2012:2022,
  table_names = c("copper_ca_north.csv", "copper_ca_south.csv"),
  prefix = "es")

```

## Unresolved problems and major uncertainties{-}


```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir,'shared_text','es_unresolved_problems_uncertainties.Rmd')
read_child(filein)
```


## Decision table and projections{-}


```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir,'shared_text','es_forecasts.Rmd')
read_child(filein)
```


```{r, results = 'asis'}

create_projection_table(
    management_dir = management_dir, 
    doc_dir = doc_dir, 
    model_dir = model_dir,
    fixed_removals = c(91.5, 94.7),
    doc_names = c("nca", 'sca'),
    years = 2023:2034,
    table_names = c("copper_ca_north.csv", "copper_ca_south.csv"),
    prefix = 'es')

```

\pagebreak

## Scientific uncertainty{-}

```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text",'es_scientific_uncertainty.Rmd')
read_child(filein)
```

## Research and data needs{-}

```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text",'es_research_and_data_needs.Rmd')
read_child(filein)
```
