### Partnership for Interdisciplinary Studies of Coastal Oceans

The Partnership for Interdisciplinary Studies of Coastal Oceans [(PISCO)](https://www.piscoweb.org/) is an 
academic consortium conducting monitoring of coastal ecosystems in California as 
well as research to support marine protected area design.  Their work includes SCUBA 
surveys and fish recruitment monitoring within rocky reef habitats at a suite of sites 
across the state using standardized protocols so that multiple participating universities 
collect compatible data. 

The PISCO kelp forest fish survey data were downloaded from [DataONE](https://www.dataone.org/). 
We examined fish transect data collected by participating PISCO researchers at 
the University of California Santa Cruz (UCSC), University of California Santa Barbara 
(UCSB), the Vantuna Research Group (VRG) and Humboldt State University (HSU, now Cal Poly Humboldt) for potential 
development of a fishery-independent abundance index for use in the assessment model.  We 
ultimately concluded that the number of detections of `r spp` on transects was too low to 
be representative of relative abundance over time and the spatial distribution of sites
 having `r spp` were not well distributed across the coast.  Below we outline the structure 
of PISCO fish transect data, the procedure we used to filter to include `r spp` habitat,
and resulting sample sizes. Each fish transect location is surveyed by divers who count 
fish within a 30 x 2 x 2-m volume on the bottom, mid-way up the water column, and near 
the surface just below the kelp canopy.  Three replicate transects are performed within
inner, inner-mid, outer-mid, and deep zones of the reef corresponding to depths between 
5 and 20 m.  This results in 12 transect locations per reef site and 36 transect swims 
incorporating the three levels.  Divers count fish by species and estimate sizes.  Survey sites are typically grouped within a geographic area, i.e., there are three sites on Naples reef near Santa Barbara (Naples Central, Naples East, and Naples West).  

The full dataset was filtered for quality and habitat appropriate for `r spp`. 
Data was limited to surveys conducted by UCSC and UCSB because `r spp` were not 
observed by HSU and sites surveyed by VRG typically either saw very few `r spp` 
or were not consistently sampled across the time series.  The UCSC and UCSB campus 
sites were separated to develop two indices for the northern and southern models.
We eliminated sites that were sampled in less than 80 percent of the survey years for each campus.  `r Spp` were only observed on bottom transects and so mid-water and canopy transects were removed.  The inner reef (shallow) transects were removed due to rare `r spp` observations.  Divers noted approximate water visibility and transects with visibility less than 3 m were removed.  We also retained only fish greater than 17 cm to construct an adult index.  

```{asis, echo = model.area=='north'}

Early years with less consistent sampling were eliminated such that the time series for UCSC began in 2001 and extended through 2021.  The majority of UCSC sites occurred within sites that became MPAs.  Three sites that did not become MPAs were removed to create an index with a consistent change in selectivity following MPA implementation.  After filtering, sites that remained in the UCSC dataset were centered around the Monterey peninsula. Sample sizes of copper rockfish observed by year at all retained UCSC sites ranged from 1 to 28 fish (Table \ref{tab:pisco-data}).

```

```{asis, echo = model.area=='south'}

Early years with less consistent sampling were eliminated such that the time series for UCSB began in 2004 and extended through 2021.  Sites surveyed by UCSB were mixed in distribution inside and outside MPA locations and therefore were not filtered for this criterion.  After filtering, sites that remained in the UCSC dataset were centered around the northern Channel Islands with a few on the Santa Barbara Channel mainland. Sample sizes of copper rockfish observed by year at all retained sites ranged from 15 to 39 fish for UCSB (Table \ref{tab:pisco-data}).  

```

The PISCO program also conducts larval fish recruitment monitoring by sampling 
artificial settlement substrates called Standard Monitoring Units for Recruitment
of Fishes (SMURFs).  Similar to the SCUBA surveys, SMURF surveys are conducted by 
multiple universities using standardized protocols.  We examined data collected by 
the UCSB and UCSC campuses in southern and central California.  Surveys by UCSB were 
conducted between 2000 and 2018 and by UCSC between 1999 and 2016.  Juvenile `r spp` 
are difficult to distinguish from juvenile gopher rockfish (*Sebastes carnatus*) and the 
data from UCSB combines counts of these species into a complex.  For this reason, 
we determined this data to be inappropriate for construction of a `r spp` recruitment 
index to be used within the assessment.  While data from UCSC reports distinct counts 
of copper and gopher rockfish, the concern remains that the `r spp` counts may not be 
accurate due to this morphological identification difficulty.  Additionally, collections 
of `r spp` in this data set were very sparse with many years seeing none.  However, 
an extremely high number were recorded for 2016.  

### Reef Check

[Reef Check](https://www.reefcheck.org/) is an international non-profit organization utilizing citizen scientists 
to monitor reef habitats.  Data from SCUBA surveys of fish in California are available 
since 2006.  Given the low proportion of `r spp` detections on PISCO surveys, we did not 
dedicate time to analysis of Reef Check survey data for the purpose of abundance index development.  

### Visual Surveys

The SWFSC and UCSB both conduct visual surveys using ROVs and submersible vehicles. We used the observations of copper rockfish from these data to inform our understanding of the species' distribution (Figure \ref{fig:visual-surveys}). We also used these data as a visualization of data gaps that can inform future research. The visual surveys ranged from 1993 to 2018 from Monterey south to the California/Mexico border. A total of 3,976 individual `r spp` were observed at average transect depths ranging from 20 to 156 m, with an average of 67 m.  The depth ranges of these surveys, especially dives from the 2007 submersible survey of the Southern California Bight extended into much deeper waters to cover the depth range of cowcod [@yoklavich_fisheryindependent_2007]. The UCSB submersible survey sampled the natural reefs and the oil platforms southern California from 1995-2011 and could be explored as an index of abundance for copper rockfish in the future [@love_potential_2006].

### MRFSS Dockside Survey of CPFV/PC Vessels

```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text",'21f_mrfss_index.Rmd')
read_child(filein)
```

```{asis, echo = model.area=='south'}

The data were filtered to identify rockfish trips, standardized across the time series, and modeled to estimate and index of abundance for copper rockfish. The MRFSS CPFV index of abundance between 1980-1999 is generally variable but with a flat trend in abundance except for three years that spike in abundance estimates (Figure \ref{fig:mrfss-cpfv-index-fit}). These same patterns in sharp increases in the index for select years were also observed in the raw data. Given the limited information in the data to understand what was behind these unexpected spikes in the time series, the MRFSS index of abundance was not used in the final base model. 
```


```{asis, echo = model.area=='north'}

The data were filtered to identify rockfish trips, standardized across the time series, and modeled to estimate and index of abundance for copper rockfish. The MRFSS CPFV index of abundance between 1980-1999 is quite variable with notable periods of an increasing trend followed by a decline and then another increasing trend, e.g., increasing between 1982-1984, drop in 1985, and increasing between 1985-1987. These same patterns in increases and decreases in the index for select years were also observed in the raw data. The unstandardized data indicated similar peaks in average CPUE during the time series, but also years and area of unexpedectly high average CPUE (Figure \@ref(fig:mrfss-cpue-county)). The MRFSS survey was inactive from 1990-1994, years during which the Deb Wilson-Vandenberg survey was able to operate. Given the limited information in the data to understand what was behind these unexpected spikes in the time series, the MRFSS index of abundance was not used in the final base model. 
```

### CDFW ROV Survey

```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text",'10_appendix_rov.Rmd')
read_child(filein)
```

Revised data for the CDFW ROV survey were provided to the STAT late on Thursday May 18, 2023. CDFW determined that the line identifiers for the 500m transects, which we used to represent a sample, were not unique as previously described in the original data delivery on February 24, 2023. A small subset of transects were identified to have disparate 10 m sampling segments aggregated to incorrect transects (i.e., data collected across separate transects were combined into incorrect transects). This issue was identified in a total of 12 transects across all years and areas and when corrected resulted in 12 revised transects and 12 newly identified transects. Unfortunately, a clear summary of the number of 10 m segments, which transect they were subtracted or added from and which transects were impacted by area, year, and sites were not provided by CDFW. The STAT examined the number of unique transects by year north and south of Point Conception in the revised data.  The new data south of Point Conception contains a total of 894 transects across all years with 2 new transects in both 2014 and 2019. North of Point Conception there were a total of 916 transects with a total of 8 new transects, 3 in both 2016 and 2020 and 1 new transect in both 2019 and 2021. The number of transects impacted by area was relatively small and was not expected to result in a meaningful change in the estimated indices of abundance. However, when the revised data were analyzed there was a non-negligible shift in the estimated scale of the index of abundance south of Point Conception. This change in scale was not expected given the limited changes in the data described by CDFW. There was no significant change in the index north of Point Conception, which may be a result of using super-years and the sparser sampling. Further analysis of the data there revealed non-trivial changes in attributes for each transect, e.g., proportion substrate type, depth, effort estimated through usable transect area. The STAT observed these changes across transects that should not have been modified given the description that the revised data affected only 8 transects south of Point Conception (4 new and 4 revised transects). The STAT communicated these unexpected findings to CDFW on May 24, 2023. The response provided by CDFW on May 26th indicated that the estimates of the proportion of substrate types did differ from the original values based on an alternative calculation but the differences would be expected to by trivial. A description of the alternative calculations was provided, however, the STAT was unable to calculate matching values to those in the original dataset.

Given the limited time to properly review and analyze any potential data corrections and fully understand the changes to the data, the STAT decided the decision to remove the CDFW ROV data from both sub-area models. While the STAT identified significant issues with the revised data only south of Point Conception, there were overall concerns that all of the CDFW ROV data requires additional quality control, further descriptions of variable calculations, and further description and analyses of the aggregation of 10 m segments to the 500 m sampling unit to ensure that the data are accurate. The STAT is supportive of considering these data in future assessments of copper rockfish or other nearshore species once the issues identified this assessment cycle have been adequately addressed.  

A sensitivity to including the original dataset with errors estimated index of abundance and length compositions is provided in the Sensitivities Section \ref{sensitivities}. 