# Removal Data

## Commerical Landings & Discards

Since 1981, landings of copper rockfish have occurred from hook and line, net, pot, shrimp trawl, trawl, troll, and diving gear. The majority of landings for copper rockfish since 1981 are from hook and line gear across California (south of Point Conception 96% and north 87%). North of Point Conception there are some proportion of landings from trawl gear (8% primarily occurring between 1982-1985) and net gear (4% primarily occurring between 1983-1986). Since 2011, 98% and 96% of the landings south and north of Point Conception, respectively, are coming from hook and line gear.


In recent years, there has been an increase in the proportion of fish landed live for both areas. In recent years, the percentage of copper rockfish landed dead north of Point Conception has been generally less than 50% within each year. Fish landed live are primarily caught with hook and line gear. However, in recent years, north of Point Conception there have been some limited landings of live fish using pot gear. 


```{r, results = 'asis', fig.align='center'}
add_figure(
filein = file.path(dir, "plots", "landings_by_fleet_area.png"), 
caption = "Commercial landings north and south of Point Conception. The landings are separated by fish landed live versus dead. The commercial landings in the south are relatively low (less than 10 mt per year) across the majority of years excluding 1995-1998 when landings ranged from 24 to 32 mt. The commercial landings in the north are generally higher than those observed south of Point Conception, particularly between 1983 to 1998 with landings peaking in 1993 at 69 mt (sources: PacFIN and California historical catch reconstruction)",
label = 'com-landings')

``` 

```{r, results = 'asis', fig.align='center'}
add_figure(
filein = file.path(dir, "plots", "percent_dead_landings.png"), 
caption = "Proportion of commercial landings from fish landed dead north and south of Point Conception in recent years (source: PacFIN)",
width = 100,
height = 50, 
label = 'com-prop-dead')
``` 
\ 


### Additional Items for Discussion

Only the commercial landings are shown for each area. Discard mortality across time will need to considered to determine catches.

* The 2021 assessments assumed a constant discard mortality rate of 4.4% informed by WCGOP data for each area in California.
* The rate of discarding has likely varied across time. Are there particular periods of time when discarding likely increased/decreased?
* Different factors impacting discarding practices by area?


## Recreational Landings & Discards

TODO: Add the recreational landings data by proposed fleet structure

### Additional Items for Discussion

TODO: Add discussion points around recreational discarding
