

# Composition Data

## Commerical length compositions

```{r, results = 'asis'}
add_figure(
filein = file.path(dir, "plots", "com_length_samples_by_cond_area_year.png"), 
caption = "The number of length samples by year from live and dead copper rockfish from the area south and north of Point Conception. Since 1981, there are a total of 3,517 dead and 1,099 live length samples north of Point Conception and 553 live and 2,135 dead length samples south of Point Conception (source: PacFIN)",
label = 'com-length-n')

```
\

The majority of lengths are from hook and line gear for each area:

* North of Point Conception (total lengths = 4,616): 
  * 4,268 from hook and line gear,
  * 32 from net gear,
  * 139 from pot gear,
  * 15 from troll gear, and
  * 162 from trawl gear.
* South of Point Conception (total lengths = 2,688): 
  * 2,585 from hook and line gear,
  * 24 from net gear,
  * 39 from trawl gear, and
  * 36 from shrimp trawl gear.


```{r, results = 'asis'}
add_figure(
filein = file.path(dir, "plots", "length_boxplot_by_cond_area_year.png"), 
caption = "The distribution of length samples by year from live and dead copper rockfish from the area south and north of Point Conception. The black horizontal line within each box indicates the median length observed that year where the median is defined as an equal number of observations from that year that are greater than and lesser than that value. The lower range of each box indicates the 25th percentile where 25 percent of observations that year are less than that length. The upper range of each box indicates the 75th percentile where 75 percent of observations that year are less than that length (source: PacFIN)",
label = 'com-length-dist')

```
\


```{r, results = 'asis'}
add_figure(
filein = file.path(dir, "plots", "length_denstity_by_cond_area.png"), 
caption = "The density of size selected by landed condition, live or dead, for each area across all years (source: PacFIN)",
label = 'com-marginal-length-dist')

```
\
```{r, results = 'asis'}
add_figure(
filein = file.path(dir, "plots", "boxplot_length_by_port_area_cond_filtered_by_100n.png"), 
caption = "Boxplot of lengths by landed port, area, and fish condition (live or dead) across all years.  Only ports with greater than 100 length samples (live + dead > 100 samples) across all years are shown. The Ventura (VEN) and Santa Barbara (SB) ports are south of Point Conception. The ports north of Point Conception are Avila (AVL), Morro Bay (MRO), Moss Landing (MOS), Half Moon Bay (PRN), San Francisco (SF), Bodega Bay (BDG), Eureka (ERK), Crescent City (CRS) (source: PacFIN)",
label = 'com-boxplot-length-port')

```

## Recreational length compositions

The recreational length composition data summarized below represent data pulled from RecFIN collected by either the MRFSS (1980 - 2003) or CRFS (2004 - 2022) sampling programs. There are additional data sources that contain historical length samples from the CPFV fleets (1975-1979 from Collins and Crooke, 1987-1998 from Deb Wilson-Vandenberg, and 1986-1989 from Alley and Ono) that will be evaluated and used within each assessment model as appropriate but are not included here.

The total number of length samples within RecFIN across MRFSS and CRFS are:

* North of Point Conception (total lengths = 38,994): 
  * 11,969 from CPFV, and
  * 27,025 from Private/Rental vessels.
* South of Point Conception (total lengths = 31,036): 
  * 23,535 from CPFV, and
  * 7,501 from Private/Rental vessels.

In RecFIN there are lengths from shoreside modes that were not included in the analysis presented below (north of Point Conception = 148 and south = 20). All lengths below represent retained fish. There were limited length observations of released fish (north = 52 and south = 187).

```{r, results = 'asis'}
add_figure(
filein = file.path(dir, "plots", "rec_length_samples_by_area_year.png"), 
caption = "The number of length samples by year and mode for copper rockfish for areas south and north of Point Conception. Since 1980, there are a total of 11,969 CPFV and 27,025 Private/Rental length samples north of Point Conception and 23,535 CPFV and 7,501 Private/Rental length samples south of Point Conception (source: RecFIN)",
label = 'rec-length-samples')

```
\

```{r, results = 'asis'}
add_figure(
filein = file.path(dir, "plots", "all_length_dist_by_mode_area.png"), 
caption = "The density of size selected by mode, CPFV or Private/Rental, for each area across all years (source: RecFIN)",
label = 'rec-length-dist')

```
\

### Potential bias in length sampling with CPFV trip duration

The CDFW California Recreational Fisheries Survey (CRFS) collects length samples from fish caught on CPFVs. These samples are collected by both staff on board CPFV trips and at the docks when vessels return.  On board CRFS staff are unable to sample overnight trips with as high a frequency as day trips.  In many cases, these overnight trips may reach destinations that are farther from port and therefore experience lower fishing rates and contain larger fish.This could result in a bias in length distributions aggregated across trip duration if sites with larger fish are under-sampled.  

The STAT examined the length distributions of fish sampled on trips of varying duration by district.Overnight trips only occur in the southern California sampling districts 1 (San Diego, Orange, and Los Angeles counties) and 2 (Ventura and Santa Barbara counties).Some separation in copper rockfish length frequencies is observed in district 1.  

```{r, results = 'asis'}
add_figure(
filein = file.path(dir, "plots", "CopperDurationDist12.png"), 
caption = "Copper rockfish length grequency by CPFV trip duration for CRFS districts 1 & 2 for 1/2 day, 3/4 day, and overnight fishing trips (source: CRFS PC Onboard + Dockside Surveys)",
label = 'cpfv-length-duration')

```
\

To determine if overnight trips are under-sampled, relative to their frequency, we need to compare catch rates relative to sampling rates.  A sharp increase in the number of rockfish caught on overnight CPFV trips, as well as other fish species, was observed in 2014 with catches remaining relatively high through 2020. No increase was observed in the single day trips.  This was coincident with an increase in the number of overnight trips being made in 2014.  The increase in catch was likely driven by the arrival of warm water which drove increases in pelagic species.  A large proportion of the trips made in 2014 listed tuna as the target species.  Many trips targeting pelagic species will also visit sites to target groundfish, and this is the likely cause for the coincident increase in groundfish catch.      

```{r, results = 'asis'}
add_figure(
filein = file.path(dir, "plots", "cpfv_catch_multi_single.png"), 
caption = "CPFV catch of rockfish and non-rockfish on multi- and single-day trips (source: CPFV Logbooks)",
label = 'cpfv-catch-duration')

```
\

```{r, results = 'asis'}
add_figure(
filein = file.path(dir, "plots", "cpfv_trips_multi_single.png"), 
caption = "The number of of multi- and single-day CPFV trips (source: CPFV Logbooks)",
label = 'cpfv-trips-duration')

```
\

We calculated the percent of copper rockfish in southern California caught on overnight trips relative to the total number of CPFV trips.  We compared this to the percent of copper rockfish length samples collected from CPFVs that were taken from overnight trips.  The lower proportion of sampling relative to catch shows that there is under-sampling of these trips.  Given this, we will consider weighting length samples from CPFVs according to trip duration to correct for this bias, particularly since 2014.    

```{r, results = 'asis'}
add_figure(
filein = file.path(dir, "plots", "cpfv_sampling_multi.png"), 
caption = "Percentage of copper rockfish caught on multi-day the percentage of legth samples from mult-day trips (source: CPFV Logbooks and CRFS PC Onboard and Dockside Surveys)",
label = 'cpfv-sampling')

```
\

Additionally, in order to understand the potential impact of biased and unbiased sampling of trips by duration a simulation analysis was conducted. The simulation analysis examined the average size of fish and the variability around that average (standard deviation) by trip type:

* Single-day trip: average fish length of 31.9 cm with standard deviation of 6.1 cm, and
* Multi-day trip: average fish length of 35.2 cm with standard deviation of 5.6 cm.

A bias (over-sampling of single-day trips) and an unbiased (sampling aligns with the proportion of trip type) of a 1,000 total length sample were randomly generated based on the average length and standard deviation of observations from each trip type. The bias sampling approach was based on the observed proportion of samples coming from single-day trips. The most extreme difference in sampling proportion observed in the data was used to generate the biased sample where 980 lengths were collected from single-day trips and 20 lengths were collected from multi-day trips. The unbiased sample was based on the proportion of single-day and multi-day trips observed between 2014 - 2018 where 81% of the trips were single-day were 810 samples were from single-day trips and 190 samples from multi-day trips were randomly generated. 

```{r, results = 'asis'}
add_figure(
filein = file.path(dir, "plots", "cpfv_trip_sampling_bias_unbiased.png"), 
caption = "Simulated length distribution based on biased and unbiased sampling of trip by duration (single-day or multi-day). The 10%, 50%, and 90% quartile from each sample type is show by the dashed verticle lines. The median length (50% quartile) of the unbiased sample was approximately 0.5 cm greater than the median length from the biased sample. While there are small differences in the length distribution between the biased and unbiased samples, the difference is not great enough to have a measurable impact the length composition data when binned using 2 cm bins for use in an assessment model (source: simulated samples based on CPFV Logbooks and CRFS PC Onboard and Dockside Surveys)",
height = 60,
label = 'cpfv-sim-sample')

```
\

While the differences in the simulated length distribution for copper rockfish, there may be greater impacts for other species and or if the sampling bias continues (or increases) across years in the future. Additional efforts should be made to align sampling with the proportion of trip type. 