

# Composition Data

## Commerical length compositions

```{r, results = 'asis'}
add_figure(
filein = file.path(dir, "plots", "com_length_samples_by_cond_area_year.png"), 
caption = "The number of length samples by year from live and dead copper rockfish from the area south and north of Point Conception. Since 1981, there are a total of 3,517 dead and 1,099 live length samples north of Point Conception and 553 live and 2,135 dead length samples south of Point Conception (source: PacFIN)",
label = 'com-length-n')

```
\

The majority of lengths are from hook and line gear for each area:

* North of Point Conception (total lengths = 4,616): 
  * 4,268 from hook and line gear,
  * 32 from net gear,
  * 139 from pot gear,
  * 15 from troll gear, and
  * 162 from trawl gear.
* South of Point Conception (total lengths = 2,688): 
  * 2,585 from hook and line gear,
  * 24 from net gear,
  * 39 from trawl gear, and
  * 36 from shrimp trawl gear.


```{r, results = 'asis'}
add_figure(
filein = file.path(dir, "plots", "length_boxplot_by_cond_area_year.png"), 
caption = "The distribution of length samples by year from live and dead copper rockfish from the area south and north of Point Conception. The black horizontal line within each box indicates the median length observed that year where the median is defined as an equal number of observations from that year that are greater than and lesser than that value. The lower range of each box indicates the 25th percentile where 25 percent of observations that year are less than that length. The upper range of each box indicates the 75th percentile where 75 percent of observations that year are less than that length (source: PacFIN)",
label = 'com-length-dist')

```
\


```{r, results = 'asis'}
add_figure(
filein = file.path(dir, "plots", "length_denstity_by_cond_area.png"), 
caption = "The density of size selected by landed condition, live or dead, for each area across all years (source: PacFIN)",
label = 'com-marginal-length-dist')

```
\
```{r, results = 'asis'}
add_figure(
filein = file.path(dir, "plots", "boxplot_length_by_port_area_cond_filtered_by_100n.png"), 
caption = "Boxplot of lengths by landed port, area, and fish condition (live or dead).  Only ports with greater than 100 length samples (live + dead > 100 samples) across all years are shown (source: PacFIN)",
label = 'com-boxplot-length-port')

```

## Recreational length compositions

The recreational length composition data summarized below represen data pulled from RecFIN collected by either the MRFSS (1980 - 2003) or CRFS (2004 - 2022) sampling programs. There are additional data sources that contain historical length samples from the CPFV fleets (1975-1979 from Collins and Crooke, 1987-1998 from Deb Wilson-Vandenberg, and 1986-1989 from Alley and Ono) that will be evaluated and used within each assessment model as appropriate but are not included here.

The total number of length samples within RecFIN across MRFSS and CRFS are:

* North of Point Conception (total lengths = 38,994): 
  * 11,969 from CPFV, and
  * 27,025 from Private/Rental vessels.
* South of Point Conception (total lengths = 31,036): 
  * 23,535 from CPFV, and
  * 7,501 from Private/Rental vessels.

In RecFIN there are lengths from shoreside modes that were not included in the analysis presented below (north of Point Conception = 148 and south = 20). All lengths below represent released fish. There were limited length observations of released fish (north = 52 and south = 187).

```{r, results = 'asis'}
add_figure(
filein = file.path(dir, "plots", "rec_length_samples_by_area_year.png"), 
caption = "The number of length samples by year and mode for copper rockfish for areas south and north of Point Conception. Since 1980, there are a total of 11,969 CPFV and 27,025 Private/Rental length samples north of Point Conception and 23,535 CPFV and 7,501 Private/Rental length samples south of Point Conception (source: RecFIN)",
label = 'rec-length-samples')

```
\

```{r, results = 'asis'}
add_figure(
filein = file.path(dir, "plots", "all_length_dist_by_mode_area.png"), 
caption = "The density of size selected by mode, CPFV or Private/Rental, for each area across all years (source: RecFIN)",
label = 'rec-length-dist')

```
\

TODO: Add table and figures showing the around the number of single day and multi-day trips

### Potential bias in length sampling with CPFV trip duration

The CDFW California Recreational Fisheries Survey (CRFS) collects length samples from fish caught on commercial passenger fishing vessels (CPFVs).  These samples are collected by both staff on board CPFV trips and at the docks when vessels return.  On board CRFS staff are unable to sample overnight trips with as high a frequency as day trips.  In many cases, these overnight trips may reach destinations that are farther from port and therefore experience lower fishing rates and contain larger fish.  This could result in a bias in length distributions aggregated across trip durations if sites with larger fish are under-sampled.  

We examined the length distributions of fish sampled on trips of varying duration by district.  Overnight trips only occur in the southern California sampling districts 1 (San Diego, Orange, and Los Angeles counties) and 2 (Ventura and Santa Barbara counties).  Some separation in copper rockfish length frequencies is observed in district 1.  

```{r, results = 'asis'}
add_figure(
filein = file.path(dir, "plots", "CopperDurationDist12.png"), 
caption = "Copper Rockfish Length Frequency by CPFV Trip Duration, CRFS Districts 1 & 2 (source: CRFS PC Onboard + Dockside Surveys)",
label = 'cpfv-length-duration')

```
\
To determine if larger fish are under-sampled, we need to compare catch rates relative to sampling rates.  A sharp increase in the number of rockfish caught on overnight CPFV trips, as well as other fish species, was observed in 2014 with catches remaining relatively high through 2020.  No increase was observed on day trips.  This was coincident with an increase in the number of overnight trips being made in 2014.  The increase in catch was likely driven by the arrival of warm water which drove increases in pelagic species.  A large proportion of the trips made in 2014 listed tuna as the target species.  Many trips targeting pelagic species will also visit sites to target groundfish, and this is the likely cause for the coincident increase in groundfish catch.      

```{r, results = 'asis'}
add_figure(
filein = file.path(dir, "plots", "cpfv_catch_multi_single.png"), 
caption = "CPFV Catch of Rockfish and Non-Rockfish on Multi and Single-Day Trips (source: CPFV Logbooks)",
label = 'cpfv-catch-duration')

```
\

```{r, results = 'asis'}
add_figure(
filein = file.path(dir, "plots", "cpfv_trips_multi_single.png"), 
caption = "Multi and Single-Day CPFV Trips (source: CPFV Logbooks)",
label = 'cpfv-trips-duration')

```
\
We calculated the percent of copper rockfish in southern California caught on overnight trips relative to the total number of CPFV trips.  We compared this to the percent of copper rockfish length samples collected from CPFVs that were taken from overnight trips.  The lower proportion of sampling relative to catch shows that there is under-sampling of these trips.  Given this, we will consider weighting length samples from CPFVs according to trip duration to correct for this bias, particularly since 2014.    

```{r, results = 'asis'}
add_figure(
filein = file.path(dir, "plots", "cpfv_sampling_multi.png"), 
caption = "Multi and Single-Day CPFV Trips (source: CPFV Logbooks and CRFS PC Onboard and Dockside Surveys)",
label = 'cpfv-sampling')

```