## Survey length compositions

### CCFRP Survey

An initial look at the length distributions also suggests the survey observes larger fish in the MPAs from San Francisco and south.  The CCFRP data for 2022 are not yet available.

```{r, results = 'asis', fig.align='center'}
add_figure(
  filein = file.path(dir, "plots", "ccfrp_copper_lengths.png"), 
  caption = "The length distribution (cm) and sample sizes of copper rockfish encountered by CCFRP by MPA and reference pair. The combined data represent the years 2007-2021 and every fish encountered is measured (source: CCFRP)",
  label = 'ccfrp-lengths')

``` 
\


### NWFSC Hook and Line survey

Between 2004-2021 the NWFSC Hook and Line survey has caught a total of 1,151 copper rockfish with otoliths for ageing being collected from each fish. The majority of these observations have occurred outside the CCA (outside CCA = 1,057 and inside CCA = 94). Observations of copper rockfish have occurred across a range of depths between 22 - 66 fathoms with the median of observations occurring around 44 fathoms. The NWFSC Hook and Line data from 2022 is not yet available and not included in these data summaries. 


```{r, results = 'asis', fig.align='center'}
add_figure(
  filein = file.path(dir, "plots", "hkl_observations_by_length_area.png"), 
  caption = "Total observations by length (cm) of copper rockfish between 2004-2021 inside and outside of Cowcod Conservation Areas from the NWFSC Hook and Line survey (source: NWFSC Hook and Line survey)",
  label = 'hkl-length-area')

``` 
\


```{r, results = 'asis', fig.align='center'}
add_figure(
  filein = file.path(dir, "plots", "hkl_length_sex_depth.png"), 
  caption = "Measured lengths (cm) by depth in fathoms of copper rockfish between 2004-2021 from the NWFSC Hook and Line survey (source: NWFSC Hook and Line survey)",
  label = 'hkl-length-depth')

``` 
\

### NWFSC WCGBT survey


```{r, results = 'asis', fig.align='center'}
add_figure(
  filein = file.path(dir, "plots", "wcgbt_length_samples_w_otoliths_by_area.png"), 
  caption = "Number of lengths with otoliths by length and area collected by the NWFSC WCGBT survey between 2003 - 2021. A total of 195 and 584 otoliths were collected from the areas north and south of Point Conception, respectively (source: NWFSC WCGBT survey)",
  label = 'wcgbt-lengths')

``` 

