

# Biology

## Maturity and Fecundity

Currently, there is an extensive collaborative effort to collect biological samples for copper rockfish in California. These samples will support new estimates of maturity- and fecundity-at-length. These data are not yet available but are expected to be completed in time for use in the 2023 assessment of copper rockfish.  

For informational purposes, maturity and fecundity curves that were used in the 2021 assessment are shown below.

```{r, results = 'asis', fig.align='center'}
add_figure(
  filein = file.path(dir, "plots", "maturity_2021.png"), 
  caption = "Estimates of maturity-at-length used in the 2021 assessments of copper rockfish. The same maturity curve was used in California north of Point Conception, Oregon, and Washington. A unique maturity curve was estimated based on 111 samples from the NWFSC WCGBT and Hook and Line surveys south of Point Conception (source: Hannah, 2004; Melissa Head (NWFSC))",
  label = 'maturity-2021')

``` 
\


```{r, results = 'asis', fig.align='center'}
add_figure(
  filein = file.path(dir, "plots", "Fecundity.png"), 
  caption = "Estimates of fecundity-at-length used in the 2021 assessments of copper rockfish. (source: Dick et al., 2017)",
  height = 75,
  width = 75,
  label = 'fecundity-2021')

``` 
\


## Length-Weight

The length-weight relationship was estimated using all biological data available from the NWFSC West Coast Groundfish Bottom Trawl (WCGBT) and the NWFSC Hook and Line surveys. 

```{r, results = 'asis'}
add_figure(
filein = file.path(dir, "plots", "doc_Length_Weight_Sex.png"), 
caption = "Estimated length-weight relationship by sex for copper rockfish (source: NWFSC WCGBT and Hook and Line Surveys)",
height = 75,
width = 75,
label = 'weight-length')

```
\

## Length-at-Age

TODO: Add plot showing the length-at-age of available data by area

TODO: Add table of the number of additional age reads by sources that the CAP lab is working on 

## Natural Mortality

Natural mortality was fixed in the 2021 assessments at a value of 0.108 yr^-1^ based on an assumed maximum age of 50 years. The maximum age was selected based on available age data collected within Oregon and Washington and literature values. The oldest aged observed was 51 years with two observations off of the coast of Washington and Oregon in 2019. This selection was consistent with the literature examining the longevity of copper rockfish and was supported by the observed ages that had multiple observations of fish between 44 and 51 years of age.  

The input parameter value for natural mortality will be reconsidered within the 2023 assessments based on any new available age data. Additionally, the 2023 assessments will explore the ability to estimate natural mortality within the model and will conduct sensitivities and profiles to understand the information in the data on natural mortality and the impact of select values on the model estimates.

