# Introduction
## Basic Information and Life History

This assessment report describes the sub-area population of `r spp` (*Sebastes caurinus*) off the California coast south of Point Conception in U.S. waters, using data through 2022. The sub-area population north of Point Conception in California waters was also evaluated and is described in a separate assessment report. The `r spp` status for the California stock of is determined by the combined estimates of spawning output from both sub-areas and is detailed in the [management](#management) section. This assessment does not account for populations located in Mexico waters or other areas off the U.S. coast and assumes that these southern and northern populations do not contribute to the population being assessed here. 


```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text", '1_intro_life_history_fishery_info.Rmd')
read_child(filein)
```

## Ecosystem Considerations


```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text", '1_ecosystem_consideration.Rmd')
read_child(filein)
```


## Historical and Current Fishery Information

Off the coast of California south of Point Conception `r spp` is caught in both commercial and recreational fisheries. Recreational removals have been the largest source of fishing mortality of `r spp` across all years (Table \ref{tab:allcatches} and Figure \ref{fig:catch}). The recreational fishery is comprised of individual recreational fishers (Private/Rental, PR) and charter recreational private vessels (CPFV) which take groups of individuals out for day fishing trips. Across both types of recreational fishing the majority of effort occurs around rocky reefs that can be accessed via a day-trips. 

```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text", '1_intro_ca_commercial.Rmd')
read_child(filein)
```

`r Spp` residing between Point Conception and the California/Oregon border are assessed here as a single, separate stock (Figure \ref{fig:ca-map}). This designation was made based on oceanographic, geographic, and fishery conditions. The `r spp` population in California waters was split at Point Conception due to water circulation patterns that create a natural barrier between nearshore rockfish populations to the north and south. The northern border for this assessment was defined as the California/Oregon border due to substantial differences in historical and current exploitation levels. Additionally, the fairly sedentary nature of adult `r spp`, likely limits flow of fish between northern California and areas to the north. 

## Summary of Management History and Performance

```{r, echo=FALSE, results='asis'}

filein = file.path(doc_dir, "shared_text", '1_intro_management.Rmd')
read_child(filein)
```

## Foreign Fisheries
Replace text.
