# Introduction

This assessment report describes the sub-area population of `r spp` (*Sebastes caurinus*) off the California coast `r area` in U.S. waters, using data through 2022. The sub-area population north of Point Conception in California waters was also evaluated and is described in a separate assessment report. The `r spp` status for the California stock of `r spp` is determined by the combined estimates of spawning output from both sub-areas and is detailed in Management, Section \ref{management}. This assessment does not account for populations located in Mexican waters or other areas off the U.S. West Coast and assumes that these southern and northern populations do not contribute to nor take from the population being assessed here. 

## Basic Information and Life History

```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text", '1_intro_life_history_fishery_info.Rmd')
read_child(filein)
```

## Ecosystem Considerations


```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text", '1_ecosystem_consideration.Rmd')
read_child(filein)
```


## Historical and Current Fishery Information

Off the coast of California south of Point Conception `r spp` is caught in both commercial and recreational fisheries. Recreational removals have been the largest source of fishing mortality of `r spp` across all years (Table \ref{tab:allcatches} and Figure \ref{fig:catch}). The recreational fishery is comprised of individual recreational fishers (Private/Rental, PR) and commercial passenger fishing vessels (CPFV) also known as party/charter (PC) which take groups of individuals out for day fishing trips. Across both types of recreational fishing the majority of effort occurs around rocky reefs that can be accessed via day-trips. 

```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text", '1_intro_ca_commercial.Rmd')
read_child(filein)
```

`r Spp` residing between Point Conception and the Mexico/U.S. border are assessed here as a separate sub-area (Figure \ref{fig:ca-map}). This designation was made based on oceanographic, geographic, and fishery conditions. The `r spp` population in California waters was split at Point Conception due to water circulation patterns that create a natural barrier between nearshore rockfish populations to the north and south. Additionally, the fairly sedentary nature of adult `r spp` likely limits flow of fish between south and north of Point Conception. 

## Summary of Management History and Performance

```{r, echo=FALSE, results='asis'}

filein = file.path(doc_dir, "shared_text", '1_intro_management.Rmd')
read_child(filein)
```


## Foreign Fisheries


```{r, echo=FALSE, results='asis'}

filein = file.path(doc_dir, "shared_text", '1_foreign_fisheries.Rmd')
read_child(filein)
```

