
## Fishery-Dependent Data

### Commercial Fishery {#commercial-fishery}

#### Landings and Discards
\
```{r, echo=FALSE, results='asis'}

filein = file.path(doc_dir, "shared_text",'2f_commercial_removals.Rmd')
read_child(filein)
```


#### Composition Data
\

Biological data were extracted from the PacFIN Biological Data System on March 20, 2023. Length data for the commercial fleet were extracted from the PacFIN Biological Data System (BDS) with samples for north↨ of Point Conception beginning in 1983 (Tables \ref{tab:dead-com-len} and \ref{tab:live-com-len}). The commercial data was split by landed condition, live or dead, with the first data for the live fish fishery beginning in 1999. The number of length samples by fleet were highly variable with the largest number of samples by year being recorded in the mid- to late-1990s for the dead fish fishery. In recent years, the number of length samples by year are limited for both fleets. The number of samples prior to 1995 and in the 2000s for the dead fish fishery were sparse and variable across sizes. During model explorations any year with less than 20 sampled fish were considered too sparse to accurately reflect the fleet selectivity for that year (see [Appendix A](#excluded-data) for implied fits to these lengths). 

The majority of lengths sampled from the commercial fleet landing dead `r spp` ranged between approximately 25 - 45 cm starting in the early 1990s with some additional observations of larger fish in earlier years (Figure \ref{fig:com-dead-len-data}, detailed length compositions by year can be found in the Appendix, Section \ref{length-data}).  The mean length observed by year ranged between approximately 35 - 45 cm (Figure \ref{fig:mean-com-dead-len-data}). The mean observed length in the earliest data is variable ranging between 40 -45 cm, declining in the 1990s to less than 40 cm, then increasing to slightly larger mean size across the sparse data of the early 2000s, and then increasing again in the most recent years. There were only a few age samples (8 total) from the commercial dead fleet that were collected in 2022 (Figure \ref{fig:com-dead-age-data}). By chance, all of these ages were from from female fish. These data were incorporated into the model as marginal age data associated with this fleet. 

The observed distribution of sizes sampled from the commercial live fish fleet were generally variable based on the more limited sample sizes but ranging between 30 - 40 cm with missing years of data across different time periods (Figure \ref{fig:com-live-len-data}). The observed mean length of fish landed live was highly variable with means often below 35 cm with the smallest observed mean size being observed in the final year of data (Figure \ref{fig:mean-com-live-len-data}).  

The input sample sizes for all commercial data initially were calculated based on a combination of trips and fish sampled:

\begin{centering}

Input effN = $N_{\text{trips}} + 0.138 * N_{\text{fish}}$ if $N_{\text{fish}}/N_{\text{trips}}$ is $<$ 44

Input effN = $7.06 * N_{\text{trips}}$ if $N_{\text{fish}}/N_{\text{trips}}$ is $\geq$ 44

\end{centering}

During initial model evaluations alternative data weighting approaches suggested potentially high up-weighting the samples from the commercial live fish fishery. In order to ensure that the data were not up-weighted beyond the total annual sample size the input sample size was revised to be equal to the number of lengths samples.

### Recreational Fishery {#recreational-fishery}

#### Landings and Discards
\

```{r, echo=FALSE, results='asis'}

filein = file.path(doc_dir, "shared_text",'2f_recreational_removals.Rmd')
read_child(filein)
```

Recreational catch data is reported by district in CRFS where district 1 (aka South) and district 2 (aka Channel) are located `r area`. The proportion of removals by the CPFV fleet since 2004 by district are shown in Table \ref{tab:crfs-by-district} (see the Appendix, Section \ref{cpfv-samples}, for additional information about sampling and data by CDFW districts)

#### Indices of Abundance
\

A number of indices of abundance were explored for the recreational fleet (Figure \ref{fig:stand-cpue}). Discarded catch is available from onboard observer surveys, but was not included in indices. Indices developed for the assessment include:

* CDFW CPFV/PC onboard observer index (2005-2019)
* CRFS PR1 sites dockside survey (2004-2019)

Due to limited sampling during 2020 due to the COVID-19 pandemic and inseason action taken by CDFW for 2022 reducing sub-bag limits for `r spp` across California, both recreational fishery indices of abundance excluded data collected after 2019.

```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text",'21f_crfs_cpfv_index.Rmd')
read_child(filein)
```

The CRFS CPFV index of abundance was low in the early years of the time-series between 2005-2004 and then began to increase with variability among years until 2013, and declined in the final years (Figure \ref{fig:crfs-index-main}). See the Appendix Section {onboard-cpfv-index} for details on the data filtering, processing, and model selection.

Catch and effort data from CRFS dockside sampling of private boats, 2004-2019, and 2021-2022, were provided by CDFW for use in this assessment. The data include catch (number of fish) by species, number of anglers (i.e., effort units are angler trips), angler-reported distance from shore (Area X: inside/outside of 3 nm), county, port, interview site, year, month, and CRFS district. Only data through 2019 were used to develop an index of abundance due to potential changes in angler behavior in 2021 and management changes in 2022. See Appendix Section \ref{crfs-pr-index} for details on the data filtering, processing, and model selection. The CRFS PR index of abundance generally increased between 2004-2016, with the final years of the index stabilizing or slightly declining (Figure \ref{fig:crfs-pr-index-main}).


#### Composition Data
\

Length compositions were available from the following sources: 

* Recreational party/charter mode (CPFV/PC)

  + Collins and Crooke onboard observer survey (1975-1978)
  + MRFSS CPFV/PC dockside survey (1980-1989, 1993-2003)
  + Ally onboard observer survey (1984-1989)
  + CRFS CPFV/PC onboard dockside survey (2004-2022)

* Recreational private/rental mode (PR)

  + MRFSS dockside PR survey (1980-1989, 1993-2003)
  + CRFS dockside PR survey (2004-2022)

  
The number of available fish and unique trips by year and fleet are in Table \ref{tab:rec-len-samps}.  MRFSS historical biological data were downloaded from the RecFIN website in December 2022. CRFS biological data were also downloaded from RecFIN on February 18, 2023. The Collins and Crooke and Ally recreational survey data were downloaded from the SWFSC databases on February 12, 2023. In the CRFS era which reports samples by CDFW district the majority of length samples `r area` arise from CDFW district 2 (Channel Islands, Table \ref{tab:rec-samps-by-district}).

Nearly all of the length samples for both recreational fleets, CPFV and PR, were unsexed (only two sexed fish in the CPFV data were added to the unsexed data). A wide range of lengths from the recreational CPFV fleet were observed across all years with lengths generally ranging between 20 - 40 cm except for the late 1970s and early 1980s where a higher proportion of larger fish were sampled (Figure \ref{fig:rec-cpfv-len-data}). The mean of lengths observed in the recreational CPFV fleet by is variable with mean length increasing until the early 1980s, decreasing until the mid-1990s, increasing until 2000, stabilizing with some variability through the early 2010s, and then slowly increasing in the most recent years of data (Figure \ref{fig:mean-rec-cpfv-len-data}). The length distribution by CDFW district from the CPFV fleet since 2004 are shown in Figure \ref{fig:rec-cpfv-dist}. The range of lengths sampled from the recreational PR fleet are similar to those from the CPFV fleet with lengths in recent years ranging between 20 - 40 cm (Figures \ref{fig:rec-pr-len-data} and \ref{fig:mean-rec-pr-len-data}). 

Age data collected by the recreational CPFV fleet were collected in two separate years, 1975 and 2022. The historical age data were from a total of 84 unsexed fish and were incorporated in the model as marginal age data (Figure \ref{fig:com-dead-age-data}). In 2022, a total of 508 age samples from the final model year, 2022, were collected in a cooperative program with assistance from the fleet coordination by the SWFSC. These data were collected by four CPFV vessels that operate south of Point Conception following random sampling protocols. The lengths collected associated with fish collected by the cooperative for aging were compared to all the CPFV lengths collected by the CRFS sampling program (Figure \ref{fig:coop-len-comparison}). This comparison revealed that there were distinct differences in the length of fish in these two data sets where the cooperative collected data tended to have more large fish. The CRFS length data sample size was less than half of the sample size of cooperative age data collection (CRFS sampled 243 from 78 trips, Table  \ref{tab:rec-len-samps}). The source of these differences is not entirely clear, but could be arising from a difference in sampling areas within the region `r area` where there appear to be size and abundance differences in the more southern areas compared to areas around the Channel Islands. Given the differences in the age samples to the lengths sampled by the CRFS program, these ages were not linked to the CPFV fleet in the model.  However, these data are an important source of age-length information for `r spp`, so these data were added to a growth fleet in the model (see the [Growth Data](#growth-data) section)

The approach to determine the number of unique trips by data source varied. Only Collins and Crook data had unique trip numbers within the data. Other data sources that lacked clear trip identifier applied a similar methodology as developed by Brian Soper that combines multiple fields of information to attempt to estimate trips sampled. The number of trips for MRFSS data was estimated using the year, wave, ID code, sampling site (INSITE), area, and mode. A similar methodology was done for CRFS that used data, county, water area, interview site, and mode. Finally, trips for the Ally survey data were based on year, complex, landing, and district.
