## Biological Data

### Natural Mortality

```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text",'2_biology_natural_mortality.Rmd')
read_child(filein)
```


### Maturation and Fecundity {#maturation-and-fecundity}

```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text",'2_biology_maturity.Rmd')
read_child(filein)
```

The 50 percent size-at-maturity for `r spp` `r area ` was estimated at `r round(model$MGparmAdj[,"Mat50%_Fem_GP_1"][1], 2)` cm with a slope of `r round(model$MGparmAdj$Mat_slope_Fem_GP_1[1], 2)` (Figure \ref{fig:maturity}). This area-specific maturity-at-length estimate is the same to the biological maturity curve assumed for `r spp` north of Point Conception using all maturity samples. Additionally, these values are both slightly smaller than estimates by Hannah [-@hannah_length_2014] for fish observed in Oregon waters (34.8 cm) which estimated the 50 percent size-at-maturity of and slope of -0.60.

```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text",'2_biology_fecundity.Rmd')
read_child(filein)
```


### Sex Ratio

```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text",'2_biology_sex_ratio.Rmd')
read_child(filein)
```


### Length-Weight Relationship

```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text",'2_biology_weight_length.Rmd')
read_child(filein)
```


### Growth (Length-at-Age) {#length-at-age}

Length-at-age was estimated for male and female `r spp` informed by age data from the fisheries, the CCFRP survey, and independent efforts from four `r area` programs since 2002: 207 otoliths collected by the NWFSC WCGBT survey, 427 otoliths collected by a research survey conducted by Don Pearson, 77 from a research survey conducted by Abrams, and 508 otoliths collected by a cooperative research survey by the SWFSC and CPFV funded by the Sportfishing Association of California (Table \ref{tab:growth-age-samps}). The ages collected by these three sources were included in the model as a "growth" fleet that was not associated with removals or an index of abundance. 

Sex-specific growth parameters `r area` were initially estimated external to the model using the von Bertanlaffy growth curve as parameterized within Stock Synthesis at the following values:

\begin{centering}

Females $L_{age=2}$ = 19.8 cm; $L_{age=20}$ = 44.9 cm; $k$ = 0.243 per year

Males $L_{age=2}$ = 20.4 cm; $L_{age=20}$ = 44.2 cm; $k$ = 0.279 per year

\end{centering}

\vspace{0.50cm}

These values were used as starting parameter values within the base model prior to estimating each parameter for male and female `r spp`.


### Ageing Precision and Bias


```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text",'2_biology_ageing_error.Rmd')
read_child(filein)
```
