## Model Structure and Assumptions

### Modeling Platform and Structure

```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text",'31_modeling_platform.Rmd')
read_child(filein)
```


### Model Selection and Evaluation

The base assessment model for `r spp` was developed to balance parsimony and realism, and the goal was to estimate a spawning output trajectory for the population of `r spp` off the west coast of the U.S. The model contains many assumptions to achieve parsimony and uses many different sources of data to estimate reality. A series of investigative model runs were done to achieve the final base model.


### Model Changes from the Last Assessment 




### Bridging Analysis

The exploration of models began by bridging from the 2021 data-moderate assessment to Stock Synthesis version 3.30.21, which produced the same estimates for spawning biomass and depletion across the time series (Figures \ref{fig:bridge-ssb} and \ref{fig:bridge-depl}). Additional bridging analysis was conducted examining the impact on a revised model structure and updating and adding new data into the model. First, the 2021 fishery fleet structure was modified from the 2021 structure where the new assessment separated commercial data into two fleets based on fish landed condition, dead or live, and the recreational data into two fleets, CPFV and PR. The 2021 recreational and commercial data were reprocessed  into the new model structure through 2021 and new selectivity parameters were added to the 2021 for the newly split data. The new data available in for this assessment were then added to the model retaining the same model structure where feasible in the following order:

1. Update externally estimated biology parameters for length-at-age, weight-at-age, and maturity.
2. Add new catch data for all fishery fleets.
3. Add all updated commercial and recreational length and age data.
4. Add the new fishery-dependent indices of abundance.
5. Add the CDFW ROV survey index of abundance and length data.
6. Add the CCFRP index of abundance, length, and age data.
7. Add the updated NWFSC Hook and Line survey index of abundance, length, and age data.
8. Add selectivity blocks for the commercial and recreational fishing fleets.
9. Turn on the estimation of annual recruitment deviations.
10. Add conditional-age-at-length data for the growth fleet and estimate growth parameters for both sexes.

The data bridging are shown in Figures \ref{fig:data-bridge-ssb-1}-\ref{fig:data-bridge-depl-2}. Revising the model structure, updating biology, removals, length data and adding ages and fishery-dependent indices results in small changes to the estimated spawning output and stock status (Figures \ref{fig:data-bridge-ssb-1} and \ref{fig:data-bridge-depl-1}). Adding and updating survey data, adding selectivity blocks, and estimating annual recruitment deviations and growth resulted in larger revisions in the population estimates.  The largest changes in the new model relative to the 2021 assessment occurred when annual recruitment deviations were estimates resulting in a decrease in spawning output and stock status at the end of the time-series (Figures \ref{fig:data-bridge-ssb-2} and \ref{fig:data-bridge-depl-2}). Similar estimates were observed in 2021 assessment that included a sensitivity that estimated annual recruitment deviations. 

To arrive at a final base model additional revisions to the model structure, selectivity blocks, revised selectivity parameterization were done in order to determine the best fit to the data.


### Key Assumptions and Structural Choices

The specifications of the assessment are listed in Table \ref{tab:model-structure}. The model is a two-sex, age-structured model starting in 1916 with an accumulated age group at 50 years. Growth and natural mortality were assumed time invariant with constant growth estimated and natural mortality fixed at the median of the prior for both sexes. The lengths in the population were tracked by 1 cm intervals and the length data were binned into 2 cm intervals. Stock Synthesis estimates growth in the age and size plus group. To avoid issues with additional estimated growth in the plus groups, the selection of the maximum age and length bins were selected to ensure that the numbers of fish in the plus group would be low.


Add additional info on selectivity, recruitment 


### Priors

```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text",'31_model_priors.Rmd')
read_child(filein)
```


### Data Weighting



### Model Parameters
Describe estimated vs. fixed parameters, priors