## Model Structure and Assumptions

### Modeling Platform and Structure

```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text",'31_modeling_platform.Rmd')
read_child(filein)
```


### Model Selection and Evaluation

The base assessment model for `r spp` was developed to balance parsimony and realism, and the goal was to estimate a spawning output trajectory for the population of `r spp` off the west coast of the U.S. The model contains many assumptions to achieve parsimony and uses many different sources of data to estimate reality. A series of investigative model runs were done to achieve the final base model.


### Model Changes from the Last Assessment 


```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text",'31_changes_in_model_structure.Rmd')
read_child(filein)
```


### Bridging Analysis

The exploration of models began by bridging from the 2021 data-moderate assessment to Stock Synthesis version 3.30.21, which produced the same estimates for spawning biomass and depletion across the time series (Figures \ref{fig:bridge-ssb} and \ref{fig:bridge-depl}). Additional bridging analysis was conducted examining the impact on a revised model structure and updating and adding new data into the model. First, the 2021 fishery fleet structure was modified from the 2021 structure where the new assessment separated commercial data into two fleets based on fish landed condition, dead or live, and the recreational data into two fleets, CPFV and PR. The 2021 recreational and commercial data were reprocessed  into the new model structure through 2021 and new selectivity parameters were added to the 2021 for the newly split data. The new data available in for this assessment were then added to the model retaining the same model structure where feasible in the following order:

1. Update externally estimated biology parameters for length-at-age, weight-at-age, and maturity.
2. Add new catch data for all fishery fleets.
3. Add all updated commercial and recreational length and age data.
4. Add the new fishery-dependent indices of abundance.
5. Add the CDFW ROV survey index of abundance and length data.
6. Add the CCFRP index of abundance, length, and age data.
7. Add the updated NWFSC Hook and Line survey index of abundance, length, and age data.
8. Add selectivity blocks for the commercial and recreational fishing fleets.
9. Turn on the estimation of annual recruitment deviations.
10. Add conditional-age-at-length data for the growth fleet and estimate growth parameters for both sexes.

The data bridging are shown in Figures \ref{fig:data-bridge-ssb-1}-\ref{fig:data-bridge-depl-2}. Revising the model structure, updating biology, removals, length data and adding ages and fishery-dependent indices results in small changes to the estimated spawning output and stock status (Figures \ref{fig:data-bridge-ssb-1} and \ref{fig:data-bridge-depl-1}). Adding and updating survey data, adding selectivity blocks, and estimating annual recruitment deviations and growth resulted in larger revisions in the population estimates.  The largest changes in the new model relative to the 2021 assessment occurred when annual recruitment deviations were estimates resulting in a decrease in spawning output and stock status at the end of the time-series (Figures \ref{fig:data-bridge-ssb-2} and \ref{fig:data-bridge-depl-2}). Similar estimates were observed in 2021 assessment that included a sensitivity that estimated annual recruitment deviations. 

To arrive at a final base model additional revisions to the model structure, selectivity blocks, revised selectivity parameterization were done in order to determine the best fit to the data.


### Key Assumptions and Structural Choices

The specifications of the assessment are listed in Table \ref{tab:model-structure}. The model is a two-sex, age-structured model starting in 1916 with an accumulated age group at 50 years. Growth and natural mortality were assumed time invariant with constant growth estimated and natural mortality fixed at the median of the prior for both sexes. The lengths in the population were tracked by 1 cm intervals and the length data were binned into 2 cm intervals. Stock Synthesis estimates growth in the age and size plus group. To avoid issues with additional estimated growth in the plus groups, the selection of the maximum age and length bins were selected to ensure that the numbers of fish in the plus group would be low.

Time blocks on selectivity were explored extensively when setting up the initial model structure. A range of management changes to the commercial were considered when determining periods of when selectivity may have been expected to change. Commercial removals for `r spp` are relatively low when compared to recreational removals for this species which limited the amount of composition data available to support estimation of changes in selectivity. Given this and the limited evidence in the available length data, time-invariant selectivity was selected for both the commercial dead and live fish fleets. The same time block structure was assumed both the recreational CPFV and PR fleets based on gear restrictions and depth closures. Selectivity blocked into three periods: 1916-1999, 2000-2004, and 2005-2022, Model exploration revealed that that selectivity in the first and third time blocks were highly similar so the these two time periods were set to have equal selectivity. In 2022 the sub-bag limit in the California recreational fishery was reduce to only allow one `r spp`. However, the amount of length samples in 2022 were not informative about a change in selectivity. Finally, a change in selectivity was explored for the `r hkl` to shift sometime between 2012-2014, years where the number of MPA and CCA sites increased within the the survey. Exploratory models did not reveal a meaningful shift in the selectivity for this survey in that time period for `r spp` and for model parsimony a single selectivity for this fleet was assumed. 

The specification of when to estimate recruitment deviations is an assumption that affects the estimate of early model uncertainty around stock scale and status. Recruitment deviations were estimated from 1880 - 2020 to appropriately quantify uncertainty in the early model years. The earliest length- and age-composition data occur in 1975 but age data were not consistently on a yearly basis until 2003. The most informed years for estimating recruitment deviations were from about the mid-1990s to 2018. The period from 1880 - 1964 was fit using an early recruitement deviation series with little or no bias adjustment, the main period of recruitment deviates occurred from 1965 - 2020 with an upward and downward ramping of bias adjustment, and 2021 onward recruitment deviations were assumed to be 0 due to limited information at the end of the time-series. [-@methot_adjusting_2011a] summarize the reasoning behind varying levels of bias adjustment based on the information available to estimate the deviates. The standard deviation of recruitment variability was assumed to be 0.60 based on the estimated variation in recruitment from the base model.

The following distributions were assumed for data fitting wher the survey indices were lognormal and the compositional
data had a multinomial error structure.


### Priors

```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text",'31_model_priors.Rmd')
read_child(filein)
```


### Data Weighting

Length composition data for the commercial fishery started with a sample size determined from the equation listed in Sections \ref{commercial-fishery}. The input sample size for the length composition data from recreational fishery was determined based on the number of estimated trips (described in Sections \ref{recreational-fishery}), both the CCFRP and `r hkl` were set equal to the number of positive drops by year, the CDFW ROV were set equal to the number of positive transects, the `r wcgbt` was set equal to the number of fish, and the Pearson Research survey and CPFV cooperative collection program set equal to the number of trips. The majority of age-composition data were input as conditional-age-at-length with input sample size equal to the number of ages. The age-composition data from both the commercial dead and historical CPFV samples were used as marginal age-composition with the input sample size set equal to the number of ages.     

The base  model was weighted using the "Francis method", which was based on equation TA1.8 in Francis [-@francis_data_2011] which was selected based on model stability and consistency in the model to identify the minimum likelihood estimate (MLE). This formulation looks at the mean length or age and the variance of the mean to determine if across years, the variability is explained by the model. If the variability around the mean does not encompass the model predictions, then that data source should be down-weighted. This method accounts for correlation in the data (i.e., the multinomial distribution). Sensitivities were performed examining the difference in the model fits and results due to in weighting using McAllister-Ianelli Harmonic Mean Weighting [-@mcallister_bayesian_1997] and the Dirichlet Multinomial Weighting [-@thorson_model-based_2017].

### Model Parameters

There were 186 estimated parameters in the base model. These included one parameter for $R_0$, 10 parameters for growth, 5 parameters for extra variability for the fishery and survey indices, 29 parameters for length-based selectivity and time blocking of the fleets and the surveys, and 141 recruitment deviations including 35 pre-model estimates (Table \ref{tab:params}).

Fixed parameters in the model were as follows. Steepness was fixed at 0.72, the mean of the prior. A sensitivity analysis and a likelihood profile were performed for steepness. Natural mortality was fixed at 0.108 yr^-1^ for females and males, the median of the prior. Estimation of natural mortality was explored during model development. The estimate of natural mortality uncertain and poorly informed by the data. When estimated natural mortality was low (around 0.090 yr^-1^) relative to the median of the prior which was based on maximum age; however, well within the prior distribution (SE = 0.31). The observations of fish greater than 50 years of age across the West Coast, not only this assessment area, is rare, so a natural mortality that would be associated with a maximum around 60 years of age did not seem well supported. Natural mortality was fixed in the base model but estimation of this parameter for both sexes was explored via sensitivies.

The standard deviation of recruitment deviates was fixed at 0.60 ($\sigma_R$). Maturity-at-length was fixed as described above in Section \ref{maturation-and-fecundity}. Length-weight parameters were fixed at external estimates based on estimates using the `r hkl` and `r wcgbt` length-weight observations (Figure \ref{fig:est-len-wght}).
