\clearpage
# Tables

<!-- ======================================================= -->
<!-- ***************    Catches      *********************** --> 
<!-- ======================================================= -->

```{r, results = 'asis'}

years = startyr:endyr
nfleets = 4
dead_all = NULL

for (i in 1:nfleets){
  name = paste0("dead(B):_",i)
  dead = model$timeseries[model$timeseries$Yr %in% years, name]
  dead_all = cbind(dead_all, dead)
}
total.dead  <- round(apply(dead_all, 1, sum), 1)
out = cbind(years, round(dead_all, 1), total.dead)
out = as.data.frame(out)
col_names = c("Year", "Commercial Dead", "Commercial Live", "CPFV", "PR", "Total Catch")

table_format(x = out,
             caption = "Catch (mt) by fleet and the summed total catch (mt).",
             label = "allcatches",
             digits = 1,
             align = 'l',
             col_names = col_names)
```

\newpage

<!-- ======================================================= --> 
<!-- *********** Removals vs. OFL/ACL   ******************** --> 
<!-- ======================================================= --> 

```{r, results = 'asis'}

create_management_table(
  management_dir = management_dir, 
  doc_dir = doc_dir, 
  doc_names = c("nca", 'sca'),
  years = 2012:2022,
  table_names = c("copper_ca_north.csv", "copper_ca_south.csv"),
  prefix = NULL)

```

\newpage

<!-- ======================================================= -->
<!-- *************** Com. Catch Ratio  ********************* --> 
<!-- ======================================================= -->

\include{tex_tables/historical_landings_tables_2020_revised_Avila_1953.tex}

\newpage

<!-- ======================================================= -->
<!-- *************** Commercial Data *********************** --> 
<!-- ======================================================= -->

\include{tex_tables/south_dead_trips_and_samples.tex}

\newpage

\include{tex_tables/south_live_trips_and_samples.tex}

\newpage

<!-- ======================================================= -->
<!-- ************* Recreational Data *********************** --> 
<!-- ======================================================= -->


```{r, results = 'asis'}
# Add rec landings by district
tab <- read.csv(file.path(data_dir, "rec_catch", "forSS", "south_percent_catch_by_district.csv"))
col_names <- c("Year", "District 2 (Channel)", "District 1 (South)", "Percent District 2", "Percent District 1")

sa4ss::table_format(x = tab,
             caption = "Summary of the CPFV catch data in CRFS by CDFW district south of Point Conception.",
             label = "crfs-by-district",
             align = 'l',
             col_names = col_names,
             digits = 2) 
```

\newpage


```{r, results = 'asis'}
#\include{tex_tables/rec_south_sample_size_by_program.tex}

tab <- read.csv(file.path(data_dir, "rec_bds", "forSS", "rec_south_sample_size_by_program.csv"))
tab <- tab[, -1]
col_names <- c("Year", "Source", "CPFV Trips", "CPFV Samples", "PR Trips", "PR Samples")

sa4ss::table_format(x = tab,
             caption = "Summary of the recreational length samples and estimated trips for the CPFV and PR fleets.",
             label = "rec-len-samps",
             align = 'l',
             longtable = TRUE,
             col_names = col_names,
             font_size = 9,
             custom_width = TRUE,
             col_to_adjust = 2:6, 
             width = c("4cm", "2cm", "2cm", "2cm", "2cm"),
             digits = 0) 
```

\newpage

```{r, results = 'asis'}

tab <- read.csv(file.path(data_dir, "rec_bds", "forSS", "rec_bds_cpfv_samples_by_district.csv"))
tab <- tab[, -1]
col_names <- c("Year", "District 2 (Channel)", "District 1 (South)", "District 2 Percent", "District 1 Percent")

sa4ss::table_format(x = tab,
             caption = "Summary of the total recreational length samples and percentage collected in district 1 and 2.",
             label = "rec-samps-by-district",
             align = 'l',
             col_names = col_names,
             digits = 2) 
```


\newpage


<!-- ======================================================= -->
<!-- ***************   Discard Data  *********************** --> 
<!-- ======================================================= -->



<!-- ======================================================= -->
<!-- ********************   CCFRP    *********************** --> 
<!-- ======================================================= -->

\input{tex_tables/south_ccfrp_drifts_length_ages.tex}

\newpage

<!-- ======================================================= -->
<!-- *************  NWFSC HKL  Data  *********************** --> 
<!-- ======================================================= -->


\input{tex_tables/nwfsc_hkl_positive_samples_by_year.tex}

\pagebreak

\input{tex_tables/nwfsc_hkl_positive_samples_by_depth.tex}

\pagebreak



```{r, results = 'asis'}
#\input{tex_tables/nwfsc_hkl_sample_number_by_site_cca.tex}

tab <- read.csv(file.path(data_dir, "survey_indices", "nwfsc_hkl", "forSS", "sample_number_by_site_cca.csv"))
col_names <- c("Year",  "Drops", "Observations - Outside", "Observations - CCA")

sa4ss::table_format(x = tab,
             caption = "Summary of the number of observations by year and unique drops between sites outside the CCAs and inside the CCAs for copper rockfish from the NWFSC Hook and Line survey.",
             label = "nwfsc-hkl-obs",
             align = 'l',
             col_names = col_names) 
```


\pagebreak


```{r, results = 'asis'}
#\input{tex_tables/nwfsc_hkl_sample_number_by_site_cca.tex}

tab <- read.csv(file.path(data_dir, "survey_indices", "nwfsc_hkl", "forSS", "sample_number_by_site_cca.csv"))
col_names <- c("Year", "Drops", "Observations - Outside", "Observations - Closed")

sa4ss::table_format(x = tab,
             caption = "Summary of the number of observations by year and unique drops between sites open to fishing (outside) and sites within either CCA areas with no take or MPAs (closed) for copper rockfish from the NWFSC Hook and Line survey.",
             label = "nwfsc-hkl-obs-mpa",
             align = 'l',
             col_names = col_names) 
```


\pagebreak

\input{tex_tables/nwfsc_hkl_effn_lengths_ages.tex}

\newpage

<!-- ======================================================= -->
<!-- *************     CDFW  ROV     *********************** --> 
<!-- ======================================================= -->


```{r, results = 'asis'}
#\input{tex_tables/rov_south_samples_transects.tex}

tab <- read.csv(file.path(data_dir, "survey_indices", "rov", "forSS", "south_obs_designation_mpa_group_year.csv"))
col_names <- c("Year", "Location",  "Designation",  "Transects", "Observations")

sa4ss::table_format(x = tab,
             caption = "Number of transect and number of observations of copper rockfish for each year, sample location, and site designation for the CDFW ROV survey",
             label = "rov-obs",
             align = 'l',
             col_names = col_names,
             custom_width = TRUE,
             col_to_adjust = 2, 
             width = c("3cm"),
             digits = 0) 
```

\newpage

<!-- ======================================================= -->
<!-- *************    Growth Ages    *********************** --> 
<!-- ======================================================= -->


```{r, results = 'asis'}
#\input{tex_tables/south_growth_age_samples.tex}

tab <- read.csv(file.path(data_dir, "ages", "forSS", "south_growth_age_samples.csv"))
col_names <- c("Year", "Source", "Number of Ages")

sa4ss::table_format(x = tab,
             caption = "Available age data by year and source used in the growth fleets.",
             label = "growth-age-samps",
             align = 'l',
             col_names = col_names,
             custom_width = TRUE,
             col_to_adjust = 2, 
             width = c("4cm"),
             digits = 0) 
```


\newpage

<!-- ======================================================= -->
<!-- *************  PISCO SAMPLES    *********************** --> 
<!-- ======================================================= -->


```{r, results = 'asis'}

tab <- read.csv(file.path(data_dir, "survey_indices", "pisco", "nCPR_table_N_S.csv"))
col_names <- c("Year", "UCSC Raw Count", "UCSC Filtered Count", "UCSB Raw Count", "UCSB Filtered Count")

table_format(x = tab,
             caption = "All and filtered observations by year and sampling institution for PISCO.",
             label = "pisco-data",
             align = 'l',
             col_names = col_names)
```

\newpage

<!-- ======================================================= -->
<!-- *************  NWFSC WCGBT  Data  *********************** --> 
<!-- ======================================================= -->

\input{tex_tables/wcgbt_samples_by_year.tex}

\newpage

<!-- ======================================================= -->
<!-- ***********   Model Structure      ******************** --> 
<!-- ======================================================= -->

\input{tex_tables/model_structure_south.tex}

\newpage

<!-- ======================================================= -->
<!-- ***********   Model Parameters     ******************** --> 
<!-- ======================================================= -->


```{r, results = 'asis'}
mod_params = model$parameters[, 
                                (names(model$parameters) %in%
                                c("Num","Label","Value","Phase","Min",
                                  "Max","Status","Parm_StDev",
                                  "Pr_type","Prior","Pr_SD"))] 
mod_params[,'Value'] = round(as.numeric(mod_params[,'Value']),3)                                 
# Combine bounds into one column
mod_params$Min = paste('(', mod_params$Min, ', ', mod_params$Max, ')', sep='')
# Combine prior info to one column
mod_params$PR_type = ifelse(mod_params$Pr_type == 'No_prior' , 'None', paste(mod_params$Pr_type,' (', mod_params$Prior,  ', ', mod_params$Pr_SD, ')', sep = ''))
# Set long value to scientific notation
mod_params[mod_params$Label == "Wtlen_1_Fem",3] = format(mod_params[mod_params$Label == "Wtlen_1_Fem",3], scientific = TRUE)
mod_params[mod_params$Label == "Wtlen_1_Mal",3] = format(as.numeric(mod_params[mod_params$Label == "Wtlen_1_Mal",3]), scientific = TRUE)
mod_params[mod_params$Label == "Eggs_scalar_Fem",3] = format(as.numeric(mod_params[mod_params$Label == "Eggs_scalar_Fem",3]), scientific = TRUE)
mod_params[mod_params$Label == "L_at_Amax_Mal_GP_1",3] = round(as.numeric(mod_params[mod_params$Label == "L_at_Amax_Mal_GP_1",3]), 4)
mod_params[mod_params$Label == "VonBert_K_Mal_GP_1",3] = round(as.numeric(mod_params[mod_params$Label == "VonBert_K_Mal_GP_1",3]), 3)
mod_params[mod_params$Label == "CV_old_Mal_GP_1",3] = round(as.numeric(mod_params[mod_params$Label == "CV_old_Mal_GP_1",3]), 3)
# Remove the max, prior and prior sd columns
drops = c('Max', 'Prior', 'Pr_type', 'Pr_SD', 'Num')
mod_params = mod_params[, !(names(mod_params) %in% drops)]
rownames(mod_params) = c()
mod_params[,"Label"] = gsub("\\_", " ", mod_params[,"Label"])
mod_params[,"PR_type"] = gsub("\\_", " ", mod_params[,"PR_type"])
# Add column names
col_names = c('Parameter',
                         'Value',
                         'Phase',
                         'Bounds',
                         'Status',
                         'SD',
                         'Prior (Exp.Val, SD)')
table_format(x = mod_params,
             caption = "List of parameters used in the base model, including estimated values and standard deviations (SD), bounds (minimum and maximum), estimation phase (negative values not estimated), status (indicates if parameters are near bounds), and prior type information (mean and SD).",
             label = "params",
             align = 'l',
             col_names = col_names,
             longtable = TRUE,
             font_size = 9,
             landscape = TRUE,
             custom_width = TRUE,
             col_to_adjust = c(1,7), 
             width = c("7cm", "4cm"))                         
```

\newpage

<!-- ======================================================= -->
<!-- ***********    Like Contributions  ******************** --> 
<!-- ======================================================= -->

\include{tex_tables/south_likelihoods.tex}

\newpage


<!-- ======================================================= -->
<!-- ***********   Data Weights         ******************** --> 
<!-- ======================================================= -->


```{r, results = 'asis'}
tab <- read.csv(file.path(sens_dir, "data_weights.csv"))
col_names <- c("Fleet", "Data Type", "Francis", "MI", "Dirichlet")

sa4ss::table_format(x = tab,
             caption = "Suggested data weights for each data weighting methodology by fleet and data type.",
             label = "dw",
             align = 'l',
             digits = 2,
             col_names = col_names) 
```

\newpage

<!-- ======================================================= -->
<!-- ***********       Time Series      ******************** --> 
<!-- ======================================================= -->

\include{tex_tables/south_TimeSeries.tex}


\newpage


```{r, results = 'asis'}
create_biomass_table(
    doc_dir = doc_dir, 
    prefix = NULL,
    doc_names = c("nca", 'sca'),
    years = 1916:2023)
# tab:ca-status

```

\newpage


<!-- ======================================================= -->
<!-- ****************     Sensitivities      *************** --> 
<!-- ======================================================= -->


\include{tex_tables/sensitivities_1_final.tex}


\newpage


\include{tex_tables/sensitivities_2_final.tex}

\newpage

\include{tex_tables/sensitivities_3_final.tex}

\newpage

<!-- ======================================================= -->
<!-- ********  Reference Points & Management *************** --> 
<!-- ======================================================= -->

\include{tex_tables/south_e_ReferencePoints.tex}

\newpage

\include{tex_tables/north_e_ReferencePoints.tex}

\newpage

```{r, results = 'asis'}

ref_south <- read.csv(file.path(south_model_dir, "tables", "e_ReferencePoints_ES.csv"))
ref_north <- read.csv(file.path(north_model_dir, "tables", "e_ReferencePoints_ES.csv"))

out <- c(
  round(ref_south[1, "Estimate"] + ref_north[1, "Estimate"], 2),
  round(ref_south[2, "Estimate"] + ref_north[2, "Estimate"], 2),
  round(ref_south[3, "Estimate"] + ref_north[3, "Estimate"], 2),
  round(ref_south[4, "Estimate"] + ref_north[4, "Estimate"], 2),
  round((ref_south[4, "Estimate"] + ref_north[4, "Estimate"]) /(ref_south[1, "Estimate"] + ref_north[1, "Estimate"]), 3),
  round(ref_south[7, "Estimate"] + ref_north[7, "Estimate"], 2),
  round(ref_south[10, "Estimate"] + ref_north[10, "Estimate"], 2),
  round(ref_south[12, "Estimate"] + ref_north[12, "Estimate"], 2),
  round(ref_south[15, "Estimate"] + ref_north[15, "Estimate"], 2),
  round(ref_south[17, "Estimate"] + ref_north[17, "Estimate"], 2),
  round(ref_south[20, "Estimate"] + ref_north[20, "Estimate"], 2)
)
row_names <- c("Unfished Spawning Output", "Unfished Age 3+ Biomass (mt)", "Unfished Recruitment", "Spawning Output (2023)",
               "Relative Spawning Ouput",
               "Proxy Spawning Output (SB40%)", "Yield with SPR Based on SB40% (mt)", "Proxy Spawning Output (SPR50)", 
               "Yield with SPR50 (mt)", "Spawning Output at MSY", "MSY (mt)")

out <- cbind(row_names, out)
col_names <- c("Quantity", "Estimate")

table_format(x = out,
             caption = "Summary of reference points and management quantities for copper rockfish in California waters",
             label = "ref-point-all",
             align = 'l',
             digits = 3,
             col_names = col_names,
             longtable = TRUE,
             custom_width = TRUE,
             col_to_adjust = c(1), 
             width = c("6cm"))  

```

```{r, results = 'asis'}

create_projection_table(
    management_dir = management_dir, 
    doc_dir = doc_dir, 
    model_dir = model_dir, 
    fixed_removals = c(91.53, 94.69),
    doc_names = c("nca", 'sca'),
    years = 2023:2034,
    table_names = c("copper_ca_north.csv", "copper_ca_south.csv"),
    prefix = NULL)

```

\newpage
