\clearpage
# Tables

<!-- ======================================================= -->
<!-- ***************    Catches      *********************** --> 
<!-- ======================================================= -->

```{r, results = 'asis'}

years = startyr:endyr
nfleets = 4
dead_all = NULL

for (i in 1:nfleets){
  name = paste0("dead(B):_",i)
  dead = model$timeseries[model$timeseries$Yr %in% years, name]
  dead_all = cbind(dead_all, dead)
}
total.dead  <- round(apply(dead_all, 1, sum), 1)
out = cbind(years, round(dead_all, 1), total.dead)
out = as.data.frame(out)
col_names = c("Year", "Commercial (Dead)", "Commercial (Live)", "Rec. CPFV", "Rec. PR", "Total Landings")

table_format(x = out,
             caption = "Removals (mt) by fleet and the summed total landings (mt).",
             label = "allcatches",
             digits = 1,
             align = 'l',
             col_names = col_names)
```

<!-- ======================================================= --> 
<!-- *********** Removals vs. OFL/ACL   ******************** --> 
<!-- ======================================================= --> 


<!-- ======================================================= -->
<!-- *************** Com. Catch Ratio  ********************* --> 
<!-- ======================================================= -->

\include{tex_tables/historical_landings_tables_2020_revised_Avila_1953.tex}

\newpage


<!-- ======================================================= -->
<!-- ***************   Discard Data  *********************** --> 
<!-- ======================================================= -->




<!-- ======================================================= -->
<!-- *************  NWFSC HKL  Data  *********************** --> 
<!-- ======================================================= -->


\input{tex_tables/nwfsc_hkl_positive_samples_by_year.tex}

\pagebreak

\input{tex_tables/nwfsc_hkl_positive_samples_by_depth.tex}

\pagebreak

\input{tex_tables/nwfsc_hkl_sample_number_by_site_cca.tex}

\pagebreak

\input{tex_tables/nwfsc_hkl_effn_lengths_ages.tex}


<!-- ======================================================= -->
<!-- *************     CDFW  ROV     *********************** --> 
<!-- ======================================================= -->

\input{tex_tables/rov_south_samples_transects.tex}


<!-- ======================================================= -->
<!-- *************  NWFSC WCGBT  Data  *********************** --> 
<!-- ======================================================= -->

\input{tex_tables/south_strata_observations.tex}

\input{tex_tables/south_growth_age_samples.tex}

<!-- ======================================================= -->
<!-- *************    Growth Ages    *********************** --> 
<!-- ======================================================= -->



<!-- ======================================================= -->
<!-- ***********   Model Structure      ******************** --> 
<!-- ======================================================= -->


<!-- ======================================================= -->
<!-- ***********   Model Parameters     ******************** --> 
<!-- ======================================================= -->


```{r, results = 'asis'}
mod_params = model$parameters[, 
                                (names(model$parameters) %in%
                                c("Num","Label","Value","Phase","Min",
                                  "Max","Status","Parm_StDev",
                                  "Pr_type","Prior","Pr_SD"))] 
mod_params[,'Value'] = round(as.numeric(mod_params[,'Value']),3)                                 
# Combine bounds into one column
mod_params$Min = paste('(', mod_params$Min, ', ', mod_params$Max, ')', sep='')
# Combine prior info to one column
mod_params$PR_type = ifelse(mod_params$Pr_type == 'No_prior' , 'None', paste(mod_params$Pr_type,' (', mod_params$Prior,  ', ', mod_params$Pr_SD, ')', sep = ''))
# Set long value to scientific notation
mod_params[mod_params$Label == "Wtlen_1_Fem",3] = format(mod_params[mod_params$Label == "Wtlen_1_Fem",3], scientific = TRUE)
mod_params[mod_params$Label == "Wtlen_1_Mal",3] = format(as.numeric(mod_params[mod_params$Label == "Wtlen_1_Mal",3]), scientific = TRUE)
mod_params[mod_params$Label == "Eggs_scalar_Fem",3] = format(as.numeric(mod_params[mod_params$Label == "Eggs_scalar_Fem",3]), scientific = TRUE)
mod_params[mod_params$Label == "L_at_Amax_Mal_GP_1",3] = round(as.numeric(mod_params[mod_params$Label == "L_at_Amax_Mal_GP_1",3]), 4)
mod_params[mod_params$Label == "VonBert_K_Mal_GP_1",3] = round(as.numeric(mod_params[mod_params$Label == "VonBert_K_Mal_GP_1",3]), 3)
mod_params[mod_params$Label == "CV_old_Mal_GP_1",3] = round(as.numeric(mod_params[mod_params$Label == "CV_old_Mal_GP_1",3]), 3)
# Remove the max, prior and prior sd columns
drops = c('Max', 'Prior', 'Pr_type', 'Pr_SD', 'Num')
mod_params = mod_params[, !(names(mod_params) %in% drops)]
rownames(mod_params) = c()
mod_params[,"Label"] = gsub("\\_", " ", mod_params[,"Label"])
mod_params[,"PR_type"] = gsub("\\_", " ", mod_params[,"PR_type"])
# Add column names
col_names = c('Parameter',
                         'Value',
                         'Phase',
                         'Bounds',
                         'Status',
                         'SD',
                         'Prior (Exp.Val, SD)')
table_format(x = mod_params,
             caption = "List of parameters used in the base model, including estimated values and standard deviations (SD), bounds (minimum and maximum), estimation phase (negative values not estimated), status (indicates if parameters are near bounds), and prior type information (mean and SD).",
             label = "params",
             align = 'l',
             col_names = col_names,
             longtable = TRUE,
             font_size = 9,
             landscape = TRUE,
             custom_width = TRUE,
             col_to_adjust = c(1,7), 
             width = c("7cm", "4cm"))                         
```

<!-- ======================================================= -->
<!-- ***********    Like Contributions  ******************** --> 
<!-- ======================================================= -->

\include{tex_tables/likelihoods.tex}

<!-- ======================================================= -->
<!-- ********  Reference Points & Management *************** --> 
<!-- ======================================================= -->

\include{tex_tables/e_ReferencePoints.tex}

<!-- ======================================================= -->
<!-- ***********       Time Series      ******************** --> 
<!-- ======================================================= -->

\include{tex_tables/TimeSeries.tex}

\newpage


<!-- ======================================================= -->
<!-- ****************     Sensitivities      *************** --> 
<!-- ======================================================= -->



<!-- ======================================================= -->
<!-- ********  Reference Points & Management *************** --> 
<!-- ======================================================= -->
