\clearpage

\floatplacement{figure}{H}

# Figures

## Data 


<!-- ======================================================= -->
<!-- ***************  life history  ************************ --> 
<!-- ======================================================= -->

```{r, results = 'asis'}
add_figure(
filein = file.path(doc_dir, "shared_figures", "copper_length_by_half_month.png"), 
caption = "Distribution of YOY copper rockfish lengths from fish genetically identified from D. Baetscher.",
label = 'copper-smurf-length')
```

\pagebreak


<!-- ====================================================================== -->  
<!-- ****************** Catches Used in the Model ************************* --> 
<!-- ====================================================================== -->  

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "catch2 landings stacked.png"), 
caption = "Landings by fleet used in the base model where catches in metric tons by fleet are stacked",
label = 'catch')
```	

\pagebreak



<!-- ====================================================================== --> 
<!-- *******************    Assessment Map      *************************** --> 
<!-- ====================================================================== --> 

```{r, results = 'asis'}
add_figure(
filein = file.path(doc_dir, "shared_figures", "map.png"), 
caption = "Map of management area and the 2023 assessments areas for copper rockfish",
label = 'ca-map')
```

\pagebreak

<!-- ====================================================================== --> 
<!-- ******************* Data Used in the Model *************************** --> 
<!-- ====================================================================== --> 

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "data_plot.png"), 
caption = "Summary of data sources used in the base model",
label = 'data-plot')
```	

\pagebreak
<!-- ======================================================= -->
<!-- *************** Commercial Data *********************** --> 
<!-- ======================================================= -->

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lendat_bubflt1mkt0.png"), 
caption = "Length composition data from the commercial dead fleet",
label = 'com-dead-len-data')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lendat_data_weighting_TA1.8_Commercial_dead.png"), 
caption = "Mean length for commercial dead fleet with 95 percent confidence intervals",
label = 'mean-com-dead-len-data')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_agefit__aggregated_across_time.png"), 
caption = "Age composition data from the commercial dead and recreational CPFV fleets. The commercial samples were all from 2022 and the CPFV samples were all from 1975",
label = 'com-dead-age-data')
```

\pagebreak


```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lendat_bubflt2mkt0.png"), 
caption = "Length composition data from the commercial live fleet",
label = 'com-live-len-data')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lendat_data_weighting_TA1.8_Commercial_live.png"), 
caption = "Mean length for commercial live fleet with 95 percent confidence intervals",
label = 'mean-com-live-len-data')
```

\pagebreak

<!-- ======================================================= -->
<!-- ************* Recreational Indices ******************** --> 
<!-- ======================================================= -->


```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "index9_standcpueall.png"), 
caption = "Standardized indices overlaid with each index rescaled to have a mean observation equal to 1.0. Note, the MRFSS CPFV (Rec_CPFV) fishery-dependent index of abundance was not fit in the model but is included here for illustration.",
label = 'stand-cpue')
```

\pagebreak


```{r, results = 'asis'}
add_figure(
filein = file.path(data_dir, "rec_indices", "crfs_cpfv_onboard", "south",  "main_effects", "Index.png"), 
caption = "Estimated annual index of abundances for the CPFV fleet based on CRFS survey data.",
label = 'crfs-index-main')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(data_dir, "rec_indices", "crfs_pr_dockside", "south",  "rm_last2yrs", "Index.png"), 
caption = "Estimated annual index of abundances for the CPFV fleet based on CRFS survey data.",
label = 'crfs-pr-index-main')
```

\pagebreak

<!-- ======================================================= -->
<!-- ************* Recreational Data *********************** --> 
<!-- ======================================================= -->

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lendat_bubflt3mkt0_page2.png"), 
caption = "Length composition data from the recreational CPFV fleet",
label = 'rec-cpfv-len-data')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lendat_data_weighting_TA1.8_Rec_CPFV.png"), 
caption = "Mean length for recreational CPFV fleet with 95 percent confidence intervals",
label = 'mean-rec-cpfv-len-data')
```

\pagebreak


```{r, results = 'asis'}
add_figure(
filein = file.path(data_dir, "ages", "plots", "coop_crfs_length_comparison.png"), 
caption = "Comparison of all length collected by the CRFS sampling program for the CPFV fleet to the lengths from the fish with ages from the cooperative sampling program. The length distributions in the area north of Point Conception are in general agreement while the distribution of lengths collected by this program does not align with the length samples from CRFS.",
label = 'coop-len-comparison')
```

\pagebreak


```{r, results = 'asis'}
add_figure(
filein = file.path(data_dir, "rec_bds",  "plots", "rec_south_ggridges_lengths_cpfv_district.png"), 
caption = "Length distributions observed in the CPFV fleet by CDFW district 1 (South) and 2 (Channel) since 2004",
label = 'rec-cpfv-dist')
```

\pagebreak


```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lendat_bubflt4mkt0_page2.png"), 
caption = "Length composition data from the recreational PR fleet",
label = 'rec-pr-len-data')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lendat_data_weighting_TA1.8_Rec_Private.png"), 
caption = "Mean length for recreational PR fleet with 95 percent confidence intervals",
label = 'mean-rec-pr-len-data')
```

\pagebreak


<!-- ======================================================= -->
<!-- *************  Add Survey Locations Map  ************** --> 
<!-- ======================================================= -->

```{r, results = 'asis'}
add_figure(
filein = file.path(data_dir, "plots", "SouthernCAAllData_blocklabeled.png"), 
caption = "Sample locations from each of the fishery-independent data source indicating the number of observations across all years. The yellow outline indicates the location of MPAs. The CDFW area blocks are indicated by the numerical values inside each grid area with blocks were copper rockfish would be expected to be found are shaded darker blue.",
label = 'survey-locations')
```

\pagebreak


<!-- ======================================================= -->
<!-- ***************     CCFRP           ******************* --> 
<!-- ======================================================= -->

```{r, results = 'asis'}
add_figure(
filein = file.path(data_dir, "survey_indices", "ccfrp", "south", "area_weighted", "Index.png"), 
caption = "Estimated CCFRP Hook and Line survey index of abundance for copper rockfish.",
label = 'ccfrp-index-main')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lendat_bubflt5mkt0.png"), 
caption = "Length composition data from the CCFRP Hook and Line survey",
label = 'ccfrp-len-data')
```

\pagebreak


```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lendat_data_weighting_TA1.8_CCFRP.png"), 
caption = "Mean length for the CCFRP Hook and Line survey with 95 percent confidence intervals",
label = 'ccfrp-mean-len-data')
```

\pagebreak


```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_gstagedat_bubflt5mkt0.png"), 
caption = "Age composition data from the CCFRP Hook and Line survey",
label = 'ccfrp-age-data')
```

\pagebreak


<!-- ======================================================= -->
<!-- ***************  NWFSC HKL Survey   ******************* --> 
<!-- ======================================================= -->

```{r, results = 'asis'}
add_figure(
filein = file.path(data_dir, "survey_indices", "nwfsc_hkl", "maps", "Map_HL_Sites_lndscp.jpg"), 
caption = "Area sampled by the NWFSC Hook and Line survey",
label = 'nwfsc-hkl-map')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(data_dir, "survey_indices", "nwfsc_hkl", "plots", "hkl_copper_by_site_count_all_years.png"), 
caption = "Observations of copper rockfish by the NWFSC Hook and Line survey by sample area, inside and outside Cowcod Conservation areas (CCA)",
label = 'nwfsc-hkl-site')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(data_dir, "survey_indices", "nwfsc_hkl", "plots", "raw_cpue_nwfsc_hkl_by_mpa_vs_open_by_region.png"), 
caption = "Raw CPUE inside and outside protected areas by region sampled by the NWFSC Hook and Line survey.",
label = 'nwfsc-hkl-region-main')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(data_dir, "survey_indices", "nwfsc_hkl", "plots", "nwfsc_hkl_observations_by_depth.png"), 
caption = "Number of observations by depth (m) inside and outside the CCAs by the NWFSC Hook and Line survey.",
label = 'nwfsc-hkl-depth')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(data_dir, "survey_indices", "nwfsc_hkl", "glm_delta_lognormal_year_area_depth_drop_vermilion_bocaccio_all_areas_re_site_area_weighted", "Index.png"), 
caption = "Estimated NWFSC Hook and Line survey index of abundance for copper rockfish.",
label = 'nwfsc-hkl-index-main')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(data_dir, "survey_indices", "nwfsc_hkl", "plots", "hkl_observations_by_length_sex_area.png"), 
caption = "Observed length (cm) distribution of copper rockfish by the NWFSC Hook and Line survey by sample area, inside and outside Cowcod Conservation areas (CCA)",
label = 'nwfsc-hkl-site-len')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lendat_bubflt7mkt0.png"), 
caption = "Length composition data from the NWFSC Hook and Line survey",
label = 'hkl-len-data')
```

\pagebreak


```{r, results = 'asis'}
add_figure(
filein = file.path(data_dir, "survey_indices", "nwfsc_hkl", "plots", "nwfsc_hkl_age_at_length.png"), 
caption = "Age and length by sex for copper rockfish in the NWFSC Hook and Line survey.",
label = 'nwfsc-hkl-len-age')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lendat_data_weighting_TA1.8_NWFSC_HKL.png"), 
caption = "Mean length for NWFSC Hook and Line survey with 95 percent confidence intervals",
label = 'mean-hkl-len-data')
```

\pagebreak

<!-- ======================================================= -->
<!-- ***************     ROV             ******************* --> 
<!-- ======================================================= -->

```{r, results = 'asis'}
sa4ss::add_figure(
filein = file.path(data_dir, "survey_indices", "rov", "plots", "rov_transect_collapsed_copper_south_protection_count.png"), 
caption = "The location and size of observations across all years and transects for the CDFW ROV survey for copper rockfish.",
label = 'rov-obs-loc')
```

\pagebreak

```{r, results = 'asis'}
sa4ss::add_figure(
filein = file.path(data_dir, "survey_indices", "rov", "plots", "south_raw_cpue_by_mpa_group_by_year.png"), 
caption = "The trend of the calculated CPUE by each MPA and Reference group by year from the CDFW ROV survey.",
label = 'rov-raw-cpue')
```

\pagebreak

```{r, results = 'asis'}
sa4ss::add_figure(
filein = file.path(data_dir, "survey_indices", "rov", "plots", "rov_length_by_area_designation_april_data.png"), 
caption = "The distribution of lengths across all years for MPA and Reference areas north and south of Point Conception from the CDFW ROV survey.",
label = 'rov-len')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lendat_bubflt6mkt0.png"), 
caption = "Length composition data from the CDFW ROV survey",
label = 'rov-len-data')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lendat_data_weighting_TA1.8_CDFW_ROV.png"), 
caption = "Mean length for the CDFW ROV survey with 95 percent confidence intervals",
label = 'mean-rov-len-data')
```

\pagebreak



<!-- ======================================================= -->
<!-- ***************     Growth Data      ****************** --> 
<!-- ======================================================= -->


```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lendat_flt9mkt0.png"), 
caption = "Length distribution by year for fish sampled by the NWFSC WCGBT survey.",
label = 'growth-wcgbt-len')
```

\pagebreak



```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lendat_data_weighting_TA1.8_WCGBT_Growth.png"), 
caption = "Mean length distribution by year for fish sampled by the NWFSC WCGBT survey.",
label = 'growth-mean-wcgbt-len')

```

\pagebreak


```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lendat_flt10mkt0.png"), 
caption = "Length distribution by year for fish sampled by the Pearson Research study (2005-2007) and the CPFV cooperative collection program (2022).",
label = 'growth-coop-len')
```

\pagebreak



```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lendat_data_weighting_TA1.8_COOP_Growth.png"), 
caption = "Mean length distribution by year for fish sampled by the Pearson Research Program (2005-2007) and the CPFV cooperative colletion program (2022).",
label = 'growth-mean-coop-len')
```

\pagebreak



```{r, results = 'asis'}
add_figure(
filein = file.path(data_dir, "ages",  "plots", "south_growth_length_comparison.png"), 
caption = "Length distribution of fish by collection source that were used as conditional age-at-length data in the growth fleet.",
label = 'growth-len-dist')
```

\pagebreak


```{r, results = 'asis'}
add_figure(
filein = file.path(data_dir, "ages",  "plots", "south_growth_age_comparison.png"), 
caption = "Age distribution of fish by collection source that were used as conditional age-at-length data in the growth fleet.",
label = 'growth-age-dist')
```

\pagebreak

<!-- ======================================================= -->
<!-- ***************  NWFSC WCGBT Survey  ****************** --> 
<!-- ======================================================= -->

```{r, results = 'asis'}
add_figure(
filein = file.path(data_dir, "wcgbt", "south", "plots", "cpue_map.png"), 
caption = "Location and catch-per-unit-effort by location south of Point Conception by the NWFSC WCGBT survey.",
label = 'wcgbt-cpue')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(data_dir, "wcgbt", "south", "plots", "presence-absence_proportion_by_depth.png"), 
caption = "Number of positive tows from the NWFSC WCGBT survey across all years by depth in meters.",
label = 'wcgbt-depth')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(data_dir, "wcgbt", "plots", "wcgbt_south_age_at_length_by_area.png"), 
caption = "Age and length by sex for copper rockfish caught south of Point Conception by the NWFSC WCGBT survey.",
label = 'wcgbt-len-age')
```

\pagebreak

## Biology


<!-- ======================================================= -->  
<!-- ******************   Biology  ************************* --> 
<!-- ======================================================= -->  

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "bio6_maturity.png"), 
caption = "Maturity as a function of length",
label = 'maturity')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "bio9_fecundity_len.png"), 
caption = "Fecundity as a function of length",
label = 'fecundity')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(data_dir, "wcgbt", "plots", "length_fraction_female.png"), 
caption = "Fraction of each sex by length by the NWFSC WCGBT survey",
label = 'frac-sex-len')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(data_dir, "biology", "plots", "Length_Weight_All.png"), 
caption = "Estimated weight-at-length",
label = 'weight-length')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(data_dir, "ages", "ageing_error", "B0_S3", "Reader_1_vs_Reader_2.png"), 
caption = "Distribution of double reads between age reader 1 and 2.",
label = 'age-error-dist')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots",  "numbers5_ageerrorSD.png"), 
caption = "Ageing imprecision standard deviation of observed age in years.",
label = 'age-error')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots",  "numbers10_ageerror_matrix_1.png"), 
caption = "Distribution of observed age at true age for ageing error type 1.",
label = 'age-error-matrix')
```

\pagebreak

## Model Results

### Bridging

<!-- ======================================================= -->  
<!-- ******************   Bridge   ************************* --> 
<!-- ======================================================= -->

```{r, results = 'asis'}
add_figure(
filein = file.path(bridge_dir, "_plots", "0_model_convert_compare2_spawnbio_uncertainty.png"),
caption = "Model version bridge comparison of estimated spawning output",
label = 'bridge-ssb')
```

\pagebreak

```{r, results = 'asis'}

add_figure(
filein = file.path(bridge_dir, "_plots", "0_model_convert_compare4_Bratio_uncertainty.png"),
caption = "Model version bridge comparison of estimated fraction unfished",
label = 'bridge-depl')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(bridge_dir, "_plots", "full_bridge_1_compare2_spawnbio_uncertainty.png"),
caption = "Model structure and data bridging comparison of estimated spawning output",
label = 'data-bridge-ssb-1')
```

\pagebreak

```{r, results = 'asis'}

add_figure(
filein = file.path(bridge_dir, "_plots", "full_bridge_1_compare4_Bratio_uncertainty.png"),
caption = "Model structure and data bridging comparison of estimated fraction unfished",
label = 'data-bridge-depl-1')
```

\pagebreak


```{r, results = 'asis'}
add_figure(
filein = file.path(bridge_dir, "_plots", "full_bridge_2_compare2_spawnbio_uncertainty.png"),
caption = "Model structure and data bridging comparison of estimated spawning output",
label = 'data-bridge-ssb-2')
```

\pagebreak

```{r, results = 'asis'}

add_figure(
filein = file.path(bridge_dir, "_plots", "full_bridge_2_compare4_Bratio_uncertainty.png"),
caption = "Model structure and data bridging comparison of estimated fraction unfished",
label = 'data-bridge-depl-2')
```

\pagebreak


<!-- ====================================================================== -->
<!-- *********************   CA Regulations Figure   ********************** --> 
<!-- ====================================================================== -->

### Model Structure

```{r, results = 'asis'}

add_figure(
filein = file.path(management_dir, "fishing_regs.png"),
caption = "The CDFW recreational season length and depth restriction for nearshore rockfish by month from 2000 to 2003. A triangle indicates a regulation change mid-month. The regions defined base on the following latitudes: Northern ($42^\\circ 00^\\prime$ N. lat. to $40^\\circ 10^\\prime$ N. lat.), Mendocino ($40^\\circ 10^\\prime$ N. lat. to $38^\\circ 57^\\prime$ N. lat.), San Francisco ($38^\\circ 57^\\prime$ N. lat. to $37^\\circ 11^\\prime$ N. lat.), Central ($37^\\circ 11^\\prime$ N. lat. to $34^\\circ 27^\\prime$ N. lat.), Southern ($34^\\circ 27^\\prime$ N. lat. to U.S./Mexico border). Not all management areas have been consistently defined over time. The northern  and southern management areas have remained the same. From 2001-2003 the Central management area was defined as $40^\\circ 10^\\prime$ N. lat. to  $34^\\circ 27^\\prime$ N. lat. In 2004, the Central area was split into a North-Central and South-Central areas at $36^\\circ 00^\\prime$ N. lat. In 2005, the regions from $40^\\circ 10^\\prime$ N lat. to $34^\\circ 27^\\prime$ N. lat. were redefined. The North-Central encompasses $40^\\circ 10^\\prime$ N. lat. to $37^\\circ 11^\\prime$ N. lat., Monterey South-Central from $37^\\circ 11^\\prime$ N. lat. to $36^\\circ 00^\\prime$ N. lat., and Morro Bay South-Central from $36^\\circ 00^\\prime$ N. lat. to $34^\\circ 27^\\prime$ N. lat.",
label = 'depth-closures')
```

\pagebreak


<!-- ====================================================================== -->
<!-- *********************    Priors            ********************** --> 
<!-- ====================================================================== -->


<!-- ====================================================================== -->
<!-- *********************  Model Est. Biology       ********************** --> 
<!-- ====================================================================== -->

### Estimated Biology


```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "bio1_sizeatage.png"),
caption = "Model estimated length-at-age in the beginning of the year. Shaded area indicates 95 percent distribution of length-at-age around the estimated growth curve",
label = 'mod-est-len-age')
```

\pagebreak

### Selectivity

<!-- ====================================================================== -->
<!-- *********************    Selectivity            ********************** --> 
<!-- ====================================================================== -->


```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "south_selectivity.png"),
caption = "Estimated selectivity for each fleet and survey in the base model.",
label = 'est-selex')
```

\newpage

### Recruitment

<!-- ======================================================= -->  
<!-- ****************** Recruitment ************************ --> 
<!-- ======================================================= -->

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "ts11_Age-0_recruits_(1000s)_with_95_asymptotic_intervals.png"), 
caption = "Estimated time series of age-0 recruits (1000s)",
label = 'recruits')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "recdevs2_withbars.png"), 
caption = "Estimated time series of recruitment deviations",
label = 'rec-devs')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "SR_curve2.png"), 
caption = "Stock-recruit curve with labels on first, last, and years with log-deviations greater than 0.50.♣ Point colors indicate year, with warmer colors indicating earlier years and cooler colors in showing later years",
label = 'bh-curve')
```

\pagebreak


```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "recruit_fit_bias_adjust.png"), 
caption = "Points are transformed variances. Red line shows current settings for bias adjustment specified in control file. Blue line shows least squares estimate of alternative bias adjustment relationship for recruitment deviations (which may or may not be an improvement)",
label = 'bias-adjust')
```

\newpage

### Fits to Data

<!-- ====================================================================== -->
<!-- *************** Fit to the Length & Age Data  ************************ --> 
<!-- ====================================================================== -->


```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots",  "comp_lenfit__aggregated_across_time.png"), 
caption = "Length composition aggregated across years by fleet with the model estimated fit to the data by sex (green unsexed, red female, and blue male).",
label = 'len-agg-fit')
```

\pagebreak


```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lenfit_residsflt1mkt0.png"), 
caption = "Pearson residuals for commercial fleet. Closed bubbles are positive residuals (observed > expected) and open bubbles are negative residuals (observed < expected)",
label = 'com-dead-pearson')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lenfit_data_weighting_TA1.8_Commercial_dead.png"), 
caption = "Mean length for commercial dead lengths with 95 percent confidence intervals based on current samples sizes",
label = 'com-dead-mean-len-fit')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_agefit__aggregated_across_time.png"), 
caption = "Age composition data aggregated across time by fleet.",
label = 'agg-marg-age-fit')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_agefit_residsflt1mkt0.png"), 
caption = "Pearson residuals for commercial dead age data. Closed bubbles are positive residuals (observed > expected) and open bubbles are negative residuals (observed < expected)",
label = 'com-dead-age-pearson')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lenfit_residsflt2mkt0.png"), 
caption = "Pearson residuals for commercial live fleet. Closed bubbles are positive residuals (observed > expected) and open bubbles are negative residuals (observed < expected)",
label = 'com-live-pearson')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lenfit_data_weighting_TA1.8_Commercial_live.png"), 
caption = "Mean length for commercial live fish lengths with 95 percent confidence intervals based on current samples sizes",
label = 'com-live-mean-len-fit')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lenfit_residsflt3mkt0_page2.png"), 
caption = "Pearson residuals for recreational CPFV fleet. Closed bubbles are positive residuals (observed > expected) and open bubbles are negative residuals (observed < expected)",
label = 'rec-cpfv-pearson')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lenfit_data_weighting_TA1.8_Rec_CPFV.png"), 
caption = "Mean length for recreational CPFV lengths with 95 percent confidence intervals based on current samples sizes",
label = 'rec-cpfv-mean-len-fit')
```

\pagebreak


```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_agefit_residsflt3mkt0.png"), 
caption = "Pearson residuals for recreational CPFV age data. Closed bubbles are positive residuals (observed > expected) and open bubbles are negative residuals (observed < expected)",
label = 'rec-cpfv-age-pearson')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lenfit_residsflt4mkt0_page2.png"), 
caption = "Pearson residuals for recreational private/rental fleet. Closed bubbles are positive residuals (observed > expected) and open bubbles are negative residuals (observed < expected)",
label = 'rec-pr-pearson')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lenfit_data_weighting_TA1.8_Rec_Private.png"), 
caption = "Mean length for recreational private/rental lengths with 95 percent confidence intervals based on current samples sizes",
label = 'rec-pr-mean-len-fit')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lenfit_residsflt5mkt0.png"), 
caption = "Pearson residuals for CCFRP Hook and Line survey length data. Closed bubbles are positive residuals (observed > expected) and open bubbles are negative residuals (observed < expected)",
label = 'ccfrp-len-pearson')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lenfit_data_weighting_TA1.8_CCFRP.png"), 
caption = "Mean length for CCFRP Hook and Line survey lengths with 95 percent confidence intervals based on current samples sizes",
label = 'ccfrp-mean-len-fit')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_condAAlfit_residsflt5mkt0.png"), 
caption = "Pearson residuals for CCFRP Hook and Line survey conditional-age-at-length data. Closed bubbles are positive residuals (observed > expected) and open bubbles are negative residuals (observed < expected)",
label = 'ccfrp-age-pearson')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lenfit_residsflt6mkt0.png"), 
caption = "Pearson residuals for CDFW ROV survey length data. Closed bubbles are positive residuals (observed > expected) and open bubbles are negative residuals (observed < expected)",
label = 'rov-pearson')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lenfit_data_weighting_TA1.8_CDFW_ROV.png"), 
caption = "Mean length for CDFW ROV survey lengths with 95 percent confidence intervals based on current samples sizes",
label = 'rov-mean-len-fit')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lenfit_residsflt7mkt0.png"), 
caption = "Pearson residuals for NWFSC Hook and Line survey length data. Closed bubbles are positive residuals (observed > expected) and open bubbles are negative residuals (observed < expected)",
label = 'nwfsc-hkl-pearson')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lenfit_data_weighting_TA1.8_NWFSC_HKL.png"), 
caption = "Mean length for NWFSC Hook and Line survey lengths with 95 percent confidence intervals based on current samples sizes",
label = 'nwfsc-hkl-mean-len-fit')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_condAALfit_residsflt7mkt0_page1.png"), 
caption = "Pearson residuals for NWFSC Hook and Line survey conditional-age-at-length data. Closed bubbles are positive residuals (observed > expected) and open bubbles are negative residuals (observed < expected)",
label = 'nwfsc-hkl-age-pearson-1')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_condAALfit_residsflt7mkt0_page2.png"), 
caption = "Pearson residuals for NWFSC Hook and Line survey conditional-age-at-length data. Closed bubbles are positive residuals (observed > expected) and open bubbles are negative residuals (observed < expected)",
label = 'nwfsc-hkl-age-pearson-2')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_condAALfit_residsflt7mkt0_page3.png"), 
caption = "Pearson residuals for NWFSC Hook and Line survey conditional-age-at-length data. Closed bubbles are positive residuals (observed > expected) and open bubbles are negative residuals (observed < expected)",
label = 'nwfsc-hkl-age-pearson-3')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_condAALfit_data_weighting_TA1.8_condAgeNWFSC_HKL.png"), 
caption = "Mean age for NWFSC Hook and Line survey age data with 95 percent confidence intervals based on current samples sizes",
label = 'nwfsc-hkl-mean-age-fit')
```

\pagebreak


```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lenfit_residsflt9mkt0.png"), 
caption = "Pearson residuals for NWFSC WCGBT survey fleet length data. Closed bubbles are positive residuals (observed > expected) and open bubbles are negative residuals (observed < expected)",
label = 'wcgbt-len-pearson')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lenfit_data_weighting_TA1.8_WCGBT_Growth.png"), 
caption = "Mean length for the NWFSC WCGBT survey lengths with 95 percent confidence intervals based on current samples sizes",
label = 'wcgbt-mean-len-fit')
```

\pagebreak


```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_condAALfit_residsflt9mkt0_page1.png"), 
caption = "Pearson residuals for the NWFSC WCGBT survey conditional-age-at-length data. Closed bubbles are positive residuals (observed > expected) and open bubbles are negative residuals (observed < expected)",
label = 'wcgbt-age-pearson-1')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_condAALfit_residsflt9mkt0_page2.png"), 
caption = "Pearson residuals for the NWFSC WCGBT survey conditional-age-at-length data. Closed bubbles are positive residuals (observed > expected) and open bubbles are negative residuals (observed < expected)",
label = 'wcgbt-age-pearson-2')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_condAALfit_residsflt9mkt0_page3.png"), 
caption = "Pearson residuals for the NWFSC WCGBT survey conditional-age-at-length data. Closed bubbles are positive residuals (observed > expected) and open bubbles are negative residuals (observed < expected)",
label = 'wcgbt-age-pearson-3')
```

\pagebreak


```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_condAALfit_data_weighting_TA1.8_condAgeWCGBT_Growth.png"), 
caption = "Mean age for the NWFSC WCGBT survey age data with 95 percent confidence intervals based on current samples sizes",
label = 'wcgbt-mean-age-fit')
```

\pagebreak


```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lenfit_residsflt10mkt0.png"), 
caption = "Pearson residuals for Pearson and CPFV cooperative collection length data. Closed bubbles are positive residuals (observed > expected) and open bubbles are negative residuals (observed < expected)",
label = 'coop-len-pearson')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lenfit_data_weighting_TA1.8_COOP_Growth.png"), 
caption = "Mean length for the Pearson and CPFV cooperative collection lengths with 95 percent confidence intervals based on current samples sizes",
label = 'coop-mean-len-fit')
```

\pagebreak


```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_condAALfit_residsflt10mkt0.png"), 
caption = "Pearson residuals for the Pearson and CPFV cooperative collection conditional-age-at-length data. Closed bubbles are positive residuals (observed > expected) and open bubbles are negative residuals (observed < expected)",
label = 'coop-age-pearson')
```

\pagebreak


```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_condAALfit_data_weighting_TA1.8_condAgeCOOP_Growth.png"), 
caption = "Mean age for the Pearson and CPFV cooperative collection age data with 95 percent confidence intervals based on current samples sizes",
label = 'coop-mean-age-fit')
```

\pagebreak


<!-- ======================================================= -->  
<!-- ************* Fit to the Indices ********************** --> 
<!-- ======================================================= -->


```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "index5_logcpuefit_CRFS_CPFV.png"), 
caption = "Fit to log index data on log scale for the recreational CRFS CPFV index of abundance. Lines indicate 95% uncertainty interval around index values based on the model assumption of lognormal error. Thicker lines indicate input uncertainty before addition of estimated additional uncertainty parameter.",
label = 'crfs-cpfv-index-fit')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "index5_logcpuefit_Rec_Private.png"), 
caption = "Fit to log index data on log scale for the recreational private index of abundance. Lines indicate 95% uncertainty interval around index values based on the model assumption of lognormal error. Thicker lines indicate input uncertainty before addition of estimated additional uncertainty parameter.",
label = 'crfs-pr-index-fit')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "index5_logcpuefit_CCFRP.png"), 
caption = "Fit to log index data on log scale for the CCFRP Hook and Line survey index of abundance. Lines indicate 95% uncertainty interval around index values based on the model assumption of lognormal error. Thicker lines indicate input uncertainty before addition of estimated additional uncertainty parameter.",
label = 'ccfrp-index-fit')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "index5_logcpuefit_CDFW_ROV.png"), 
caption = "Fit to log index data on log scale for the CDFW ROV index of abundance. Lines indicate 95% uncertainty interval around index values based on the model assumption of lognormal error. Thicker lines indicate input uncertainty before addition of estimated additional uncertainty parameter.",
label = 'rov-index-fit')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "index5_logcpuefit_NWFSC_HKL.png"), 
caption = "Fit to log index data on log scale for the NWFSC Hook and Line index of abundance. Lines indicate 95% uncertainty interval around index values based on the model assumption of lognormal error. Thicker lines indicate input uncertainty before addition of estimated additional uncertainty parameter.",
label = 'nwfsc-hkl-index-fit')
```

\pagebreak

### Time-series

<!-- ======================================================= -->  
<!-- ****************** Time Series ************************ --> 
<!-- ======================================================= -->


```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "ts7_Spawning_output_with_95_asymptotic_intervals_intervals.png"), 
caption = "Estimated time series of spawning output for the area south of Point Conception in California.",
label = 'ssb')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "ts1_Total_biomass_(mt).png"), 
caption = "Estimated time series of total biomass for the area south of Point Conception in California",
label = 'tot-bio')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "ts9_Relative_spawning_output_intervals.png"), 
caption = "Estimated time series of relative spawning output for the area south of Point Conception in California",
label = 'depl')
```

\pagebreak


```{r, results = 'asis'}
add_figure(
filein = file.path(doc_dir, "shared_figures", "spawning_output_combined.png"), 
caption = "Estimated combined time series of spawning output for copper rockfish in California waters",
label = 'sb-all')

```


\clearpage


```{r, results = 'asis'}
add_figure(
filein = file.path(doc_dir, "shared_figures", "depletion_combined.png"), 
caption = "Estimated combined time series of relative spawning output for copper rockfish in California waters",
label = 'depl-all')

```

\clearpage

### Sensitivity Analyses and Retrospectives

<!-- ====================================================================== -->
<!-- ******************      Sensitivities    ***************************** --> 
<!-- ====================================================================== -->

 
```{r, echo=FALSE, results='asis'}
add_figure(
filein = file.path(sens_dir, "_plots",  "Sensi_REplot_structure_horizontal"),
caption = "Comparison of the relative change in estimated management quantities as compared to the base model for structural sensitivities. The quantities compared are the estimate of unfished spawning biomass (SB~0~), spawning output in 2023 (SB~2023~), the relative spawning output (SB~2023~/SB~0~), the yield based on a spawner per recruit harvest rate (Yield~SPR=0.50~), and the fishing mortality at that harvest rate (F~SPR=0.50~). The colored boxes indicate the 95 percent confidence interval around the point estimate of the quantity from the base model where each color corresponds with a specific quantity in the legend.  A model with matching estimates as the base model would reflect a relative change of 0, a model with estimates less than the base model would have a negative relative change, and a model with estimates greater than the base model would have a positive relative change.",
label = 'sens-structure')
```


\newpage


 
```{r, echo=FALSE, results='asis'}
add_figure(
filein = file.path(sens_dir, "_plots",  "Sensi_REplot_data_horizontal"),
caption = "Comparison of the relative change in estimated management quantities as compared to the base model for data sensitivities. The quantities compared are the estimate of unfished spawning biomass (SB~0~), spawning output in 2023 (SB~2023~), the relative spawning output (SB~2023~/SB~0~), the yield based on a spawner per recruit harvest rate (Yield~SPR=0.50~), and the fishing mortality at that harvest rate (F~SPR=0.50~). The colored boxes indicate the 95 percent confidence interval around the point estimate of the quantity from the base model where each color corresponds with a specific quantity in the legend.  A model with matching estimates as the base model would reflect a relative change of 0, a model with estimates less than the base model would have a negative relative change, and a model with estimates greater than the base model would have a positive relative change.",
label = 'sens-data')
```

\newpage

 
```{r, echo=FALSE, results='asis'}
nm = paste0(south_model_name, "_final_1_compare2_spawnbio_uncertainty.png")
add_figure(
filein = file.path(sens_dir, "_plots",  nm),
caption = "Change in estimated spawning output by sensitivity",
label = 'sens-ssb-1')
```

\newpage

```{r, echo=FALSE, results='asis'}
nm = paste0(south_model_name, "_final_1_compare4_Bratio_uncertainty.png")
add_figure(
filein = file.path(sens_dir, "_plots", nm),
caption = "Change in estimated fraction unfished by sensitivity",
label = 'sens-depl-1')
```

\newpage

 
```{r, echo=FALSE, results='asis'}
nm = paste0(south_model_name, "_final_4_compare2_spawnbio_uncertainty.png")
add_figure(
filein = file.path(sens_dir, "_plots",  nm),
caption = "Change in estimated spawning output by sensitivity",
label = 'sens-ssb-4')
```

\newpage

```{r, echo=FALSE, results='asis'}
nm = paste0(south_model_name, "_final_4_compare4_Bratio_uncertainty.png")
add_figure(
filein = file.path(sens_dir, "_plots", nm),
caption = "Change in estimated fraction unfished by sensitivity",
label = 'sens-depl-4')
```

\newpage

```{r, echo=FALSE, results='asis'}
nm = paste0(south_model_name, "_final_2_compare2_spawnbio_uncertainty.png")
add_figure(
filein = file.path(sens_dir, "_plots", nm),
caption = "Change in estimated spawning output by sensitivity",
label = 'sens-ssb-2')
```

\newpage

```{r, echo=FALSE, results='asis'}
nm = paste0(south_model_name, "_final_2_compare4_Bratio_uncertainty.png")
add_figure(
filein = file.path(sens_dir, "_plots", nm),
caption = "Change in estimated fraction unfished by sensitivity",
label = 'sens-depl-2')
```

\newpage


```{r, echo=FALSE, results='asis'}
nm = paste0(south_model_name, "_final_3_compare2_spawnbio_uncertainty.png")
add_figure(
filein = file.path(sens_dir, "_plots", nm),
caption = "Change in estimated spawning output by sensitivity",
label = 'sens-ssb-3')
```

\newpage

```{r, echo=FALSE, results='asis'}
nm = paste0(south_model_name, "_final_3_compare4_Bratio_uncertainty.png")
add_figure(
filein = file.path(sens_dir, "_plots", nm),
caption = "Change in estimated fraction unfished by sensitivity",
label = 'sens-depl-3')
```

\newpage


<!-- ====================================================================== -->
<!-- ******************     Retrospectives    ***************************** --> 
<!-- ====================================================================== -->


```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text",'34_retro_figures.Rmd')
read_child(filein)
```



### Likelihood Profiles

<!-- ====================================================================== -->
<!-- ******************       Profile         ***************************** --> 
<!-- ====================================================================== -->


```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text",'34_likelihood_figures.Rmd')
read_child(filein)
```


<!-- ====================================================================== -->
<!-- ************* Comparison w/ Previous Assessments ********************** --> 
<!-- ====================================================================== -->

```{r, echo=FALSE, results='asis'}
add_figure(
filein = file.path(doc_dir, "shared_figures", "south_total_biomass_comparison.png"),
caption = "Comparison of the estimated total biomass (mt) for the base model to previous assessments in 2021 and 2013",
label = 'comp-assess-sb')
```

\newpage


```{r, echo=FALSE, results='asis'}
add_figure(
filein = file.path(doc_dir, "shared_figures", "south_assess_compare_compare4_Bratio_uncertainty.png"),
caption = "Comparison of the estimated fraction unfished for the base model to previous assessments in 2021 and 2013",
label = 'comp-assess-depl')
```

\newpage


### Reference Points and Forecasts

<!-- ====================================================================== -->
<!-- ******************    Reference Points    **************************** --> 
<!-- ====================================================================== -->


```{r, results = 'asis'}
add_figure(
filein = file.path(doc_dir, "shared_figures", "compare6_SPRratio_uncertainty.png"), 
caption = "Estimated 1 - relative spawning ratio (SPR) by year for both sub-area models south and north of Point Conception",
label = '1-spr')
```

\clearpage

```{r, results = 'asis'}
add_figure(
filein = file.path(doc_dir, "shared_figures", "compare15_phase_plot.png"), 
caption = "Phase plot of the relative biomass (also referred to as fraction unfished) versus the SPR ratio where each point represents the biomass ratio at the start of the year and the relative fishing intensity in that same year. Lines through the final point show the 95 percent intervals based on the asymptotic uncertainty for each dimension. The shaded ellipse is a 95 percent region which accounts for the estimated correlations between the biomass ratio and SPR ratio",
label = 'phase')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(doc_dir, "shared_figures", "north_yield2_yield_curve_with_refpoints.png"), 
caption = "Equilibrium yield curve for the base case model north of Point Conception. Values are based on the 2022
fishery selectivities and with steepness fixed at 0.72",
label = 'yield-north')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(doc_dir, "shared_figures", "south_yield2_yield_curve_with_refpoints.png"), 
caption = "Equilibrium yield curve for the base case model south of Point Conception. Values are based on the 2022
fishery selectivities and with steepness fixed at 0.72",
label = 'yield-south')
```

\pagebreak
