# Appendices 

## Detailed Fits to Composition Data {#detailed-fit-comps}

### Length Composition Data {#length-data}

```{r, results='asis'}
plot_info = read.csv(file.path(model_dir, "plots", "plotinfotable_for_doc.csv"))
len_fit = plot_info[which(plot_info$category == "LenComp"), ]
plot.vec = grep("comp_lenfit_flt", len_fit$label)
filein = file.path(model_dir, "plots")
for (a in plot.vec){
	cap = gsub("<br>", " ", gsub("_", " ", len_fit$caption[a]))
	lab = gsub("_", "-", len_fit$label[a])
	add_figure(filein = file.path(filein, len_fit$file[a]), 
			   caption = cap, 
			   label = lab,
			   alt_caption = "See the CompReport file for detailed information on the composition data and the model fits.")
}
```

\newpage

### Age Composition Data {#age-data}


```{r, results='asis'}
plot_info = read.csv(file.path(model_dir, "plots", "plotinfotable_for_doc.csv"))
len_fit = plot_info[which(plot_info$category == "AgeComp"), ]
plot.vec = grep("comp_agefit_flt", len_fit$label)
filein = file.path(model_dir, "plots")
for (a in plot.vec){
	cap = gsub("<br>", " ", gsub("_", " ", len_fit$caption[a]))
	lab = gsub("_", "-", len_fit$label[a])
	add_figure(filein = file.path(filein, len_fit$file[a]), 
			   caption = cap, 
			   label = lab, 
			   alt_caption = "See the CompReport file for detailed information on the composition data and the model fits.")
}
```

\newpage



### Conditional-Age-at-Length Composition Data {#caal-data}


```{r, results='asis'}
plot_info = read.csv(file.path(model_dir, "plots", "plotinfotable_for_doc.csv"))
len_fit = plot_info[which(plot_info$category == "A@LComp"), ]
plot.vec = c(grep("comp_condAALfit_residsflt5mkt0", len_fit$label),
  grep("comp_condAALfit_residsflt7mkt0", len_fit$label),
	grep("comp_condAALfit_residsflt9mkt0", len_fit$label))[-8]
find = sort(len_fit$label[plot.vec], index.return = TRUE)$ix
plot.vec = plot.vec[find[2:length(find)]]
filein = file.path(model_dir, "plots")
for (a in plot.vec){
	cap = gsub("_", " ", len_fit$caption[a])
	lab = gsub("_", "-", len_fit$label[a])
	add_figure(filein = file.path(filein, len_fit$file[a]), 
			   caption = cap, 
			   label = lab, 
			   alt_caption = "See the CompReport file for detailed information on the composition data and the model fits.")
}
```


```{r, results='asis'}
plot_info = read.csv(file.path(model_dir, "plots", "plotinfotable_for_doc.csv"))
len_fit = plot_info[which(plot_info$category == "A@LComp"), ]
plot.vec = c(grep("comp_condAALfit_Andre_plotsflt5mkt0", len_fit$label),
  grep("comp_condAALfit_Andre_plotsflt7mkt0", len_fit$label),
	grep("comp_condAALfit_Andre_plotsflt9mkt0", len_fit$label))
find = sort(len_fit$label[plot.vec], index.return = TRUE)$ix
plot.vec = plot.vec[find[2:length(find)]]
filein = file.path(model_dir, "plots")
for (a in plot.vec){
	cap = gsub("\n", ". ", gsub("%", " percent", gsub("<br>", " ", gsub("_", " ", len_fit$caption[a]))))
	lab = gsub("_", "-", len_fit$label[a])
	add_figure(filein = file.path(filein, len_fit$file[a]), 
			   caption = cap, 
			   label = lab, 
			   alt_caption = "See the CompReport file for detailed information on the composition data and the model fits.")
}

```

\pagebreak

## Implied Fits to Exluded Data {#excluded-data}

### Length Data 

The implied fits to the data not included in the base model due to low annual sample size are shown below.  

```{r, results='asis'}
plot_info = read.csv(file.path(model_dir, "plots", "plotinfotable_for_doc.csv"))
len_fit = plot_info[which(plot_info$category == "LenComp"), ]
plot.vec = c(grep("comp_gstlenfit_flt1mkt0", len_fit$label),
             grep("comp_gstlenfit_flt2mkt0", len_fit$label),
             grep("comp_gstlenfit_flt3mkt0", len_fit$label),
             grep("comp_gstlenfit_flt4mkt0", len_fit$label))
filein = file.path(model_dir, "plots")
for (a in plot.vec){
	cap = gsub("<br>", " ", gsub("_", " ", len_fit$caption[a]))
	lab = gsub("_", "-", len_fit$label[a])
	add_figure(filein = file.path(filein, len_fit$file[a]), 
			   caption = cap, 
			   label = lab,
			   alt_caption = "See the CompReport file for detailed information on the composition data and the model fits.")
}
``` 

\pagebreak


### MRFSS CPFV Fishery-Dependent Indices of Abundance

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "index5_logcpuefit_Rec_CPFV.png"), 
caption = "Implied fit to log index data on log scale for the recreational (MRFSS) CPFV index of abundance. Lines indicate 95 percent uncertainty interval around index values based on the model assumption of lognormal error. Thicker lines (if present) indicate input uncertainty before addition of estimated additional uncertainty parameter.",
alt_caption = "The implied model fit generally fits the trend in the index but the 1983 1988 and 1994 index points appear to be outliers with each year estimated well above the surrounding years. These years are well above the implied model fit.",
label = 'mrfss-cpfv-index-fit')
```

\pagebreak

### CDFW ROV Survey

Data from the CDFW ROV survey were not included in the base model. A sensitivity to the inclusion of these data were included in the Sensitivities Section \ref{sensitivities}. The estimated index of abundance from the uncorrected data (see Section \ref{cdfw-rov-not-included} for additional information) is shown below with a plot of the length composition data by year `r area`. 


```{r, results = 'asis'}
sa4ss::add_figure(
filein = file.path(model_dir, "plots", "index2_cpuefit_CDFW_ROV.png"), 
caption = "The estimated weighted relative index of abundance for the CDFW ROV survy and the implied fit to the index from the model.",
alt_caption = "The implied model fit follows the same trend as the index with the implied fit falling within the uncertainty interval for all years.",
label = 'rov-index')
```

\newpage


```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir,  "plots", "comp_gstlenfit_flt6mkt0.png"), 
caption = "Annual length composition data from the CDFW ROV survey south of Point Conception and the implied model fit given a fixed selectivity curve.",
alt_caption = "The implied model fits align with the observed annual length distributions.",
label = 'rov-len-data')
```

\pagebreak

### NWFSC WCGBT Survey Index of Abundance

Data from the NWFSC WCGBT survey were not used in the base model to develop an index of abundance. A sensitivity to the base model explored including the estimated index of abundance shown below 

```{r, results = 'asis'}
add_figure(
filein = file.path(data_dir, "survey_indices", "wcgbt", "110m_2005minyear", "copper_rockfish", "wcgbts",  "delta_lognormal_mix", "index", "index.png"), 
caption = "Estimated index of abundance based on NWFSC WCGBT survey data starting in 2005 and limiting to observations between 55-110 m where CA is the area south of Point Conception and coastwide is all data within California.",
alt_caption = "The uncertainty intervals for numerous years are large and there is no clear trend in the index likely due to limited observations",
label = 'wcgbt-index')
```

\pagebreak
