## Development of Indices of Abundance

### California Onboard CPFV Index of Abundance {#onboard-cpfv-index}


```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text",'21f_crfs_cpfv_index.Rmd')
read_child(filein)
```

We applied a number of data filters to the available data presented in Table 
\@ref(tab:onboard-filter). The onboard CPFV index restricts the time series to 2005-2019. The onboard observer survey 
began in 1999, but the sample sizes were small during the first year of the program. The 
years 1999-2004 also represent years where a number of regulations changed including gear limits, 
bag limits, and spatial closures.  Due to COVID-19, no onboard sampling took place in 2020. In 2021, the onboard sampling resumed in August, at which point a large portion of the southern California fleet had switched target species to fish highly migratory species. The 2021 stock assessment for `r spp` had also been released by August 2021 indicating the portion of the population south of Point Conception was depleted, estimated to be below the management threshold of 25 percent of unfished.  The southern California CPFV fleet began an organized effort to avoid copper rockfish and encourage their clientele to release and descend copper rockfish when encountered. In 2022, the CDFW implemented the one copper rockfish sub-bag limit and combined with avoidance by the fleet, the data in this year does not represent the available copper rockfish biomass. 

The data filters also included the removal of the number of observed anglers and time fished at the tail ends of the distributions, and removal of drifts occurring in depths outside the expected range of copper rockfish (Table \@ref(tab:onboard-filter) and Figure \@ref(fig:onboard-depths)). The availability of high resolution data were lacking for the area south of Point Conception, hence, we retained all drifts from within a CDFW block that had at least 100 drifts and at least 5 percent of those encountered copper rockfish. A total of 17,605 drifts were retained for index standardization with 3,035 of those drifts encountered copper rockfish (Table \@ref(tab:onboard-percentpos). 

In the assessment model, the recreational CPFV fleet is modeled as retained plus discarded fish. The proportion of observed discarded copper rockfish is small, averaging 4 percent over the time series (Table \@ref(tab:onboard-keepdiscard)) and are included in the index. We modeled catch per angler minutes fished (CPUE) by fishing drift. Prior to any modeling, the SWFSC QA/QC'd the data to ensure the location information was correct. Each drift was overlaid in ArcPro with the available interpreted substrate layer that characterizes rocky and hard substrate, assigned to a rocky reef and the distance of the drift start location calculated. In addition, the depth of the start location was interpreted from the 2 m resolution bathymetry as well as 90 m resolution bathymetry layer for comparison. For drifts missing depth location, we assigned depth based on the best available depth based on the bathymetry.

To appropriately weight the onboard observer survey index by the available 
rocky substrate within a region, each drift was assigned to the closest area 
of rocky habitat. Hard bottom was extracted from 
the [California Seafloor Mapping Project](http://seafloor.otterlabs.org/index.html), 
along the mainland coast of southern California. These data 
were collected in state waters at a resolution of two meters, but did not extend into state waters 
past the mainland coast. Additional interpreted bathymetric data classifying the bottom type as 
rock or soft bottom were compiled by analysts at the University of California Santa Cruz and are now
also available from CDFW's website. We used the available interpreted rocky substrate data to expand the 
known area of rocky substrate to areas in southern California that lack substrate type.  This 
expansion of the estimated rocky substrate assumes that the proportions of rocky substrate within 
and outside state waters are similar. Copper rockfish are a nearshore species and the majority of 
observed encounters were within state waters (Table \@ref(tab:onboard-waterarea)). This is, of course, an estimation of the amount of rocky substrate, and represents the best available data. The calculations can be found in the online supplementary material.

The covariates explored for model selection included year and four categorical region levels (District 1 mainland, District 2 mainland, Southern Channel Islands and Northern Channel Islands), a year and area interaction, a categorical variable for month, and continuous depth and depth-squared. Trends in the average CPUE by region were similar 
in the filtered data set (Figure \@ref(fig:onboard-regioncpue)). A year and region interaction 
was included after visualizing the trends in average CPUE over time. The full model was selected by AICc 
(Table \@ref(tab:onboard-modelselect)). In southern California, whether a trip is a half-day or three-quarter-day or overnight trip has a significant impact on the available fishing grounds.  The half-day CPFV vessels fish in the shallower, nearshore waters along the along the mainland coast. The three-quarter and overnight or multi-day
vessels are able to access the same areas of the Northern Channel Islands, where as the southern Channel Islands 
are further offshore and the observations are predominantly from overnight trips. The overnight and 
multi-day trips may target multiple target species, i.e., tuna and rockfish, depending on the time of the year.

Indices were fit via MLE from the sdmTMB package in R. The Q-Q plot for the negative binomial 
model indicated a poor fit to the data, which as not surprising given the low percent of observed drifts encountering copper rockfish. A delta-lognormal error distribtuion was selected over a delta-gamma based on AIC.  The Q-Q plot indicated a much improved fit compared to the negative binomial model (Table \@ref(fig:onboard-qq)).

The final index was weighted based on the estimates of rocky substrate within each of the four regions. 
The relative abundance increases during the first part of the time series (Table \@ref(tab:onboard-index) 
and Figure \@ref(fig:onboard-index)).  

\newpage

<!--Tables -->

```{r, results = 'asis'}
library(dplyr)
ind <- read.csv(file.path(data_dir, "rec_indices", "crfs_cpfv_onboard", "south",
                    "keep_discard_prop.csv")) %>%
  mutate(Proportion.discarded = scales::percent(round(Proportion.discarded,3)))
col_names = c("Year",	"Number Kept",	"Number Discarded", "Proportion discarded")

sa4ss::table_format(x = ind,
             caption = "Number of observed copper rockfish retained and discarded by year.",
             label = "onboard-keepdiscard",
             col_names = col_names)                         
```

\newpage

```{r, results = 'asis'}
ind <- read.csv(file.path(data_dir, "rec_indices", "crfs_cpfv_onboard", "south",
                    "start2005", "target_water_area.csv")) %>%
  mutate(percent_N = scales::percent(round(percent_N, 3)))
col_names = c("District", "Year", "Inside State Waters",	"Outside State Waters",
               "Percent Inside")

sa4ss::table_format(x = ind,
             caption = "Number of observed drifts inside and outside of state waters.",
             label = "onboard-waterarea",
             col_names = col_names)                         
```


\newpage

```{r, results = 'asis'}
ind <- read.csv(file.path(data_dir, "rec_indices", "crfs_cpfv_onboard", "south",
                    "start2005", "percent_pos.csv")) %>%
  mutate(percentpos = scales::percent(round(percentpos, 3)))
col_names = c("Year" ,"Trips with Target", "Trips without Target", "Total trips", "Percent with Target")

sa4ss::table_format(x = ind,
             caption = "Retain trips and the number of trips with target species for the onboard CPFV survey.",
             label = "onboard-percentpos",
             col_names = col_names)
```

\newpage


```{r, results = 'asis'}
ind <- read.csv(file.path(data_dir, "rec_indices", "crfs_cpfv_onboard", "south",
                          "start2005", "data_filters.csv"))
col_names = c("Filter",	"Description",	"Number of Samples", "Positive Samples")

sa4ss::table_format(x = ind,
             caption = "Data filtering steps for the onboard CPFV survey.",
             label = "onboard-filter",
             col_names = col_names,
             landscape = TRUE,
             align = 'l',
             custom_width = TRUE,
             col_to_adjust = c(2),
             width = c('6cm'))
```


\newpage

```{r, results = 'asis'}
ind <- read.csv(file.path(data_dir, "rec_indices", "crfs_cpfv_onboard", "south",
                    "model_selection.csv"))

sa4ss::table_format(x = ind,
             caption = "Model selection for the onboard CPFV survey.",
             label = "onboard-modelselect")                         
```


\newpage

```{r, results = 'asis'}

ind <- read.csv(file.path(data_dir, "rec_indices", "crfs_cpfv_onboard", 
                          "south", "start2005",
                            "area_weighted_logn", "index_forSS.csv"))
ind <- ind[, c(1,4,5)]
col_names = c("Year", "Estimate", "logSE")

sa4ss::table_format(x = ind,
             caption = "Estimated relative index of abundance for the onboard CPFV survey.",
             label = "onboard-index",
             digits = 4, 
             col_names = col_names)                         
```

\newpage

<!--Figures -->


```{r, results = 'asis'}
sa4ss::add_figure(
filein = file.path(data_dir, "rec_indices", "crfs_cpfv_onboard", "south", 
                   "copper_depths_gisdepthadded.png"), 
caption = "Distribution by year of depths where copper rockfish observed.",
label = 'onboard-depths')
```

\newpage


```{r, results = 'asis'}
sa4ss::add_figure(
filein = file.path(data_dir, "rec_indices", "crfs_cpfv_onboard", "south",
                   "drifts_by_depth_district.png"),
caption = "Stacked bar plot of the depth of observed copper rockfish by district.",
label = 'onboard-depths')
```

\newpage

```{r, results = 'asis'}
sa4ss::add_figure(
filein = file.path(data_dir, "rec_indices", "crfs_cpfv_onboard", "south", "start2005",
                   "average_cpue_by_region.png"), 
caption = "Average CPUE by region prior to standardization.",
label = 'onboard-regioncpue')
```


\newpage

```{r, results = 'asis'}
sa4ss::add_figure(
filein = file.path(data_dir, "rec_indices", "crfs_cpfv_onboard", "south", "start2005",
                   "area_weighted_logn", "index.png"), 
caption = "Index for the onboard CPFV survey.",
label = 'onboard-index')
```

\newpage

```{r, results = 'asis'}
sa4ss::add_figure(
filein = file.path(data_dir, "rec_indices", "crfs_cpfv_onboard", "south","start2005",
                   "area_weighted_logn", "qq.png"), 
caption = "Q-Q plot for the onboard CPFV survey.",
label = 'onboard-qq')
```

\newpage

