
## CRFS PR Dockside Index of Abundance {#crfs-pr-index}

Catch and effort data from CRFS dockside sampling of private boats, 2004-2022, 
were provided by CDFW for use in this assessment. The PR dockside data housed 
on the Recreational Fisheries Information Network (RecFIN) were 
determined to include a number of complexities that precluded the ability to 
use them for the development of an index of abundance. For the time period from 2004-2014 the STAT 
re-created the interview, or trip level, data from the "i" sample files. For 2015-2022 
the STAT used files provided by CDFW from the CRFS dockside sampling program.

The data for both time periods included catch by species, number of anglers contributing to the catch, angler-reported area of fishing, gear, county, port, interview site, year, month, and CRFS district. The catch included 
the number of fish observed by the CRFS sample, the number of unobserved retained fish reported 
by the angler, and the number of discarded and descended fish reported by the angler.
The sample size of the unfiltered private boat data is much larger than the CPFV onboard observer data set, 
with 256,738 samples statewide from 2004-2022, 169,912 south of Point Conception and 86,826 north of Point Conception. 

Records were limited to the primary private and rental boats public-access sites, PR1 sites, which encompasses over 90 percent of the total private boat effort (Table \@ref(tab:pr-filter)). The CRFS interviews contain a small fraction 
(407 trips over the entire time series) of samples where the retained catch for rockfish is over the daily bag limit of 10 fish per person. We did not remove these data from the index, but did only include sampler examined catch. Rockfish species can be difficult to distinguish and there have not been any verification studies conducted to determine the uncertainty in angler reported unobserved catch. Additional data filters included the exclusion of any samples from January and February, since those months have been closed to the recreational fishery south of Point 
Conception since 2005.  The time series was also restricted to 2004-2019. Sampling during the COVID-19 period (2020-2021) resulted in a higher fraction of the sampler examined catch in the "rockfish, general" category due to the social distancing requirements (Table \@ref(tab:pr-rfgen)). The CDFW implemented a one fish sub-bag limit for copper rockfish in 2022 and the quantiles and distribution of CPUE suggest that this regulation change impacted fishing behavior in the private boat fleet (Table \@ref(tab:pr-cpue) and ‼Figure \@ref(fig:pr-bag)).

The angler reported water area was restricted to ocean areas in U.S. waters and a reported primary gear 
of hook and line or troll gear.  A number of trips reporting troll as the primary gear reported
a secondary gear of hook and line. To determine if the angler(s) interviewed targeted rockfish and
fished in rocky habitat, we retained trips if the angler reported the primary target species 
as rockfish or bottomfish or if rockfish was reported as the secondary target species. This filter 
replaced the Stephens-MacCall [@stephens_multispecies_2004] filtering approach that have been used for some assessment in the past. This filtering retained 13,340 angler interviews for index standardization, with 3,739 including sampled examined copper rockfish (Table \@ref(tab:pr-filter)).  

We modeled retained catch per angler days with a negative binomial genearlized linear model in the R package sdmTMB.
The Q-Q plots indicate a reasonable fit (Figure \@ref(fig:pr-qq)).  There are a handful of samples 
with higher than average CPUE and the authors checked with CDFW to determine whether the samples should still be included. CDFW indicated data sheets were not available prior to 2012, but the catches were less than 
the bag limits, and should be assumed to be correct. Indices with a year and district interaction were not 
considered in model selection due to the fact that fishing locations are unknown; the scale of the relative 
abundance of copper rockfish is higher in District 2, but there is some overlap in the fishing locations accessed 
by this fleet (Figure \@ref(fig:pr-districtcpue)). 

Based on AICc values from maximum likelihood fits (Table \@ref(tab:pr-modelselect)), a main effects model including year, month and primary target species as categorical covariates was selected (Table \@ref(tab:pr-index) and Figure \@ref(fig:pr-index)).

<!--Tables -->

\newpage

```{r, results = 'asis'}
ind <- read.csv(file.path(
  data_dir, "rec_indices", "crfs_pr_dockside", "bag_change_visuals",
  "pr_bag_limit_by_year.csv"
)) %>%
 mutate_at(2:6, funs(round(., 3)))

col_names <- c("Year", "Minimum", "Q1", "Q2", "Q3", "Maximum")

sa4ss::table_format(
  x = ind,
  caption = "Summary of the copper rockfish CPUE, number of fish retained per
             angler day, by year.",
  label = "pr-cpue",
  digits = 2,
  col_names = col_names
)
```

\newpage

```{r, results = 'asis'}
ind <- read.csv(file.path(
  data_dir, "rec_indices", "crfs_pr_dockside", "PR_obs_unobs.csv"
)) %>%
  mutate(Percent.RFGEN = scales::percent(Percent.RFGEN))

col_names <- c("Year", "Unspeciated", "Speciated", "Percent unspeciated")

sa4ss::table_format(
  x = ind,
  caption = "Summary of the number of speciated and unspeciated (RFGEN) rockfish 
  per year across all of California.",
  label = "pr-rfgen",
  col_names = col_names
)
```

\newpage

```{r, results = 'asis'}
ind <- read.csv(file.path(
  data_dir, "rec_indices", "crfs_pr_dockside", "south",
  "rm_last2yrs", "percent_pos.csv"
)) %>%
  mutate(percentpos = scales::percent(round(percentpos, 3)))
col_names <- c(
  "Year", "Trips with Target", "Trips without Target", "Total trips",
  "Percent with Target"
)

sa4ss::table_format(
  x = ind,
  caption = "Number of samples and percent positive for the dockside PR survey.",
  label = "pr-percentpos",
  col_names = col_names
)
```

\newpage


```{r, results = 'asis'}
ind <- read.csv(file.path(
  data_dir, "rec_indices", "crfs_cpfv_onboard", "south",
  "start2005", "data_filters.csv"
))
col_names <- c("Filter", "Description", "Number of Samples", "Positive Samples")

sa4ss::table_format(
  x = ind,
  caption = "Data filtering steps for the onboard CPFV survey.",
  label = "pr-filter",
  col_names = col_names,
  font_size = 9,
  landscape = TRUE,
  longtable = TRUE,
  align = 'l',
  custom_width = TRUE,
  col_to_adjust = c(2),
  width = c("8cm")
)
```

\newpage

```{r, results = 'asis'}
ind <- read.csv(file.path(
  data_dir, "rec_indices", "crfs_pr_dockside", "south", "rm_last2yrs",
  "model_selection.csv"
))

sa4ss::table_format(
  x = ind,
  caption = "Model selection for the dockside PR survey.",
  label = "pr-modelselect"
)
```


\newpage

```{r, results = 'asis'}
ind <- read.csv(file.path(
  data_dir, "rec_indices", "crfs_pr_dockside",
  "south", "rm_last2yrs", "Index_forSS.csv"
))
ind <- ind[, c(1, 4, 5)]
col_names <- c("Year", "Estimate", "logSE")

sa4ss::table_format(
  x = ind,
  caption = "Estimated relative index of abundance for the dockside PR survey.",
  label = "pr-index",
  digits = 4,
  col_names = col_names
)
```

\newpage

<!--Figures -->


```{r, results = 'asis'}
sa4ss::add_figure(
  filein = file.path(
    data_dir, "rec_indices", "crfs_pr_dockside", "bag_change_visuals",
    "pr_copper_cpue_year_area_max5.png"
  ),
  caption = "Distribution by year of the number of copper rockfish retained per angler. 
  This includes sampler observed and angler reported catch. The vertical line at 1 represents the sub-bag 
  limit implemented in 2022.",
  label = "pr-bag"
)
```

\newpage

```{r, results = 'asis'}
sa4ss::add_figure(
  filein = file.path(
    data_dir, "rec_indices", "crfs_pr_dockside", "south", "rm_last2yrs",
    "average_cpue_by_district.png"
  ),
  caption = "Average CPUE by district prior to standardization.",
  label = "pr-districtcpue"
)
```


\newpage

```{r, results = 'asis'}
sa4ss::add_figure(
  filein = file.path(
    data_dir, "rec_indices", "crfs_pr_dockside", "south", "rm_last2yrs",
    "index.png"
  ),
  caption = "Index for the dockside PR survey.",
  label = "pr-index"
)
```

\newpage

```{r, results = 'asis'}
sa4ss::add_figure(
  filein = file.path(
    data_dir, "rec_indices", "crfs_pr_dockside", "south",
    "rm_last2yrs", "qq.png"
  ),
  caption = "Q-Q plot for the dockside PR survey.",
  label = "pr-qq"
)
```

\newpage

