# Appendix F. CCFRP Index of Abundance {#ccfrp-index}

The California Collaborative Fisheries Research Program, [CCFRP](https://www.mlml.calstate.edu/ccfrp/), 
is a fishery-independenthook-and-line survey designed to monitor nearshore fish populations at a series of sampling locations both inside and adjacent to MPAs [@starr_variation_2015a; @wendt_collaborative_2009].  The CCFRP survey began in 2007 along the central coast of California and was designed in collaboration 
with academics, NMFS scientists and fishermen. From 2007-2016 the CCFRP project was focused on the central California coast, and has monitored four MPAs consistently. In 2017, the CCFRP expanded coastwide within California. The University of California Santa Barbara and Scripps Institute of Oceanography conduct the 
southern California CCFRP sampling and monitor xxx MPA and reference paired sites.

The survey design for CCFRP consists 500 x 500 m cells both within and 
adjacent to each MPA. On any given survey day site cells are randomly 
selected within a stratum (MPA and/or reference cells). CPFVs are chartered 
for the survey and the fishing captain is allowed to search within the cell for 
a fishing location. During a sampling event, each cell is fished for a total of 
30-45 minutes by volunteer anglers. Each fish encountered is recorded, measured, and released (or descended to depth)
and can later be linked back to a particular angler. 
CCFRP samples shallower depths to avoid barotrauma-induced mortality.  Starting in 2017, a subset of fish have been retained to collect otoliths and fin clips that provide needed biological information for nearshore species. For the index of abundance, CPUE was modeled at the level of the drift, similar to the fishery-dependent onboard observer survey described above.

The CCFRP data are quality controlled at the time they are key punched and little 
filtering was needed for the index. Cells not consistently sampled over time were 
excluded as well as cells that never encountered `r spp`. Copper rockfish were observed 
at the South La Jolla, Carrington Point and and Anacapa Island MPAs. After applying filters to remove drfits from sites that were not consistently sampled, marked for exclusion in the data, or did not fish a minimum of two minute, 856 drifts remained for for index standardization, with 399 drifts encountering `r spp`. 

We modeled retained catch per angler hour (CPUE; number of fish per angler hour) 
using  Plots of the average CPUE inside (MPA) and outside (REF) MPAs at each site are 
in Figure \@ref(fig:ccfrp-avg-cpue) and shows the distinct trends of decreasing average 
CPUE at Carrington Point. Trends among the three sampled MPAs differed with the majority of copper rockfish 
encountered by CCFRP at the Carrington Point MPA.  The trends in average CPUE over 
the six year time series inside and outside of the MPA both show a decline in copper rockfish CPUE. 

A negative binomial model was fit to the drift-level data (catch with a log offset for angler 
hours). Because the average observed CPUE among the MPAs indicated differing trends, we explore 
a region:year interaction, which was not significant. The model selected by AICc included depth, 
depth squared, region and MPA or reference site \@ref(tab:ccfrp-model-selection)), The final model included
year, mpa/reference categorization, depth, depth squared, and a year:mpa/reference interaction. 
The model was fit using the sdmTMB R package. The final index (Table \@ref(tab:ccfrp-index)) represents a similar trend to the unstandardized average CPUE (Figure \@ref(fig:ccfrp-index)).


Based on work completed at the SWFSC, we estimated that the percent of rocky reef habitat 
from Point Conception to the California/Mexican border within state waters is 
892 $km^2$, of which approximately 23% is in MPAs that prohibit the harvest of 
groundfish (pers comm. Rebecca Miller, UCSC). There is recreational fishing outside 
of state waters, but habitat maps are not available at the same 2-m resolution and do 
not allow for direct comparisons. To estimate the area 
of rocky substrate south of Point Conception, we separated the southern California Bight 
into four areas, 1) CRFS District 
1 along the mainland coast, 2) CRFS District 2 along the mainland coast, 
3) state waters encompassing the southern 
Channel Islands, and 4) state waters encompassing the northern Channel Islands. 
 We calculated the total area in each of the 
four regions, as well as the total area with available interpretted substrate. 
 By also calculating the total area open and closed to fishing, i.e., MPAs and CCAs, 
 we expanded the known fraction of rocky substrate to the areas within state 
waters where no substrate interpretted maps exist.  This resulted in an estimate of 
27% of the available rocky substrate 
within areas closed to fishing in southern California state waters. 


```{r, results = 'asis'}

tab <- read.csv(file.path(data_dir, "survey_indices", "ccfrp", "south", "dataFilters.csv"))

sa4ss::table_format(x = tab,
             caption = "Data filtering for the CCFRP survey.",
             label = "ccfrp-data-filter",
             align = 'l',
             longtable = TRUE,
             font_size = 7,
             landscape = TRUE)                         
```

\newpage

```{r, results = 'asis'}

tab <- read.csv(file.path(data_dir, "survey_indices", "ccfrp", "south", "model_selection.csv"))

sa4ss::table_format(x = tab,
             caption = "Model selection for the CCFRP survey.",
             label = "ccfrp-model-selection",
             align = 'l',
             longtable = TRUE,
             font_size = 7,
             landscape = TRUE)                         
```

\newpage

```{r, results = 'asis'}

ind <- read.csv(file.path(data_dir, "survey_indices", "ccfrp", "south", 
"area_weighted", "index_forSS.csv"))
ind <- ind[, c(1,4,5)]
col_names = c("Year", "Estimate", "logSE")

sa4ss::table_format(x = ind,
             caption = "Estimated relative index of abundance for the CCFRP survey.",
             label = "ccfrp-index",
             col_names = col_names)                         
```

\newpage

```{r, results = 'asis'}
sa4ss::add_figure(
filein = file.path(data_dir, "survey_indices", "ccfrp", "south", "area_weighted", "qq.png"), 
caption = "QQ-plot for the CCFRP survey.",
label = 'ccfrp-qq')
```

\newpage 

```{r, results = 'asis'}
sa4ss::add_figure(
filein = file.path(data_dir, "survey_indices", "ccfrp", "south", "mpa_site_cpue.png"), 
caption = "Average CPUE by site with trends prior to standardization in the MPA and REF areas.",
label = 'ccfrp-avg-cpue')
```

\newpage

```{r, results = 'asis'}
sa4ss::add_figure(
filein = file.path(data_dir, "survey_indices", "ccfrp", "south", "area_weighted", "Index.png"), 
caption = "The weighted relative index of abundance.",
label = 'ccfrp-index')
```

\newpage

