# Appendix F. NWFSC Hook and Line Index of Abundance

Since 2004, the NWFSC has conducted an annual hook and line survey targeting shelf rockfish in the genus *Sebastes* at fixed stations (e.g., sites, Figure \ref{fig:nwfsc-hkl-map}) in the Southern California Bight. Key species of rockfish targeted by the `r hkl` are bocaccio (*S. paucispinis*), cowcod (*S. levis*), greenspotted (*S. chlorostictus*), and vermilion/sunset (*S. miniatus* and *S. crocotulus*) rockfishes, although a wide range of rockfish species have been observed by this survey. During each site visit, three deckhands simultaneously deploy 5-hook sampling rigs (this is referred to as a single drop) for a maximum of 5 minutes per line, but individual lines may be retrieved sooner at the angler's discretion (e.g., to avoid losing fish). Five drops are attempted at each site for a maximum possible catch of 75 fish per site per year (3 anglers x 5 hooks x 5 drops). Further details regarding the sample frame, site selection, and survey methodology are described by Harms et al. [-@harms_noaa_2008]. 


The sites considered for the creation of a relative index of abundance were limited to sites that have caught at least 1 `r spp` across all years. A range of alternative model structures were explored to generate an index of abundances. This included alternative levels of aggregation (hook, drop, or site), probability distributions (negative binomial, delta-gamma, or delta-lognormal), and covariates (year, site number, depth, swell height, inside/outside CCA, and/or the number of vermilion/sunset or bocaccio rockfishes observed, Table ref{tab:nwfsc-hkl-model-selection}). The overall trend in the index of abundance were highly similar across the explored probability distributions and model configurations. The number of observation in `r spp` in the CCA were limited. The calculated CPUE inside and outside the CCA were similar for `r spp` (Figure \ref{fig:nwfsc-hkl-cca}). Given this, the index selected for the base model include all observations of `r spp` across all sampled sites. Sensitivities to excluding the CCA observations were conducted.

All modeling was initially conducted using sdmTMB [@anderson_sdmtmb_2022] with the final selected model fit using the "rstanarm" R package (v. 2.21.3). All diagnostics appearred reasonable. The final selected model was a negative binomial model that included covariates terms for year, site number, drop, swell height, and the number of bocaccio and vermilion/sunset rockfishes separately. A comparison between the standardized estimated relative index of abundance compared with the calculated raw catch-per-unit-effort (CPUE) is show Figure \ref{fig:nwfsc-hkl-index-raw}. The final index of abundance is shown in Figure \ref{fig:nwfsc-hkl-index} and Table \ref{tab:nwfsc-hkl-index}

\pagebreak


\input{tex_tables/nwfsc_hkl_model_selection.tex}



```{r, results = 'asis'}
add_figure(
filein = file.path(data_dir,  "nwfsc_hkl", "plots", "standardized_cpue_nwfsc_hkl_inside_outside.png"), 
caption = "Standardized CPUE inside and outside the CCA.",
label = 'nwfsc-hkl-cca')
```

\newpage

```{r, results = 'asis'}
add_figure(
filein = file.path(data_dir, "survey_indices", "nwfsc_hkl", "plots", "stand_index_raw_versus_est.png"), 
caption = "Standardized comparison of estimated relative index of abundance and the raw cath-per-unit-effort.",
label = 'nwfsc-hkl-index-raw')
```

\newpage

```{r, results = 'asis'}
add_figure(
filein = file.path(data_dir, "survey_indices", "nwfsc_hkl", "rstan_full_nb_glm_year_site_drop_swell_bocaccio_vermilon", "Index.png"), 
caption = "Estimated index of abundance for copper rockfish.",
label = 'nwfsc-hkl-indices')
```
