## CPFV Fleet Description, Trip Types, and Sampling  {#cpfv-samples}

During the 2021 copper rockfish stock assessment review meeting and during the pre-assessment workshop for the 2023 groundfish assessments, concern was raised regarding possible biases in the available data from the CPFV fleet. This appendix describes the CPFV fleet, including the differences between the fleet north and south of Point Conception and why sampling by trip type was raised as a concern in southern California.  The goal of this exploratory analysis was to compare the CPFV logbook data and the onboard observer sampled trips to describe the proportion of sampled trips by trip type and the distribution of copper rockfish catches across trip types. We then used CPFV data from the two most recent years pre-COVID (2018 and 2019) to illustrate how the distribution of sampling effort compares to the distribution of fishing effort and catches of copper rockfish. 


*CPFV Fleet Description:* The CPFV fleets north and south of Point Conception are fundamentally different in terms of the size of the vessels, available target species, and accessible areas and depths. The CPFVs north of Point Conception targeting groundfish do not typically target other species on the same trip, with the exception being a half-day groundfish trip mixed with a half-day of Dungeness crab pot fishing.  Overnight trips are extremely rare in northern California and weather is a more constraining factor as you move north along the coast. There are few Coast Guard inspected vessels north of Bodega Bay, California and the recreational fleet is dominated by smaller six-pack vessels with limited capacity.  

In southern California, the diversity of target species is higher and includes several state-managed gamefish, coastal pelagics, and highly migratory species. There are three distinct trip types in southern California. The shortest of these is a half-day trip where a CPFV will run two trips a day. The three-quarter to full-day trips are able to access fishing grounds further offshore, such as the Channel Islands. Overnight and multi-day access areas including remote destinations such as San Nicholas Island and may target a combination of species, i.e., trips targeting tunas, but also catching rockfish. A number of CPFVs in southern California also transit to fish in Mexican waters for rockfish. The diversity of trip types and variety target species within a CPFV trip in southern California pose a challenge for both sampling and managing the fisheries. If either catch rates or size compositions vary across trip, in the absence of representative sampling, stock assessments may not be able to accurately account for that variability resulting in the possibility that selectivity and the input catches may be biased.


*Available CPFV Catch and Effort Data:* The components of the CDFW sampling programs used in this analysis are the CRFS CPFV onboard observer survey, CRFS angler interviews, and the mandatory, self-reported CPFV logbooks. 

The CRFS program divides California into six districts, and these represent the finest spatial stratification of catch and effort estimates for stock assessments and management (Figure \@ref(fig:crfs-districts)). The [CRFS sampling manual](https://nrm.dfg.ca.gov/FileHandler.ashx?DocumentID=62348&inline) outlines the sampling methodologies for each survey component. The [California Fisheries Recreational Fisheries Survey Methods](https://nrm.dfg.ca.gov/FileHandler.ashx?DocumentID=36136&inline) indicates the CPFV mode "sampling goal is to sample onboard at the historical sampling frequency of two to five percent of estimated CPFV trips of interest (e.g., trips targeting groundfish, inshore and coastal pelagic species) at each CPFV landing and to sample other CPFV trip types dockside." 

The CRFS data collected onboard are a key component to obtaining species-specific information from the CPFV fleet because the state of California allows the filleting of fish at sea. To accurately identify rockfish species and obtain measurements of whole fish, the majority of CPFV angler interviews occur onboard the vessel. 

The CPFV logbooks include information on the the general location fished, number of anglers, number of fish retained and discarded, use of descending devices, as examples. The CPFV fleet, in the absense of an onboard observer, is not required to speciate the catch and only one CDFW block number (i.e., location identifying grid system) is recorded per entry. For these reasons the CPFV logbook data are not often used to develop an index of abundance for groundfish species. However, the CPFV logbook data provide insight into the spatial distribution of fishing effort and changes in effort over time.
 

*Data Summaries from 2018-2019:* In order to maintain confidentiality, we aggregated data within each dataset across 2018 and 2019, and across districts four and six (i.e., no trips were observed onboard in CRFS District 5 during 2018-2019).

We filtered the CPFV logbook data to trips that recorded at least one rockfish and the CPFV onboard observer data to trips that encountered at least 1 percent groundfish species. Additional filters were applied to the CPFV logbook data such as removing trips that recorded the primary fishing location in Mexican waters (6 percent of all trips). We also removed a small fraction (less than 10 trips) recorded as multi-day trips, but that reported a fishing location along the mainland of southern California. 

The combined onboard observer sampling rate for 2018-2019 was 3 percent of all CPFV trips statewide in the filtered data. No trips were observed onboard in CRFS District 5 during 2018-2019. However, 1,051 CPFV logbooks were submitted from District 5 ports that recorded at least one rockfish. When we grouped the data by the modeled areas north and south of Point Conception, we found that  2 percent of all trips in northern California were sampled onboard. In southern California, 4 percent of single-day trips were observed and less than 1 percent of multi-day trips were observed.

We then explored the southern California data further to look at sampling effort by trip type. The CPFV logbooks indicated if a trip was a single- or multi-day, but the logbooks do not differentiate between a half-day or three-quarter day trip. We assigned each CPFV logbook trip from southern California to a sub-region (District 1 mainland, District 2 mainland, northern Channel Islands, Southern Channel Islands, and Offshore) based upon the recorded block number (Table \@ref(tab:logbook-triptype)). The trips assigned to "Southern CA Offshore" were a catch-all that included blocks outside the range of a half-day trip, but not within the vicinity of an island. We separated out the "Southern CA Offshore" trips because it is likely their target species was not rockfish. Approximately 16 percent of the CPFV logbooks in southern California were from multi-day trips. As expected, the trips recording a CDFW block near the mainland were recorded as half-day trips. More than twice as many trips to the northern Channel Islands were single-day trips versus multi-day trips. The vessels in District 2 typically offer fewer half-day day trips and fish the nearshore when weather precludes crossing the channel to the northern Channel Islands on a three-quarter day trip. 


To put these sampling rates in context for copper rockfish, we looked at the total estimated mortality by district related to the distribution of sampling. The total mortality of copper rockfish in metric tons from 2018-2019 from the CPFV fleet by CRFS District is shown in Table \@ref(tab:catch-example). Fifty-two percent of the total copper rockfish mortality was from northern California and 48 percent from southern California.  Within northern California, 50 percent of the total mortality originated from District 3, and in southern California, 81 percent of the total mortality originated from District 2. 

From the onboard observer trips in District 1, 37 percent of the observed copper rockfish were from half-day day trips, 42 percent from three-quarter to full-day trips, and 21 percent of the observed copper rockfish were from the five observed multi-day trips (Table \@ref(tab:onboard-coppers)). 

In District 2, 17 percent of the observed copper rockfish were from half-day day trips, 75 percent from the three-quarter to full day trips, and 8 percent from multi-day trips. When weather allows, the northern Channel Islands can be accessed from CRFS District 2 during a three-quarter to full-day trip or a multi-day trip, depending on the port. For instance, the CPFVs from Channel Islands Sportfishing in Oxnard, California access the northern Channel Islands during multi-day trips, and the same areas are accessed by the three-quarter to full-day trips out of Santa Barbara Landing. 

The majority of length samples for the CPFV fleet are taken onboard the observed trips. The shift in the distribution of lengths from each trip type is evident from the overnight trips from District 1 with larger fish encountered on the overnight trips (Figure \ref{fig:copper-lengths}.  The average length of fish encountered on half-day trips out of District 2 is 33.1 cm compared to 36.3 for three-quarter day trips and 36.6 for overnight trips.  

To account for the differences in the the differences in catch rates and size compositions observed across trip types and areas, we would need to collect estimates of catch and effort at a finer-scale than the CRFS district. While the logbooks are not perfect, and there is a fraction of non-compliance, they highlight the intense fishing pressure in some areas and may help identify the how to distribute sampling efforts. For example, increased sampling in Districts 4-6 would also provide information on the length composition of the fish encountered by the CPFV fleet, especially considering the increase in average length with latitude (Figure \@ref(fig:copper-lengths)). The increased sampling in District 4-6 would also provide the data needed to create an accurate index of relative abundance from the onboard observer data, which can easily be considered one of the most valuable fishery-dependent data sources available. Based on additional data from the logbooks it may be possible to identify an approximate fraction of half-day to three-quarter day trips.
The lengths in Table \@ref(tab:copper-lengths) are currently all weighted equally in the length compositions within the current assessment models. Future research is needed to determine the effects of the changing size composition by trip type within stock assessment models, especially for southern California where larger fish are encountered on longer trips. Weighting the length composition data by the catch from each trip type is one possible method to account for the differences observed in Figure \@ref(fig:copper-lengths). 


\newpage

```{r, results = 'asis'}
sa4ss::add_figure(
filein = file.path(data_dir, "rec_indices", "cpfv_logbook_summaries", "crfs_districts.png"), 
caption = "Map of the CDFW CRFS sampling Districts.",
label = 'crfs-districts')
```

\pagebreak

```{r, results = 'asis'}
sa4ss::add_figure(
filein = file.path(data_dir, "rec_indices", "cpfv_logbook_summaries", "length_by_triptype.png"), 
caption = "Distribution of the lengths of copper rockfish measured from 2018-2019 from dockside angler interviews by district.",
label = 'copper-lengths')
```

\pagebreak

```{r, include = FALSE}
#ind <- read.csv(file.path(data_dir, "rec_indices", "cpfv_logbook_summaries", "area_percent_observed.csv"))
#col_names = c("Area", "Single day", "Multi day")

#sa4ss::table_format(x = ind,
#             caption = "The percent of trips sampled onboard by trip type and area for 2018 and 2019, using the number of trips #observed and CPFV logbook trips described in the text.",
#             label = "percent-observed",
#             col_names = col_names)                         
```


```{r, results = 'asis'}
ind <- read.csv(file.path(data_dir, "rec_indices", "cpfv_logbook_summaries", "copp_catch_2018_2019.csv"))
col_names = c("District", "2018", "2019", "Total")

sa4ss::table_format(x = ind,
             caption = "Total mortality in metric tons of copper rockfish from 2018 and 2019 from the CPFV fleet by CRFS District.",
             label = "catch-example",
              align = "r",
             col_names = col_names)                         
```


```{r, results = 'asis'}
ind <- read.csv(file.path(data_dir, "rec_indices", "cpfv_logbook_summaries", "fordoc_onboard_copper_summary.csv"))
col_names = c("District",  "1/2 day trips", "3/4-1 day trips","Overnight trips")

sa4ss::table_format(x = ind,
             caption = "Number of copper rockfish observed during the CPFV trips sampled onboard by district and trip type from 2018-2019.",
              align = "r",
             label = "onboard-coppers",
             col_names = col_names)                         
```


```{r, results = 'asis'}
ind <- read.csv(file.path(data_dir, "rec_indices", "cpfv_logbook_summaries", "number_copper_lengths_triptype.csv"))
col_names = c("District",  "1/2 day trips", "3/4-1 day trips","Overnight trips")

sa4ss::table_format(x = ind,
             caption = "Number of copper rockfish measured by district and trip type from the angler interviews in 2018-2019.",
              align = "r",
             label = "copper-lengths",
             col_names = col_names)                         
```

\pagebreak

```{r, results = 'asis'}
ind <- read.csv(file.path(data_dir, "rec_indices", "cpfv_logbook_summaries", "fordoc_Onboard_trip_duration_observed.csv"))
col_names = c("District", "1/2 day trips", "3/4-1 day trips","Overnight trips", "Percent trips with copper rockfish", "Total number of copper rockfishobserved")
ind[is.na(ind$Overnight), "Overnight"] <- 0
ind[is.na(ind$Copper.observed), c("Copper.observed", "Percent.of.trips.encountering.copper")] <- "-"

sa4ss::table_format(x = ind,
             caption = "Number of CPFV trips sampled as part of the onboard observer survey during 2018-2019, the percent of trips with copper rockfish observed, and the total number of recorded copper rockfish by trip type and District. District 4 and 6 were combined to retain confidentiality.  No trips from District 5 were sampled.",
             label = "onboard-trips",
             landscape = TRUE,
             align = 'l',
             col_names = col_names)                         
```

\pagebreak

```{r, results = 'asis'}
ind <- read.csv(file.path(data_dir, "rec_indices", "cpfv_logbook_summaries", "fordoc_logbook_by_triptype.csv"))
col_names = c("Region", "Multi-day", "Single-day")
ind[is.na(ind)] <- 0

sa4ss::table_format(x = ind,
             caption = "Number of CPFV logbook entries with at least one rockfish, grouped by region fished and trip type from 2018-2019.",
              align = "r",
             label = "logbook-triptype",
             col_names = col_names)                         
```


\pagebreak