---
geometry: margin=1in
month: "`r format(Sys.Date(), '%B')`"
year: "`r format(Sys.Date(), '%Y')`"
preamble: 
header-includes: 
  - \usepackage{lineno}
  - \usepackage[inline]{showlabels}
csl: canadian-journal-of-fisheries-and-aquatic-sciences.csl
output:
  sa4ss::techreport_pdf:
    default
  bookdown::pdf_document2:
    keep_tex: true
lang: en
bibilography: [pfmcassess.bib, wcassess.bib]
papersize: letter
---

\linenumbers

<!-- Common lat/long 
Cape Mendocino, Pt. Conception and OR border -->
\newcommand\CapeM{$40^\circ 10^\prime N$}
\newcommand\PtC{$34^\circ 27^\prime N$}
\newcommand\CAOR{$42^\circ 00^\prime N$}


```{r opts, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
knitr::knit_hooks$set(plot = function(x,options) {
      base = knitr::opts_knit$get('base.url')
      if (is.null(base)) base = ''
      alt = ifelse (is.null(options$alt),"",options$alt)
      cap = ifelse (is.null(options$caption),"",options$caption)
      if (alt != ""){
        sprintf('![%s](%s%s "%s")', cap, base, x, alt)
      } else {
        sprintf('![%s](%s%s)', cap, base, x)
        }
  })

load('saved_directories.Rdata')
load("00opts.Rdata")

spp <- "copper rockfish"
Spp <- "Copper rockfish"
hkl <- "NWFSC Hook and Line survey"
wcgbt <- "NWFSC WCGBT survey"
area <- "south of Point Conception"

if(file.exists("00mod.Rdata")){
  load("00mod.Rdata")
} else {
  print("Model output not being read. Please run the read_model() function.")
}

source(file.path(doc_dir, "helper_functions.R"))

#source(file.path(r_dir, "get_derived_quants.R"))


```

<!--chapter:end:00a.Rmd-->

---
author:
  - name: Chantel R. Wetzel
    code: 1
    first: C
    middle: R
    family: Wetzel
  - name: Melissa H. Monk
    code: 2
    first: M
    middle: H
    family: Monk
  - name: Julia Coates
    code: 3
    first: J
    middle: ''
    family: Coates
author_list: Wetzel, C.R., M.H. Monk, J. Coates
affiliation:
  - code: 1
    address: Northwest Fisheries Science Center, U.S. Department of Commerce, National
      Oceanic and Atmospheric Administration, National Marine Fisheries Service, 2725
      Montlake Boulevard East, Seattle, Washington 98112
  - code: 2
    address: Southwest Fisheries Science Center, U.S. Department of Commerce, National
      Oceanic and Atmospheric Administration, National Marine Fisheries Service, 110
      McAllister Way, Santa Cruz, California 95060
  - code: 3
    address: .na.character
address:
  - ^1^Northwest Fisheries Science Center, U.S. Department of Commerce, National Oceanic
    and Atmospheric Administration, National Marine Fisheries Service, 2725 Montlake
    Boulevard East, Seattle, Washington 98112
  - ^2^Southwest Fisheries Science Center, U.S. Department of Commerce, National Oceanic
    and Atmospheric Administration, National Marine Fisheries Service, 110 McAllister
    Way, Santa Cruz, California 95060
  - ^3^NA
---

<!--chapter:end:00authors.Rmd-->

---
bibliography:
  - sa4ss.bib
  - wcassess.bib
  - pfmcassess.bib
---

<!--chapter:end:00bibliography.Rmd-->

---
title: Status of copper rockfish (_Sebastes caurinus_) along the U.S. California coast south
  of Point Conception in 2023
---

<!--chapter:end:00title.Rmd-->

\pagebreak
\pagenumbering{roman}
\setcounter{page}{1}

\renewcommand{\thetable}{\roman{table}}
\renewcommand{\thefigure}{\roman{figure}}


\setlength\parskip{0.5em plus 0.1em minus 0.2em}

\vspace{500cm}


# Disclaimer{-}
_**These materials do not constitute a formal publication and are for information only. They are in a pre-review, pre-decisional state and should not be formally cited or reproduced. They are to be considered provisional and do not represent any determination or policy of NOAA or the Department of Commerce.**_


\pagebreak

<!--chapter:end:01a.Rmd-->

```{r executive, echo = FALSE}
executive <- list()
executive[["stock"]] <- paste0("This assessment reports the status of ",
  spp, " (_", spp.sci, "_) off the ", coast, 
  " coast using data through 2022.")
```

# Executive summary{-}

```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text",'01_executive_summary.Rmd')
read_child(filein)
```

<!--chapter:end:01executive.Rmd-->

\pagebreak
\setlength{\parskip}{5mm plus1mm minus1mm}
\pagenumbering{arabic}
\setcounter{page}{1}
\renewcommand{\thefigure}{\arabic{figure}}
\renewcommand{\thetable}{\arabic{table}}
\setcounter{table}{0}
\setcounter{figure}{0}

<!--chapter:end:10a.Rmd-->

# Introduction

This assessment report describes the sub-area population of `r spp` (*Sebastes caurinus*) off the California coast `r area` in U.S. waters, using data through 2022. The sub-area population north of Point Conception in California waters was also evaluated and is described in a separate assessment report. The `r spp` status for the California stock of is determined by the combined estimates of spawning output from both sub-areas and is detailed in the [Management](#management) section. This assessment does not account for populations located in Mexico waters or other areas off the U.S. coast and assumes that these southern and northern populations do not contribute to the population being assessed here. 

## Basic Information and Life History

```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text", '1_intro_life_history_fishery_info.Rmd')
read_child(filein)
```

## Ecosystem Considerations


```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text", '1_ecosystem_consideration.Rmd')
read_child(filein)
```


## Historical and Current Fishery Information

Off the coast of California south of Point Conception `r spp` is caught in both commercial and recreational fisheries. Recreational removals have been the largest source of fishing mortality of `r spp` across all years (Table \ref{tab:allcatches} and Figure \ref{fig:catch}). The recreational fishery is comprised of individual recreational fishers (Private/Rental, PR) and charter recreational private vessels (CPFV) which take groups of individuals out for day fishing trips. Across both types of recreational fishing the majority of effort occurs around rocky reefs that can be accessed via a day-trips. 

```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text", '1_intro_ca_commercial.Rmd')
read_child(filein)
```

`r Spp` residing between Point Conception and the California/Oregon border are assessed here as a single, separate stock (Figure \ref{fig:ca-map}). This designation was made based on oceanographic, geographic, and fishery conditions. The `r spp` population in California waters was split at Point Conception due to water circulation patterns that create a natural barrier between nearshore rockfish populations to the north and south. The northern border for this assessment was defined as the California/Oregon border due to substantial differences in historical and current exploitation levels. Additionally, the fairly sedentary nature of adult `r spp`, likely limits flow of fish between northern California and areas to the north. 

## Summary of Management History and Performance

```{r, echo=FALSE, results='asis'}

filein = file.path(doc_dir, "shared_text", '1_intro_management.Rmd')
read_child(filein)
```

## Foreign Fisheries


```{r, echo=FALSE, results='asis'}

filein = file.path(doc_dir, "shared_text", '1_foreign_fisheries.Rmd')
read_child(filein)
```


<!--chapter:end:11introduction.Rmd-->

# Data

Data comprise the foundational components of stock assessment models. The decision to include or exclude particular data sources in an assessment model depends on many factors.
These factors often include, but are not limited to,
the way in which data were collected (e.g., measurement method and consistency);
the spatial and temporal coverage of the data;
the quantity of data available per desired sampling unit;
the representativeness of the data to inform the modeled processes of importance;
timing of when the data were provided;
limitations imposed by the Pacific Fishery Management Council Groundfish Terms of Reference; and
the presence of an avenue for the inclusion of the data in the assessment model.
Attributes associated with a data source can change through time,
as can the applicability of the data source when different modeling approaches are explored (e.g., stock structure or time-varying processes).
Therefore, the specific data sources included or excluded from this assessment should not necessarily constrain the selection of data sources applicable to future stock assessments for `r spp`.
Even if a data source is not directly used in the stock assessment they can provide valuable insights into biology, fishery behavior, or localized dynamics.

Data from a wide range of programs were available for possible inclusion in the current assessment model.
Descriptions of each data source included in the model (Figure \@ref(fig:data-plot)) and sources that were explored but not included in the base model are provided below.
Data that were excluded from the base model were explicitly explored during the development of this stock assessment or have not changed since their past exploration in a previous `r spp` stock assessment.
In some cases, the inclusion of excluded data sources were explored through sensitivity analyses (see Section \@ref(assessment-model)).

<!--chapter:end:20data.Rmd-->


## Fishery-Dependent Data

### Commercial Fishery {#commercial-fishery}

#### Landings and Discards
\
```{r, echo=FALSE, results='asis'}

filein = file.path(doc_dir, "shared_text",'2f_commercial_removals.Rmd')
read_child(filein)
```


#### Composition Data
\

Biological data were extracted from the PacFIN Biological Data System on March 20, 2023. Length data for the commercial fleet were extracted from the PacFIN Biological Data System (BDS) with samples for north↨ of Point Conception beginning in 1983 (Tables \ref{tab:dead-com-len} and \ref{tab:live-com-len}). The commercial data was split by landed condition, live or dead, with the first data for the live fish fishery beginning in 1999. The number of length samples by fleet were highly variable with the largest number of sample by year being recorded in the mid- to late-1990s for the dead fish fishery. In recent years, the number of length samples by year are limited for both fleets. The number of samples prior to 1995 and in the 2000s for the dead fish fishery were sparse and variable across sizes. During model explorations any year with less than 20 sampled fish were considered too sparse to accurately reflect the fleet selectivity for that year (see [Appendix A](#excluded-data) for implied fits to these lengths). 

The majority of lengths observed by the commercial fleet landed dead `r spp` ranged between approximately 25 - 45 cm starting in the early 1990s with some additional observations of larger fish in earlier years (Figure \ref{fig:com-dead-len-data}, detailed length compositions by year can be found in the Appendix, Section \ref{length-data}).  The mean length observed by year ranged between approximately 35 - 45 cm (Figure \ref{fig:mean-com-dead-len-data}). The mean observed length in the earliest data is variable ranging between 40 -45 cm, declining in the 1990s to less than 40 cm, then increasing to slightly larger mean size across the sparse data of the early 2000s, and then increasing in the most recent years data. There were only a few age samples (8 total) from the commercial dead fleet that were collected in 2022 (Figure \ref{fig:com-dead-age-data}). Randomly all of these ages were from from female fish. These data were incorporated into the model as marginal age data associated with this fleet. 

The observed distribution of sizes sampled from the commercial live fish fleet were generally variable based on the more limited sample sizes but ranging between 30 - 40 cm with missing years of data across different time periods (Figure \ref{fig:com-live-len-data}). The observed mean length of fish landed live was highly variable with means often below 35 cm with the smallest observed mean size being observed in the final year of data (Figure \ref{fig:mean-com-live-len-data}).  

The input sample sizes for all commercial data initially were calculated based on a combination of trips and fish sampled:

\begin{centering}

Input effN = $N_{\text{trips}} + 0.138 * N_{\text{fish}}$ if $N_{\text{fish}}/N_{\text{trips}}$ is $<$ 44

Input effN = $7.06 * N_{\text{trips}}$ if $N_{\text{fish}}/N_{\text{trips}}$ is $\geq$ 44

\end{centering}

During initial model evaluations alternative data weighting approaches suggested potentially high up-weighting the samples from the commercial live fish fishery. In order to ensure that the data were not up-weighted beyond the total annual sample size the input sample size was revised to be equal to the number of lengths samples.

### Recreational Fishery {#recreational-fishery}

#### Landings and Discards
\

```{r, echo=FALSE, results='asis'}

filein = file.path(doc_dir, "shared_text",'2f_recreational_removals.Rmd')
read_child(filein)
```

#### Indices of Abundance

A number of indices of abundance were explored for the recreational fleet. Discarded catch is available from onboard observer surveys, but was not included in indices. Indices developed for the assessment include:

* MRFSS era dockside survey of the CPFV/PC fleet (1980-1999)
* CDFW CPFV/PC onboard observer index (1999-2019)
* CRFS PR1 sites dockside survey (2004-2019)

Due to limited sampling during 2020 due to the COVID-19 pandemic and inseason action taken by CDFW for 2022 reducing sub-bag limits for `r spp` across California, both recreational fishery indices of abundance excluded data collected after 2019.

```{r, echo=FALSE, results='asis'}
filein = file.path(getwd(), "shared_text",'mrfss_index.Rmd')
read_child(filein)
```

The data were filtered to identify rockfish trips, standardized across the time-series, and modeled to estimate and index of abundance for `r spp` (see [Appendix B](#mrfss-index) for details). The MRFSS CPFV index of abundance between 1980-1999 is generally variable but with a flat trend in abundance except for three years that spike in abundance estimates (Figure \ref{fig:mrfss-index-main}). These same patterns in sharp increases in the index for select years were also observed in the raw data. Given the limited information in the data to understand what was behind these unexpected spikes in the time series, the MRFSS index of abundance was not used in the final base model. 

```{r, echo=FALSE, results='asis'}
filein = file.path(getwd(), "shared_text",'crfs_cpfv_index.Rmd')
read_child(filein)
```

The CRFS CPFV index of abundance was low in the early years of the time-series between 1999-2004 and then began to increase with variability among years until 2013, and declined in the final years (Figure \ref{fig:crfs-index-main}). See [Appendix C](#onboard-cpfv-index) for details on the data filtering, processing, and model selection.

Catch and effort data from CRFS dockside sampling of private boats, 2004-2019, and 2021-2022, were provided by CDFW for use in this assessment. The data include catch (number of fish) by species, number of anglers (i.e., effort units are angler trips), angler-reported distance from shore (Area X: inside/outside of 3 nm), county, port, interview site, year, month, and CRFS district. Only data through 2019 were used to develop an index of abundance due to potential changes in angler behavior in 2021 and management changes in 2022. See [Appendix D](#crfs-pr-index) for details on the data filtering, processing, and model selection. The CRFS PR index of abundance generally increased between 2004-2016, with the final years in the index stabilizing or slightly declining (Figure \ref{fig:crfs-pr-index-main}).


#### Composition Data
\

Length compositions were available from the following sources: 

* Recreational party/charter mode (CPFV/PC)

  + Collins and Crooke onboard observer survey (1975-1978)
  + MRFSS CPFV/PC dockside survey (1980-1989, 1993-2003)
  + Ally onboard observer survey (1984-1989)
  + CRFS CPFV/PC onboard dockside survey (2004-2022)

* Recreational private/rental mode (PR)

  + MRFSS dockside PR survey (1980-1989, 1993-2003)
  + CRFS dockside PR survey (2004-2022)

  
The number of available fish and unique trips by year and fleet are in Table \ref{tab:rec-len-samps}. MRFSS historical biological data were downloaded from RecFIN website in December 2022. CRFS biological data were also downloaded from RecFIN on February 18, 2023. The Collins and Crooke and Ally recreational survey data were downloaded from the SWFSC databases on February 12, 2023. 

Practically all of length samples for both recreational fleets, CPFV and PR, were unsexed (only two sexed fish in the CPFV data that were added to the unsexed data). A wide range of lengths from the recreational CPFV fleet were observed across all years with lengths generally ranging between 20 - 40 cm except for the late 1970s and early 1980s where a higher proportion of larger fish were sampled (Figure \ref{fig:rec-cpfv-len-data}). The mean length of lengths observed in the recreational CPFV fleet by is variable with mean length increasing until the early 1980s, decreasing until the mid-1990s, increasing until 2000, stabilizing with some variability through the early 2010s, and then slowly increasing in the most recent years data (Figure \ref{fig:mean-rec-cpfv-len-data}). The range of lengths sampled from the recreational PR fleet are similar to those from the CPFV fleet with lengths in recent years ranging between 20 - 40 cm (Figures \ref{fig:rec-pr-len-data} and \ref{fig:mean-rec-pr-len-data}). 

Age data collected by the recreational CPFV fleet were collected in two separate years, 1975 and 2022. The historical age data were from a total of 84 unsexed fish and were incorporated in the model as marginal age data (Figure \ref{fig:com-dead-age-data}). In 2022, a total of 508 age samples from the final model year, 2022, collected by a cooperative sampling program with the fleet coordinated by the SWFSC. These data were collected by four CPFV vessels that operate south of Point Conception following random sampling protocols. The lengths from the cooperative collected ages were compared to all the CPFV lengths collected by the CRFS sampling program (Figure \ref{fig:coop-len-comparison} South). This comparison revealed that there were distinct differences in the length of fish in these two data sets where the cooperative collection data tended to have more large fish sampled. The CRFS length data sample size was less than half of the sample size compared to cooperative age data collection (CRFS sampled 243 from 78 trips, Table  \ref{tab:rec-len-samps}). The source of these differences are not entirely clear, but could be arising from difference in sampling areas within the region `r area` where there appear to be size and abundance differences in the more southern areas compared to areas around the Channel Islands. Given the differences in the age samples to the length sampled by the CRFS program, these ages were not linked to the CPFV fleet in the model.  However, these data are an important source of age-length information for `r spp`, so these data were added to a growth fleet in the model (see the [Growth Data](#growth-data) section)

The approach to determine the number of unique trips by data source varied. Only Collins and Crook data had unique trip numbers within the data. Other data sources that lacked clear trip identifier applied a similar methodology as developed by Brian Soper that combines multiple fields of information to attempt to estimate trips sampled. The number of trips for MRFSS data was estimated using the year, wave, ID code, sampling site (INSITE), area, and mode. A similar methodology was done for CRFS that used data, county, water area, interview site, and mode. Finally, trips for the Ally survey data were based on year, complex, landing, and district.

<!--chapter:end:21f-.Rmd-->

## Fishery-Independent Data

Three fishery-independent data sources with indices of abundance were included in the base model. These surveys sampled rocky habitat across the area `r area` (Figure \ref{fig:survey-locations}) sampled both areas opens to fishing (termed reference areas) and Marine Protected Areas (MPAs, Figure \ref{fig:ref-mpa}).

<!--chapter:end:21s-.Rmd-->

### California Collaborative Fisheries Reserach Program

#### Index of Abundance
\

Since 2007, the \gls{s-ccfrp} has monitored several areas in California to evaluate the performance of \glspl{mpa} and understand nearshore fish populations
[@Wendt2009; @Starr2015]. In 2017, the survey expanded beyond the four \Gls{mpa}s in central California
(A&ntilde;o Nuevo, Point Lobos, Point Buchon, and Piedras Blancas) to include the entire California coast.
Fish are collected by volunteer anglers aboard \glspl{cpfv} guided by one of the following academic institutions based on proximity to fishing location: Humboldt State University; Bodega Marine Laboratories; Moss Landing Marine Laboratories; Cal Poly San Luis Obispo; University of California, Santa Barbara; and Scripps Institution of Oceanography.

Surveys consist of fishing with hook-and-line gear for 30-45 minutes within randomly chosen 500 by 500 m grid cells within and outside \glspl{mpa}. Prior to 2017, all fish were measured for length and release or descended to depth; since then, some were sampled for otoliths and fin clips.

The estimated index of abundance was weighted based sample locations outside (reference) and inside MPAs (73 and 80 percent of areas open to fishing in the north and south, respectively, see Appendix Section \ref{cdfw-rov-index} for additional information). The highest index point is associated with the first index year, 2017, varies between 2018-2021, and has the lowest index in 2022 (Figure \ref{fig:ccfrp-index-main}, see Appendix Section \ref{ccfrp-index} for additional information on the development of the index).

#### Composition Data
\

Length measurements were available each year the CCFRP has operated `r area` and age data were collected in 2022 by the survey (Table \ref{tab:ccfrp-samps}). The length data by designation, MPA and Reference, were weighted based on the estimated rocky habitat within each designation north and south of Point Conception (73 and 80 percent of areas open to fishing in the north and south, respectively, see Appendix Section \ref{cdfw-rov-index} for additional information). The lengths observed by the survey ranged between 20-45 cm across the sample years with the mean lengths observed ranging between 33-36 cm (Figures \ref{fig:ccfrp-len-data} and \ref{fig:ccfrp-mean-len-data}). The survey collected age data from a subset of fish sampled in 2022 (Figure \ref{fig:ccfrp-age-data}). The read ages from these sampled fish ranged between 4-24 years of age.

<!--chapter:end:21s-ccfrp.Rmd-->

### Northwest Fisheries Science Center Hook and Line

#### Index of Abundance 
\

Since 2004, the NWFSC has conducted an annual hook and line survey targeting shelf rockfish in the genus *Sebastes* at fixed stations (e.g., sites, Figure \ref{fig:nwfsc-hkl-map}) in the Southern California Bight. Key species of rockfish targeted by the `r hkl` are bocaccio (*S. paucispinis*), cowcod (*S. levis*), greenspotted (*S. chlorostictus*), and vermilion/sunset (*S. miniatus* and *S. crocotulus*) rockfishes, although a wide range of rockfish species have been observed by this survey. During each site visit, three deckhands simultaneously deploy 5-hook sampling rigs (this is referred to as a single drop) for a maximum of 5 minutes per line, but individual lines may be retrieved sooner at the angler's discretion (e.g., to avoid losing fish). Five drops are attempted at each site for a maximum possible catch of 75 fish per site per year (3 anglers fishing with a line with 5 hooks across a total of 5 drops per site). Further details regarding the sample frame, site selection, and survey methodology are described by Harms et al. [-@harms_noaa_2008]. 

From 2004 through 2013, sampling was conducted only outside the Cowcod Conservation Areas (CCAs). Beginning in 2014, 40 sites inside the CCAs were sampled, and roughly another 40 sites have been added in subsequent years inside the CCAs. It is important to note that some portions of the CCAs allow take for select species at depths less that 73 meters. The survey currently has 201 sites (79 inside and 122 outside the CCAs). Additionally, 16 stations within the original sample design sample areas that have been converted into either state or federal MPAs between 2007 - 2011.  

`r Spp` have been observed at multiple sampling sites by the `r hkl` each year between 2004 - 2022 (Table \ref{tab:nwfsc-hkl-obs}). Across all sample years and sample sites the `r hkl`  has observed a total of 1,213 `r spp`. While `r spp` have been observed both outside and inside the CCAsin areas that restric take or MPAs (Figures \ref{fig:nwfsc-hkl-site}), the vast majority of observations of `r spp` have been in open areas (1,060 observations, Table \ref{tab:nwfsc-hkl-obs}).  The number of `r spp` observations within the no take areas of the CCAs or MPA and open areas was explored to determine if the catch rates of `r spp` differed among the areas which determined there was not a significant different in the observations among these areas. Additionally, the data from the `r hkl` was broken out into three regions: mainland, Northern Channel Islands, and Southern Channel Islands.  The highest catch rate of `r spp` was observed around the Northern Channel Islands (Figure \ref{fig:nwfsc-hkl-region-main}). 

While `r spp` have not been encountered is large numbers similar to some of the other commonly encountered species (vermilion/sunset, bocaccio, greenspotted rockfish) in the `r hkl`, `r spp` has been observed every year that the survey has been conducted (Table \ref{tab:nwfsc-hkl-pos-year}). Observations of `r spp` commonly occur across a range of depths between 30 - 120 m with observations peaking around 80 m (Table \ref{tab:nwfsc-hkl-pos-depth} and Figure \ref{fig:nwfsc-hkl-depth}). The STAT explored alternative model structures to generate a standardized index of relative abundance. The final model selected was a model with a delta-lognormal model with factors of year, region, drop,  covariates of number of vermilion and bocaccio observed, year region interaction, and with random site effects. A single index of abundance was calculated using all observations from this survey (Figure \ref{fig:nwfsc-hkl-index-main}). Details regarding the index of abundance, sample sizes and model selection can be found in the Appendix Section \ref{nwfsc-hkl-model}.

#### Composition Data 
\

`r Spp` caught in the `r hkl` were generally between 30 and 50 cm for both sexes (Figures \ref{fig:nwfsc-hkl-site-len} and \ref{fig:hkl-len-data}). The number of lengths and ages collected by the survey are shown in Table \ref{tab:nwfsc-hkl-samples} and the length-at-age by sex is shown in Figure \ref{fig:nwfsc-hkl-len-age}. The mean length observed by year was variable with an appreciable drop in the mean sized observed in 2012 but has gradually increased in the subsequent years (Figure \ref{fig:mean-hkl-len-data}). 

<!--chapter:end:21s-hkl.Rmd-->

### California Department of Fish and Wildlife Remotely Operated Vehicle Survey

#### Index of Abundance
\

```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text",'10_appendix_rov.Rmd')
read_child(filein)
```

The number of transects by year, location, site designation, and the numbers of `r spp` observed are shown in Table \ref{tab:rov-obs}. South of Point Conception the CDFW ROV survey generally saw the largest numbers of `r spp` north of the Channel Islands similar to the `r hkl` (Figure \ref{fig:rov-obs-loc}). The trend in the calculated catch-per-unit-effort based on the data alone was highly variable across sampling locations and by MPA or Reference area (Figure \ref{fig:rov-raw-cpue}).   

CDFW provided an initial analysis of the CDFW ROV survey data which helped form the considered modeling approaches for these data. The STAT explored alternative model structures to generate a standardized index of relative abundance for this survey. The final model selected was a model was a delta-gamma hurdle model where the numbers of fish observed were predicted by year, site designation (MPA or Reference), proportion soft terrain, year/site designation interaction, and random effect for the year/location interaction  Details regarding the index of abundance, sample sizes and model selection can be found in the Appendix Section \ref{cdfw-rov-index}.

#### Composition Data 
\

Length measurement were made from images taken with stereo-cameras by the CDFW ROV survey in 2014, 2015, 2019, 2020, and 2021. The ROV was equipped with two locally recorded stereo cameras mounted in a fixed orientation in parallel with the primary forward-facing camera used for navigation, identification and enumeration. Paired stereo video cameras were calibrated to provide accurate feature measurements by MARE prior to in-field data collection. Fish length was determined based on a photogrammetric intersection to calculate 3D coordinates from measured image coordinates to measure fork length to the nearest millimeter. Processors selected two 3D points, fish head and tail, on both time-synced port and starboard stereo images. Processors made note of an generated precision value that was computed alongside each measurement. The software then computed the Euclidean distance between the two 3D points to give a length measurement. Sizes were rounded to the nearest centimeter. The precision of estimates was determined and represents the repeatability and geometric quality of a measurement, and is dependent upon the location of the individual in the camera view and the clarity of the point measured. Precision values greater than 10 mm were recorded in the database alongside measurements, as precision values less than 10 mm meant measurements were deemed fully repeatable. Fish observations from initial species scoring were marked “not sizable” if the nose/tail of the fish was cut off in either stereo view, the fish was missing in one view, or the orientation of the fish obscured measurement or produced an extreme precision measurement. Fish were marked “not visible” if the fish was not visible in either the port or starboard image. Fish marked “not sizable” and “not visible” were removed from the final data set submitted by CDFW. 

The sizes observed by MPA and Reference areas north and south of Point Conception varied with a higher density of smaller fish being observed in the Reference areas (Figure \ref{fig:rov-len}). The length data by designation, MPA and Reference, were weighted based on the estimated rocky habitat within each designation north and south of Point Conception (73 and 80 percent of areas open to fishing in the north and south, respectively,  see Appendix Section \ref{cdfw-rov-index} for additional information). The CDFW ROV survey observed `r spp` between 15-50 cm in length with lower mean lengths observed in 2014 and 2015 compared to the later period between 2019-2021 (Figures \ref{fig:rov-len-data} and \ref{fig:mean-rov-len-data}).

<!--chapter:end:21s-rov.Rmd-->

### Growth Data {#growth-data}

A significant amount of additional length-at-age not associated with fishery fleets or surveys incorporated in the model were available for `r spp`. These age data collection efforts from three programs `r area` since 2004: 621 otoliths collected by the NWFSC WCGBT survey, 33 otoliths collected by a research survey conducted by Don Pearson, and 506 otoliths collected by a cooperative research survey by the SWFSC and CPFV funded by the Sportfishing Association of California (Table \ref{tab:growth-age-samps}). Numerous explorations were conducted to evaluate how best to incorporate these data within the base model were conducted. These data were split into two growth fleets based on the collection method. The samples from the `r wcgbt` were split into their own growth fleet and the lengths associated with the ages were added to the model to estimate a length-base selectivity for these samples collected via trawl gear (Figures \ref{fig:growth-wcgbt-len} and \ref{fig:growth-mean-wcgbt-len}).  The ages collected by Pearson and the CPFV cooperative research samples were combined into a second growth fleet. The length associated with these fish were included in the model to estimate a length-based selectivity (Figures \ref{fig:growth-coop-len} and \ref{fig:growth-mean-coop-len}). These collection had a wide distribution of length and ages observed (Figures \ref{fig:growth-len-dist} and \ref{fig:growth-age-dist}).

<!--chapter:end:21s-ygrowth.Rmd-->

## Additional Considered Data Sources


```{r, echo=FALSE, results='asis'}
filein <- file.path(doc_dir, "shared_text",'21_surveys_not_included_pisco_scuba.Rmd')
read_child(filein)
```

Early years with less consistent sampling were eliminated such that the time series for UCSB began in 2004 and extended through 2021.  Sites surveyed by UCSB were mixed in distribution inside and outside MPA locations and therefore were not filtered for this criterion.  After filtering, sites that remained in the UCSC dataset were centered around the northern Channel Islands with a few on the Santa Barbara Channel mainland.  Sample sizes of `r spp` observed by year at all retained sites ranged from 15 to 39 fish for UCSB (Table: nCPR_table_N_S.csv). 

```{r, echo=FALSE, results='asis'}
filein <- file.path(doc_dir, "shared_text",'21_surveys_not_included_other.Rmd')
read_child(filein)
```


### Northwest Fisheries Science Center West Coast Groundfish Bottom Trawl Survey

The Northwest Fisheries Science Center (NWFSC) West Coast Groundfish Bottom Trawl (WCGBT) survey is based on a random-grid design; covering the coastal waters from a depth of 55-1,280 m [@bradburn_2003_2011]. This design generally uses four industry-chartered vessels per year assigned to a roughly equal number of randomly selected grid cells and divided into two 'passes' of the coast. Two vessels fish from north to south during each pass between late May to early October. This design therefore incorporates both vessel-to-vessel differences in catchability, as well as variance associated with selecting a relatively small number (approximately 700) of possible cells from a very large set of possible cells spread from the Mexican to the Canadian borders.

The observations of `r spp` by the `r wcgbt` are limited. The `r wcgbt` uses trawl gear to sample sandy bottom areas off the West Coast and _a priori_ it would not be expected to be an informative data source for `r spp`, which are generally more closely associated with rock substrate. The `r wcgbt` had limited positive tows by year that observed `r spp` within this area, preventing the calculation of an index of abundance for `r spp` (Table \ref{tab:wcgbt-pos-tows}). The catch-per-unit-effort across all years for the NWFSC WCGBT survey is generally small, excluding one single tow from 2012 where 1.9 mt of `r spp` were caught (Figure \ref{fig:wcgbt-cpue}). The observations of `r spp` by the NWFSC WCGBT survey commonly occur between 50 - 120 meters (Figure \ref{fig:wcgbt-depth}). The `r wcgbt` has regularly collected length and age samples from positive tows for `r spp` `r area` (Figure \ref{fig:wcgbt-len-age}). These data were used as conditional-age-at-length data to inform the estimation of growth within the model. See the [Length-at-Age](#length-at-age) section for data used to inform growth estimation.


### California Cooperative Oceanic Fisheries Investigations

The California Cooperative Oceanic Fisheries Investigations (CalCOFI) survey began in 1951 and conducts quarterly cruises off southern and central California, collecting a suite of hydrographic and biological data at fixed stations and while underway; ichthyoplankon sampling with a paired bongo started in 1978. Data on larval abundance from the CalCOFI Ichthyoplankton survey have been used in stock assessments of several species, including bocaccio, cowcod and shortbelly rockfish. Although the long-term dataset is limited to a subset of species for which morphological identification of larvae has been possible, recent research has been successful at identifying a broader range of species based on genetic
identification of larvae (Thompson et al. 2016). Larval fish were enumberated from winter samples from 1998 to 2013.  Out of 36 sites, 12 observed a larval `r spp` at least once, predominantly around the northern Channel Islands.  After selecting for only those sites that observed `r spp`, we examined the proportion of positive net tows by year and the average number of `r spp` observed per tow.  Given that these values were low and the sites observing `r spp` were not well distributed, we did not use these data to develop a recruitment index for use in the assessment. 

### Southern California Bight Publicly Owned Treatment Works

In the Southern California Bight, a number of monitoring programs exist to evaluate the potential consequences of effluent discharges from waste water treatment facilities on the coastal marine environment. As over 20 million people live within an hour’s drive of the ocean in this region, a major impact to this ecosystem includes a cumulative total of 1.5 billion
liters of treated effluent released each day to the ocean, originating from 17 major waste water treatment plants. Most of these publicly owned treatment works support monitoring programs to evaluate the impacts on water and sediment quality, and associated ecological communities. For several, this includes bottom trawl surveys of coastal habitats, and data from the longest running trawl surveys, despite being limited spatially to waters closer to population centers, have previously been used in stock assessments of cowcod (_Sebastes levis_) [@dick_status_2019] and California scorpionfish (_Scorpaena guttata_) [@monk_status_2017]. Investigations indicated the `r spp` are rarely observed in this survey and did not support the development of an index for this assessment.

<!--chapter:end:21s-zsurveys_not_included.Rmd-->

## Biological Data

### Natural Mortality

```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text",'2_biology_natural_mortality.Rmd')
read_child(filein)
```


### Maturation and Fecundity {#maturation-and-fecundity}

```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text",'2_biology_maturity.Rmd')
read_child(filein)
```

The 50 percent size-at-maturity for `r spp` `r area `was estimated at `r round(model$MGparmAdj[,"Mat50%_Fem_GP_1"][1], 1)` cm with a slope of `r round(model$MGparmAdj$Mat_slope_Fem_GP_1[1], 2)` (Figure \ref{fig:maturity}). This area-specific maturity-at-length estimate is relatively similar but with fish maturing at a slightly smaller size compared to the biological maturity curve assumed for `r spp` north of Point Conception. Additionally, these values are both slightly smaller compared to estimates by Hannah [-@hannah_length_2014] for fish observed in Oregon waters (34.8 cm) which estimated the 50 percent size-at-maturity of and slope of -0.60.

```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text",'2_biology_fecundity.Rmd')
read_child(filein)
```


### Sex Ratio

```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text",'2_biology_sex_ratio.Rmd')
read_child(filein)
```


### Length-Weight Relationship

```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text",'2_biology_weight_length.Rmd')
read_child(filein)
```


### Growth (Length-at-Age) {#length-at-age}

Length-at-age was estimated for male and female `r spp` informed by age data from the fisheries, the CCFRP survey, and independent age data collected effort from three programs `r `area` since 2002: 207 otoliths collected by the NWFSC WCGBT survey, 427 otoliths collected by a research survey conducted by Don Pearson, 77 from a research survey conducted by Abrams, and 508 otoliths collected by a cooperative research survey by the SWFSC and CPFV funded by the Sportfishing Association of California (Table \ref{tab:growth-age-samps}). The ages collected by these three sources were included in the model as a "growth" fleet that was not associated with removals or an index of abundance. 

Sex-specific growth parameters `r area` were initially estimated external to the model at the following values:

\begin{centering}

Females $L_{\infty}$ = 45.1; $L1$ = 1.13 cm; $k$ = 0.257 per year

Males $L_{\infty}$ = 44.8 cm; $L1$ = 4.75 cm; $k$ = 0.262 per year

\end{centering}

\vspace{0.50cm}

These values were used as starting parameter values within the base model prior to estimating each parameter for male and female `r spp`.


### Ageing Precision and Bias


```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text",'2_biology_ageing_error.Rmd')
read_child(filein)
```

<!--chapter:end:22biology.Rmd-->

## Environmental and Ecosystem Data

This assessment did not explicitly incorporate environmental data.

<!--chapter:end:23enviro.Rmd-->

# Assessment Model

<!--chapter:end:30model.Rmd-->

## Summary of Previous Assessments and Reviews

### History of Modeling Approaches 


```{r, echo=FALSE, results='asis'}

filein = file.path(doc_dir, "shared_text", '31_summary_previous_assessments.Rmd')
read_child(filein)
```


### Most Recent STAR Panel and SSC Recommendations 


```{r, echo=FALSE, results='asis'}

filein = file.path(doc_dir, "shared_text", '31_ssc_summary.Rmd')
read_child(filein)
```


### Response to Groundfish Subcommittee Requests

To be completed post-STAR panel.

<!--chapter:end:31summary.Rmd-->

## Model Structure and Assumptions

### Modeling Platform and Structure

```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text",'31_modeling_platform.Rmd')
read_child(filein)
```


### Model Selection and Evaluation

The base assessment model for `r spp` was developed to balance parsimony and realism, and the goal was to estimate a spawning output trajectory for the population of `r spp` off the west coast of the U.S. The model contains many assumptions to achieve parsimony and uses many different sources of data to estimate reality. A series of investigative model runs were done to achieve the final base model.


### Model Changes from the Last Assessment 


```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text",'31_changes_in_model_structure.Rmd')
read_child(filein)
```


### Bridging Analysis

The exploration of models began by bridging from the 2021 data-moderate assessment to Stock Synthesis version 3.30.21, which produced the same estimates for spawning biomass and depletion across the time series (Figures \ref{fig:bridge-ssb} and \ref{fig:bridge-depl}). Additional bridging analysis was conducted examining the impact on a revised model structure and updating and adding new data into the model. First, the 2021 fishery fleet structure was modified from the 2021 structure where the new assessment separated commercial data into two fleets based on fish landed condition, dead or live, and the recreational data into two fleets, CPFV and PR. The 2021 recreational and commercial data were reprocessed  into the new model structure through 2021 and new selectivity parameters were added to the 2021 for the newly split data. The new data available in for this assessment were then added to the model retaining the same model structure where feasible in the following order:

1. Update externally estimated biology parameters for length-at-age, weight-at-age, and maturity.
2. Add new catch data for all fishery fleets.
3. Add all updated commercial and recreational length and age data.
4. Add the new fishery-dependent indices of abundance.
5. Add the CDFW ROV survey index of abundance and length data.
6. Add the CCFRP index of abundance, length, and age data.
7. Add the updated NWFSC Hook and Line survey index of abundance, length, and age data.
8. Add selectivity blocks for the commercial and recreational fishing fleets.
9. Turn on the estimation of annual recruitment deviations.
10. Add conditional-age-at-length data for the growth fleet and estimate growth parameters for both sexes.

The data bridging are shown in Figures \ref{fig:data-bridge-ssb-1}-\ref{fig:data-bridge-depl-2}. Revising the model structure, updating biology, removals, length data and adding ages and fishery-dependent indices results in small changes to the estimated spawning output and stock status (Figures \ref{fig:data-bridge-ssb-1} and \ref{fig:data-bridge-depl-1}). Adding and updating survey data, adding selectivity blocks, and estimating annual recruitment deviations and growth resulted in larger revisions in the population estimates.  The largest changes in the new model relative to the 2021 assessment occurred when annual recruitment deviations were estimates resulting in a decrease in spawning output and stock status at the end of the time-series (Figures \ref{fig:data-bridge-ssb-2} and \ref{fig:data-bridge-depl-2}). Similar estimates were observed in 2021 assessment that included a sensitivity that estimated annual recruitment deviations. 

To arrive at a final base model additional revisions to the model structure, selectivity blocks, revised selectivity parameterization were done in order to determine the best fit to the data.


### Key Assumptions and Structural Choices

The specifications of the assessment are listed in Table \ref{tab:model-structure}. The model is a two-sex, age-structured model starting in 1916 with an accumulated age group at 50 years. Growth and natural mortality were assumed time invariant with constant growth estimated and natural mortality fixed at the median of the prior for both sexes. The lengths in the population were tracked by 1 cm intervals and the length data were binned into 2 cm intervals. Stock Synthesis estimates growth in the age and size plus group. To avoid issues with additional estimated growth in the plus groups, the selection of the maximum age and length bins were selected to ensure that the numbers of fish in the plus group would be low.

Time blocks on selectivity were explored extensively when setting up the initial model structure. A range of management changes to the commercial were considered when determining periods of when selectivity may have been expected to change. Commercial removals for `r spp` are relatively low when compared to recreational removals for this species which limited the amount of composition data available to support estimation of changes in selectivity. Given this and the limited evidence in the available length data, time-invariant selectivity was selected for both the commercial dead and live fish fleets. The same time block structure was assumed both the recreational CPFV and PR fleets based on gear restrictions and depth closures. Selectivity blocked into three periods: 1916-1999, 2000-2004, and 2005-2022, Model exploration revealed that that selectivity in the first and third time blocks were highly similar so the these two time periods were set to have equal selectivity. In 2022 the sub-bag limit in the California recreational fishery was reduce to only allow one `r spp`. However, the amount of length samples in 2022 were not informative about a change in selectivity. Finally, a change in selectivity was explored for the `r hkl` to shift sometime between 2012-2014, years where the number of MPA and CCA sites increased within the the survey. Exploratory models did not reveal a meaningful shift in the selectivity for this survey in that time period for `r spp` and for model parsimony a single selectivity for this fleet was assumed. 

The specification of when to estimate recruitment deviations is an assumption that affects the estimate of early model uncertainty around stock scale and status. Recruitment deviations were estimated from 1880 - 2020 to appropriately quantify uncertainty in the early model years. The earliest length- and age-composition data occur in 1975 but age data were not consistently on a yearly basis until 2003. The most informed years for estimating recruitment deviations were from about the mid-1990s to 2018. The period from 1880 - 1964 was fit using an early recruitement deviation series with little or no bias adjustment, the main period of recruitment deviates occurred from 1965 - 2020 with an upward and downward ramping of bias adjustment, and 2021 onward recruitment deviations were assumed to be 0 due to limited information at the end of the time-series. [-@methot_adjusting_2011a] summarize the reasoning behind varying levels of bias adjustment based on the information available to estimate the deviates. The standard deviation of recruitment variability was assumed to be 0.60 based on the estimated variation in recruitment from the base model.

The following distributions were assumed for data fitting wher the survey indices were lognormal and the compositional
data had a multinomial error structure.


### Priors

```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text",'31_model_priors.Rmd')
read_child(filein)
```


### Data Weighting

Length composition data for the commercial fishery started with a sample size determined from the equation listed in Sections \ref{commercial-fishery}. The input sample size for the length composition data from recreational fishery was determined based on the number of estimated trips (described in Sections \ref{recreational-fishery}), both the CCFRP and `r hkl` were set equal to the number of positive drops by year, the CDFW ROV were set equal to the number of positive transects, the `r wcgbt` was set equal to the number of fish, and the Pearson Research survey and CPFV cooperative collection program set equal to the number of trips. The majority of age-composition data were input as conditional-age-at-length with input sample size equal to the number of ages. The age-composition data from both the commercial dead and historical CPFV samples were used as marginal age-composition with the input sample size set equal to the number of ages.     

The base  model was weighted using the "Francis method", which was based on equation TA1.8 in Francis [-@francis_data_2011] which was selected based on model stability and consistency in the model to identify the minimum likelihood estimate (MLE). This formulation looks at the mean length or age and the variance of the mean to determine if across years, the variability is explained by the model. If the variability around the mean does not encompass the model predictions, then that data source should be down-weighted. This method accounts for correlation in the data (i.e., the multinomial distribution). Sensitivities were performed examining the difference in the model fits and results due to in weighting using McAllister-Ianelli Harmonic Mean Weighting [-@mcallister_bayesian_1997] and the Dirichlet Multinomial Weighting [-@thorson_model-based_2017].

### Model Parameters

There were 186 estimated parameters in the base model. These included one parameter for $R_0$, 10 parameters for growth, 5 parameters for extra variability for the fishery and survey indices, 29 parameters for length-based selectivity and time blocking of the fleets and the surveys, and 141 recruitment deviations including 35 pre-model estimates (Table \ref{tab:params}).

Fixed parameters in the model were as follows. Steepness was fixed at 0.72, the mean of the prior. A sensitivity analysis and a likelihood profile were performed for steepness. Natural mortality was fixed at 0.108 yr^-1^ for females and males, the median of the prior. Estimation of natural mortality was explored during model development. The estimate of natural mortality uncertain and poorly informed by the data. When estimated natural mortality was low (around 0.090 yr^-1^) relative to the median of the prior which was based on maximum age; however, well within the prior distribution (SE = 0.31). The observations of fish greater than 50 years of age across the West Coast, not only this assessment area, is rare, so a natural mortality that would be associated with a maximum around 60 years of age did not seem well supported. Natural mortality was fixed in the base model but estimation of this parameter for both sexes was explored via sensitivies.

The standard deviation of recruitment deviates was fixed at 0.60 ($\sigma_R$). Maturity-at-length was fixed as described above in Section \ref{maturation-and-fecundity}. Length-weight parameters were fixed at external estimates based on estimates using the `r hkl` and `r wcgbt` length-weight observations (Figure \ref{fig:est-len-wght}).

<!--chapter:end:32structure.Rmd-->

## Base Model Results

The base model described here is only for the portion of the stock `r spp` in California.  Descriptions of the summed biomass and stock status for the California stock of `r spp` are described in later sections.  

The base model parameter estimates along with approximate asymptotic standard errors (SD column) are shown in Table \ref{tab:params} and the likelihood components are shown in Table \ref{tab:south-likes}. Estimates of derived reference points and approximate 95 percent asymptotic confidence intervals for only the population `r area` are shown in Table \ref{tab:south-referenceES}. Estimates of the `r spp` population size `r area` over time are shown in Table \ref{tab:south-timeseries}. 

### Parameter Estimates

The estimates of growth parameters by sex varied relative to the externally estimated starting values.  The length-at-age 2 and the length-at-age 20 estimates for both sexes was slightly less than the external estimates but were well within the 95 percent confidence interval given the estimated uncertainty (Table \ref{tab:params} and Figure \ref{fig:mod-est-len-age}). The estimated $k$ for female were greater than the values estimated externally using the survey age data while the male value was similar to the external estimate (`r round(model$parameters[model$parameters$Label == "VonBert_K_Fem_GP_1", 3],3)` yr^-1^ for females and `r round(model$parameters[model$parameters$Label == "VonBert_K_Mal_GP_1", 3],3)` yr^-1^ for males).  The majority of female and male `r spp` growth occurs at younger ages, reaching near maximum length by age 10-15, with female `r spp` reaching marginally larger maximum lengths (Figure \ref{fig:mod-est-len-age}). 

Length-based selectivity curves were estimated for the fishery and survey fleets. The majority of fishery and survey fleets were parameterizing using the double normal selectivity paramterization in SS3 except for the commercal dead and `r hkl` fleet with were parameterized as logistic asymptotic selectivity. The estimated selectivities are shown in Figure \ref{fig:est-selex}. The selectivity for commercial dead fleet was estimated to be asymptotic . The commercial live fish fishery selects fish at small sizes with dome-shaped selectivity. Both recreational fleets were estimated dome-shaped selectivity for each selectivity period with the CPFV fleet selecting a higher portion of large fish at the end of the time series. The CCFRP and CDFW ROV surveys estimated peak selectivity around 40 cm with selectivity decreasing for larger fish. The `r hkl` estimated asymptotic selectivity only reaching maximum selectivity for the largest fish. The `r wcgbt` which samples soft bottom via trawl gear had relatively low selectivity for the majority of sizes with only selectivity peaking at the largest sizes. Finally, the estimated length-based selectivity from the CPFV cooperative collection and Pearson Reseach study was asymptotic with full selectivity for fish of 35 cm and larger.  Both of these last two fleets included only lengths and ages to inform growth estimation. As noted in the Growth data section that describes these data, the estimated selectivity for the samples collected by the CPFV vessels participating in the cooperative sampling program was distinctly than that from the CPFV fleet operating `r area` as a whole.  This is likely due to the areas accessible and trip type (half-day, three-quarter day, or overnight) between the CDFW districts 1 and 2 within this area.

The catchability for each of the surveys was analytically solved comparing observed to expected vulnerable biomass across all years. The analytical values for catchability were very small given the survey methodologies and are reported in Table \ref{tab:params} in log-space.  Additional fishery and survey index variability, process error added directly to each year's input standard deviation for the were estimated within the model. The model estimated the largest added variance of `r round(model$parameters[model$parameters$Label == "Q_extraSD_Rec_Private(4)", 3], 3)` for the recreational PR fishery index. In contrast the model estimated only limited additional variability in order to fit the recreational CRFS CPFV fishery index (`r round(model$parameters[model$parameters$Label == "Q_extraSD_CRFS_CPFV(8)", 3], 3)`). The model fit the trends in the `r hkl` index of abundance relatively well with only a small amount of added variance  being estimated to fit this time series (`r round(model$parameters[model$parameters$Label == "Q_extraSD_NWFSC_HKL(7)", 3], 3)`). The model estimated an added variance of `r round(model$parameters[model$parameters$Label == "Q_extraSD_CCFRP(5)", 3], 3)` and `r round(model$parameters[model$parameters$Label == "Q_extraSD_CDFW_ROV(6)", 3], 3)` to the indices from the CCFRP and CDFW ROV surveys, respectively.

The time series of estimated recruitments and annual recruitment deviations are shown in Figures \ref{fig:recruits} and \ref{fig:rec-devs}. Years with the highest recruitment deviations were estimated to have occurred in 2010 and 2013 with the lowest being estimated in 2018 and 2019. There is limited information regarding recruitment prior to 1980 but are estimated in the base model to account for uncertainty around the unfished condition.  The historical age age data from the CPFV fleet from 1975 were identified to have a disproportional influence on estimated recruitment in the late 1960s relative to all other data sources in the model. These data resulted in a sharp spike in recruitment during these years that was substantially higher than any other year in the model.  Given that these estimates were extreme and appeared to be informed by limited data, the decision was made to reduce the influence of this one year of limited age data for model stability (lambda value of 0.10 for these data). Sensitivities showed that the overall ending model estimates were not impacted by this decsion. Estimated recruitment deviations during years with the majority of the compositional data, after 1980, have relatively high uncertainty intervals indicating lack of support for clear strong or poor recruitment years across data sources. Recruitment deviations after 2017 are relatively uncertain but with large negative recruitment deviations. Recruitment is estimated based on the spawner-recruit curve in 2021 and 2022  (Figure \ref{fig:bh-curve}). The recruitment bias adjustment applied within the model across years is shown in Figure \ref{fig:bias-adjust}.


### Fits to the Data

Fits to the length data are shown based on the Pearson residuals-at-length, the annual mean lengths, and aggregated length composition data for the fishery and survey fleets in the model. Annual length composition fits are shown in the Appendix, Section \ref{length-data}.  

The Pearson residuals for the commercial dead fishery length data are shown in Figure \ref{fig:com-dead-pearson}. The data across time are limited making it difficult to discern patterns in the Pearson residuals across time particularly since the data were not sufficient to support the estimation in varying selectivity across time which would be expected given changes in management. The mean length observed by year from the commercial fleet were uncertain but with a relatively stable mean size in the final years of the model but with a larger mean size observed in the available data prior to 1990 (Figure \ref{fig:com-dead-mean-len-fit}). There were only limited ages available from the commercial dead fleet in 2022 with a rather large Pearson residuals (Figures \ref{fig:agg-marg-age-fit} and \ref{fig:com-dead-age-pearson}), noting that there were only 8 ages available that happened to all be female. The Pearson residuals for the commercial live fish fishery did not appear to have patterns or periods of misfit to th data (Figure \ref{fig:com-live-pearson}) and the model appeared to fit the mean size across time which was highly variable (Figure \ref{fig:com-live-mean-len-fit}). 

The Pearson residuals for the recreational CPFV length data are variable by year (Figure \ref{fig:rec-cpfv-pearson}). Pearson residuals were positive, observations greater than expected, for larger fish prior in the earliest data. Additionally, there appears to be a series of diagonal positive residuals moving across years starting around 2005 which may be a year-class moving through the population that the model is under-estimating. Explorations of alternative selectivity forms failed to resolve this pattern in residuals. The mean length observed by the CPFV fleet was fit relatively well by the model with the largest mean size being observed in the early years of the data with the mean size roughly stabilizing between the late 1980s though 2010, after which there was a mean decline in the mean size and then slowly increasing at the end of the model period (Figure \ref{fig:rec-cpfv-mean-len-fit). Age data were available for the CPFV fleet only in 1975 with all ages being unsexed fish (Figure \ref{fig:agg-marg-age-fit}). The peak of the distribution of these ages was under-fit by the model (Figure \ref{fig:rec-cpfv-age-pearson}). These ages where highly influential in model leading to a large recruitment deviation that was significantly higher than any other year estimated. All data weighting approaches explored wanted to significantly upweight these data. Due to the highly influential nature of this single year of data these data were downweighted in the model. Model explorations showed that down-weighting of these data did not effect the ending model estimates but resulted in a more stable model.



### Population Trajectory

### Reference Points



<!--chapter:end:33results.Rmd-->

## Model Diagnostics

### Convergence

Proper convergence was determined by starting the minimization process from dispersed values of the maximum likelihood estimates to determine if the model found a better minimum. Starting parameters were jittered using the jitter function built into Stock Synthesis, using jitter input of 0.10. This was repeated 100 times with only XX out of 100 runs returning to the base model likelihood. However, a better, lower negative log-likelihood, model fit was not found. In the jittering analysis models with similar log-likelihood values (difference < 0.50 units) were often found with little difference in overall model estimates indicating a relatively flat likelihood surface around the maximum likelihood estimate. Additionally, jitters using a smaller jitter value yielded an increased frequency of runs returning to the base model with no models finding a better fit to the data. Through the jittering done as explained and likelihood profiles, we are confident that the base model as presented represents the best fit to the data given the assumptions made. There were no difficulties in inverting the Hessian to obtain estimates of variability, although much of the early model investigation was done without attempting to estimate a Hessian.

### Sensitivity Analyses {#sensitivities}

Sensitivity analyses were conducted to examine the relative influence of specific changes to data inputs and model structural assumptions to further address uncertainty associated with the base model estimates and derived management quantities.  The majority of the sensitivity models are the result of a single change relative to base model (i.e., they are not the result of cumulative changes such as the modeling approach used with the bridging analysis). Comparisons of likelihood values and estimates of key parameters from the sensitivity analysis are shown in Tables \ref{tab:tab-sens-1}-\ref{tab:tab-sens-2} and Figures \ref{fig:sens-ssb-1}-\ref{fig:sens-depl-2}. Many additional sensitivity runs were explored during development and testing of the base model. This section focuses on the main data and structural sensitivity model runs and includes the following:
Structural Sensitivities

\begin{enumerate}
   
  \item  list of items

\end{enumerate}

Data Sensitivities

\begin{enumerate}
   
  \item Remove ...
  
\end{enumerate}


### Retrospective Analysis

A ten-year retrospective analysis was conducted by successively removing years of data ranging from 2013 - 2022 (i.e., "Data -1 Years" corresponds to data through 2021). 

Figure \ref{fig:retro-ssb}
Figure \ref{fig:retro-depl}

### Likelihood Profiles

Likelihood profiles were conducted for $R_0$, steepness, and sex-specific natural mortality values separately. These likelihood profiles were conducted by fixing the parameter at specific values and estimated the remaining parameters based on the fixed parameter value.

Figure \ref{fig:r0-profile}
Figure \ref{fig:r0-ssb}
Figure \ref{fig:r0-depl}

Figure \ref{fig:h-profile}
Figure \ref{fig:h-ssb}
Figure \ref{fig:h-depl}

Figure \ref{fig:m-profile}
Figure \ref{fig:m-ssb}
Figure \ref{fig:m-depl}

### Historical Analysis

### Unresolved Problems and Major Uncertainties

<!--chapter:end:34diagnostics.Rmd-->

# Management {#management}

## Reference Points

Reference points were calculated using the estimated selectivity and catch distributions among fleets in the most recent year of the model (`r endyr`, Table \ref{tab:south_referenceES}). The estimated sustainable total yields  were `r round(model$derived_quants[model$derived_quants$Label == 'Dead_Catch_SPR', 'Value'], 2)` mt when using an $\text{SPR}_{50\%}$ reference harvest rate. The spawning output equivalent to 40 percent of unfished spawning output ($\text{SB}_{40\%}$) was `r round(model$derived_quants[model$derived_quants$Label == 'SSB_Btgt', 'Value'], 2)` million eggs. 

The `r endyr` spawning output relative to unfished equilibrium spawning output, `r round(100*model$derived_quants[model$derived_quants$Label == 'Bratio_2023','Value'], 1)` percent, is below the management threshold limit of 25 percent of unfished spawning output (Figure \ref{fig:depl}). The fishing intensity, $1-\text{SPR}$, has been above the harvest rate limit ($\text{SPR}_{50\%}$) in recent years, except 2020 when overall removals declined due to impacts of COVID-19 which reduced recreational fishing effort (Table \ref{tab:south_timeseries} and Figure \ref{fig:1-spr}). The stock is estimated to be below the management target with fishing intensity exceeding the target across recent years (Figure \ref{fig:phase}). Table \ref{tab:south_referenceES} shows the full suite of estimated reference points for the base model and Figure \ref{fig:yield} shows the equilibrium curve based on a steepness value fixed at `r model$parameters[model$parameters$Label == "SR_BH_steep","Value"]`.

## Unresolved Problems and Major Uncertainties

```{r, echo=FALSE, results='asis'}
filein = file.path(getwd(),'shared_text','unresolved_problems_uncertainties.Rmd')
read_child(filein)
```

## Harvest Projections and Decision Tables

A ten year projection of the base model with catches equal to the estimated Acceptable Biological Catch (ABC) based on the category 2 time-varying $\sigma$ with $P^*$ = 0.45 for years 2023-2032 (Table XX). Since the stock is estimated to be below the management target of 40 percent the buffer value in Table XX reflects both the 40-10 harvest control rule adjustment and the time-varying scientific uncertainty buffer.

The removals in 2021 and 2022 were initially determined by first summing the adopted ACLs South of 40$^\circ$ 10' Lat. N. and the portion of the North of 40$^\circ$ 10' Lat. N. allocated to California (25 percent - PFMC Groundfish Management Team pers. comm.). Once the total ACLs for California were determined the portion of the ACL allocated to the area south of Point Conception was based on the percentage of total removals in each area of California (north and south of Point Conception) from 2017 - 2019 based on recommendations from the Grounfish Management Team. 

The axes of uncertainty in the decision table is based on the uncertainty around the spawning biomass in `r endyr+1` ($\sigma$ = `r round(model$Pstar_sigma,3) ` ) via the log($R_0$) parameter. The $\sigma$ value was used to identify the 12.5 and 87.5 percentiles of the asymptotic standard deviation for the current year, `r endyr+1`, spawning biomass from the base model to identify the low and high states of nature (i.e., 1.15 standard deviations corresponding to the 12.5 and 87.5 percentiles). Once the `r endyr + 1` spawning biomass for the low and high states of nature were identified a search across log($R_0$) values were done to attain the current year spawning biomass values. The log($R_0$) values that corresponded with the lower and upper percentiles were XX and XX.  

Across the low and high states of nature and across alternative future harvest scenarios the fraction of unfished ranges between XX - XX by the end of the 10 year projection period (Table XX). The fraction unfished across the state of natures assuming the ACL removals (the ABC adjusted by the 40:10 harvest control rule) remains below the management target.  


## Evaluation of Scientific Uncertainty

```{r, echo=FALSE, results='asis'}
filein = file.path(getwd(), "shared_text",'scientific_uncertainty.Rmd')
read_child(filein)
```

## Research and Data Needs

<!--chapter:end:40management.Rmd-->

# Acknowledgments
Here are all the mad props!

<!--chapter:end:41acknowledgments.Rmd-->

\clearpage

# References
<!-- If you want to references to appear somewhere before the end, add: -->
<div id="refs"></div>
<!-- where you want it to appear -->
<!-- The following sets the appropriate indentation for the references
  but it cannot be used with bookdown and the make file because it leads
  to a bad pdf.
\noindent
\vspace{-2em}
\setlength{\parindent}{-0.2in}
\setlength{\leftskip}{0.2in}
\setlength{\parskip}{8pt}
 -->

<!--chapter:end:49bibliography.Rmd-->

\clearpage
# Tables

<!-- ======================================================= -->
<!-- ***************    Catches      *********************** --> 
<!-- ======================================================= -->

```{r, results = 'asis'}

years = startyr:endyr
nfleets = 4
dead_all = NULL

for (i in 1:nfleets){
  name = paste0("dead(B):_",i)
  dead = model$timeseries[model$timeseries$Yr %in% years, name]
  dead_all = cbind(dead_all, dead)
}
total.dead  <- round(apply(dead_all, 1, sum), 1)
out = cbind(years, round(dead_all, 1), total.dead)
out = as.data.frame(out)
col_names = c("Year", "Commercial (Dead)", "Commercial (Live)", "Rec. CPFV", "Rec. PR", "Total Landings")

table_format(x = out,
             caption = "Removals (mt) by fleet and the summed total landings (mt).",
             label = "allcatches",
             digits = 1,
             align = 'l',
             col_names = col_names)
```

\newpage

<!-- ======================================================= --> 
<!-- *********** Removals vs. OFL/ACL   ******************** --> 
<!-- ======================================================= --> 

```{r, results = 'asis'}

create_management_table(
  management_dir = management_dir, 
  doc_dir = doc_dir, 
  doc_names = c("nca", 'sca'),
  years = 2012:2022,
  table_names = c("copper_ca_north.csv", "copper_ca_south.csv"),
  prefix = NULL)

```

\newpage

<!-- ======================================================= -->
<!-- *************** Com. Catch Ratio  ********************* --> 
<!-- ======================================================= -->

\include{tex_tables/historical_landings_tables_2020_revised_Avila_1953.tex}

\newpage

<!-- ======================================================= -->
<!-- *************** Commercial Data *********************** --> 
<!-- ======================================================= -->

\include{tex_tables/south_dead_trips_and_samples.tex}

\newpage

\include{tex_tables/south_live_trips_and_samples.tex}

\newpage

<!-- ======================================================= -->
<!-- ************* Recreational Data *********************** --> 
<!-- ======================================================= -->

\include{tex_tables/rec_south_sample_size_by_program.tex}


\newpage


<!-- ======================================================= -->
<!-- ***************   Discard Data  *********************** --> 
<!-- ======================================================= -->



<!-- ======================================================= -->
<!-- ********************   CCFRP    *********************** --> 
<!-- ======================================================= -->

\input{tex_tables/south_ccfrp_drifts_length_ages.tex}

\newpage

<!-- ======================================================= -->
<!-- *************  NWFSC HKL  Data  *********************** --> 
<!-- ======================================================= -->


\input{tex_tables/nwfsc_hkl_positive_samples_by_year.tex}

\pagebreak

\input{tex_tables/nwfsc_hkl_positive_samples_by_depth.tex}

\pagebreak

\input{tex_tables/nwfsc_hkl_sample_number_by_site_cca.tex}

\pagebreak

\input{tex_tables/nwfsc_hkl_effn_lengths_ages.tex}


<!-- ======================================================= -->
<!-- *************     CDFW  ROV     *********************** --> 
<!-- ======================================================= -->

\input{tex_tables/rov_south_samples_transects.tex}

\newpage

<!-- ======================================================= -->
<!-- *************    Growth Ages    *********************** --> 
<!-- ======================================================= -->

\input{tex_tables/south_growth_age_samples.tex}

\newpage

<!-- ======================================================= -->
<!-- *************  NWFSC WCGBT  Data  *********************** --> 
<!-- ======================================================= -->

\input{tex_tables/wcgbt_samples_by_year.tex}

\newpage

<!-- ======================================================= -->
<!-- ***********   Model Structure      ******************** --> 
<!-- ======================================================= -->

\input{tex_tables/model_structure_south.tex}

\newpage

<!-- ======================================================= -->
<!-- ***********   Model Parameters     ******************** --> 
<!-- ======================================================= -->


```{r, results = 'asis'}
mod_params = model$parameters[, 
                                (names(model$parameters) %in%
                                c("Num","Label","Value","Phase","Min",
                                  "Max","Status","Parm_StDev",
                                  "Pr_type","Prior","Pr_SD"))] 
mod_params[,'Value'] = round(as.numeric(mod_params[,'Value']),3)                                 
# Combine bounds into one column
mod_params$Min = paste('(', mod_params$Min, ', ', mod_params$Max, ')', sep='')
# Combine prior info to one column
mod_params$PR_type = ifelse(mod_params$Pr_type == 'No_prior' , 'None', paste(mod_params$Pr_type,' (', mod_params$Prior,  ', ', mod_params$Pr_SD, ')', sep = ''))
# Set long value to scientific notation
mod_params[mod_params$Label == "Wtlen_1_Fem",3] = format(mod_params[mod_params$Label == "Wtlen_1_Fem",3], scientific = TRUE)
mod_params[mod_params$Label == "Wtlen_1_Mal",3] = format(as.numeric(mod_params[mod_params$Label == "Wtlen_1_Mal",3]), scientific = TRUE)
mod_params[mod_params$Label == "Eggs_scalar_Fem",3] = format(as.numeric(mod_params[mod_params$Label == "Eggs_scalar_Fem",3]), scientific = TRUE)
mod_params[mod_params$Label == "L_at_Amax_Mal_GP_1",3] = round(as.numeric(mod_params[mod_params$Label == "L_at_Amax_Mal_GP_1",3]), 4)
mod_params[mod_params$Label == "VonBert_K_Mal_GP_1",3] = round(as.numeric(mod_params[mod_params$Label == "VonBert_K_Mal_GP_1",3]), 3)
mod_params[mod_params$Label == "CV_old_Mal_GP_1",3] = round(as.numeric(mod_params[mod_params$Label == "CV_old_Mal_GP_1",3]), 3)
# Remove the max, prior and prior sd columns
drops = c('Max', 'Prior', 'Pr_type', 'Pr_SD', 'Num')
mod_params = mod_params[, !(names(mod_params) %in% drops)]
rownames(mod_params) = c()
mod_params[,"Label"] = gsub("\\_", " ", mod_params[,"Label"])
mod_params[,"PR_type"] = gsub("\\_", " ", mod_params[,"PR_type"])
# Add column names
col_names = c('Parameter',
                         'Value',
                         'Phase',
                         'Bounds',
                         'Status',
                         'SD',
                         'Prior (Exp.Val, SD)')
table_format(x = mod_params,
             caption = "List of parameters used in the base model, including estimated values and standard deviations (SD), bounds (minimum and maximum), estimation phase (negative values not estimated), status (indicates if parameters are near bounds), and prior type information (mean and SD).",
             label = "params",
             align = 'l',
             col_names = col_names,
             longtable = TRUE,
             font_size = 9,
             landscape = TRUE,
             custom_width = TRUE,
             col_to_adjust = c(1,7), 
             width = c("7cm", "4cm"))                         
```

\newpage

<!-- ======================================================= -->
<!-- ***********    Like Contributions  ******************** --> 
<!-- ======================================================= -->

\include{tex_tables/south_likelihoods.tex}

\newpage

<!-- ======================================================= -->
<!-- ********  Reference Points & Management *************** --> 
<!-- ======================================================= -->

\include{tex_tables/south_e_ReferencePoints.tex}

\newpage


<!-- ======================================================= -->
<!-- ***********       Time Series      ******************** --> 
<!-- ======================================================= -->

\include{tex_tables/south_TimeSeries.tex}


\newpage


```{r, results = 'asis'}
create_biomass_table(
    doc_dir = doc_dir, 
    prefix = NULL,
    doc_names = c("nca", 'sca'),
    years = 2013:2023)

```

\newpage



```{r, results = 'asis'}

create_projection_table(
    management_dir = management_dir, 
    doc_dir = doc_dir, 
    fixed_removals = c(70, 70),
    doc_names = c("nca", 'sca'),
    years = 2023:2034,
    table_names = c("copper_ca_north.csv", "copper_ca_south.csv"),
    prefix = NULL)

```

\newpage

<!-- ======================================================= -->
<!-- ****************     Sensitivities      *************** --> 
<!-- ======================================================= -->

```{r, results = 'asis'}

tab <- read.csv(file.path(sens_dir, paste0(south_model_name, "_1_sensitivities_final.csv")), comment.char = "")

col_names = c('Parameter',
                         'Base Model',
                         'Estimate M',
                         'Estimate h',
                         'Estimate M & h',
                         'No Rec. Devs.',
                         'CPFV Selectiivty Asym.',
                         'Dirichlet DW', "McAllister-Iannelli DW")

table_format(x = tab,
             caption = "Estimates from each sensitivity.",
             label = "tab-sens-1",
             align = 'l',
             col_names = col_names,
             longtable = TRUE,
             font_size = 9,
             digits = 2, 
             landscape = TRUE,
             custom_width = TRUE,
             col_to_adjust = c(1), 
             width = c("7cm")) 
  

```


\newpage

```{r, results = 'asis'}

tab <- read.csv(file.path(sens_dir, paste0(south_model_name, "_2_sensitivities_final.csv")), comment.char = "")

col_names = c('Parameter',
                         'Base Model',
                         'Rm. Coop. Ages',
                         'Rm. WCGBT Ages',
                         'Rm. CCFRP',
                         'Rm. All Ages',
                         'Rm. CDFW ROV',
                         'Rm. NWFSC HKL',
                         'Rm. All Surveys', "Rm. Fishery Indices")

table_format(x = tab,
             caption = "Estimates from each sensitivity.",
             label = "tab-sens-2",
             align = 'l',
             col_names = col_names,
             digits = 2, 
             longtable = TRUE,
             font_size = 9,
             landscape = TRUE,
             custom_width = TRUE,
             col_to_adjust = c(1), 
             width = c("7cm")) 
  
```

\newpage

<!-- ======================================================= -->
<!-- ********  Reference Points & Management *************** --> 
<!-- ======================================================= -->

<!--chapter:end:52tables.Rmd-->

\clearpage
# Figures

## Data 

<!-- ====================================================================== --> 
<!-- *******************    Assessment Map      *************************** --> 
<!-- ====================================================================== --> 

```{r, results = 'asis'}
add_figure(
filein = file.path(doc_dir, "shared_figures", "map.png"), 
caption = "Map of management area and the 2023 assessments areas for copper rockfish",
label = 'ca-map')
```

\pagebreak

<!-- ====================================================================== -->  
<!-- ****************** Catches Used in the Model ************************* --> 
<!-- ====================================================================== -->  

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "catch2 landings stacked.png"), 
caption = "Landings by fleet used in the base model where catches in metric tons by fleet are stacked",
label = 'catch')
```	

\pagebreak
<!-- ====================================================================== --> 
<!-- ******************* Data Used in the Model *************************** --> 
<!-- ====================================================================== --> 

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "data_plot.png"), 
caption = "Summary of data sources used in the base model",
label = 'data-plot')
```	

\pagebreak
<!-- ======================================================= -->
<!-- *************** Commercial Data *********************** --> 
<!-- ======================================================= -->

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lendat_bubflt1mkt0.png"), 
caption = "Length composition data from the commercial dead fleet",
label = 'com-dead-len-data')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lendat_data_weighting_TA1.8_Commercial_dead.png"), 
caption = "Mean length for commercial dead fleet with 95 percent confidence intervals",
label = 'mean-com-dead-len-data')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lendat_data_weighting_TA1.8_Commercial_dead.png"), 
caption = "Age composition data from the commercial dead and recreational CPFV fleets. The commercial samples were all from 2022 and the CPFV samples were all from 1975",
label = 'com-dead-age-data')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(data_dir, "ages", "plots", "coop_crfs_length_comparison.png"), 
caption = "Comparison of all length collected by the CRFS sampling program for the CPFV fleet to the lengths from the fish with ages from the cooperative sampling program. The length distributions in the area north of Point Conception are in general agreement while the distribution of lengths collected by this program does not align with the length samples from CRFS.",
label = 'coop-len-comparison')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lendat_bubflt2mkt0.png"), 
caption = "Length composition data from the commercial live fleet",
label = 'com-live-len-data')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lendat_data_weighting_TA1.8_Commercial_live.png"), 
caption = "Mean length for commercial live fleet with 95 percent confidence intervals",
label = 'mean-com-live-len-data')
```

\pagebreak
<!-- ======================================================= -->
<!-- ************* Recreational Indices ******************** --> 
<!-- ======================================================= -->

```{r, results = 'asis'}
add_figure(
filein = file.path(data_dir, "rec_indices", "mrfss_cpfv_dockside", "south",  "forSS", "Index.png"), 
caption = "Estimated annual index of abundances for the CPFV fleet based on MRFSS survey data.",
label = 'mrfss-index-main')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(data_dir, "rec_indices", "crfs_cpfv_onboard", "south",  "main_effects", "Index.png"), 
caption = "Estimated annual index of abundances for the CPFV fleet based on CRFS survey data.",
label = 'crfs-index-main')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(data_dir, "rec_indices", "crfs_pr_dockside", "south",  "rm_last2yrs", "Index.png"), 
caption = "Estimated annual index of abundances for the CPFV fleet based on CRFS survey data.",
label = 'crfs-pr-index-main')
```

\pagebreak

<!-- ======================================================= -->
<!-- ************* Recreational Data *********************** --> 
<!-- ======================================================= -->

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lendat_bubflt3mkt0_page2.png"), 
caption = "Length composition data from the recreational CPFV fleet",
label = 'rec-cpfv-len-data')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lendat_data_weighting_TA1.8_Rec_CPFV.png"), 
caption = "Mean length for recreational CPFV fleet with 95 percent confidence intervals",
label = 'mean-rec-cpfv-len-data')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lendat_bubflt4mkt0_page2.png"), 
caption = "Length composition data from the recreation PR fleet",
label = 'rec-pr-len-data')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lendat_data_weighting_TA1.8_Rec_Private.png"), 
caption = "Mean length for recreational PR fleet with 95 percent confidence intervals",
label = 'mean-rec-pr-len-data')
```

\pagebreak

<!-- ======================================================= -->
<!-- *************  Add Survey Locations Map  ************** --> 
<!-- ======================================================= -->

```{r, results = 'asis'}
add_figure(
filein = file.path(data_dir, "survey_indices", "plots", "south_survey_locations_designation.png"), 
caption = "Sample locations by each of the fishery-independent data sources used in the base model with indices of abundance, lengths, and ages if collected.",
label = 'survey-locations')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(data_dir, "survey_indices", "plots", "south_survey_locations.png"), 
caption = "Sample locations by area, areas open to fishing (reference) and MPAS, for each of the fishery-independent data sources used in the base model with indices of abundance, lengths, and ages if collected.",
label = 'ref-mpa')
```

\pagebreak
<!-- ======================================================= -->
<!-- ***************     CCFRP           ******************* --> 
<!-- ======================================================= -->

```{r, results = 'asis'}
add_figure(
filein = file.path(data_dir, "survey_indices", "ccfrp", "south", "area_weighted", "Index.png"), 
caption = "Estimated index of abundance from the CCFRP survey",
label = 'ccfrp-index-main')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lendat_bubflt5mkt0.png"), 
caption = "Length composition data from the CCFRP survey",
label = 'ccfrp-len-data')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_gstagedat_bubflt5mkt0.png"), 
caption = "Age composition data from the CCFRP survey",
label = 'ccfrp-age-data')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lendat_data_weighting_TA1.8_CCFRP.png"), 
caption = "Mean length for the CCFRP survey with 95 percent confidence intervals",
label = 'ccfrp-mean-len-data')
```

\pagebreak


<!-- ======================================================= -->
<!-- ***************  NWFSC HKL Survey   ******************* --> 
<!-- ======================================================= -->

```{r, results = 'asis'}
add_figure(
filein = file.path(data_dir, "survey_indices", "nwfsc_hkl", "maps", "Map_HL_Sites_lndscp.jpg"), 
caption = "Area sampled by the NWFSC Hook and Line survey",
label = 'nwfsc-hkl-map')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(data_dir, "survey_indices", "nwfsc_hkl", "plots", "hkl_copper_by_site_count_all_years.png"), 
caption = "Observations of copper rockfish by the NWFSC Hook and Line survey by sample area, inside and outside Cowcod Conservation areas (CCA)",
label = 'nwfsc-hkl-site')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(data_dir, "survey_indices", "nwfsc_hkl", "plots", "raw_cpue_nwfsc_hkl_by_mpa_vs_open_by_region.png"), 
caption = "Raw CPUE inside and outside protected areas by region sampled by the NWFSC Hook and Line survey.",
label = 'nwfsc-hkl-region-main')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(data_dir, "survey_indices", "nwfsc_hkl", "plots", "nwfsc_hkl_observations_by_depth.png"), 
caption = "Number of observations by depth (m) inside and outside the CCAs.",
label = 'nwfsc-hkl-depth')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(data_dir, "survey_indices", "nwfsc_hkl", "glm_delta_lognormal_year_area_depth_drop_vermilion_bocaccio_all_areas_re_site_area_weighted", "Index.png"), 
caption = "Estimated index of abundance for copper rockfish.",
label = 'nwfsc-hkl-index-main')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(data_dir, "survey_indices", "nwfsc_hkl", "plots", "hkl_observations_by_length_sex_area.png"), 
caption = "Observed length (cm) distribution of copper rockfish by the NWFSC Hook and Line survey by sample area, inside and outside Cowcod Conservation areas (CCA)",
label = 'nwfsc-hkl-site-len')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(data_dir, "survey_indices", "nwfsc_hkl", "plots", "nwfsc_hkl_age_at_length.png"), 
caption = "Age and length by sex for copper rockfish in the NWFSC Hook and Line survey.",
label = 'nwfsc-hkl-len-age')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lendat_bubflt7mkt0.png"), 
caption = "Length composition data from the NWFSC Hook and Line survey",
label = 'hkl-len-data')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lendat_data_weighting_TA1.8_NWFSC_HKL.png"), 
caption = "Mean length for NWFSC Hook and Line survey with 95 percent confidence intervals",
label = 'mean-hkl-len-data')
```

\pagebreak

<!-- ======================================================= -->
<!-- ***************     ROV             ******************* --> 
<!-- ======================================================= -->

```{r, results = 'asis'}
sa4ss::add_figure(
filein = file.path(data_dir, "survey_indices", "rov", "plots", "rov_transect_collapsed_copper_south_protection_count.png"), 
caption = "The location and size of observations across all years and transects.",
label = 'rov-obs-loc')
```

\pagebreak

```{r, results = 'asis'}
sa4ss::add_figure(
filein = file.path(data_dir, "survey_indices", "rov", "plots", "south_raw_cpue_by_mpa_group_by_year.png"), 
caption = "The trend of the calculated CPUE by each MPA and Reference group by year.",
label = 'rov-raw-cpue')
```

\pagebreak

```{r, results = 'asis'}
sa4ss::add_figure(
filein = file.path(data_dir, "survey_indices", "rov", "plots", "rov_length_by_area_designation_april_data.png"), 
caption = "The distribution of lengths across all years for MPA and Reference areas north and south of Point Conception.",
label = 'rov-len')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lendat_bubflt6mkt0.png"), 
caption = "Length composition data from the CDFW ROV survey",
label = 'rov-len-data')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lendat_data_weighting_TA1.8_CDFW_ROV.png"), 
caption = "Mean length for the CDFW ROV survey with 95 percent confidence intervals",
label = 'mean-rov-len-data')
```

\pagebreak

<!-- ======================================================= -->
<!-- ***************     Growth Data      ****************** --> 
<!-- ======================================================= -->


```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lendat_flt9mkt0.png"), 
caption = "Length distribution by year for fish sampled by the NWFSC WCGBT survey.",
label = 'growth-wcgbt-len')
```

\pagebreak



```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lendat_data_weighting_TA1.8_WCGBT_Growth.png"), 
caption = "Mean length distribution by year for fish sampled by the NWFSC WCGBT survey.",
label = 'growth-mean-wcgbt-len')

```

\pagebreak


```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lendat_flt10mkt0.png"), 
caption = "Length distribution by year for fish sampled by the Pearson Research study (2005-2007) and the CPFV cooperative collection program (2022).",
label = 'growth-coop-len')
```

\pagebreak



```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lendat_data_weighting_TA1.8_COOP_Growth.png"), 
caption = "Mean length distribution by year for fish sampled by the Pearson Research Program (2005-2007) and the CPFV cooperative colletion program (2022).",
label = 'growth-mean-coop-len')
```

\pagebreak



```{r, results = 'asis'}
add_figure(
filein = file.path(data_dir, "ages",  "plots", "south_growth_length_comparison.png"), 
caption = "Length distribution of fish by collection source that were used as conditional age-at-length data in the growth fleet.",
label = 'growth-len-dist')
```

\pagebreak


```{r, results = 'asis'}
add_figure(
filein = file.path(data_dir, "ages",  "plots", "south_growth_age_comparison.png"), 
caption = "Age distribution of fish by collection source that were used as conditional age-at-length data in the growth fleet.",
label = 'growth-age-dist')
```

\pagebreak

<!-- ======================================================= -->
<!-- ***************  NWFSC WCGBT Survey  ****************** --> 
<!-- ======================================================= -->

```{r, results = 'asis'}
add_figure(
filein = file.path(data_dir, "wcgbt", "south", "plots", "cpue_map.png"), 
caption = "Location and catch-per-unit-effort by location caught south of Point Conception by the NWFSC WCGBT survey.",
label = 'wcgbt-cpue')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(data_dir, "wcgbt", "south", "plots", "presence-absence_proportion_by_depth.png"), 
caption = "Number of positive tows across all years by depth in meters.",
label = 'wcgbt-depth')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(data_dir, "wcgbt", "plots", "wcgbt_south_age_at_length_by_area.png"), 
caption = "Age and length by sex for copper rockfish caught south of Point Conception by the NWFSC WCGBT survey.",
label = 'wcgbt-len-age')
```

\pagebreak

## Biology

<!-- ======================================================= -->
<!-- ***************  life history  ************************ --> 
<!-- ======================================================= -->

```{r, results = 'asis'}
add_figure(
filein = file.path(doc_dir, "shared_figures", "copper_length_by_half_month.png"), 
caption = "Distribution of YOY copper rockfish lengths from fish genetically identified from D. Baetscher.",
label = 'copper-smurf-length')
```

\pagebreak

<!-- ======================================================= -->  
<!-- ******************   Biology  ************************* --> 
<!-- ======================================================= -->  

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "bio6_maturity.png"), 
caption = "Maturity as a function of length",
label = 'maturity')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "bio9_fecundity_len.png"), 
caption = "Fecundity as a function of length",
label = 'fecundity')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(data_dir, "wcgbt", "plots", "length_fraction_female.png"), 
caption = "Fraction of each sex by length by the NWFSC WCGBT survey",
label = 'frac-sex-len')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(data_dir, "biology", "plots", "Length_Weight_All.png"), 
caption = "Estimated weight-at-length",
label = 'weight-length')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(data_dir, "ages", "ageing_error", "B0_S3", "Reader_1_vs_Reader_2.png"), 
caption = "Distribution of double reads between age reader 1 and 2.",
label = 'age-error-dist')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots",  "numbers5_ageerrorSD.png"), 
caption = "Ageing imprecision standard deviation of observed age in years.",
label = 'age-error')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots",  "numbers10_ageerror_matrix_1.png"), 
caption = "Distribution of observed age at true age for ageing error type 1.",
label = 'age-error-matrix')
```

\pagebreak

## Model Results

### Bridging

<!-- ======================================================= -->  
<!-- ******************   Bridge   ************************* --> 
<!-- ======================================================= -->

```{r, results = 'asis'}
add_figure(
filein = file.path(bridge_dir, "_plots", "0_model_convert_compare2_spawnbio_uncertainty.png"),
caption = "Model version bridge comparison of estimated spawning output",
label = 'bridge-ssb')
```

\pagebreak

```{r, results = 'asis'}

add_figure(
filein = file.path(bridge_dir, "_plots", "0_model_convert_compare4_Bratio_uncertainty.png"),
caption = "Model version bridge comparison of estimated fraction unfished",
label = 'bridge-depl')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(bridge_dir, "_plots", "full_bridge_1_compare2_spawnbio_uncertainty.png"),
caption = "Model structure and data bridging comparison of estimated spawning output",
label = 'data-bridge-ssb-1')
```

\pagebreak

```{r, results = 'asis'}

add_figure(
filein = file.path(bridge_dir, "_plots", "full_bridge_1_compare4_Bratio_uncertainty.png"),
caption = "Model structure and data bridging comparison of estimated fraction unfished",
label = 'data-bridge-depl-1')
```

\pagebreak


```{r, results = 'asis'}
add_figure(
filein = file.path(bridge_dir, "_plots", "full_bridge_2_compare2_spawnbio_uncertainty.png"),
caption = "Model structure and data bridging comparison of estimated spawning output",
label = 'data-bridge-ssb-2')
```

\pagebreak

```{r, results = 'asis'}

add_figure(
filein = file.path(bridge_dir, "_plots", "full_bridge_2_compare4_Bratio_uncertainty.png"),
caption = "Model structure and data bridging comparison of estimated fraction unfished",
label = 'data-bridge-depl-2')
```

\pagebreak

<!-- ====================================================================== -->
<!-- *********************    Priors            ********************** --> 
<!-- ====================================================================== -->



### Biology

<!-- ====================================================================== -->
<!-- *********************  Model Est. Biology       ********************** --> 
<!-- ====================================================================== -->


```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "bio5_weightatsize.png"),
caption = "Assumed weight-length relationship for each sex.",
label = 'est-len-wght')
```


```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "bio1_sizeatage.png"),
caption = "Model estimated length-at-age in the beginning of the year. Shaded area indicates 95 percent distribution of length-at-age around the estimated growth curve",
label = 'mod-est-len-age')
```

\pagebreak

### Selectivity

<!-- ====================================================================== -->
<!-- *********************    Selectivity            ********************** --> 
<!-- ====================================================================== -->


```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "south_selectivity.png"),
caption = "Estimated selectivity for each fleet and survey in the base model.",
label = 'est-selex')
```




### Recruitment

<!-- ======================================================= -->  
<!-- ****************** Recruitment ************************ --> 
<!-- ======================================================= -->

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "ts11_Age-0_recruits_(1000s)_with_95_asymptotic_intervals.png"), 
caption = "Estimated time series of age-0 recruits (1000s)",
label = 'recruits')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "recdevs2_withbars.png"), 
caption = "Estimated time series of recruitment deviations",
label = 'rec-devs')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "SR_curve.png"), 
caption = "Stock-recruit curve. Point colors indicate year, with warmer colors indicating earlier years and cooler colors in showing later years",
label = 'bh-curve')
```

\pagebreak


```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "recruit_fit_bias_adjust.png"), 
caption = "Points are transformed variances. Red line shows current settings for bias adjustment specified in control file. Blue line shows least squares estimate of alternative bias adjustment relationship for recruitment deviations (which may or may not be an improvement)",
label = 'bias-adjust')
```



### Fits to Data

<!-- ====================================================================== -->
<!-- *************** Fit to the Length & Age Data  ************************ --> 
<!-- ====================================================================== -->

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lenfit_residsflt1mkt0.png"), 
caption = "Pearson residuals for commercial fleet. Closed bubble are positive residuals (observed > expected) and open bubbles are negative residuals (observed < expected)",
label = 'com-dead-pearson')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lenfit_data_weighting_TA1.8_Commercial_dead.png"), 
caption = "Mean length for commercial dead lengths with 95 percent confidence intervals based on current samples sizes",
label = 'com-dead-mean-len-fit')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_agefit__aggregated_across_time.png"), 
caption = "Age composition data aggregated across time by fleet.",
label = 'agg-marg-age-fit')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_agefit_residsflt1mkt0.png"), 
caption = "Pearson residuals for commercial dead age data. Closed bubble are positive residuals (observed > expected) and open bubbles are negative residuals (observed < expected)",
label = 'com-dead-age-pearson')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lenfit_residsflt2mkt0.png"), 
caption = "Pearson residuals for commercial live fleet. Closed bubble are positive residuals (observed > expected) and open bubbles are negative residuals (observed < expected)",
label = 'com-live-pearson')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lenfit_data_weighting_TA1.8_Commercial_live.png"), 
caption = "Mean length for commercial live fish lengths with 95 percent confidence intervals based on current samples sizes",
label = 'com-live-mean-len-fit')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lenfit_residsflt3mkt0_page2.png"), 
caption = "Pearson residuals for recreational CPFV fleet. Closed bubble are positive residuals (observed > expected) and open bubbles are negative residuals (observed < expected)",
label = 'rec-cpfv-pearson')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lenfit_data_weighting_TA1.8_Rec_CPFV.png"), 
caption = "Mean length for recreational CPFV lengths with 95 percent confidence intervals based on current samples sizes",
label = 'rec-cpfv-mean-len-fit')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_agefit_residsflt3mkt0.png"), 
caption = "Pearson residuals for recreational CPFV age data. Closed bubble are positive residuals (observed > expected) and open bubbles are negative residuals (observed < expected)",
label = 'rec-cpfv-age-pearson')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lenfit_residsflt4mkt0_page2.png"), 
caption = "Pearson residuals for recreational private/rental fleet. Closed bubble are positive residuals (observed > expected) and open bubbles are negative residuals (observed < expected)",
label = 'rec-pr-pearson')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lenfit_data_weighting_TA1.8_Rec_Private.png"), 
caption = "Mean length for recreational private/rental lengths with 95 percent confidence intervals based on current samples sizes",
label = 'rec-pr-mean-len-fit')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lenfit_residsflt5mkt0.png"), 
caption = "Pearson residuals for CCFRP survey length data. Closed bubble are positive residuals (observed > expected) and open bubbles are negative residuals (observed < expected)",
label = 'ccfrp-len-pearson')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lenfit_data_weighting_TA1.8_CCFRP.png"), 
caption = "Mean length for CCFRP survey lengths with 95 percent confidence intervals based on current samples sizes",
label = 'ccfrp-mean-len-fit')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_condAAlfit_residsflt5mkt0.png"), 
caption = "Pearson residuals for CCFRP survey conditional-age-at-length data. Closed bubble are positive residuals (observed > expected) and open bubbles are negative residuals (observed < expected)",
label = 'ccfrp-age-pearson')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lenfit_residsflt6mkt0.png"), 
caption = "Pearson residuals for CDFW ROV survey length data. Closed bubble are positive residuals (observed > expected) and open bubbles are negative residuals (observed < expected)",
label = 'rov-pearson')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lenfit_data_weighting_TA1.8_CDFW_ROV.png"), 
caption = "Mean length for CDFW ROV survey lengths with 95 percent confidence intervals based on current samples sizes",
label = 'rov-mean-len-fit')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lenfit_residsflt7mkt0.png"), 
caption = "Pearson residuals for NWFSC Hook and Line survey length data. Closed bubble are positive residuals (observed > expected) and open bubbles are negative residuals (observed < expected)",
label = 'nwfsc-hkl-pearson')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_lenfit_data_weighting_TA1.8_NWFSC_HKL.png"), 
caption = "Mean length for NWFSC Hook and Line survey lengths with 95 percent confidence intervals based on current samples sizes",
label = 'nwfsc-hkl-mean-len-fit')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_condAALfit_residsflt7mkt0_page1.png"), 
caption = "Pearson residuals for NWFSC Hook and Line survey conditional-age-at-length data. Closed bubble are positive residuals (observed > expected) and open bubbles are negative residuals (observed < expected)",
label = 'nwfsc-hkl-age-pearson-1')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_condAALfit_residsflt7mkt0_page2.png"), 
caption = "Pearson residuals for NWFSC Hook and Line survey conditional-age-at-length data. Closed bubble are positive residuals (observed > expected) and open bubbles are negative residuals (observed < expected)",
label = 'nwfsc-hkl-age-pearson-2')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_condAALfit_residsflt7mkt0_page3.png"), 
caption = "Pearson residuals for NWFSC Hook and Line survey conditional-age-at-length data. Closed bubble are positive residuals (observed > expected) and open bubbles are negative residuals (observed < expected)",
label = 'nwfsc-hkl-age-pearson-3')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_condAALfit_data_weighting_TA1.8_condAgeNWFSC_HKL.png"), 
caption = "Mean age for NWFSC Hook and Line survey age data with 95 percent confidence intervals based on current samples sizes",
label = 'nwfsc-hkl-mean-age-fit')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_condAALfit_residsflt9mkt0_page1.png"), 
caption = "Pearson residuals for the growth conditional-age-at-length data. Closed bubble are positive residuals (observed > expected) and open bubbles are negative residuals (observed < expected)",
label = 'growth-age-pearson-1')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_condAALfit_residsflt9mkt0_page2.png"), 
caption = "Pearson residuals for the growth conditional-age-at-length data. Closed bubble are positive residuals (observed > expected) and open bubbles are negative residuals (observed < expected)",
label = 'growth-age-pearson-2')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_condAALfit_residsflt9mkt0_page3.png"), 
caption = "Pearson residuals for the growth conditional-age-at-length data. Closed bubble are positive residuals (observed > expected) and open bubbles are negative residuals (observed < expected)",
label = 'growth-age-pearson-3')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_condAALfit_data_weighting_TA1.8_condAgeWCGBT_Growth.png"), 
caption = "Mean age for the growth age data with 95 percent confidence intervals based on current samples sizes",
label = 'growth-mean-age-fit-wcgbt')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "comp_condAALfit_data_weighting_TA1.8_condAgeCOOP_Growth.png"), 
caption = "Mean age for the growth age data with 95 percent confidence intervals based on current samples sizes",
label = 'growth-mean-age-fit')
```

\pagebreak
<!-- ======================================================= -->  
<!-- ************* Fit to the Indices ********************** --> 
<!-- ======================================================= -->

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "index5_logcpuefit_Rec_CPFV.png"), 
caption = "Fit to log index data on log scale for the recreational (MRFSS) CPFV index of abundance. Lines indicate 95% uncertainty interval around index values based on the model assumption of lognormal error. Thicker lines (if present) indicate input uncertainty before addition of estimated additional uncertainty parameter.",
label = 'mrfss-cpfv-index-fit')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "index5_logcpuefit_CRFS_CPFV.png"), 
caption = "Fit to log index data on log scale for the recreational CRFS CPFV index of abundance. Lines indicate 95% uncertainty interval around index values based on the model assumption of lognormal error. Thicker lines (if present) indicate input uncertainty before addition of estimated additional uncertainty parameter.",
label = 'crfs-cpfv-index-fit')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "index5_logcpuefit_Rec_Private.png"), 
caption = "Fit to log index data on log scale for the recreational private index of abundance. Lines indicate 95% uncertainty interval around index values based on the model assumption of lognormal error. Thicker lines (if present) indicate input uncertainty before addition of estimated additional uncertainty parameter.",
label = 'crfs-pr-index-fit')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "index5_logcpuefit_CCFRP.png"), 
caption = "Fit to log index data on log scale for the CCFRP index of abundance. Lines indicate 95% uncertainty interval around index values based on the model assumption of lognormal error. Thicker lines (if present) indicate input uncertainty before addition of estimated additional uncertainty parameter.",
label = 'ccfrp-index-fit')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "index5_logcpuefit_CDFW_ROV.png"), 
caption = "Fit to log index data on log scale for the CDFW ROV index of abundance. Lines indicate 95% uncertainty interval around index values based on the model assumption of lognormal error. Thicker lines (if present) indicate input uncertainty before addition of estimated additional uncertainty parameter.",
label = 'rov-index-fit')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "index5_logcpuefit_NWFSC_HKL.png"), 
caption = "Fit to log index data on log scale for the NWFSC Hook and Line index of abundance. Lines indicate 95% uncertainty interval around index values based on the model assumption of lognormal error. Thicker lines (if present) indicate input uncertainty before addition of estimated additional uncertainty parameter.",
label = 'nwfsc-hkl-index-fit')
```

\pagebreak

### Time-series

<!-- ======================================================= -->  
<!-- ****************** Time Series ************************ --> 
<!-- ======================================================= -->


```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "ts7_Spawning_output_with_95_asymptotic_intervals_intervals.png"), 
caption = "Estimated time series of spawning biomass",
label = 'ssb')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "ts1_Total_biomass_(mt).png"), 
caption = "Estimated time series of total biomass",
label = 'tot-bio')
```

\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "ts9_Relative_spawning_output_intervals.png"), 
caption = "Estimated time series of fraction of unfished spawning biomass",
label = 'depl')
```

\pagebreak

### Sensitivity Analyses and Retrospectives

<!-- ====================================================================== -->
<!-- ******************      Sensitivities    ***************************** --> 
<!-- ====================================================================== -->

 
```{r, echo=FALSE, results='asis'}
nm = paste0(south_model_name, "_final_1_compare2_spawnbio_uncertainty.png")
add_figure(
filein = file.path(sens_dir, "_plots",  nm),
caption = "Change in estimated spawning output by sensitivity",
label = 'sens-ssb-1')
```

\newpage

```{r, echo=FALSE, results='asis'}
nm = paste0(south_model_name, "_final_1_compare4_Bratio_uncertainty.png")
add_figure(
filein = file.path(sens_dir, "_plots", nm),
caption = "Change in estimated fraction unfished by sensitivity",
label = 'sens-depl-1')
```

\newpage

```{r, echo=FALSE, results='asis'}
nm = paste0(south_model_name, "_final_2_compare2_spawnbio_uncertainty.png")
add_figure(
filein = file.path(sens_dir, "_plots", nm),
caption = "Change in estimated spawning output by sensitivity",
label = 'sens-ssb-2')
```

\newpage

```{r, echo=FALSE, results='asis'}
nm = paste0(south_model_name, "_final_2_compare4_Bratio_uncertainty.png")
add_figure(
filein = file.path(sens_dir, "_plots", nm),
caption = "Change in estimated fraction unfished by sensitivity",
label = 'sens-depl-2')
```

\newpage


<!-- ====================================================================== -->
<!-- ******************     Retrospectives    ***************************** --> 
<!-- ====================================================================== -->


```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text",'34_retro_figures.Rmd')
read_child(filein)
```



### Likelihood Profiles

<!-- ====================================================================== -->
<!-- ******************       Profile         ***************************** --> 
<!-- ====================================================================== -->


```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text",'34_likelihood_figures.Rmd')
read_child(filein)
```



<!-- ====================================================================== -->
<!-- ************* Comparison w/ Previous Assessments ********************** --> 
<!-- ====================================================================== -->



### Reference Points and Forecasts

<!-- ====================================================================== -->
<!-- ******************    Reference Points    **************************** --> 
<!-- ====================================================================== -->


```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "SPR2_minusSPRseries.png"), 
caption = "Estimated 1 - relative spawning ratio (SPR) by year",
label = '1-spr')
```

\clearpage

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "SPR4_phase.png"), 
caption = "Phase plot of the relative biomass (also referred to as fraction unfished) versus the SPR ratio where each point represents the biomass ratio at the start of the year and the relative fishing intensity in that same year. Lines through the final point show the 95 percent intervals based on the asymptotic uncertainty for each dimension. The shaded ellipse is a 95 percent region which accounts for the estimated correlations between the biomass ratio and SPR ratio",
label = 'phase')
```


\pagebreak

```{r, results = 'asis'}
add_figure(
filein = file.path(model_dir, "plots", "yield2_yield_curve_with_refpoints.png"), 
caption = "Equilibrium yield curve for the base case model. Values are based on the 2022
fishery selectivities and with steepness fixed at 0.72",
label = 'yield')
```

\pagebreak

<!--chapter:end:53figures.Rmd-->

# Appendix A {#detailed-fit-comps}

## Detailed Fit to Length Composition Data {#length-data}

```{r, results='asis'}
plot_info = read.csv(file.path(model_dir, "plots", "plotinfotable_for_doc.csv"))
len_fit = plot_info[which(plot_info$category == "LenComp"), ]
plot.vec = grep("comp_lenfit_flt", len_fit$label)
filein = file.path(model_dir, "plots")
for (a in plot.vec){
	cap = len_fit$caption[a]
	lab = len_fit$label[a]
	add_figure(filein = file.path(filein, len_fit$file[a]), 
			   caption = cap, 
			   label = lab)
}
```

\newpage

## Detailed Fit to Age Composition Data {#age-data}


```{r, results='asis'}
plot_info = read.csv(file.path(model_dir, "plots", "plotinfotable_for_doc.csv"))
len_fit = plot_info[which(plot_info$category == "AgeComp"), ]
plot.vec = grep("comp_agefit_flt", len_fit$label)
filein = file.path(model_dir, "plots")
for (a in plot.vec){
	cap = len_fit$caption[a]
	lab = len_fit$label[a]
	add_figure(filein = file.path(filein, len_fit$file[a]), 
			   caption = cap, 
			   label = lab)
}
```

\newpage



## Detailed Fit to Conditional-Age-at-Length Composition Data {#caal-data}


```{r, results='asis'}
plot_info = read.csv(file.path(model_dir, "plots", "plotinfotable_for_doc.csv"))
len_fit = plot_info[which(plot_info$category == "A@LComp"), ]
plot.vec = c(grep("comp_condAALfit_residsflt5mkt0", len_fit$label),
  grep("comp_condAALfit_residsflt7mkt0", len_fit$label),
	grep("comp_condAALfit_residsflt9mkt0", len_fit$label))
find = sort(len_fit$label[plot.vec], index.return = TRUE)$ix
plot.vec = plot.vec[find[2:length(find)]]
filein = file.path(model_dir, "plots")
for (a in plot.vec){
	cap = len_fit$caption[a]
	lab = len_fit$label[a]
	add_figure(filein = file.path(filein, len_fit$file[a]), 
			   caption = cap, 
			   label = lab)
}
```


```{r, results='asis'}
plot_info = read.csv(file.path(model_dir, "plots", "plotinfotable_for_doc.csv"))
len_fit = plot_info[which(plot_info$category == "A@LComp"), ]
plot.vec = c(grep("comp_condAALfit_Andre_plotsflt5mkt0", len_fit$label),
  grep("comp_condAALfit_Andre_plotsflt7mkt0", len_fit$label),
	grep("comp_condAALfit_Andre_plotsflt9mkt0", len_fit$label))
find = sort(len_fit$label[plot.vec], index.return = TRUE)$ix
plot.vec = plot.vec[find[2:length(find)]]
filein = file.path(model_dir, "plots")
for (a in plot.vec){
	cap = len_fit$caption[a]
	lab = len_fit$label[a]
	add_figure(filein = file.path(filein, len_fit$file[a]), 
			   caption = cap, 
			   label = lab)
}

```

## Implied Fit to Excluded Length Data {#excluded-data}

The implied fits to the data not included in the base model due to low annual sample size are shown below.  

```{r, results='asis'}
plot_info = read.csv(file.path(model_dir, "plots", "plotinfotable_for_doc.csv"))
len_fit = plot_info[which(plot_info$category == "LenComp"), ]
plot.vec = c(grep("comp_gstlenfit_flt1mkt0", len_fit$label),
             grep("comp_gstlenfit_flt2mkt0", len_fit$label),
             grep("comp_gstlenfit_flt3mkt0", len_fit$label),
             grep("comp_gstlenfit_flt4mkt0", len_fit$label))
filein = file.path(model_dir, "plots")
for (a in plot.vec){
	cap = len_fit$caption[a]
	lab = len_fit$label[a]
	add_figure(filein = file.path(filein, len_fit$file[a]), 
			   caption = cap, 
			   label = lab)
}
``` 

\newpage

<!--chapter:end:60appendix_caal.Rmd-->

# Appendix B. MRFSS CPFV Dockside Index of Abundance {#mrfss-index}

```{r, echo=FALSE, results='asis'}

filein = file.path(getwd(), "shared_text",'mrfss_index.Rmd')
read_child(filein)
```

From 1980 to 2003 the MRFSS program conducted dockside intercept surveys of the 
recreational CPFV fishing fleet. No MRFSS CPUE data are available for the years 
1990-1992, due to a hiatus in sampling related to funding issues. Sampling of 
California CPFVs north of Point Conception was further delayed, and CPFV samples 
in 1993 and 1994 are limited to San Luis Obispo County. 
For purposes of this assessment, the MRFSS time series was truncated at 1999 due 
to sampling overlap with the 
onboard observer program, i.e., the same observer samples the catch while 
onboard the vessel and also conducts the dockside intercept survey for 
the same vessel.  The onboard observer data provide higher resolution data of retained 
and discarded catch.

Each entry in the RecFIN Type 3 database corresponds to a 
single fish examined by a sampler at a particular survey site. Since only a 
subset of the catch may be sampled, each record also 
identifies the total number of that species possessed by the group of anglers 
being interviewed.  The number of anglers and the hours fished are also recorded. 
The data, as they exist in RecFIN, do not indicate which records 
belong to the same boat trip. A description of the algorithms and process used to 
aggregate the RecFIN records to the trip level is outlined in the Supplemental Materials 
(“Identifying Trips in RecFIN”).

Trips recorded with a primary area fished in Mexico or in bays, e.g., 
San Francisco Bay, were excluded before any filtering on species composition.
For indices representing only north of Point Conception, the years 1993-1994 were 
excluded due to limited spatial coverage.

The Stephens-MacCall [-@Stephens2004] filtering approach was used to predict the 
probability of catching copper rockfish, based 
on the species composition of the sampler examined catch in a given trip. Prior 
to applying the Stephens-MacCall filter, we identified potentially informative 
predictor species, i.e., species with sufficient sample sizes and temporal coverage 
(present in at least 5\% of all trips) to inform the binomial model.  The remaining 
 xx species all co-occurred with copper rockfish in at least one trip 
and were retained for the Stephens-MacCall logistic regression. Coefficients 
from the Stephens-MacCall analysis (a binomial GLM) are positive 
for species that are more likely to co-occur with copper rockfish, 
and negative for species that are less likely to be caught with copper rockfish 
(Figure \@ref(fig:fig-sm-mrfss)).
The top five species with high probability of co-occurrence with copper rockfish include
copper, greenspotted, bocaccio, and olive rockfishes and ocean whitefish, all of which are associated with rocky reef and kelp 
habitats. The five species with the lowest probability of co-occurrence were 
kelp bass, Pacific bonito, white croaker, California sheephead, and barred sandbass.

While the filter is useful in identifying co-occurring or non-occurring species 
assuming all effort was exerted in pursuit of a single target, the targeting of 
more than one species or species complex ("mixed trips") can result in co-occurrence of species in the catch that do not truly co-occur in terms of habitat
associations informative for an index of abundance. Stephens and MacCall 
[-@Stephens2004] recommended including all trips above a threshold where the 
false negatives and false positives are equally balanced.  However, this does 
not have any biological relevance and for this data set, and we assume that if a 
copper rockfish was landed, the anglers fished in appropriate habitat, 
especially given copper rockfish is strongly associated with rocky habitat.


Stephens and MacCall [-@Stephens2004] proposed filtering (excluding) trips from the index 
standardization based on a criterion of balancing the number of false positives 
and false negatives. False positives (FP) are trips that are predicted to catch 
a copper rockfish based on the species composition of the catch, but did not. False 
negatives (FN) are trips that were not predicted to catch a copper rockfish, given the 
catch composition, but caught at least one. The Stephens-MacCall filtering method identified the probability of occurrence at which the rate of "false 
positives" equals "false negatives" of 0.31. The 
trips selected using this criteria were compared to an alternative method 
including all the "false positive" trips, regardless of the probability of 
encountering copper rockfish. 
This assumes that if copper rockfish were caught, the anglers must have fished in 
appropriate habitat during the trip. The catch included in this index is 
"sampler-examined" and the samplers are well trained in species identification.


The threshold probability that balances FP and FN excludes 
5383 trips that did not catch a copper rockfish (84% 
of the trips), and 308 trips (5% of the data) that 
caught a copper rockfish. We retained the latter set of trips (FN), assuming that 
catching a copper rockfish indicates that a non-negligible fraction of the fishing 
effort occurred in habitat where copper rockfish occur. Only “true negatives” 
(the 5383 
trips that neither caught copper rockfish, nor were predicted to catch them by the model) 
were excluded from the index standardization. The final dataset selected included 
1043 trips, 70% 
of which encountered copper rockfish.  Sample sizes by the factors selected to model are in Tables 
\@ref(tab:tab-region-mrfss) and \@ref(tab:tab-year-mrfss).


Initial exploration of negative binomial models for this dataset proved to be 
ill-fitting. The proportion of zeroes predicted by the Bayesian negative binomial 
models were different enough from the fraction of zeroes in the raw data, that 
a negative binomial model was not considered for model selection. We modeled catch 
per angler hour (CPUE; number of fish per angler hour) with a Bayesian delta-GLM model. 
Models incorporating temporal (year, 2-month waves) 
and geographic (region and primary area fished (inshore <3 nm, offshore >3 nm) 
factors were evaluated. For assessments north of Point Conception, two regions were defined based on counties, 1) Del Norte 
to Santa Cruz ("N") and 2) Monterey to San Luis Obispo ("C"). For assessment models south 
of Point Conception, the region represents individual counties. Note that Santa Barbara 
county spans north and south of Point Conception, but all accessible fishing ports in Santa Barbara county are south of Point Conception and vessels rarely (if ever) transit Point Conception.  Indices with a year and area interaction were not considered in model selection; trends in the average CPUE by region were similar in the filtered data set (Figure \@ref(fig:fig-areacpue-mrfss)). 

<!--For models that span counties north and south of Pt. Conception, Santa Barbara to 
San Diego counties compose a third region ("S"). 
-->

The positive observations were modeled with a Lognormal distribution 
that was selected over a Gamma model
by a $\Delta AIC$ of 51.8, and supported by Q-Q plots of the positive observations fit to both distributions (Figure \@ref(fig:fig-dist-fits-mrfss)).  The delta-GLM
method allows selection of differing linear predictors between the binomial and positive models. Based on AIC values from maximum likelihood fits, 

<!--chapter:end:61appendix_mrfss.Rmd-->



# Appendix C. California Onboard CPFV Index of Abundance {#onboard-cpfv-index}


```{r, echo=FALSE, results='asis'}
filein = file.path(getwd(), "shared_text",'crfs_cpfv_index.Rmd')
read_child(filein)
```

The CRFS onboard observer data went through a QA/QC process at the SWFSC which included mapping 
fishing drifts in ArcPro to determine if the recorded latitude and longitude were correct.  

In the assessment model, the recreational CPFV fleet is modeled as retained plus
discarded fish. The proportion of observed discarded copper rockfish is small, 
averaging 4% over the time series (\@ref(tab:onboard-keepdiscard)) and are included in the index.

We applied a number of data filters to the available data presented in Table 
\@ref(tab:onboard-filter). The onboard CPFV index restricts the time series to 2005-2019. The onboard observer survey 
began in 1999, but the sample sizes were small during the first year of the program. The 
years 1999-2004 also represent years where a number of regulations changed including gear limits, 
bag limits, and spatial closures.  Due to COVID-19, no onboard sampling took place in 2020. In 2021 the onboard sampling 
resumed in August, at which point a large portion of the southern California fleet 
had switched target species and fish highly migratory species. The 2021 stock assessment 
had also been released by August 2021 indicating the stock was below the biomass 
at 40%.  The southern California CPFV began an organized effort to avoid copper 
rockfish and encourage their clientele to release and descend copper rockfish 
when encountered. In 2022, the CDFW implemented the one copper rockfish sub-bag 
limit and combined with avoidance by the fleet, does not represent the available 
copper rockfish biomass. See the online supplementary material
or the history of regulation changes section for details.

The filters also included removal of the number of observed anglers and time fished at the tail 
ends of the distributions, remooval of drifts occurring in depths outside copper rockfish's range 
(Table \@ref(tab:onboard-filter) and Figure \@ref(fig:onboard-depths)). Because the availability of high resolution data were lacking 
for the south, we retained all drifts from within a CDFW block that had at least 100 drifts and 
at least 5% of those encountered copper rockfish. We retained 17,605 drifts for index
 standardization, and 3,035 of those drifts encountered copper rockfish 
Table \@ref(tab:onboard-percentpos). 

We modeled catch per angler minutes fished (CPUE) by fishing drift. Prior to any modeling,
the SWFSC QA/QC'd the data to ensure the location information was correct. 
Each drift was overlaid with the available interpreted substrate layer that characterizes rocky and hard substrate, assigned to a rocky reef and the distance of the 
drift start location calculated.  In addition, the depth of the start location was 
interpreted from the 2 m resolution bathymetry as well as 90 m resolution bathymetry 
layer for comparison. For drifts missing depth location, we assigned depth based on the best available depth based on the bathymetry.

To appropriately weight the onboard observer survey index by the available 
rocky substrate within a region, each drift was assigned to the closest area 
of rocky habitat. Hard bottom was extracted from 
the [California Seafloor Mapping Project](http://seafloor.otterlabs.org/index.html), 
along the mainland coast of southern California. These data 
were collected in state waters at a resolution of two meters, but did not extend into state waters 
past the mainland coast. Additional interpreted bathymetric data classifying the bottom type as 
rock or soft bottom were compiled by analysts at the University of California Santa Cruz and are now
also available from CDFW's website. We used the available interepreted rocky substrate data to expand the 
known area of rocky substrate to areas in southern California that lack substrate type.  This 
expansion of the estiamated rocky substrate assumes that the proportions of rocky substrate within 
and outside state waters are similar.  Copper rockfish are a nearshore species and the majority of 
observed encounters were within state waters (Table \@ref(tab:onboard-waterarea)).
is a course estimation of the amount of rocky substrate, and represents the best available data. 
The calculations can be found in the online supplementary material.

The covariates explored for model selection included year and four levels region as categorical 
region (District 1 mainland, District 2 mainland, Southern Channel Islands and Northern 
Channel Islands), a year and area interaction, categorical variable for month, and continuous depth and depth-squared.
rends in the average CPUE by region were similar 
in the filtered data set (Figure \@ref(fig:onboard-regioncpue)). A year and region interaction 
was included after visualizing the trends in average CPUE over time (Figure \@ref(fig:onboard-average_cpue_by_region)). The full model was selected by AICc 
(Table \@ref(tab:onboard-model_selection)). In southern California, whether a trip is a 1/3 or 3/4 or overnight 
trip has a significant impact on the available fishing grounds.  The 1/2 day CPFV vessels 
fishnthe shallower, nearshore waters along the along the mainland areas. The 3/4 and overnight or multi-day
vessels are able to access the same areas of the Northern Channel Islands, where as the southern Channel Islands 
are further offshore and the observations are predominantly from overnight trips. The overnight and 
multi-day trips may target multiple target species, i.e., tuna and rockfish, depending on the time of the year.

Indices were fit via MLE from the sdmTMB package in R. The QQ plot fot the negative binoimal 
model indicated a poor fit to the data, which as not surprising given the low percent of 
observed drifts encountering copper rockfish. A delta-Lognormal 
was selected over a delta-gamma by a delta AIC of xxxxx.  The QQ plot indicated a much improved fit compared to the negative 
binomaial model (Table \@ref(fig:onboard-qq)).

The final index was weighted based on the estimates of rocky substrate within each of the four regions. 
The relative abundance increases during the first part of the time series (Table \@ref(tab:onboard-index) 
and Figure \@ref(fig:onboard-index)).  

<!--Tables -->

```{r, results = 'asis'}
library(dplyr)
ind <- read.csv(file.path(data_dir, "rec_indices", "crfs_cpfv_onboard", "south",
                    "keep_discard_prop.csv")) %>%
  mutate(Proportion.discarded = scales::percent(round(Proportion.discarded,3)))
col_names = c("Year",	"Number Kept",	"Number Discarded", "Proportion discarded")

sa4ss::table_format(x = ind,
             caption = "Number of observed copper rockfish retained and discarded by year.",
             label = "onboard-keepdiscard",
             col_names = col_names)                         
```

\newpage

```{r, results = 'asis'}
ind <- read.csv(file.path(data_dir, "rec_indices", "crfs_cpfv_onboard", "south",
                    "start2005", "target_water_area.csv")) %>%
  mutate(percent_N = scales::percent(round(percent_N, 3)))
col_names = c("District", "Year", "Inside State Waters",	"Outside State Waters",
               "Percent Inside")

sa4ss::table_format(x = ind,
             caption = "Number of observed drifts inside and outside of state waters.",
             label = "onboard-waterarea",
             col_names = col_names)                         
```


\newpage

```{r, results = 'asis'}
ind <- read.csv(file.path(data_dir, "rec_indices", "crfs_cpfv_onboard", "south",
                    "start2005", "percent_pos.csv")) %>%
  mutate(percentpos = scales::percent(round(percentpos, 3)))
col_names = c("Year" ,"Trips with Target", "Trips without Target", "Total trips", "Percent with Target")

sa4ss::table_format(x = ind,
             caption = "Data filtering steps for the onboard CPFV survey.",
             label = "onboard-percentpos",
             col_names = col_names)
```

\newpage


```{r, results = 'asis'}
ind <- read.csv(file.path(data_dir, "rec_indices", "crfs_cpfv_onboard", "south",
                          "start2005", "data_filters.csv"))
col_names = c("Filter",	"Description",	"Number of Samples", "Positive Samples")

sa4ss::table_format(x = ind,
             caption = "Data filtering steps for the onboard CPFV survey.",
             label = "onboard-filter",
             col_names = col_names,
             col_to_adjust = c(3),
             width = c('5cm'))
```


\newpage

```{r, results = 'asis'}
ind <- read.csv(file.path(data_dir, "rec_indices", "crfs_cpfv_onboard", "south",
                    "model_selection.csv"))

sa4ss::table_format(x = ind,
             caption = "Model selection for the onboard CPFV survey.",
             label = "onboard-modelselect")                         
```


\newpage

```{r, results = 'asis'}

ind <- read.csv(file.path(data_dir, "rec_indices", "crfs_cpfv_onboard", 
                          "south", "start2005",
                            "area_weighted_logn", "index_forSS.csv"))
ind <- ind[, c(1,4,5)]
col_names = c("Year", "Estimate", "logSE")

sa4ss::table_format(x = ind,
             caption = "Estimated relative index of abundance for the onboard CPFV survey.",
             label = "onboard-index",
             col_names = col_names)                         
```

\newpage

<!--Figures -->


```{r, results = 'asis'}
sa4ss::add_figure(
filein = file.path(data_dir, "rec_indices", "crfs_cpfv_onboard", "south", 
                   "copper_depths_gisdepthadded.png"), 
caption = "Distribution by year of depths where copper rockfish observed.",
label = 'onboard-depths')
```
\newpage


```{r, results = 'asis'}
sa4ss::add_figure(
filein = file.path(data_dir, "rec_indices", "crfs_cpfv_onboard", "south",
                   "drifts_by_depth_district.png"),
caption = "Stacked bar plot of the depth of observed copper rockfish by district.",
label = 'onboard-depths')
```

\newpage

```{r, results = 'asis'}
sa4ss::add_figure(
filein = file.path(data_dir, "rec_indices", "crfs_cpfv_onboard", "south", "start2005",
                   "average_cpue_by_region.png"), 
caption = "Average CPUE by region prior to standardization.",
label = 'onboard-regioncpue')
```


\newpage

```{r, results = 'asis'}
sa4ss::add_figure(
filein = file.path(data_dir, "rec_indices", "crfs_cpfv_onboard", "south", "start2005",
                   "area_weighted_logn", "index.png"), 
caption = "Index for the onboard CPFV survey.",
label = 'onboard-index')
```

\newpage

```{r, results = 'asis'}
sa4ss::add_figure(
filein = file.path(data_dir, "rec_indices", "crfs_cpfv_onboard", "south","start2005",
                   "area_weighted_logn", "qq.png"), 
caption = "QQ-plot for the onboard CPFV survey.",
label = 'onboard-qq')
```

\newpage


<!--chapter:end:62appendix_crfs_onboard.Rmd-->

# Appendix D. CRFS PR Dockside Index of Abundance {#crfs-pr-index}

Catch and effort data from CRFS dockside sampling of private boats, 2004-2022, 
were provided by CDFW for use in this assessment. The PR dockside data housed 
on the Recreational Fisheries Information Network (RecFIN) were 
determined to include a number of complexities that precluded the ability to 
use them for an index of abundance. For the time period from 2004-2014 the authors 
re-created the interivew, or trip level, data from the "i" sample files.  For 2015-2022 
the authors used files provided by CDFW from the CRFS dockside sampling program.

The data for both time periods included catch by species, number of anglers contributing to the catch, angler-reported area of fishing, 
gear, county, port, interview site, year, month, and CRFS district. The catch included 
the number of fish observed by the CRFS sample, the number of unobserved retained fish reported 
by the angler, and the number of discarded and descended fish reported by the angler.
The sample size of the 
unfiltered private boat data is much larger than the CPFV onboard observer data set, 
with 256,738 samples statewide from 2004-2022, 169,912 south 
of Point Conception and 86,826 north of Point Conception. 

Records were limited to the primary private and rental boats public-access sites, 
PR1 sites, which encompasses over 90% of the total private boat effort 
(Table \@ref(tab:pr-filter)). The CRFS interviews contain a small fraction 
(407 trips over the entire time series) of samples where the retained catch for 
rockfish is over the daily bag limit of 10 
fish per person. We did not remove these data from the index, but did 
only include sampler examined catch.  Rockfish species can be difficult to distinguish and there 
have not been any verifiction studies conducted to determine the undertainty in angler reported 
unboserved catch.
Additional data filters included the exclusion of any samples from January and 
February, since those months have been closed to the recreational fishery south of Point 
Conception since 2005.  The time series was also restricted to 2004-2019.  Sampling during the 
COVID period (2020-2021) resulted in a higher fraction of the sampled examined catch in the 
"rockfish, general" 
category due to the social distancing requirements (Table \@ref(tab:pr-rfgen)). The CDFW 
implemented a one fish sub-bag 
limit for copper rockfish in 2022 and the qauntiles and distribution of CPUE suggest that this 
regulation change impacted fishing behavior in the private boat fleet (Table \@ref(tab:pr-cpue) and 
Figure \@ref(pr-bag)).

The angler reported water area was restricted to ocean areas in U.S. waters 
and a reported primary gear 
of hook-and-line or troll gear.  A number of trips with the primary gear reported troll reported
a secondary gear of hook-and-line. To determine if the angler(s) interviewed targeted rockfish and
fished in rocky habitat, we retained trips if the angler reported the primary target species 
as rockfish or bottomfish or if rockfish was reported as the secondary target species. This filter 
replaced the Stephens-MacCall (@stephens-multispecies-2004) filtering approach.

We retained 13,340 angler interviews for 
index standardization, with 3,739 included sampled examined copper rockfish
(Table \@ref(tab:pr-filter)).  

We modeled retained catch per angler days with a negative binomial GLM in the R package sdmTMB.
The QQ plots indicate a reasonable fit (Figure \@ref(fig:pr-qq)).  There are a handful of samples 
with higher than average CPUE and the authors check with CDFW to determine whether the samples should still be included. 
The CDFW indicated data sheets were not avaialble prior to 2012, but the catches were less than 
the bag limits, and should be assumed correct. Indices with a year and district interaction were not 
considered in model selection due to the fact that fishing locations are unknown; the scale of the relative 
abundance of copper is higher in District 2, but there is some overlap in the fishing locations accessed 
by this fleet (Figure \@ref(fig:pr-districtcpue)). 

Based on AICc values from maximum likelihood fits Table \@ref(tab:pr-modelselect)), 
a main effects model including year, month and primary target species as categorical covariates 
were selected (Table \@ref(tab:pr-index) and Figure \@ref(fig:pr-index)).

<!--Tables -->

\newpage

```{r, results = 'asis'}
ind <- read.csv(file.path(
  data_dir, "rec_indices", "crfs_pr_dockside", "bag_change_visuals",
  "pr_bag_limit_by_year.csv"
)) %>%
 mutate_at(2:6, funs(round(., 3)))

col_names <- c("Year", "Minimum", "Q1", "Q2", "Q3", "Maximum")

sa4ss::table_format(
  x = ind,
  caption = "Summary of the copper rockfish CPUE, number of fish retained per
             angler day, by year.",
  label = "pr-cpue",
  col_names = col_names
)
```

\newpage

```{r, results = 'asis'}
ind <- read.csv(file.path(
  data_dir, "rec_indices", "crfs_pr_dockside", "PR_obs_unobs.csv"
)) %>%
  mutate(Percent.RFGEN = scales::percent(Percent.RFGEN))

col_names <- c("Year", "Unspeciated", "Speciated", "Percent unspeciated")

sa4ss::table_format(
  x = ind,
  caption = "Summary of the number of speciated and unspeciated (RFGEN) rockfish 
  per year across all of California.",
  label = "pr-rfgen",
  col_names = col_names
)
```

\newpage

```{r, results = 'asis'}
ind <- read.csv(file.path(
  data_dir, "rec_indices", "crfs_pr_dockside", "south",
  "rm_last2yrs", "percent_pos.csv"
)) %>%
  mutate(percentpos = scales::percent(round(percentpos, 3)))
col_names <- c(
  "Year", "Trips with Target", "Trips without Target", "Total trips",
  "Percent with Target"
)

sa4ss::table_format(
  x = ind,
  caption = "Number of samples and percent positive for the dockside PR survey.",
  label = "pr-percentpos",
  col_names = col_names
)
```

\newpage


```{r, results = 'asis'}
ind <- read.csv(file.path(
  data_dir, "rec_indices", "crfs_cpfv_onboard", "south",
  "start2005", "data_filters.csv"
))
col_names <- c("Filter", "Description", "Number of Samples", "Positive Samples")

sa4ss::table_format(
  x = ind,
  caption = "Data filtering steps for the onboard CPFV survey.",
  label = "pr-filter",
  col_names = col_names,
  font_size = 9,
  landscape = TRUE,
  custom_width = TRUE,
  col_to_adjust = c(3),
  width = c("8cm")
)
```

\newpage

```{r, results = 'asis'}
ind <- read.csv(file.path(
  data_dir, "rec_indices", "crfs_pr_dockside", "south", "rm_last2yrs",
  "model_selection.csv"
))

sa4ss::table_format(
  x = ind,
  caption = "Model selection for the dockside PR survey.",
  label = "pr-modelselect"
)
```


\newpage

```{r, results = 'asis'}
ind <- read.csv(file.path(
  data_dir, "rec_indices", "crfs_pr_dockside",
  "south", "rm_last2yrs", "Index_forSS.csv"
))
ind <- ind[, c(1, 4, 5)]
col_names <- c("Year", "Estimate", "logSE")

sa4ss::table_format(
  x = ind,
  caption = "Estimated relative index of abundance for the dockside PR survey.",
  label = "pr-index",
  col_names = col_names
)
```

\newpage

<!--Figures -->


```{r, results = 'asis'}
sa4ss::add_figure(
  filein = file.path(
    data_dir, "rec_indices", "crfs_pr_dockside", "bag_change_visuals",
    "pr_copper_cpue_year_area_max5.png"
  ),
  caption = "Distribution by year of the number of copper rockfish retained per angler. 
  This includes sampler observed and angler reported catch. The vertical line at 1 represents the sub-bag 
  limit implemented in 2022.",
  label = "pr-bag"
)
```

\newpage

```{r, results = 'asis'}
sa4ss::add_figure(
  filein = file.path(
    data_dir, "rec_indices", "crfs_pr_dockside", "south", "rm_last2yrs",
    "average_cpue_by_district.png"
  ),
  caption = "Average CPUE by district prior to standardization.",
  label = "pr-districtcpue"
)
```


\newpage

```{r, results = 'asis'}
sa4ss::add_figure(
  filein = file.path(
    data_dir, "rec_indices", "crfs_pr_dockside", "south", "rm_last2yrs",
    "index.png"
  ),
  caption = "Index for the dockside PR survey.",
  label = "pr-index"
)
```

\newpage

```{r, results = 'asis'}
sa4ss::add_figure(
  filein = file.path(
    data_dir, "rec_indices", "crfs_pr_dockside", "south",
    "rm_last2yrs", "qq.png"
  ),
  caption = "QQ plot for the dockside PR survey.",
  label = "pr-qq"
)
```

\newpage


<!--chapter:end:64appendix_crfs_dockside.Rmd-->

# Appendix F. CCFRP Index of Abundance {#ccfrp-index}

The California Collaborative Fisheries Research Program, [CCFRP](https://www.mlml.calstate.edu/ccfrp/), 
is a fishery-independent 
hook-and-line survey designed to monitor nearshore fish populations at a series of sampling 
locations both inside and adjacent to MPAs 
[@starr_variation_2015a; @wendt_collaborative_2009].  The CCFRP survey began in 
2007 along the central coast of California and was designed in collaboration 
with academics, NMFS scientists and fishermen. 
From 2007-2016 the CCFRP project was focused on the central California coast,
and has monitored four MPAs consistently. In 2017, the CCFRP expanded coastwide within California.  
The University of California Santa Barbara and Scripps Institute of Oceanography conduct the 
southern Califonria CCFRP sampling and monitor xxx MPA and reference paired sites.

The survey design for CCFRP consists 500 x 500 m cells both within and 
adjacent to each MPA. On any given survey day site cells are randomly 
selected within a stratum (MPA and/or reference cells).  CPFVs are chartered 
for the survey and the fishing captain is allowed to search within the cell for 
a fishing location.  During a sampling event, each cell is fished for a total of 
30-45 minutes by volunteer anglers. Each fish encountered is recorded, measured, 
and can be linked back to a particular angler, and released (or descended to depth). 
CCFRP samples shallower depths to avoid barotrauma-induced mortality.  
Starting in 2017, a subset of fish have been retained to collect otoliths and fin 
clips that provide needed biological information for nearshore species. For the 
index of abundance, CPUE was modeled at the level of the drift, similar to the 
fishery-dependent onboard observer survey described above.

The CCFRP data are quality controlled at the time they are key punched and little 
filtering was needed for the index. Cells not consistently sampled over time were 
excluded as well as cells that never encountered `r spp`. Copper rockfish were observed 
at the South La Jolla, Carrington Point and and Anacapa Island.
The full dataset for these location in southern California contained xxx drifts, xx 
of which encountered `r spp`.  After applying filters to remove drfits from sites that 
were not consistently sampled, 
marked for exclusion in the data, or did not fish a minimum of two minute, 856 drifts 
remained for for index standardization, with 399 drifts encountering `r spp`. 

Trends among the three MPAs sampled differed with the majority of copper rockfish 
encountered by CCFRP at the Carrington Point MPA.  The trends in average CPUE over 
the six year time series inside 
and outside of the MPA both show a decline in copper rockfish CPUE. 
The final index (Table \@ref(tab:tab-index-ccfrp)) 
represents a similar trend to the unstandardized average 
CPUE (Figure \@ref(fig:fig-cpue-ccfrp)).

We modeled retained catch per angler hour (CPUE; number of fish per angler hour) 
using  Plots of the average CPUE inside (MPA) and outside (REF) MPAs at each site are 
in Figure \@ref(fig:ccfrp-sitecpue) and shows the distinct trends of decreasing average 
CPUE at Carrington Point.

A negative binomial model was fit to the drift-level data (catch with a log offset for angler 
hours). Because the average observed CPUE among the MPAs indidcated differing trends, we explore 
a region:year interaction, which was not significant. The model selected by AICc included depth, 
depth squared, region and MPA or reference site \@ref(tab:ccfrp-model)), The final model included
yrea, mpa/reference categorization, depth, depth squared, and a year:mpa/reference interaction. 
The model was fit using the sdmTMB R package (version xxx1). 


Based on work completed at the SWFSC, we estimated that the percent of rocky reef habitat 
from Point Conception to the California/Mexican border within state waters is 
892 $km^2$, of which approximately 23% is in MPAs that prohibit the harvest of 
groundfish (pers comm. Rebecca Miller, UCSC). There is recreational fishing outside 
of state waters, but habitat maps are not available at the same 2-m resolution and do 
not allow for direct comparisons. To estimate the area 
of rocky substrate south of Point conception, we separted the southern California Bight 
into four areas, 1) CRFS District 
1 along the mainland coast, 2) CRFS District 2 along the mainland coast, 
3) state waters encompassing the southern 
Channel Islands, and 4) state waters encompassing the northern Channel Islands. 
 We calculated the total area in each of the 
four regions, as well as the total area with available interpretted substrate. 
 By also calculating the total area open and closed to fishing, i.e., MPAs and CCAs, 
 we expanded the known fraction of rocky substrate to the areas within state 
waters where no substrated interpretted maps exist.  This resulted in an estimate of 
27% of the available rocky substrate 
within closed areas to fishing in southern California state waters. 


```{r, results = 'asis'}

tab <- read.csv(file.path(data_dir, "survey_indices", "ccfrp", "south", "dataFilters.csv"))

sa4ss::table_format(x = tab,
             caption = "Data filtering for the CCFRP survey.",
             label = "ccfrp-data-filter",
             align = 'l',
             longtable = TRUE,
             font_size = 7,
             landscape = TRUE)                         
```

\newpage

```{r, results = 'asis'}

tab <- read.csv(file.path(data_dir, "survey_indices", "ccfrp", "south", "model_selection.csv"))

sa4ss::table_format(x = tab,
             caption = "Model selection for the CCFRP survey.",
             label = "ccfrp-model-selection",
             align = 'l',
             longtable = TRUE,
             font_size = 7,
             landscape = TRUE)                         
```

\newpage

```{r, results = 'asis'}

ind <- read.csv(file.path(data_dir, "survey_indices", "ccfrp", "south", 
"area_weighted", "index_forSS.csv"))
ind <- ind[, c(1,4,5)]
col_names = c("Year", "Estimate", "logSE")

sa4ss::table_format(x = ind,
             caption = "Estimated relative index of abundance for the CCFRP survey.",
             label = "ccfrp-index",
             col_names = col_names)                         
```

\newpage

```{r, results = 'asis'}
sa4ss::add_figure(
filein = file.path(data_dir, "survey_indices", "ccfrp", "south", "area_weighted", "qq.png"), 
caption = "QQ-plot for the CCFRP survey.",
label = 'ccfrp-qq')
```

\newpage 

```{r, results = 'asis'}
sa4ss::add_figure(
filein = file.path(data_dir, "survey_indices", "ccfrp", "south", "mpa_site_cpue.png"), 
caption = "Average CPUE by site with trends prior to standardization in the MPA and REF areas.",
label = 'ccfrp-avg-cpue')
```

\newpage

```{r, results = 'asis'}
sa4ss::add_figure(
filein = file.path(data_dir, "survey_indices", "ccfrp", "south", "area_weighted", "Index.png"), 
caption = "The weighted relative index of abundance.",
label = 'ccfrp-index')
```



<!--chapter:end:65appendix_ccfrp.Rmd-->

# Appendix F. NWFSC Hook and Line Index of Abundance {#nwfsc-hkl-model}

Since 2004, the NWFSC has conducted an annual hook and line survey targeting shelf rockfish in the genus *Sebastes* at fixed stations (e.g., sites, Figure \ref{fig:nwfsc-hkl-map}) in the Southern California Bight. Key species of rockfish targeted by the `r hkl` are bocaccio (*S. paucispinis*), cowcod (*S. levis*), greenspotted (*S. chlorostictus*), and vermilion/sunset (*S. miniatus* and *S. crocotulus*) rockfishes, although a wide range of rockfish species have been observed by this survey. During each site visit, three deckhands simultaneously deploy 5-hook sampling rigs (this is referred to as a single drop) for a maximum of 5 minutes per line, but individual lines may be retrieved sooner at the angler's discretion (e.g., to avoid losing fish). Five drops are attempted at each site for a maximum possible catch of 75 fish per site per year (3 anglers x 5 hooks x 5 drops). Further details regarding the sample frame, site selection, and survey methodology are described by Harms et al. [-@harms_noaa_2008]. 

Over time, select sampling sites in the original survey design have been converted to either federal or state MPAs begining around 2011. Additionally, the survey began sampling in two cowcod conservation areas (CCA) in the California Bight starting in 2014 which has portions of depth where take is prohibited. The data were examined for potential impact of catch rates of `r spp` in the `r hkl` between open and protected areas in order to best understand how to model these data.  The catch-per-unit-effort of `r spp` were calculated for protected and open sites in three regions: mainland, Northern Channel Island, and Southern Channel Island (Figure \ref{fig:nwfsc-hkl-index-raw}). An exploratory negative binomial model determined that the catch rates of `r spp` between open and protected areas not significantly different so the decision was made to use all data for `r spp` to generate an index of abundance in a manner that did not specifically account for open and protected sites. 

The sites considered for the creation of a relative index of abundance were limited to sites that have caught at least 1 `r spp` across all years.  To appropriately weight the survey index by the available rocky substrate by region in the California Bight, each site was assigned as mainland, Northern Channel Island, or Southern Channel Island. Estimates of hard bottom was extracted from the [California Seafloor Mapping Project](http://seafloor.otterlabs.org/index.html) for each of these regions. These data were collected into state waters at a resolution of two meters. South of Point  Conception, additional interpreted bathymetric data classifying the bottom type as  rock or soft bottom were compiled by Emily Saarman (University of California Santa Cruz) and also available  from CDFW's website. The estimates of rocky substrate for each of these regions were 19.5, 36.5, and 44.1 percent in the mainland, Southern Channel Islands, and Northern Channel Islands, respectively. 

A range of alternative model structures were explored to generate an index of abundances. This included alternative levels of aggregation (hook, drop, or site), probability distributions (negative binomial, delta-gamma, or delta-lognormal), and covariates (year, site, depth, swell height, region, year-region interaction, and/or the number of vermilion/sunset or bocaccio rockfishes observed). The overall trend in the index of abundance were highly similar across the explored probability distributions and model configurations. Based on QQ-plots, residuals, and AIC the delta-lognormal distribution was selected with covariates for year, region, drop, polynomial depth term, number of bocaccio, number of vermilion, year-region interaction, and site as a random-effect was selected as the final model using sdmTMB [@anderson_sdmtmb_2022] (Figures \ref{fig:nwfsc-hkl-qq}, \ref{fig:nwfsc-hkl-resid-1}, and \ref{fig:nwfsc-hkl-resid-2}). 


\newpage

\input{tex_tables/nwfsc_hkl_formatted_index.tex}

\newpage

```{r, results = 'asis'}
add_figure(
filein = file.path(data_dir, "survey_indices", "nwfsc_hkl", "plots", "raw_cpue_nwfsc_hkl_by_mpa_vs_open_by_region.png"), 
caption = "Raw catch-per-unit-effort by region and area protection for the NWFSC Hook and Line suvey.",
label = 'nwfsc-hkl-index-raw')
```

\newpage

```{r, results = 'asis'}
add_figure(
filein = file.path(data_dir, "survey_indices", "nwfsc_hkl", "glm_delta_lognormal_year_area_depth_drop_vermilion_bocaccio_all_areas_re_site_area_weighted", "Index.png"), 
caption = "Estimated index of abundance by the NWFSC Hook and Line survey for copper rockfish.",
label = 'nwfsc-hkl-index')
```

\newpage

```{r, results = 'asis'}
add_figure(
filein = file.path(data_dir, "survey_indices", "nwfsc_hkl", "glm_delta_lognormal_year_area_depth_drop_vermilion_bocaccio_all_areas_re_site_area_weighted", "qq.png"), 
caption = "QQ plot.",
label = 'nwfsc-hkl-qq')
```

\newpage

```{r, results = 'asis'}
add_figure(
filein = file.path(data_dir, "survey_indices", "nwfsc_hkl", "glm_delta_lognormal_year_area_depth_drop_vermilion_bocaccio_all_areas_re_site_area_weighted", "residuals_page1.png"), 
caption = "QQ plot.",
label = 'nwfsc-hkl-resid-1')
```

\newpage

```{r, results = 'asis'}
add_figure(
filein = file.path(data_dir, "survey_indices", "nwfsc_hkl", "glm_delta_lognormal_year_area_depth_drop_vermilion_bocaccio_all_areas_re_site_area_weighted", "residuals_page2.png"), 
caption = "QQ plot.",
label = 'nwfsc-hkl-resid-2')
```



<!--chapter:end:66appendix_nwfsc_hkl.Rmd-->


# Appendix G. CDFW ROV Index of Abundance {#cdfw-rov-index}

```{r, echo=FALSE, results='asis'}
filein = file.path(doc_dir, "shared_text",'10_appendix_rov.Rmd')
read_child(filein)
```

Minimal filtering were done to the data. Transects were removed based on four factors: 1) extreme estimates of effort (the estimated area of view below the ROV termed usable area), 2) any locations that were not visited multiple years, 3) transect that were conducted crossing from MPA into reference areas, and 4) transects conducted across depths that never observed `r spp` within the survey (Table \ref{tab:rov-filtered}). Once the data were filtered the average calculated CPUE for each MPA and Reference groups were plotted to visualize the data (Table \ref{tab:rov-obs} and Figure \ref{fig:rov-raw-cpue}).

A range of alternative model structures were explored to generate an index of abundances including alternative error structures, covariates, and factors were considered when exploring how best to model these data. Based on model selection a model where the numbers of fish observed were predicted by year, site designation (MPA or Reference), proportion soft terrain, year/site designation interaction, and random effect for the year/location interaction was selected (Table \ref{tab:rov-model-selection}). The location indicates the area of the sample where most locations included samples by MPA and reference designations. A delta-gamma model was selected based on the distribution of the data and diagnostics (Figure \ref{fig:rov-qq}) using sdmTMB [@anderson_sdmtmb_2022]. 

The model estimates were then area-weighted based on the estimated percent of habitat within MPAs and areas open to fishing. The area estimates were based on existing seafloor mapping data. Unfortunately, all areas `r area` have not been fully mapped for habitat structure. The STAT along with Rebecca Miller (SWFSC/University of California Santa Cruz) used existing seafloor mapping within state waters off the southern California coast to interpret the area of rocky habitat within three regions: mainland, southern Channel Islands, and northern Channel Islands. Within each area the fraction of interpreted rocky substrate areas across each region and the rocky substrate area within MPAs and CCAs were estimated. The area estimates by region and inside/outside MPAs and CCAs were extrapolated to provide estimates of unmapped seafloor within each region. The estimates by region were then combined to provide estimates of 73% of rocky habitat open to fishing with 27% within MPAs and CCAs. The weighted relative index of abundance is shown in Table \ref{tab:rov-index} and Figure \ref{fig:rov-index}.

\newpage

\input{tex_tables/rov_removed_records_south.tex}


\newpage

```{r, results = 'asis'}

tab <- read.csv(file.path(data_dir, "survey_indices", "rov", "forSS", "rov_south_model_selection.csv"))

sa4ss::table_format(x = tab,
             caption = "Model selection for the ROV survey.",
             label = "rov-model-selection",
             align = 'l',
             longtable = TRUE,
             font_size = 7,
             landscape = TRUE)                         
```

\newpage

```{r, results = 'asis'}

ind <- read.csv(file.path(data_dir, "survey_indices", "rov", "delta_gamma_south_designation_depth_year_soft_73_27", "index_forSS.csv"))
ind <- ind[, c(1,4,5)]
col_names = c("Year", "Estimate", "logSE")

sa4ss::table_format(x = ind,
             caption = "Estimated relative index of abundance for the ROV survey.",
             label = "rov-index",
             col_names = col_names)                         
```


\newpage

```{r, results = 'asis'}
sa4ss::add_figure(
filein = file.path(data_dir, "survey_indices", "rov", "delta_gamma_south_designation_depth_year_soft_73_27", "qq.png"), 
caption = "QQ-plot for the ROV survey.",
label = 'rov-qq')
```

\newpage

```{r, results = 'asis'}
sa4ss::add_figure(
filein = file.path(data_dir, "survey_indices", "rov", "delta_gamma_south_designation_depth_year_soft_73_27", "Index.png"), 
caption = "The weighted relative index of abundance.",
label = 'rov-index')
```

\newpage

<!--chapter:end:67appendix_rov.Rmd-->

