---
geometry: margin=1in
month: "`r format(Sys.Date(), '%B')`"
year: "`r format(Sys.Date(), '%Y')`"
preamble: 
header-includes: 
  - \usepackage{lineno}
  - \usepackage[inline]{showlabels}
csl: canadian-journal-of-fisheries-and-aquatic-sciences.csl
output:
  sa4ss::techreport_pdf:
    default
  bookdown::pdf_document2:
    keep_tex: true
lang: en
papersize: letter
---

\linenumbers

<!-- Common lat/long 
Cape Mendocino, Pt. Conception and OR border -->
\newcommand\CapeM{$40^\circ 10^\prime N$}
\newcommand\PtC{$34^\circ 27^\prime N$}
\newcommand\CAOR{$42^\circ 00^\prime N$}


```{r opts, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
knitr::knit_hooks$set(plot = function(x,options) {
      base = knitr::opts_knit$get('base.url')
      if (is.null(base)) base = ''
      alt = ifelse (is.null(options$alt),"",options$alt)
      cap = ifelse (is.null(options$caption),"",options$caption)
      if (alt != ""){
        sprintf('![%s](%s%s "%s")', cap, base, x, alt)
      } else {
        sprintf('![%s](%s%s)', cap, base, x)
        }
  })

load('saved_directories.Rdata')
load("00opts.Rdata")

spp <- "copper rockfish"
Spp <- "Copper rockfish"
hkl <- "NWFSC Hook and Line survey"
wcgbt <- "NWFSC WCGBT survey"
area <- "south of Point Conception"

if(file.exists("00mod.Rdata")){
  load("00mod.Rdata")
} else {
  print("Model output not being read. Please run the read_model() function.")
}

source(file.path(doc_dir, "helper_functions.R"))

#source(file.path(r_dir, "get_derived_quants.R"))


```

<!--chapter:end:00a.Rmd-->

---
author:
  - name: Chantel R. Wetzel
    code: 1
    first: C
    middle: R
    family: Wetzel
  - name: Melissa H. Monk
    code: 2
    first: M
    middle: H
    family: Monk
  - name: Julia Coates
    code: 3
    first: J
    middle: ''
    family: Coates
author_list: Wetzel, C.R., M.H. Monk, J. Coates
affiliation:
  - code: 1
    address: Northwest Fisheries Science Center, U.S. Department of Commerce, National
      Oceanic and Atmospheric Administration, National Marine Fisheries Service, 2725
      Montlake Boulevard East, Seattle, Washington 98112
  - code: 2
    address: Southwest Fisheries Science Center, U.S. Department of Commerce, National
      Oceanic and Atmospheric Administration, National Marine Fisheries Service, 110
      McAllister Way, Santa Cruz, California 95060
  - code: 3
    address: .na.character
address:
  - ^1^Northwest Fisheries Science Center, U.S. Department of Commerce, National Oceanic
    and Atmospheric Administration, National Marine Fisheries Service, 2725 Montlake
    Boulevard East, Seattle, Washington 98112
  - ^2^Southwest Fisheries Science Center, U.S. Department of Commerce, National Oceanic
    and Atmospheric Administration, National Marine Fisheries Service, 110 McAllister
    Way, Santa Cruz, California 95060
  - ^3^NA
---

<!--chapter:end:00authors.Rmd-->

---
bibliography:
  - sa4ss.bib
  - wcassess.bib
  - pfmcassess.bib
---

<!--chapter:end:00bibliography.Rmd-->

# Appendix D. CRFS PR Dockside Index of Abundance {#crfs-pr-index}

Catch and effort data from CRFS dockside sampling of private boats, 2004-2022, 
were provided by CDFW for use in this assessment. The PR dockside data housed 
on the Recreational Fisheries Information Network (RecFIN) were 
determined to include a number of complexities that precluded the ability to 
use them for an index of abundance. For the time period from 2004-2014 the authors 
re-created the interivew, or trip level, data from the "i" sample files.  For 2015-2022 
the authors used files provided by CDFW from the CRFS dockside sampling program.

The data for both time periods included catch by species, number of anglers contributing to the catch, angler-reported area of fishing, 
gear, county, port, interview site, year, month, and CRFS district. The catch included 
the number of fish observed by the CRFS sample, the number of unobserved retained fish reported 
by the angler, and the number of discarded and descended fish reported by the angler.
The sample size of the 
unfiltered private boat data is much larger than the CPFV onboard observer data set, 
with 256,738 samples statewide from 2004-2022, 169,912 south 
of Point Conception and 86,826 north of Point Conception. 

Records were limited to the primary private and rental boats public-access sites, 
PR1 sites, which encompasses approximately 90% of the total private boat effort 
(Table \@ref(tab:pr-filter)). The CRFS interviews contain a small fraction (407 trips over the 
entire time series)
of samples where the retained catch for rockfish is over the daily bag limit of 10 
fish per person. We did not remove these data from the index, but did 
only include sampler examined catch.  Rockfish species can be difficult to distinguish and there 
have not been any verifiction studies conducted to determine the undertainty in angler reported 
unboserved catch.
Additional data filters included the exclusion of any samples from January and 
February, since those months have been closed to the recreational fishery south of Point 
Conception since 2005.  The time series was also restricted to 2004-2019.  Sampling during the 
COVID period (2020-2021) resulted in a higher fraction of the sampled examined catch in the "rockfish, general" 
category due to the social distancing requirements (Table \@ref(tab:pr-rfgen)). The CDFW implemented a one fish sub-bag 
limit for copper rockfish in 2022 and the qauntiles and distribution of CPUE suggest that this 
regulation change impacted fishing behavior in the private boat fleet (Table \@ref(tab:pr-cpue) and 
Figure \@ref(pr-bag)).

The angler reported water area was restricted to ocean areas in U.S. waters 
and a reported primary gear 
of hook-and-line or troll gear.  A number of trips with the primary gear reported troll reported
a secondary gear of hook-and-line. To determine if the angler(s) interviewed targeted rockfish and
fished in rocky habitat, we retained trips if the angler reported the primary target species 
as rockfish or bottomfish or if rockfish was reported as the secondary target species. This filter 
replaced the Stephens-MacCall (@stephens-multispecies-2004) filtering approach.

We retained 13,340 angler interviews for 
index standardization, with 3,739 included sampled examined copper rockfish
(Table \@ref(tab:pr-filter)).  

We modeled retained catch per angler days with a negative binomial GLM in the R package sdmTMB.
The QQ plots indicate a reasonable fit (Figure \@ref(fig:pr-qq)).  There are a handful of samples 
with higher than average CPUE and the authors check with CDFW to determine whether the samples should still be included. 
The CDFW indicated data sheets were not avaialble prior to 2012, but the catches were less than 
the bag limits, and should be assumed correct. Indices with a year and district interaction were not 
considered in model selection due to the fact that fishing locations are unknown; the scale of the relative 
abundance of copper is higher in District 2, but there is some overlap in the fishing locations accessed 
by this fleet (Figure \@ref(fig:pr-districtcpue)). 

Based on AICc values from maximum likelihood fits Table \@ref(tab:pr-modelselect)), 
a main effects model including year, month and primary target species as categorical covariates 
were selected (Table \@ref(tab:pr-index) and Figure \@ref(fig:pr-index)).

<!--Tables -->

\newpage

```{r, results = 'asis'}
ind <- read.csv(file.path(
  data_dir, "rec_indices", "crfs_pr_dockside", "bag_change_visuals",
  "pr_bag_limit_by_year.csv"
)) %>%
 mutate_at(2:6, funs(round(., 3)))

col_names <- c("Year", "Minimum", "Q1", "Q2", "Q3", "Maximum")

sa4ss::table_format(
  x = ind,
  caption = "Summary of the copper rockfish CPUE, number of fish retained per
             angler day, by year.",
  label = "pr-cpue",
  col_names = col_names
)
```

\newpage

```{r, results = 'asis'}
ind <- read.csv(file.path(
  data_dir, "rec_indices", "crfs_pr_dockside", "PR_obs_unobs.csv"
)) %>%
  mutate(Percent.RFGEN = scales::percent(Percent.RFGEN))

col_names <- c("Year", "Unspeciated", "Speciated", "Percent unspeciated")

sa4ss::table_format(
  x = ind,
  caption = "Summary of the number of speciated and unspeciated (RFGEN) rockfish 
  per year across all of California.",
  label = "pr-rfgen",
  col_names = col_names
)
```

\newpage

```{r, results = 'asis'}
ind <- read.csv(file.path(
  data_dir, "rec_indices", "crfs_pr_dockside", "south",
  "rm_last2yrs", "percent_pos.csv"
)) %>%
  mutate(percentpos = scales::percent(round(percentpos, 3)))
col_names <- c(
  "Year", "Trips with Target", "Trips without Target", "Total trips",
  "Percent with Target"
)

sa4ss::table_format(
  x = ind,
  caption = "Number of samples and percent positive for the dockside PR survey.",
  label = "pr-percentpos",
  col_names = col_names
)
```

\newpage


```{r, results = 'asis'}
ind <- read.csv(file.path(
  data_dir, "rec_indices", "crfs_cpfv_onboard", "south",
  "start2005", "data_filters.csv"
))
col_names <- c("Filter", "Description", "Number of Samples", "Positive Samples")

sa4ss::table_format(
  x = ind,
  caption = "Data filtering steps for the onboard CPFV survey.",
  label = "pr-filter",
  col_names = col_names,
   font_size = 9,
    landscape = TRUE,
    custom_width = TRUE,
 col_to_adjust = c(3),
 width = c("8m")
)
```

\newpage

```{r, results = 'asis'}
ind <- read.csv(file.path(
  data_dir, "rec_indices", "crfs_pr_dockside", "south", "rm_last2yrs",
  "model_selection.csv"
))

sa4ss::table_format(
  x = ind,
  caption = "Model selection for the dockside PR survey.",
  label = "pr-modelselect"
)
```


\newpage

```{r, results = 'asis'}
ind <- read.csv(file.path(
  data_dir, "rec_indices", "crfs_pr_dockside",
  "south", "rm_last2yrs", "Index_forSS.csv"
))
ind <- ind[, c(1, 4, 5)]
col_names <- c("Year", "Estimate", "logSE")

sa4ss::table_format(
  x = ind,
  caption = "Estimated relative index of abundance for the dockside PR survey.",
  label = "pr-index",
  col_names = col_names
)
```

\newpage

<!--Figures -->


```{r, results = 'asis'}
sa4ss::add_figure(
  filein = file.path(
    data_dir, "rec_indices", "crfs_pr_dockside", "bag_change_visuals",
    "pr_copper_cpue_year_area_max5.png"
  ),
  caption = "Distribution by year of the number of copper rockfish retained per angler. 
  This includes sampler observed and angler reported catch. The vertical line at 1 represents the sub-bag 
  limit implemented in 2022.",
  label = "pr-bag"
)
```

\newpage

```{r, results = 'asis'}
sa4ss::add_figure(
  filein = file.path(
    data_dir, "rec_indices", "crfs_pr_dockside", "south", "rm_last2yrs",
    "average_cpue_by_district.png"
  ),
  caption = "Average CPUE by district prior to standardization.",
  label = "pr-districtcpue"
)
```


\newpage

```{r, results = 'asis'}
sa4ss::add_figure(
  filein = file.path(
    data_dir, "rec_indices", "crfs_pr_dockside", "south", "rm_last2yrs",
    "index.png"
  ),
  caption = "Index for the dockside PR survey.",
  label = "pr-index"
)
```

\newpage

```{r, results = 'asis'}
sa4ss::add_figure(
  filein = file.path(
    data_dir, "rec_indices", "crfs_pr_dockside", "south",
    "rm_last2yrs", "qq.png"
  ),
  caption = "QQ plot for the dockside PR survey.",
  label = "pr-qq"
)
```

\newpage


<!--chapter:end:64appendix_crfs_dockside.Rmd-->

